### 2018-11-13 manuscript/manuscript.RmD
- initializing of project - first run of analyses

---
title             : "Who Needs Privacy?"
shorttitle        : "Who Needs Privacy?"

author: 
  - name          : "Tobias Dienlin"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "University of Hohenheim, Department of Media Psychology (540F)"
    email         : "tobias.dienlin@uni-hohenheim.de"
  - name          : "Miriam Metzger"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "University of Hohenheim"
  - id            : "2"
    institution   : "University of California, Santa Barbara"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2018-11-13 src/analyses.RmD
- initializing of project - first run of analyses

---
title: "Who Needs Privacy?"
subtitle: "Analyses"
output:
  pdf_document: default
---

```{r knitr-setup, include=F}
knitr::opts_chunk$set(warning=F, echo=F)
options(digits = 3)
```

```{r r-setup, include=F, echo=F}
# list packages to be used
packages <- c("devtools", "lavaan", "MBESS", "magrittr", "psych", "semPlot", "tidyverse")

# install packages
install <- FALSE  # change to TRUE to install packages
if(isTRUE(install)) (
  lapply(packages, install.packages, repos = 'http://cran.us.r-project.org')
)
# devtools::install_git("https://github.com/tdienlin/td")

# load packages
lapply(packages, library, character.only = TRUE)
library(td)
```

```{r data-wrangling, include=F, echo=F}
# read data
# note: a bit complicated, as second row contains variable attributes
d <- read_csv("../data/data.csv", skip = 2, col_names = FALSE) %>% 
  set_names(colnames(read_csv("../data/data.csv", n_max = 1)))

# prepare table with item content
items <- data.frame(
  name = colnames(read_csv("../data/data.csv", n_max = 1)),  # extract item names
  content = colnames(read_csv("../data/data.csv", skip = 1, n_max = 2))  # extract item content
) %>% 
  mutate(content = gsub("To what extent do you agree or disagree with the following / statements[?][-]", "", content)) %>% 
  mutate(content = gsub("To what extent do you agree or disagree with the / following statements[?][-]", "", content)) %>% 
  mutate(content_breaks = sapply(content, string_break, 30))

# filter pretest data
d <- d[-(1:11), ]

# recode
d <- d %>% 
  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.)))
```

# Measures
## Need for Privacy

```{r, fig.height=15, fig.width=12}
d_tmp <- select(d, starts_with("N4P"))
name_tmp <- "pri_nee"
recoded_tmp <- c("N4P.INT_1", "N4P.INT_5", "N4P.INT_8")

ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, starts_with("N4P"))  # new selection bc of recoding
```

### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

Solution suggests 4 or 3 factors

### EFA 4 factors

```{r}
tmp <- omega(d_tmp, nfactors = 4, fm = "ml")
```

Shows several items with negative or low loadings, which will be excluded in updated version.

\newpage

```{r}
tmp <- omega(select(d_tmp, 
                    -N4P.BOT_4, -N4P.BOT_3, -N4P.SOC_7, -N4P.INT_5, -N4P.INT_3), 
             nfactors = 4, fm = "ml")
```

Produces a fitting solution.

\newpage

```{r}
tmp$schmid$sl
```

Using four factors, looking at the items's content we do not find an easily interpretable solution.

\newpage
### EFA 3 factors

```{r}
tmp <- omega(d_tmp, nfactors = 3, fm = "ml")
```

Shows several items with negative or low loadings, which will be excluded in updated version.

\newpage

```{r}
tmp <- omega(select(d_tmp,
                    -N4P.BOT_4, -N4P.BOT_3, -N4P.INT_5, -N4P.INT_3, -N4P.INT_7, -N4P.INT_4), 
             nfactors = 3, fm = "ml")
```

Produces a fitting solution.

\newpage

```{r}
tmp$schmid$sl
```

Interpretation

* factor 1 measures privacy from the government (vertical)
* factor 2 measures privacy from identification (combined)
* factor 3 measures privacy from other people (horizontal)

### CFA

```{r}
model <- '
  pri_nee_ver =~ N4P.SOC_4 + N4P.SOC_1 + N4P.SOC_3 + N4P.SOC_9 + N4P.SOC_2 + N4P.SOC_5
  pri_nee_ide =~ N4P.INT_1 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_8 + N4P.SOC_6 + N4P.INT_2 + N4P.INT_6 
  pri_nee_hor =~ N4P.BOT_1 + N4P.BOT_2 + N4P.INT_6 + N4P.INT_9 + N4P.INT_2
  pri_nee_gen =~ N4P.SOC_4 + N4P.SOC_1 + N4P.SOC_3 + N4P.SOC_9 + N4P.SOC_2 + N4P.SOC_5 + N4P.INT_1 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_8 + N4P.SOC_6 + N4P.INT_2 + N4P.INT_6 + N4P.BOT_1 + N4P.BOT_2 + N4P.INT_6 + N4P.INT_9 + N4P.INT_2
  pri_nee_gen ~~ 0*pri_nee_ver + 0*pri_nee_hor + 0*pri_nee_ide
  pri_nee_ver ~~ 0*pri_nee_hor + 0*pri_nee_ide
  pri_nee_hor ~~ 0*pri_nee_ide
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
semPaths(fit, bifactor = "pri_nee_gen", layout = "tree3")
```

\newpage
## Integrity

```{r, fig.height=8, fig.width=12}
d_tmp <- select(d, starts_with("INT_"))
name_tmp <- "int"
recoded_tmp <- c("INT_1", "INT_2", "INT_5", "INT_6", "INT_7", 
                 "INT_8", "INT_9", "INT_10", "INT_11")

ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, starts_with("INT_"))  # new selection bc of recoding
```

### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

### EFA

```{r}
tmp <- omega(d_tmp, fm = "ml", nfactors = 3)
```

Shows no clear solution for three factors.

\newpage

```{r}
tmp <- omega(d_tmp, fm = "ml", nfactors = 2)
```

Shows solution for two factors. Delete items INT_4 and INT_3 for not loading on general factor

\newpage

```{r}
tmp <- omega(select(d_tmp, -INT_3, -INT_4), fm = "ml", nfactors = 2)
```

\newpage

```{r}
tmp$schmid$sl
```

Interpretation

* factor 1 measures ...
* factor 2 measures ...

### CFA

```{r}
model <- '
  int_1 =~ INT_1 + INT_2 + a*INT_5 + a*INT_6 + a*INT_7 + INT_8
  int_2 =~ b*INT_8 + b*INT_9 + b*INT_10 + b*INT_11
  int_gen =~ INT_1 + INT_2 + INT_5 + INT_6 + INT_7 + INT_8 + INT_9 + INT_10 + INT_11
  int_gen ~~ 0*int_1 + 0*int_2
  int_1 ~~ 0*int_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), 
       cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       select(as.data.frame(predict(fit)), ends_with("_gen")))
```

## Sociability

```{r, fig.height=8, fig.width=12}
d_tmp <- select(d, SOC_1 : SOC_8)
name_tmp <- "soc"
recoded_tmp <- c("SOC_1", "SOC_3", "SOC_5", "SOC_7")

p_int <- ggplot(d_tmp %>% 
                  gather(name, value) %>% 
                  left_join(items, "name"),
                  aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)
p_int

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, SOC_1 : SOC_8)  # new selection bc of recoding
```

### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

\newpage

### EFA

```{r}
tmp <- omega(d_tmp, fm = "ml", nfactors = 3)
```

Shows no clear solution for three factors.

\newpage

```{r}
tmp <- omega(d_tmp, fm = "ml", nfactors = 2)
```

Shows solution for two factors. Differentiates between inverted and regular items.

\newpage

```{r}
tmp$schmid$sl
```

Interpretation

* factor 1 measures ...
* factor 2 measures ...

### CFA

```{r}
model <- '
  soc_1 =~ a*SOC_1 + SOC_3 + SOC_5 + a*SOC_7
  soc_2 =~ b*SOC_2 + SOC_4 + SOC_6 + b*SOC_8 + SOC_1 + SOC_7
  soc_gen =~ SOC_1 + SOC_2 + SOC_3 + SOC_4 + SOC_5 + SOC_6 + SOC_7 + SOC_8
  soc_gen ~~ 0*soc_1 + 0*soc_2
  soc_1 ~~ 0*soc_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), 
       cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       select(as.data.frame(predict(fit)), ends_with("_gen")))
```

## Fearfulness

```{r}
d_tmp <- select(d, starts_with("FEA_"))
name_tmp <- "fea"
recoded_tmp <- c("FEA_1", "FEA_3", "FEA_5", "FEA_7")

ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, starts_with("FEA_"))  # new selection bc of recoding
```

### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

### EFA 4 factors

```{r}
tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
```

Produces a fitting solution.

\newpage

```{r}
tmp$schmid$sl
```

\newpage
### CFA

```{r}
model <- '
  fea_1 =~ a*FEA_2 + a*FEA_4 + a*FEA_6 + FEA_8
  fea_2 =~ FEA_1 + b*FEA_3 + b*FEA_5 + b*FEA_7
  fea_gen =~ FEA_2 + FEA_4 + FEA_7 + FEA_8 + FEA_1 + FEA_3 + FEA_5 + FEA_6

  fea_gen ~~ 0*fea_1 + 0*fea_2
  fea_1 ~~ 0*fea_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       select(as.data.frame(predict(fit)), ends_with("_gen")))
```

\newpage

## Traditionalism

```{r}
d_tmp <- select(d, TRA_1 : TRA_8)
name_tmp <- "tra"
recoded_tmp <- c("TRA_2", "TRA_4", "TRA_6")

ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, TRA_1 : TRA_8)  # new selection bc of recoding
```

### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

### EFA 4 factors

```{r}
tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
```

Produces a fitting solution.

\newpage

```{r}
tmp$schmid$sl
```

\newpage
### CFA

```{r}
model <- '
  tra_1 =~ a*TRA_1 + a*TRA_3 + a*TRA_5 + a*TRA_7 + a*TRA_8
  tra_2 =~ TRA_2 + TRA_4 + TRA_6 
  tra_gen =~ TRA_1 + TRA_2 + TRA_3 + TRA_4 + TRA_5 + TRA_6 + TRA_7 + TRA_8

  tra_gen ~~ 0*tra_1 + 0*tra_2
  tra_1 ~~ 0*tra_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       select(as.data.frame(predict(fit)), ends_with("_gen")))
```

\newpage

## Risk Avoidance

```{r}
d_tmp <- select(d, RIT_1 : RIT_8)
name_tmp <- "rit"
recoded_tmp <- c("RIT_1", "RIT_3", "RIT_5")

ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, RIT_1 : RIT_8)  # new selection bc of recoding
```

### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

### EFA 4 factors

```{r}
tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
```

Produces a fitting solution.

\newpage

```{r}
tmp$schmid$sl
```

\newpage
### CFA

```{r}
model <- '
  rit_1 =~ a*RIT_2 + a*RIT_4 + a*RIT_5 + a*RIT_7 + a*RIT_8
  rit_2 =~ RIT_1 + RIT_3 + RIT_5
  rit_gen =~ RIT_1 + RIT_2 + RIT_3 + RIT_4 + RIT_5 + RIT_6 + RIT_7 + RIT_8

  rit_gen ~~ 0*rit_1 + 0*rit_2
  rit_1 ~~ 0*rit_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       select(as.data.frame(predict(fit)), ends_with("_gen")))
```

## Big five

```{r}
d_tmp <- select(d, BFI_1 : BFI_10)
name_tmp <- "BFI"

ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)
```

### Correlations

```{r}
cor(d_tmp, use = "pairwise.complete.obs")
```

The dimensions show low correlations; as a result, we will use only 1 item (the one which is not inverted), to measure each dimension. This includes the following items:

* BFI_2, BFI_3, BFI_5, BFI_8, BFI_9

# Results

```{r}
d <- cbind(d, int_gen, soc_gen, fea_gen, tra_gen, rit_gen)
```

```{r}
name_tmp <- "main"
model <- '
  pri_nee_ver =~ N4P.SOC_4 + N4P.SOC_1 + N4P.SOC_3 + N4P.SOC_9 + N4P.SOC_2 + N4P.SOC_5
  pri_nee_ide =~ N4P.INT_1 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_8 + N4P.SOC_6 + N4P.INT_2 + N4P.INT_6 
  pri_nee_hor =~ N4P.BOT_1 + N4P.BOT_2 + N4P.INT_6 + N4P.INT_9 + N4P.INT_2
  pri_nee_gen =~ N4P.SOC_4 + N4P.SOC_1 + N4P.SOC_3 + N4P.SOC_9 + N4P.SOC_2 + N4P.SOC_5 + N4P.INT_1 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_8 + N4P.SOC_6 + N4P.INT_2 + N4P.INT_6 + N4P.BOT_1 + N4P.BOT_2 + N4P.INT_6 + N4P.INT_9 + N4P.INT_2

  pri_nee_gen ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen
  pri_nee_ver ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen
  pri_nee_ide ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen
  pri_nee_hor ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen

  int_gen ~~ soc_gen + fea_gen + tra_gen + rit_gen
  soc_gen ~~ fea_gen + tra_gen + rit_gen
  fea_gen ~~ tra_gen + rit_gen
  tra_gen ~~ rit_gen

  pri_nee_gen ~~ 0*pri_nee_ver + 0*pri_nee_hor + 0*pri_nee_ide
  pri_nee_ver ~~ 0*pri_nee_hor + 0*pri_nee_ide
  pri_nee_hor ~~ 0*pri_nee_ide
'
fit <- sem(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
```

## With big five

```{r}
name_tmp <- "main_bigfive"
model <- '
  pri_nee_ver =~ N4P.SOC_4 + N4P.SOC_1 + N4P.SOC_3 + N4P.SOC_9 + N4P.SOC_2 + N4P.SOC_5
  pri_nee_ide =~ N4P.INT_1 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_8 + N4P.SOC_6 + N4P.INT_2 + N4P.INT_6 
  pri_nee_hor =~ N4P.BOT_1 + N4P.BOT_2 + N4P.INT_6 + N4P.INT_9 + N4P.INT_2
  pri_nee_gen =~ N4P.SOC_4 + N4P.SOC_1 + N4P.SOC_3 + N4P.SOC_9 + N4P.SOC_2 + N4P.SOC_5 + N4P.INT_1 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_8 + N4P.SOC_6 + N4P.INT_2 + N4P.INT_6 + N4P.BOT_1 + N4P.BOT_2 + N4P.INT_6 + N4P.INT_9 + N4P.INT_2

  pri_nee_gen ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + BFI_2 + BFI_3 + BFI_5 + BFI_8 + BFI_9
  pri_nee_ver ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + BFI_2 + BFI_3 + BFI_5 + BFI_8 + BFI_9
  pri_nee_ide ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + BFI_2 + BFI_3 + BFI_5 + BFI_8 + BFI_9
  pri_nee_hor ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + BFI_2 + BFI_3 + BFI_5 + BFI_8 + BFI_9

  int_gen ~~ soc_gen + fea_gen + tra_gen + rit_gen + BFI_2 + BFI_3 + BFI_5 + BFI_8 + BFI_9
  soc_gen ~~ fea_gen + tra_gen + rit_gen + BFI_2 + BFI_3 + BFI_5 + BFI_8 + BFI_9
  fea_gen ~~ tra_gen + rit_gen + BFI_2 + BFI_3 + BFI_5 + BFI_8 + BFI_9
  tra_gen ~~ rit_gen + BFI_2 + BFI_3 + BFI_5 + BFI_8 + BFI_9
  rit_gen ~~ BFI_2 + BFI_3 + BFI_5 + BFI_8 + BFI_9
  BFI_2 ~~ BFI_3 + BFI_5 + BFI_8 + BFI_9
  BFI_3 ~~ BFI_5 + BFI_8 + BFI_9
  BFI_5 ~~ BFI_8 + BFI_9
  BFI_8 ~~ BFI_9

  pri_nee_gen ~~ 0*pri_nee_ver + 0*pri_nee_hor + 0*pri_nee_ide
  pri_nee_ver ~~ 0*pri_nee_hor + 0*pri_nee_ide
  pri_nee_hor ~~ 0*pri_nee_ide
'
fit <- sem(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
```

# Visualization

```{r}
d_effects <- coeffs_tab(main_fit) %>%
  mutate(sig = ifelse(p < .05, "1", "0"))

std_ci <- ci.src(beta.k = d_effects$beta, b.k = d_effects$b, 
                 N = 400, conf.level = .95, SE.b.k = .10, s.Y = sqrt(.955), )

p_effects <- ggplot(d_effects, aes(x = beta)) +
  geom_point(aes(y = Predictor, color = sig)) +
  scale_color_manual(values = c("#000000", "#FF0000")) +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 0.1, linetype = "dashed") +
  geom_vline(xintercept = -0.1, linetype = "dashed") +
  theme_bw() + 
  facet_grid(~ Outcome)
```

### 2018-11-14 manuscript/manuscript.RmD
- manuscript: included parts of original publication

@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+  Objective: This study analyzes how personality relates to peoples' desire for privacy.
+Specifically, we investigated whether the syllogism "I don't mind surveillance because I have nothing to hide" is correct: Do people who lack integrity (given they have something to hide) indeed desire more privacy?
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+  Method: Study 1 featured an online questionnaire (_N_ = 268, _M_\textsubscript{age} = 20 years, 72\% female) and Study 2 a laboratory experiment (_N_ = 87, _M_\textsubscript{age} = 20 years, 51\% female), where participants wrote an essay about past negative, positive, or neutral behaviors to analyze effects on desire for privacy.
 
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
+  Results: Study 1 showed that respondents who are more shy, less anxious, and more risk averse desired more privacy.
+Respondents who self-reported lacking integrity reported desiring more privacy from government and more anonymity.
+Study 2 replicated these results and showed a statistical trend (_p_ = .052) that writing about negative past behaviors increased desire for interpersonal privacy.
+Moreover, the integrity IAT showed significant relations with desire for privacy from government.
 
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  Conclusion: It is possible to predict peoples' desire for privacy based on their lack of integrity.
+However, other neutral personality facets also explain desire for privacy.
+Hence, putting everyone who desires privacy under general suspicion would be incorrect.
 
@@
 
-bibliography      : ["r-references.bib"]
+bibliography      : 
+  - "../bibliography/r-references.bib"
+  - "../bibliography/references.bib"
 
@@
 output            : papaja::apa6_pdf
+header-includes:
+  - \setlength{\parskip}{0em}
+  - \raggedbottom
 ---
@@
 
+In his novel _The Circle_, @Eggers.2013 describes a dystopian society in which people are gradually forfeiting their privacy.
+People decide to become "transparent", which means that they start carrying a small camera around the neck in order to broadcast their daily lives to the Internet.
+Eventually, this causes a societal upheaval: "The pressure on those who hadn't gone transparent went from polite to oppressive.
+The question, from pundits and constituents, was obvious and loud: If you aren't transparent, what are you hiding?" [@Eggers.2013, p.
+129].
+The main argument being offered to justify the surveillance is: "If you have nothing to hide, you have nothing to fear." This syllogism is familiar, given that it commonly appears in also nonfictional conversations [@Sieradski.2013].
+Consider, for example, the following tweet: "I don't download illegally.
+I don't have anything on my comp[uter] to hide.
+Hell, I'm sure the \#NSA gave up on me years ago." [@BeautifulDisaster.2015].
+
+Why do people desire privacy?
+To date there is only little research on why people desire privacy and how the desire for privacy can be predicted by aspects of personality.
+For example, and to the best of our knowledge, so far no study exists that has analyzed the nothing-to-hide argument from a scientific and empirical perspective.
+Why do some people not care whether government agencies such as the NSA are collecting their data [@Greenwald.2013], and why do others protest vehemently in order to protect their privacy?
+
+Answering this question is important: Given that government agencies are collecting large amounts of data hoping to reduce criminality and terrorism, and given that government agencies are collecting this data preemptively and without concrete suspicions, it is relevant to find out whether this practice of mass surveillance can be justified based on the nothing-to-hide argument.
+As a result, the main question of this paper is: Do people who desire more privacy really have more to hide and, more generally, what are personality facets that determine peoples' overall desire for privacy?
+
+## Desire for Privacy
+
+Privacy captures the extent of voluntary withdrawal from others [@Westin.1967].
+Several models suggest that privacy is a multi-dimensional concept: For example, in a theory-driven treatise @Burgoon.1982 argued that privacy has four dimensions: informational, social, psychological, and physical privacy.
+@Pedersen.1979, by contrast, did an empirical factor analysis (initially starting with 94 items) and suggested that privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity.
+In addition, @Schwartz.1968 differentiated between horizontal and vertical privacy: Whereas horizontal privacy captures withdrawal from peers, vertical privacy refers to withdrawal from superiors or institutions (e.g., government agencies).
+Next to being multi-dimensional, privacy is also contingent [@Dienlin.2014]: One can, for example, distinguish between the objective privacy context, the subsequent subjective perception of privacy, the psychological desire for privacy (which is both a situational and dispositional need), and the resulting privacy behavior (as represented by self-disclosure).
+For the purpose of this study, we combine the aforementioned theories and focus on (a) vertical privacy with regard to the desire for withdrawal from government surveillance, (b) horizontal privacy in terms of the desire for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by the general desire for anonymity.
+
+### The relation between integrity and desire for privacy
+
+Which specific aspects of personality help predict desire for privacy?
+At its core, the nothing-to-hide argument implies that lack of integrity is an important predictor of why people desire privacy.
+This becomes especially apparent when we consider the definition of Solove's (2007) nothing-to-hide argument (notably, Solove is a strong critic of the nothing-to-hide argument):
+
+The NSA surveillance, data mining, or other government information gathering programs will result in the disclosure of particular pieces of information to a few government officials, or perhaps only to government computers.
+This very limited disclosure of the particular information involved is not likely to be threatening to the privacy of law-abiding citizens.
+Only those who are engaged in illegal activities have a reason to hide this information.
+[@Solove.2007; p.
+753]
+
+This definition helps illustrate the link between lack of integrity and desire for privacy: People who have "engaged in illegal activities" can be considered, by definition, to lack integrity [@Paunonen.2002], which is why they have a reason "to hide this information" (or, in other words, to desire more privacy).
+In terms of a scientific definition of integrity there is no real consensus, however most scholars agree that integrity "incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness" [@Connelly.2006; p.
+82].
+
+Several theoretical arguments exist why lack of integrity might correlate with desire for privacy.
+In general, any self-disclosure is a potential risk because others might disagree, disapprove, or misuse the information in other contexts [@Petronio.2000].
+Privacy regulation theory showed that if self-disclosures are too risky, people raise their desired level of privacy, intensify their boundary regulation, and employ more mechanisms to seclude and protect themselves [@Altman.1976].
+In traditional contexts, this could range from moderate behaviors like closing doors, to extreme behaviors such as physically tossing someone out of the room [@Altman.1976].
+In modern contexts, protecting one's privacy can mean to avoid photographs or to deliberately shun public places that have surveillance cameras.
+People who have actually committed something bad, treacherous, or illegal become even more vulnerable and face a significant risk of self-disclosure, because others will surely disapprove of these activities [@Petronio.2000].
+Hence, the foregoing arguments illuminate an indirect link between integrity and desire for privacy: By definition, people who participate in negative activities are considered to lack integrity [@Paunonen.2002].
+People who have engaged in negative activities have, by definition, more to hide, and disclosures concerning those activities pose a high risk.
+Because of this increased risk, people will arguably desire more privacy, as a means to mitigate their felt risk [@Altman.1976].
+In this way, the current research extends Altman's privacy regulation theory (1976) by suggesting that lack of integrity is an important yet unexamined factor that could increase peoples' desired level of privacy.
+
+A few studies can be found that imply a relation between privacy and integrity.
+For example, several studies found that surveillance reduces cheating behaviors [@Corcoran.1987, Covey.1989].
+@Covey.1989 asked students to solve an impossible maze.
+In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior.
+In the low surveillance condition, the experimenter stood behind the students, did not monitor their behavior, and visual dividers were used to block the experimenter's view of the students.
+Results showed that students were more likely to cheat in the low surveillance condition, suggesting that in situations of surveillance (i.e., less privacy), people show fewer cheating behaviors (i.e., more integrity).
+Similarly, people are more likely to prevent others from stealing when security cameras are visible [@vanBommel.2014], which is also a sign of higher integrity.
+Next, in a longitudinal sample with 457 respondents in Germany [@Trepte.2013], people who reported needing more privacy were less satisfied with their lives (_r_ = -.47), had more (_r_ = .41) and less positive affect (_r_ = -.39).
+More importantly however, people who felt they needed more privacy were also less authentic on their SNSs profiles (_r_ = -.48) and less authentic in their personal relationships [_r_ = -.28; @Trepte.2013].
+For example, people who agreed to items like "I do not talk about personal issues unless my conversation partner brings them up first" were more likely to report that their online profiles did not truly represent their personality.
+Given the argument that authenticity is a subset of integrity [@Sheldon.2004], we reason that the concept of integrity might relate to the desired level of privacy.
+Finally, @Pedersen.1982 showed that three dimensions of need for privacy related to self-esteem: In his study with _N_ = 70 undergraduate students, respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21) and preferred solitude (_r_ = .24).
+Granted, self-esteem and integrity are generally distinct concepts; however, Pedersen's specific operationalization of self-esteem integrated several aspects of integrity (e.g., by using items such as "moral, nice, fair, unselfish, good, honest, reputable, sane" to measure self-esteem).
+Thus, our overarching hypothesis is that people who lack integrity have a greater desire for privacy.
+
+In Study 1, we used a questionnaire-based design to analyze how lack of integrity and other personality facets relate to desire for privacy.
+In accordance with the reasoning mentioned above, we suggest that people with less integrity feel a greater desire for privacy.
+Specifically, we argue that integrity may relate to the desire for privacy from (a) government surveillance, as governments have the legitimate power to prosecute illegal activities.
+Next, we hypothesize that integrity relates to the desire privacy for (b) anonymity.
+Anonymity makes it more difficult for both legal and social agents to identify and address potential wrongdoers, which is why people with less integrity will prefer situations in which they are anonymous.
+Finally, lack of integrity likely also relates to an increased desire for privacy from (c) other people, as most other people will disapprove of immoral or illegal activities, and might reveal those activities to authorities.
+
+Hypothesis 1: People who feel lower in self-perceived integrity desire more privacy from government surveillance (H1a), more anonymity (H1b), and more privacy from other persons (H1c).
+
+### Shyness
+
+Critics of the nothing-to-hide argument hold that people who desire privacy should not automatically be confronted with suspicion, and that privacy has several purposes that are not related to criminal behavior [@Marlinspike.2013].
+@Westin.1967, for example, defined four primary purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
+These are all important social factors for which people desire privacy.
+Hence, the argument is that people who desire privacy can have several legitimate reasons for doing so; reasons which are essential for psychosocial wellbeing and which relate to different factors of personality.
+Below, we thus explore other (neutral) aspects of personality that potentially predict desire for privacy.
+In order to be more precise, we follow the advice by @Paunonen.2001 and, instead of using generic personality factors as predictors, refer to specific personality facets.
+
+First, we argue that people who are more reserved, who feel less comfortable in social situations, generally desire more anonymity and more interpersonal privacy.
+Given that privacy is, by definition, a voluntary withdrawal from society [@Westin.1967], we expect that people who are more reserved or more shy desire more privacy from others.
+Several empirical studies support this hypothesis: Extroverted people desire less privacy [@Morton.2013], people who describe themselves as introverted thinkers are more likely to prefer social isolation [@Pedersen.1982], and introverted people are more likely to report invasions of privacy [@Stone.1986].
+Finally, we did not find convincing theoretical and empirical arguments for why shyness should relate to an increased desire for privacy from government surveillance, which is why we did not include a hypothesis on this relation.
+
+Hypothesis 2: People who are more shy desire more anonymity (H2a) and more privacy from other persons (H2b).
+
+### Anxiety
+
+Of course, there are also reasons why people might desire less privacy.
+Government agencies often curtail privacy with the aim to prevent crime: For example, the NSA's surveillance programs are often considered a direct response to the 9 / 11 terrorists attacks [@Greenwald.2013].
+It seems plausible that people who are more afraid of terrorist attacks are also more likely to consent to these surveillance programs, given that these programs promise to reduce the likelihood of future attacks.
+One can then argue that people who are afraid of terrorist attacks are also more afraid of threats overall, which is why we suggest that people who are, in general, more anxious desire less privacy from government surveillance and less anonymity.
+We did not include a hypothesis on the potential relation between anxiety and desire for interpersonal privacy.
+On the one hand, one could argue that people who are more anxious are more reserved, given that social interactions can pose significant risks [especially with strangers or weak ties; @Granovetter.1973].
+At the same time, one could suggest that especially those people who are more anxious desire less privacy from others (and especially their strong ties), in order to cope better with their daily challenges.
+At the end, given that we measure interpersonal privacy on a general level (and do not distinguish between desire for privacy from (a) weak ties and (b) strong ties), it seems plausible that both effects could cancel each other out.
+
+Hypothesis 3: People who are more anxious desire less privacy from government surveillance (H3a) and more anonymity (H3b).
+
+### Risk aversion
+
+Disclosing personal information always poses a certain risk, given that others can misuse self-disclosed personal information in different contexts, which can lead to severe consequences [@Altman.1976].
+Not everyone will feel intimidated by this hypothetical threat---except those who have a general tendency to avoid taking unnecessary risks.
+The most cautious strategy to minimize risks of personal self-disclosures would be, arguably, to keep as much information as possible private.
+Hence, we suggest that people who are, in general, more risk averse have a good reason to desire more privacy in all three aforementioned contexts.
+
+Hypothesis 4: People who are more risk averse desire more privacy from government surveillance (H4a), more anonymity (H4b), and more privacy from other persons (H4c).
+
+### Traditionality
+
+The personal computer and the Internet have rendered the world increasingly digitized: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.
+Given the features of digital information [i.e., information is persistent, searchable, reproducible, and scalable; @boyd.2008], this allows for unprecedented ways and degrees of surveillance.
+Mark Zuckerberg famously observed that privacy is no longer a "social norm," rather that people share personal information [@Johnson.2010].
+Hence, in order to be part of contemporary life (e.g., by using SNSs), it seems necessary to give up some privacy.
+However, arguably not everyone is willing to pay that price, and especially people who are more conservative might prefer to stick to their usual routines and decide against giving up their privacy.
+This is supported by empirical research: Older people, who are generally less open and more traditional [@Donnellan.2008], are more concerned about their privacy than younger people [@Fife.2012].
+Taken together, we suggest that people who are more traditional also desire more privacy in all three aforementioned contexts.
+
+Hypothesis 5: People who are more traditional desire more privacy from government surveillance (H5a), more anonymity (H5b), and more privacy from other persons (H5c).
+
 # Methods
+
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
 
-## Participants
+## Procedure and participants
 
-## Material
+Participants were students from a university in the western U.S.
+who received course credit for taking part in the study.
+The sample consisted of _N_ = 296 respondents, with an age that ranged from 18 to 56 years (_M_ = 20 years).
+72\% of the respondents were female.
+The median participation time was 24 minutes.
+Regarding ethnicity, 37\% of the respondents were Non-Hispanic White / Caucasian, 4\% Black / African American, 21\% Hispanic / Latino, 24\% Asian / Pacific Islander, 0\% Native American, 5\% others, and 8\% nonresponse.
 
-## Procedure
+## Measures
 
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+Despite the fact that we mostly used well-established scales, confirmatory factor analyses (CFAs) showed that some of the original items had to be deleted in order to achieve adequate factorial validity.
+The final scales showed acceptable fit (CFI \textgreater .90, TLI \textgreater .90, RMSEA \textless .10, SRMR \textless .10), good composite reliability (REL($\upomega$) \textgreater .60), and adequate convergent factorial validity (AVE \textgreater .50; see Table \ref{tab:DIS_Study_4_Table_1}).
+Respondents answered all items on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).
+
+The data, all items (including deleted ones), results of CFAs, item statistics, and distribution plots can be found in the online supplementary material.[^OSM]
+
+[^OSM]: https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f}}
+
+### Desire for privacy
+
+We measured desire for privacy on three dimensions: (a) Desire for privacy from government surveillance, which represents the extent to which people want the government to abstain from collecting information about their personal life.
+One example item is "I feel the need to protect my privacy from government agencies." (b) Desire for anonymity, which measures the extent to which people feel the need to avoid identification("I need to be able to use a fake name on social network sites to preserve my privacy}).
+(c) Desire for privacy from other people, which measures the extent to which people want to withhold personal information from others("I don't feel the need to tell my friends all my secrets}).
+For each dimension, we used 3 self-developed items that build on prior studies [@Masur.2016].
+
+### Integrity
+
+Integrity measures the extent to which people comply with social norms and values.
+When measuring integrity, the question arises whether it is possible to measure integrity based on self-reports.
+Interestingly, integrity tests that are based on self-reports have been shown to work successfully, given that they can predict unwanted professional workplace behavior sufficiently [e.g., theft, drug and alcohol problems, or absenteeism; @Ones.1993].
+In order to measure lack of integrity, we thus used 4 items of the subscale integrity of the Supernumerary Personality Inventory [@Paunonen.2002].
+An example item is "I don't think there's anything wrong with cheating a little on one's income tax forms."
+
+### Shyness
+
+Shyness captures whether people prefer to spend their time alone or in company.
+We measured shyness with 4 items of the inverted extraversion subscale gregariousness [@Costa.1992].
+An example item is "I shy away from crowds of people.}
+
+### Anxiety
+
+Anxiety measures whether people are afraid of negative external influences.
+We measured anxiety with 4 items of the neuroticism subscale anxiety [@Costa.1992].
+An example item is "I am easily frightened.}
+
+### Risk avoidance
+
+Risk avoidance captures whether people abstain from taking risks.
+We measured risk avoidance with 4 items of the conscientiousness subscale deliberation [@Costa.1992].
+An example item is "I think twice before I answer a question.}
+
+### Traditionalism
+
+Traditionalism measures whether people prefer to stick with their usual routines.
+We measured traditionalism with 4 items of the inverted openness to experiences subscale actions [@Costa.1992].
+An example item is "I'm pretty set in my ways.}
+
+## Data analyses
+
+All hypotheses were tested with structural equation modeling (SEM).
+To assess the SEM assumption of multivariate normality, we computed a multivariate Shapiro-Wilk normality test.
+The results showed a violation of multivariate normality (_W_ = 0.90, _p_ \textless .001), which is why we used the more robust Satorra-Bentler scaled test statistic as estimator.
+We treated missing data with casewise deletion and tested all hypotheses with a two-tailed p \textless .050 significance level; values between _p_ = .050 and _p_ = .010 were considered trends toward significance.
+Regarding effect sizes, we classified regression coefficients with values exceeding $\upbeta$ = .10 as small effects, $\upbeta$ = .30 as medium effects, and $\upbeta$ = .50 as large effects.
+
+Unfortunately, we did not determine sample size based on a priori power analyses.
+We decided against including social desirability as a control variable, because even though social desirability can affect answers to sensitive questions [@deJong.2012], it is more likely to reflect a true personality trait than false answering behavior [@deVries.2014].
+Likewise, we did not include demographic control variables such as age or education, because we used a typical student sample with little demographic variance.
+We used `r cite_r("..\bibliography\r-references.bib")` for all our analyses.
 
@@
 
+The results of Study 1 showed that integrity relates to several dimensions of desire for privacy: People who reported being of lower integrity desired more privacy from government and more anonymity.
+In other words, people who agreed that there would be nothing wrong with cheating a little or lying occasionally were also more likely to agree that the government should not invade peoples' privacy, even if that could help to prevent terrorist attacks.
+Likewise, people who said, for example, that they would feel tempted to take things that do not belong to them were also more likely to avoid situations in which they were identifiable.
+
+In addition, desire for privacy was predicted also by other (neutral) personality facets: People who were more shy, more risk averse, and less anxious also desired more privacy.
+This implies that next to lack of integrity there are various other personality-related aspects that predict desire for privacy.
+
+People who are more shy, more risk averse, or less anxious also desire more privacy.
+For example, people who are less anxious are less likely to accept government surveillance (arguably because they are less afraid of terrorist attacks).
+When looking at the bigger implications of the results, this shows the importance to make differentiated claims on why people desire privacy: Indeed, the results suggest that some people desire privacy because they might have something to hide.
+However, putting everyone who desires privacy under a general suspicion is wrong given that shy, risk averse, and less anxious people are also more likely to desire privacy.
+
+In conclusion, our results follow @Altman.1976, who reasoned that if exposure of information is risky it is likely that people will use more mechanisms to strengthen their social boundaries and increase their desired level of privacy.
+This study thus aligns with Altman's privacy regulation theory by showing that, in several contexts, people with lower integrity had a higher level of desired privacy.
+
+## Limitations and future perspective
+
+In our analysis of predictors of privacy, we followed the recommendation by @Paunonen.2001 and did not analyze broad factors of personality (e.g., neuroticism); instead, we focused on more specific personality facets (e.g., fearfulness).
+For future research, we suggest going one step further by analyzing predictors that are even more specified.
+For example, it seems possible that people who hold dissenting political beliefs could also have a higher desire for privacy from the government.
+Similarly, it would be interesting to focus on different minority groups.
+For example, it seems plausible that people from a LGBT background might desire more privacy from government (because it is potentially repressive or unfriendly toward LGBTs).
+Finally, in this study we focused mostly on escapist motives for why people desire privacy (e.g., shyness, risk aversion).
+Interestingly, @Leary.2003 were able to show that when predicting engagement in solitary activities, it is less preferable to measure how strongly people want to escape society (avoidance oriented), but rather how much they seek solitude (approach oriented).
+Hence, future studies might want to include predictors that are more approach oriented (e.g., peoples' desire for contemplation).
+
+From a methodological perspective, future research should continue to improve the instruments we used, given that factorial validity of some scales was only moderate.
+Similarly, we recommend elaborating on the general understanding of integrity as a theoretical concept.
+To date, there is not one overarching concept of integrity that incorporates all the different aspects of integrity, yet it would be valuable to examine how other aspects of integrity (e.g., authenticity, trustworthiness, or consistency) relate to privacy desires.
+
+Power analyses showed that future research should use samples above _N_ $\approx$ 260 in order to test hypotheses with the recommended power of at least .80 (Cohen, 1992).
+
+In general, the question arises whether it is possible, or even socially desirable, to measure a person's integrity.
+On the one hand, integrity implies absolute criteria: Stealing is bad and forbidden, whereas helping is good and encouraged.
+On the other hand, integrity implies relative criteria: Whereas some cultures disapprove of lying whatever the context, others consider lying okay---for example "white lies" in order to save face or to avoid hurting someone's feelings [@Altman.1977].
+Thus, ranking behaviors, opinions, and character traits with regard to integrity is a moral dilemma.
+As a result, throughout the entire study we have understood integrity as a transgression of social norms that is strong and that most societies would agree upon (for example, most societies would consider stealing as a sign of low integrity).
+
+As a final note, we measured integrity based on self-ratings.
+One can criticize this approach by saying it is not possible to measure integrity based on self-reports because of social desirability influences.
+However, self-reports of integrity can indeed predict malevolent behavior: In a meta-analysis with 665 correlation coefficients, integrity tests related to counterproductive behaviors with a coefficient of _r_ = .47 [@Ones.1993].
+Nonetheless, future research would benefit from including behavioral manifestations of integrity, such as concrete cheating behaviors.
+If concrete cheating behaviors also increase desires for privacy, this would strengthen the underlying premise of the nothing-to-hide argument.
+
+## Conclusion
+
 \newpage
@@
 ```{r create_r-references}
-r_refs(file = "r-references.bib")
+r_refs(file = "../bibliography/r-references.bib")
 ```

### 2018-11-14 manuscript/manuscript.tex
- manuscript: included parts of original publication

--- 2018-11-14 manuscript/manuscript.RmD
@@
----
-title             : "Who Needs Privacy?"
-shorttitle        : "Who Needs Privacy?"
+\documentclass[man]{apa6}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Who Needs Privacy?},
+            pdfauthor={Tobias Dienlin~\& Miriam Metzger},
+            pdfkeywords={keywords},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-author: 
-  - name          : "Tobias Dienlin"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "University of Hohenheim, Department of Media Psychology (540F)"
-    email         : "tobias.dienlin@uni-hohenheim.de"
-  - name          : "Miriam Metzger"
-    affiliation   : "1,2"
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-affiliation:
-  - id            : "1"
-    institution   : "University of Hohenheim"
-  - id            : "2"
-    institution   : "University of California, Santa Barbara"
+  \title{Who Needs Privacy?}
+    \author{Tobias Dienlin\textsuperscript{1}~\& Miriam Metzger\textsuperscript{1,2}}
+    \date{}
 
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+\shorttitle{Who Needs Privacy?}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} University of Hohenheim\\\textsuperscript{2} University of California, Santa Barbara}
+\keywords{keywords\newline\indent Word count: X}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
+\usepackage{lineno}
+
+\linenumbers
+\setlength{\parskip}{0em}
+\raggedbottom
+
+\authornote{Add complete departmental affiliations for each
+author here. Each new line herein must be indented, like this line.
 
@@
 
-abstract: |
-  Objective: This study analyzes how personality relates to peoples' desire for privacy.
-Specifically, we investigated whether the syllogism "I don't mind surveillance because I have nothing to hide" is correct: Do people who lack integrity (given they have something to hide) indeed desire more privacy?
+Correspondence concerning this article should be addressed to Tobias
+Dienlin, University of Hohenheim, Department of Media Psychology (540F).
+E-mail:
+\href{mailto:tobias.dienlin@uni-hohenheim.de}{\nolinkurl{tobias.dienlin@uni-hohenheim.de}}}
 
-  Method: Study 1 featured an online questionnaire (_N_ = 268, _M_\textsubscript{age} = 20 years, 72\% female) and Study 2 a laboratory experiment (_N_ = 87, _M_\textsubscript{age} = 20 years, 51\% female), where participants wrote an essay about past negative, positive, or neutral behaviors to analyze effects on desire for privacy.
+\abstract{
+Objective: This study analyzes how personality relates to peoples'
+desire for privacy. Specifically, we investigated whether the syllogism
+``I don't mind surveillance because I have nothing to hide'' is correct:
+Do people who lack integrity (given they have something to hide) indeed
+desire more privacy?
 
-  Results: Study 1 showed that respondents who are more shy, less anxious, and more risk averse desired more privacy.
-Respondents who self-reported lacking integrity reported desiring more privacy from government and more anonymity.
-Study 2 replicated these results and showed a statistical trend (_p_ = .052) that writing about negative past behaviors increased desire for interpersonal privacy.
-Moreover, the integrity IAT showed significant relations with desire for privacy from government.
+Method: Study 1 featured an online questionnaire (\emph{N} = 268,
+\emph{M}\textsubscript{age} = 20 years, 72\% female) and Study 2 a
+laboratory experiment (\emph{N} = 87, \emph{M}\textsubscript{age} = 20
+years, 51\% female), where participants wrote an essay about past
+negative, positive, or neutral behaviors to analyze effects on desire
+for privacy.
 
-  Conclusion: It is possible to predict peoples' desire for privacy based on their lack of integrity.
-However, other neutral personality facets also explain desire for privacy.
-Hence, putting everyone who desires privacy under general suspicion would be incorrect.
+Results: Study 1 showed that respondents who are more shy, less anxious,
+and more risk averse desired more privacy. Respondents who self-reported
+lacking integrity reported desiring more privacy from government and
+more anonymity. Study 2 replicated these results and showed a
+statistical trend (\emph{p} = .052) that writing about negative past
+behaviors increased desire for interpersonal privacy. Moreover, the
+integrity IAT showed significant relations with desire for privacy from
+government.
 
-keywords          : "keywords"
-wordcount         : "X"
+Conclusion: It is possible to predict peoples' desire for privacy based
+on their lack of integrity. However, other neutral personality facets
+also explain desire for privacy. Hence, putting everyone who desires
+privacy under general suspicion would be incorrect.
 
-bibliography      : 
-  - "../bibliography/r-references.bib"
-  - "../bibliography/references.bib"
+}
 
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
+\theoremstyle{definition}
+\newtheorem{example}{Example}[section]
+\theoremstyle{definition}
+\newtheorem{exercise}{Exercise}[section]
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\newtheorem*{solution}{Solution}
+\begin{document}
+\maketitle
 
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-header-includes:
-  - \setlength{\parskip}{0em}
-  - \raggedbottom
----
+In his novel \emph{The Circle}, ({\textbf{???}}) describes a dystopian
+society in which people are gradually forfeiting their privacy. People
+decide to become \enquote{transparent}, which means that they start
+carrying a small camera around the neck in order to broadcast their
+daily lives to the Internet. Eventually, this causes a societal
+upheaval: \enquote{The pressure on those who hadn't gone transparent
+went from polite to oppressive. The question, from pundits and
+constituents, was obvious and loud: If you aren't transparent, what are
+you hiding?} ({\textbf{???}}). The main argument being offered to
+justify the surveillance is: \enquote{If you have nothing to hide, you
+have nothing to fear.} This syllogism is familiar, given that it
+commonly appears in also nonfictional conversations ({\textbf{???}}).
+Consider, for example, the following tweet: \enquote{I don't download
+illegally. I don't have anything on my comp{[}uter{]} to hide. Hell, I'm
+sure the \#NSA gave up on me years ago.} ({\textbf{???}}).
 
-```{r setup, include = FALSE}
-library("papaja")
-```
+Why do people desire privacy? To date there is only little research on
+why people desire privacy and how the desire for privacy can be
+predicted by aspects of personality. For example, and to the best of our
+knowledge, so far no study exists that has analyzed the nothing-to-hide
+argument from a scientific and empirical perspective. Why do some people
+not care whether government agencies such as the NSA are collecting
+their data ({\textbf{???}}), and why do others protest vehemently in
+order to protect their privacy?
 
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
+Answering this question is important: Given that government agencies are
+collecting large amounts of data hoping to reduce criminality and
+terrorism, and given that government agencies are collecting this data
+preemptively and without concrete suspicions, it is relevant to find out
+whether this practice of mass surveillance can be justified based on the
+nothing-to-hide argument. As a result, the main question of this paper
+is: Do people who desire more privacy really have more to hide and, more
+generally, what are personality facets that determine peoples' overall
+desire for privacy?
 
-In his novel _The Circle_, @Eggers.2013 describes a dystopian society in which people are gradually forfeiting their privacy.
-People decide to become "transparent", which means that they start carrying a small camera around the neck in order to broadcast their daily lives to the Internet.
-Eventually, this causes a societal upheaval: "The pressure on those who hadn't gone transparent went from polite to oppressive.
-The question, from pundits and constituents, was obvious and loud: If you aren't transparent, what are you hiding?" [@Eggers.2013, p.
-129].
-The main argument being offered to justify the surveillance is: "If you have nothing to hide, you have nothing to fear." This syllogism is familiar, given that it commonly appears in also nonfictional conversations [@Sieradski.2013].
-Consider, for example, the following tweet: "I don't download illegally.
-I don't have anything on my comp[uter] to hide.
-Hell, I'm sure the \#NSA gave up on me years ago." [@BeautifulDisaster.2015].
+\hypertarget{desire-for-privacy}{%
+\subsection{Desire for Privacy}\label{desire-for-privacy}}
 
-Why do people desire privacy?
-To date there is only little research on why people desire privacy and how the desire for privacy can be predicted by aspects of personality.
-For example, and to the best of our knowledge, so far no study exists that has analyzed the nothing-to-hide argument from a scientific and empirical perspective.
-Why do some people not care whether government agencies such as the NSA are collecting their data [@Greenwald.2013], and why do others protest vehemently in order to protect their privacy?
+Privacy captures the extent of voluntary withdrawal from others (Westin,
+1967). Several models suggest that privacy is a multi-dimensional
+concept: For example, in a theory-driven treatise ({\textbf{???}})
+argued that privacy has four dimensions: informational, social,
+psychological, and physical privacy. Pedersen (1979), by contrast, did
+an empirical factor analysis (initially starting with 94 items) and
+suggested that privacy exists on six dimensions: reserve, isolation,
+solitude, intimacy with friends, intimacy with family, and anonymity. In
+addition, Schwartz (1968) differentiated between horizontal and vertical
+privacy: Whereas horizontal privacy captures withdrawal from peers,
+vertical privacy refers to withdrawal from superiors or institutions
+(e.g., government agencies). Next to being multi-dimensional, privacy is
+also contingent (Dienlin, 2014): One can, for example, distinguish
+between the objective privacy context, the subsequent subjective
+perception of privacy, the psychological desire for privacy (which is
+both a situational and dispositional need), and the resulting privacy
+behavior (as represented by self-disclosure). For the purpose of this
+study, we combine the aforementioned theories and focus on (a) vertical
+privacy with regard to the desire for withdrawal from government
+surveillance, (b) horizontal privacy in terms of the desire for
+withdrawal from peers, friends, or acquaintances, and (c) both
+horizontal and vertical privacy as captured by the general desire for
+anonymity.
 
-Answering this question is important: Given that government agencies are collecting large amounts of data hoping to reduce criminality and terrorism, and given that government agencies are collecting this data preemptively and without concrete suspicions, it is relevant to find out whether this practice of mass surveillance can be justified based on the nothing-to-hide argument.
-As a result, the main question of this paper is: Do people who desire more privacy really have more to hide and, more generally, what are personality facets that determine peoples' overall desire for privacy?
-
-## Desire for Privacy
-
-Privacy captures the extent of voluntary withdrawal from others [@Westin.1967].
-Several models suggest that privacy is a multi-dimensional concept: For example, in a theory-driven treatise @Burgoon.1982 argued that privacy has four dimensions: informational, social, psychological, and physical privacy.
-@Pedersen.1979, by contrast, did an empirical factor analysis (initially starting with 94 items) and suggested that privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity.
-In addition, @Schwartz.1968 differentiated between horizontal and vertical privacy: Whereas horizontal privacy captures withdrawal from peers, vertical privacy refers to withdrawal from superiors or institutions (e.g., government agencies).
-Next to being multi-dimensional, privacy is also contingent [@Dienlin.2014]: One can, for example, distinguish between the objective privacy context, the subsequent subjective perception of privacy, the psychological desire for privacy (which is both a situational and dispositional need), and the resulting privacy behavior (as represented by self-disclosure).
-For the purpose of this study, we combine the aforementioned theories and focus on (a) vertical privacy with regard to the desire for withdrawal from government surveillance, (b) horizontal privacy in terms of the desire for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by the general desire for anonymity.
-
-### The relation between integrity and desire for privacy
+\hypertarget{the-relation-between-integrity-and-desire-for-privacy}{%
+\subsubsection{The relation between integrity and desire for
+privacy}\label{the-relation-between-integrity-and-desire-for-privacy}}
 
 Which specific aspects of personality help predict desire for privacy?
-At its core, the nothing-to-hide argument implies that lack of integrity is an important predictor of why people desire privacy.
-This becomes especially apparent when we consider the definition of Solove's (2007) nothing-to-hide argument (notably, Solove is a strong critic of the nothing-to-hide argument):
+At its core, the nothing-to-hide argument implies that lack of integrity
+is an important predictor of why people desire privacy. This becomes
+especially apparent when we consider the definition of Solove's (2007)
+nothing-to-hide argument (notably, Solove is a strong critic of the
+nothing-to-hide argument):
 
-The NSA surveillance, data mining, or other government information gathering programs will result in the disclosure of particular pieces of information to a few government officials, or perhaps only to government computers.
-This very limited disclosure of the particular information involved is not likely to be threatening to the privacy of law-abiding citizens.
-Only those who are engaged in illegal activities have a reason to hide this information.
-[@Solove.2007; p.
-753]
+The NSA surveillance, data mining, or other government information
+gathering programs will result in the disclosure of particular pieces of
+information to a few government officials, or perhaps only to government
+computers. This very limited disclosure of the particular information
+involved is not likely to be threatening to the privacy of law-abiding
+citizens. Only those who are engaged in illegal activities have a reason
+to hide this information. {[}({\textbf{???}}); p.~753{]}
 
-This definition helps illustrate the link between lack of integrity and desire for privacy: People who have "engaged in illegal activities" can be considered, by definition, to lack integrity [@Paunonen.2002], which is why they have a reason "to hide this information" (or, in other words, to desire more privacy).
-In terms of a scientific definition of integrity there is no real consensus, however most scholars agree that integrity "incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness" [@Connelly.2006; p.
-82].
+This definition helps illustrate the link between lack of integrity and
+desire for privacy: People who have \enquote{engaged in illegal
+activities} can be considered, by definition, to lack integrity
+({\textbf{???}}), which is why they have a reason \enquote{to hide this
+information} (or, in other words, to desire more privacy). In terms of a
+scientific definition of integrity there is no real consensus, however
+most scholars agree that integrity \enquote{incorporates a tendency to
+comply with social norms, avoid deviant behavior, and embrace a sense of
+justice, truthfulness, and fairness} {[}({\textbf{???}}); p.~82{]}.
 
-Several theoretical arguments exist why lack of integrity might correlate with desire for privacy.
-In general, any self-disclosure is a potential risk because others might disagree, disapprove, or misuse the information in other contexts [@Petronio.2000].
-Privacy regulation theory showed that if self-disclosures are too risky, people raise their desired level of privacy, intensify their boundary regulation, and employ more mechanisms to seclude and protect themselves [@Altman.1976].
-In traditional contexts, this could range from moderate behaviors like closing doors, to extreme behaviors such as physically tossing someone out of the room [@Altman.1976].
-In modern contexts, protecting one's privacy can mean to avoid photographs or to deliberately shun public places that have surveillance cameras.
-People who have actually committed something bad, treacherous, or illegal become even more vulnerable and face a significant risk of self-disclosure, because others will surely disapprove of these activities [@Petronio.2000].
-Hence, the foregoing arguments illuminate an indirect link between integrity and desire for privacy: By definition, people who participate in negative activities are considered to lack integrity [@Paunonen.2002].
-People who have engaged in negative activities have, by definition, more to hide, and disclosures concerning those activities pose a high risk.
-Because of this increased risk, people will arguably desire more privacy, as a means to mitigate their felt risk [@Altman.1976].
-In this way, the current research extends Altman's privacy regulation theory (1976) by suggesting that lack of integrity is an important yet unexamined factor that could increase peoples' desired level of privacy.
+Several theoretical arguments exist why lack of integrity might
+correlate with desire for privacy. In general, any self-disclosure is a
+potential risk because others might disagree, disapprove, or misuse the
+information in other contexts ({\textbf{???}}). Privacy regulation
+theory showed that if self-disclosures are too risky, people raise their
+desired level of privacy, intensify their boundary regulation, and
+employ more mechanisms to seclude and protect themselves
+({\textbf{???}}). In traditional contexts, this could range from
+moderate behaviors like closing doors, to extreme behaviors such as
+physically tossing someone out of the room ({\textbf{???}}). In modern
+contexts, protecting one's privacy can mean to avoid photographs or to
+deliberately shun public places that have surveillance cameras. People
+who have actually committed something bad, treacherous, or illegal
+become even more vulnerable and face a significant risk of
+self-disclosure, because others will surely disapprove of these
+activities ({\textbf{???}}). Hence, the foregoing arguments illuminate
+an indirect link between integrity and desire for privacy: By
+definition, people who participate in negative activities are considered
+to lack integrity ({\textbf{???}}). People who have engaged in negative
+activities have, by definition, more to hide, and disclosures concerning
+those activities pose a high risk. Because of this increased risk,
+people will arguably desire more privacy, as a means to mitigate their
+felt risk ({\textbf{???}}). In this way, the current research extends
+Altman's privacy regulation theory (1976) by suggesting that lack of
+integrity is an important yet unexamined factor that could increase
+peoples' desired level of privacy.
 
-A few studies can be found that imply a relation between privacy and integrity.
-For example, several studies found that surveillance reduces cheating behaviors [@Corcoran.1987, Covey.1989].
-@Covey.1989 asked students to solve an impossible maze.
-In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior.
-In the low surveillance condition, the experimenter stood behind the students, did not monitor their behavior, and visual dividers were used to block the experimenter's view of the students.
-Results showed that students were more likely to cheat in the low surveillance condition, suggesting that in situations of surveillance (i.e., less privacy), people show fewer cheating behaviors (i.e., more integrity).
-Similarly, people are more likely to prevent others from stealing when security cameras are visible [@vanBommel.2014], which is also a sign of higher integrity.
-Next, in a longitudinal sample with 457 respondents in Germany [@Trepte.2013], people who reported needing more privacy were less satisfied with their lives (_r_ = -.47), had more (_r_ = .41) and less positive affect (_r_ = -.39).
-More importantly however, people who felt they needed more privacy were also less authentic on their SNSs profiles (_r_ = -.48) and less authentic in their personal relationships [_r_ = -.28; @Trepte.2013].
-For example, people who agreed to items like "I do not talk about personal issues unless my conversation partner brings them up first" were more likely to report that their online profiles did not truly represent their personality.
-Given the argument that authenticity is a subset of integrity [@Sheldon.2004], we reason that the concept of integrity might relate to the desired level of privacy.
-Finally, @Pedersen.1982 showed that three dimensions of need for privacy related to self-esteem: In his study with _N_ = 70 undergraduate students, respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21) and preferred solitude (_r_ = .24).
-Granted, self-esteem and integrity are generally distinct concepts; however, Pedersen's specific operationalization of self-esteem integrated several aspects of integrity (e.g., by using items such as "moral, nice, fair, unselfish, good, honest, reputable, sane" to measure self-esteem).
-Thus, our overarching hypothesis is that people who lack integrity have a greater desire for privacy.
+A few studies can be found that imply a relation between privacy and
+integrity. For example, several studies found that surveillance reduces
+cheating behaviors ({\textbf{???}}, Covey.1989). ({\textbf{???}}) asked
+students to solve an impossible maze. In the high surveillance
+condition, the experimenter stood in front of the students and closely
+monitored their behavior. In the low surveillance condition, the
+experimenter stood behind the students, did not monitor their behavior,
+and visual dividers were used to block the experimenter's view of the
+students. Results showed that students were more likely to cheat in the
+low surveillance condition, suggesting that in situations of
+surveillance (i.e., less privacy), people show fewer cheating behaviors
+(i.e., more integrity). Similarly, people are more likely to prevent
+others from stealing when security cameras are visible ({\textbf{???}}),
+which is also a sign of higher integrity. Next, in a longitudinal sample
+with 457 respondents in Germany ({\textbf{???}}), people who reported
+needing more privacy were less satisfied with their lives (\emph{r} =
+-.47), had more (\emph{r} = .41) and less positive affect (\emph{r} =
+-.39). More importantly however, people who felt they needed more
+privacy were also less authentic on their SNSs profiles (\emph{r} =
+-.48) and less authentic in their personal relationships (\emph{r} =
+-.28; {\textbf{???}}). For example, people who agreed to items like
+\enquote{I do not talk about personal issues unless my conversation
+partner brings them up first} were more likely to report that their
+online profiles did not truly represent their personality. Given the
+argument that authenticity is a subset of integrity ({\textbf{???}}), we
+reason that the concept of integrity might relate to the desired level
+of privacy. Finally, Pedersen (1982) showed that three dimensions of
+need for privacy related to self-esteem: In his study with \emph{N} = 70
+undergraduate students, respondents who held a lower self-esteem were
+more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21)
+and preferred solitude (\emph{r} = .24). Granted, self-esteem and
+integrity are generally distinct concepts; however, Pedersen's specific
+operationalization of self-esteem integrated several aspects of
+integrity (e.g., by using items such as \enquote{moral, nice, fair,
+unselfish, good, honest, reputable, sane} to measure self-esteem). Thus,
+our overarching hypothesis is that people who lack integrity have a
+greater desire for privacy.
 
-In Study 1, we used a questionnaire-based design to analyze how lack of integrity and other personality facets relate to desire for privacy.
-In accordance with the reasoning mentioned above, we suggest that people with less integrity feel a greater desire for privacy.
-Specifically, we argue that integrity may relate to the desire for privacy from (a) government surveillance, as governments have the legitimate power to prosecute illegal activities.
-Next, we hypothesize that integrity relates to the desire privacy for (b) anonymity.
-Anonymity makes it more difficult for both legal and social agents to identify and address potential wrongdoers, which is why people with less integrity will prefer situations in which they are anonymous.
-Finally, lack of integrity likely also relates to an increased desire for privacy from (c) other people, as most other people will disapprove of immoral or illegal activities, and might reveal those activities to authorities.
+In Study 1, we used a questionnaire-based design to analyze how lack of
+integrity and other personality facets relate to desire for privacy. In
+accordance with the reasoning mentioned above, we suggest that people
+with less integrity feel a greater desire for privacy. Specifically, we
+argue that integrity may relate to the desire for privacy from (a)
+government surveillance, as governments have the legitimate power to
+prosecute illegal activities. Next, we hypothesize that integrity
+relates to the desire privacy for (b) anonymity. Anonymity makes it more
+difficult for both legal and social agents to identify and address
+potential wrongdoers, which is why people with less integrity will
+prefer situations in which they are anonymous. Finally, lack of
+integrity likely also relates to an increased desire for privacy from
+(c) other people, as most other people will disapprove of immoral or
+illegal activities, and might reveal those activities to authorities.
 
-Hypothesis 1: People who feel lower in self-perceived integrity desire more privacy from government surveillance (H1a), more anonymity (H1b), and more privacy from other persons (H1c).
+Hypothesis 1: People who feel lower in self-perceived integrity desire
+more privacy from government surveillance (H1a), more anonymity (H1b),
+and more privacy from other persons (H1c).
 
-### Shyness
+\hypertarget{shyness}{%
+\subsubsection{Shyness}\label{shyness}}
 
-Critics of the nothing-to-hide argument hold that people who desire privacy should not automatically be confronted with suspicion, and that privacy has several purposes that are not related to criminal behavior [@Marlinspike.2013].
-@Westin.1967, for example, defined four primary purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
+Critics of the nothing-to-hide argument hold that people who desire
+privacy should not automatically be confronted with suspicion, and that
+privacy has several purposes that are not related to criminal behavior
+({\textbf{???}}). Westin (1967), for example, defined four primary
+purposes of privacy: (1) self-development (i.e., the integration of
+experiences into meaningful patterns), (2) autonomy (i.e., the desire to
+avoid being manipulated and dominated), (3) emotional release (i.e., the
+release of tension from social role demands), and (4) protected
+communication (i.e., the ability to foster intimate relationships).
 These are all important social factors for which people desire privacy.
-Hence, the argument is that people who desire privacy can have several legitimate reasons for doing so; reasons which are essential for psychosocial wellbeing and which relate to different factors of personality.
-Below, we thus explore other (neutral) aspects of personality that potentially predict desire for privacy.
-In order to be more precise, we follow the advice by @Paunonen.2001 and, instead of using generic personality factors as predictors, refer to specific personality facets.
+Hence, the argument is that people who desire privacy can have several
+legitimate reasons for doing so; reasons which are essential for
+psychosocial wellbeing and which relate to different factors of
+personality. Below, we thus explore other (neutral) aspects of
+personality that potentially predict desire for privacy. In order to be
+more precise, we follow the advice by Paunonen and Ashton (2001) and,
+instead of using generic personality factors as predictors, refer to
+specific personality facets.
 
-First, we argue that people who are more reserved, who feel less comfortable in social situations, generally desire more anonymity and more interpersonal privacy.
-Given that privacy is, by definition, a voluntary withdrawal from society [@Westin.1967], we expect that people who are more reserved or more shy desire more privacy from others.
-Several empirical studies support this hypothesis: Extroverted people desire less privacy [@Morton.2013], people who describe themselves as introverted thinkers are more likely to prefer social isolation [@Pedersen.1982], and introverted people are more likely to report invasions of privacy [@Stone.1986].
-Finally, we did not find convincing theoretical and empirical arguments for why shyness should relate to an increased desire for privacy from government surveillance, which is why we did not include a hypothesis on this relation.
+First, we argue that people who are more reserved, who feel less
+comfortable in social situations, generally desire more anonymity and
+more interpersonal privacy. Given that privacy is, by definition, a
+voluntary withdrawal from society (Westin, 1967), we expect that people
+who are more reserved or more shy desire more privacy from others.
+Several empirical studies support this hypothesis: Extroverted people
+desire less privacy ({\textbf{???}}), people who describe themselves as
+introverted thinkers are more likely to prefer social isolation
+(Pedersen, 1982), and introverted people are more likely to report
+invasions of privacy ({\textbf{???}}). Finally, we did not find
+convincing theoretical and empirical arguments for why shyness should
+relate to an increased desire for privacy from government surveillance,
+which is why we did not include a hypothesis on this relation.
 
-Hypothesis 2: People who are more shy desire more anonymity (H2a) and more privacy from other persons (H2b).
+Hypothesis 2: People who are more shy desire more anonymity (H2a) and
+more privacy from other persons (H2b).
 
-### Anxiety
+\hypertarget{anxiety}{%
+\subsubsection{Anxiety}\label{anxiety}}
 
 Of course, there are also reasons why people might desire less privacy.
-Government agencies often curtail privacy with the aim to prevent crime: For example, the NSA's surveillance programs are often considered a direct response to the 9 / 11 terrorists attacks [@Greenwald.2013].
-It seems plausible that people who are more afraid of terrorist attacks are also more likely to consent to these surveillance programs, given that these programs promise to reduce the likelihood of future attacks.
-One can then argue that people who are afraid of terrorist attacks are also more afraid of threats overall, which is why we suggest that people who are, in general, more anxious desire less privacy from government surveillance and less anonymity.
-We did not include a hypothesis on the potential relation between anxiety and desire for interpersonal privacy.
-On the one hand, one could argue that people who are more anxious are more reserved, given that social interactions can pose significant risks [especially with strangers or weak ties; @Granovetter.1973].
-At the same time, one could suggest that especially those people who are more anxious desire less privacy from others (and especially their strong ties), in order to cope better with their daily challenges.
-At the end, given that we measure interpersonal privacy on a general level (and do not distinguish between desire for privacy from (a) weak ties and (b) strong ties), it seems plausible that both effects could cancel each other out.
+Government agencies often curtail privacy with the aim to prevent crime:
+For example, the NSA's surveillance programs are often considered a
+direct response to the 9 / 11 terrorists attacks ({\textbf{???}}). It
+seems plausible that people who are more afraid of terrorist attacks are
+also more likely to consent to these surveillance programs, given that
+these programs promise to reduce the likelihood of future attacks. One
+can then argue that people who are afraid of terrorist attacks are also
+more afraid of threats overall, which is why we suggest that people who
+are, in general, more anxious desire less privacy from government
+surveillance and less anonymity. We did not include a hypothesis on the
+potential relation between anxiety and desire for interpersonal privacy.
+On the one hand, one could argue that people who are more anxious are
+more reserved, given that social interactions can pose significant risks
+(especially with strangers or weak ties; {\textbf{???}}). At the same
+time, one could suggest that especially those people who are more
+anxious desire less privacy from others (and especially their strong
+ties), in order to cope better with their daily challenges. At the end,
+given that we measure interpersonal privacy on a general level (and do
+not distinguish between desire for privacy from (a) weak ties and (b)
+strong ties), it seems plausible that both effects could cancel each
+other out.
 
-Hypothesis 3: People who are more anxious desire less privacy from government surveillance (H3a) and more anonymity (H3b).
+Hypothesis 3: People who are more anxious desire less privacy from
+government surveillance (H3a) and more anonymity (H3b).
 
-### Risk aversion
+\hypertarget{risk-aversion}{%
+\subsubsection{Risk aversion}\label{risk-aversion}}
 
-Disclosing personal information always poses a certain risk, given that others can misuse self-disclosed personal information in different contexts, which can lead to severe consequences [@Altman.1976].
-Not everyone will feel intimidated by this hypothetical threat---except those who have a general tendency to avoid taking unnecessary risks.
-The most cautious strategy to minimize risks of personal self-disclosures would be, arguably, to keep as much information as possible private.
-Hence, we suggest that people who are, in general, more risk averse have a good reason to desire more privacy in all three aforementioned contexts.
+Disclosing personal information always poses a certain risk, given that
+others can misuse self-disclosed personal information in different
+contexts, which can lead to severe consequences ({\textbf{???}}). Not
+everyone will feel intimidated by this hypothetical threat---except
+those who have a general tendency to avoid taking unnecessary risks. The
+most cautious strategy to minimize risks of personal self-disclosures
+would be, arguably, to keep as much information as possible private.
+Hence, we suggest that people who are, in general, more risk averse have
+a good reason to desire more privacy in all three aforementioned
+contexts.
 
-Hypothesis 4: People who are more risk averse desire more privacy from government surveillance (H4a), more anonymity (H4b), and more privacy from other persons (H4c).
+Hypothesis 4: People who are more risk averse desire more privacy from
+government surveillance (H4a), more anonymity (H4b), and more privacy
+from other persons (H4c).
 
-### Traditionality
+\hypertarget{traditionality}{%
+\subsubsection{Traditionality}\label{traditionality}}
 
-The personal computer and the Internet have rendered the world increasingly digitized: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.
-Given the features of digital information [i.e., information is persistent, searchable, reproducible, and scalable; @boyd.2008], this allows for unprecedented ways and degrees of surveillance.
-Mark Zuckerberg famously observed that privacy is no longer a "social norm," rather that people share personal information [@Johnson.2010].
-Hence, in order to be part of contemporary life (e.g., by using SNSs), it seems necessary to give up some privacy.
-However, arguably not everyone is willing to pay that price, and especially people who are more conservative might prefer to stick to their usual routines and decide against giving up their privacy.
-This is supported by empirical research: Older people, who are generally less open and more traditional [@Donnellan.2008], are more concerned about their privacy than younger people [@Fife.2012].
-Taken together, we suggest that people who are more traditional also desire more privacy in all three aforementioned contexts.
+The personal computer and the Internet have rendered the world
+increasingly digitized: Social interactions, purchases, and medical
+treatments nowadays all produce digital traces, which can be combined
+into accurate latent user profiles. Given the features of digital
+information (i.e., information is persistent, searchable, reproducible,
+and scalable; {\textbf{???}}), this allows for unprecedented ways and
+degrees of surveillance. Mark Zuckerberg famously observed that privacy
+is no longer a \enquote{social norm,} rather that people share personal
+information ({\textbf{???}}). Hence, in order to be part of contemporary
+life (e.g., by using SNSs), it seems necessary to give up some privacy.
+However, arguably not everyone is willing to pay that price, and
+especially people who are more conservative might prefer to stick to
+their usual routines and decide against giving up their privacy. This is
+supported by empirical research: Older people, who are generally less
+open and more traditional ({\textbf{???}}), are more concerned about
+their privacy than younger people ({\textbf{???}}). Taken together, we
+suggest that people who are more traditional also desire more privacy in
+all three aforementioned contexts.
 
-Hypothesis 5: People who are more traditional desire more privacy from government surveillance (H5a), more anonymity (H5b), and more privacy from other persons (H5c).
+Hypothesis 5: People who are more traditional desire more privacy from
+government surveillance (H5a), more anonymity (H5b), and more privacy
+from other persons (H5c).
 
-# Methods
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+We report how we determined our sample size, all data exclusions (if
+any), all manipulations, and all measures in the study.
 
-## Procedure and participants
+\hypertarget{procedure-and-participants}{%
+\subsection{Procedure and
+participants}\label{procedure-and-participants}}
 
-Participants were students from a university in the western U.S.
-who received course credit for taking part in the study.
-The sample consisted of _N_ = 296 respondents, with an age that ranged from 18 to 56 years (_M_ = 20 years).
-72\% of the respondents were female.
-The median participation time was 24 minutes.
-Regarding ethnicity, 37\% of the respondents were Non-Hispanic White / Caucasian, 4\% Black / African American, 21\% Hispanic / Latino, 24\% Asian / Pacific Islander, 0\% Native American, 5\% others, and 8\% nonresponse.
+Participants were students from a university in the western U.S. who
+received course credit for taking part in the study. The sample
+consisted of \emph{N} = 296 respondents, with an age that ranged from 18
+to 56 years (\emph{M} = 20 years). 72\% of the respondents were female.
+The median participation time was 24 minutes. Regarding ethnicity, 37\%
+of the respondents were Non-Hispanic White / Caucasian, 4\% Black /
+African American, 21\% Hispanic / Latino, 24\% Asian / Pacific Islander,
+0\% Native American, 5\% others, and 8\% nonresponse.
 
-## Measures
+\hypertarget{measures}{%
+\subsection{Measures}\label{measures}}
 
-Despite the fact that we mostly used well-established scales, confirmatory factor analyses (CFAs) showed that some of the original items had to be deleted in order to achieve adequate factorial validity.
-The final scales showed acceptable fit (CFI \textgreater .90, TLI \textgreater .90, RMSEA \textless .10, SRMR \textless .10), good composite reliability (REL($\upomega$) \textgreater .60), and adequate convergent factorial validity (AVE \textgreater .50; see Table \ref{tab:DIS_Study_4_Table_1}).
-Respondents answered all items on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).
+Despite the fact that we mostly used well-established scales,
+confirmatory factor analyses (CFAs) showed that some of the original
+items had to be deleted in order to achieve adequate factorial validity.
+The final scales showed acceptable fit (CFI \textgreater .90, TLI
+\textgreater .90, RMSEA \textless .10, SRMR \textless .10), good
+composite reliability (REL(\(\upomega\)) \textgreater .60), and adequate
+convergent factorial validity (AVE \textgreater .50; see Table
+\ref{tab:DIS_Study_4_Table_1}). Respondents answered all items on a
+7-point Likert scale ranging from 1 (\emph{strongly disagree}) to 7
+(\emph{strongly agree}).
 
-The data, all items (including deleted ones), results of CFAs, item statistics, and distribution plots can be found in the online supplementary material.[^OSM]
+The data, all items (including deleted ones), results of CFAs, item
+statistics, and distribution plots can be found in the online
+supplementary material.\footnote{\url{https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f}\}\}}
 
-[^OSM]: https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f}}
+\hypertarget{desire-for-privacy-1}{%
+\subsubsection{Desire for privacy}\label{desire-for-privacy-1}}
 
-### Desire for privacy
+We measured desire for privacy on three dimensions: (a) Desire for
+privacy from government surveillance, which represents the extent to
+which people want the government to abstain from collecting information
+about their personal life. One example item is \enquote{I feel the need
+to protect my privacy from government agencies.} (b) Desire for
+anonymity, which measures the extent to which people feel the need to
+avoid identification(\enquote{I need to be able to use a fake name on
+social network sites to preserve my privacy\}). (c) Desire for privacy
+from other people, which measures the extent to which people want to
+withhold personal information from others(}I don't feel the need to tell
+my friends all my secrets\}). For each dimension, we used 3
+self-developed items that build on prior studies ({\textbf{???}}).
 
-We measured desire for privacy on three dimensions: (a) Desire for privacy from government surveillance, which represents the extent to which people want the government to abstain from collecting information about their personal life.
-One example item is "I feel the need to protect my privacy from government agencies." (b) Desire for anonymity, which measures the extent to which people feel the need to avoid identification("I need to be able to use a fake name on social network sites to preserve my privacy}).
-(c) Desire for privacy from other people, which measures the extent to which people want to withhold personal information from others("I don't feel the need to tell my friends all my secrets}).
-For each dimension, we used 3 self-developed items that build on prior studies [@Masur.2016].
+\hypertarget{integrity}{%
+\subsubsection{Integrity}\label{integrity}}
 
-### Integrity
+Integrity measures the extent to which people comply with social norms
+and values. When measuring integrity, the question arises whether it is
+possible to measure integrity based on self-reports. Interestingly,
+integrity tests that are based on self-reports have been shown to work
+successfully, given that they can predict unwanted professional
+workplace behavior sufficiently (e.g., theft, drug and alcohol problems,
+or absenteeism; {\textbf{???}}). In order to measure lack of integrity,
+we thus used 4 items of the subscale integrity of the Supernumerary
+Personality Inventory ({\textbf{???}}). An example item is \enquote{I
+don't think there's anything wrong with cheating a little on one's
+income tax forms.}
 
-Integrity measures the extent to which people comply with social norms and values.
-When measuring integrity, the question arises whether it is possible to measure integrity based on self-reports.
-Interestingly, integrity tests that are based on self-reports have been shown to work successfully, given that they can predict unwanted professional workplace behavior sufficiently [e.g., theft, drug and alcohol problems, or absenteeism; @Ones.1993].
-In order to measure lack of integrity, we thus used 4 items of the subscale integrity of the Supernumerary Personality Inventory [@Paunonen.2002].
-An example item is "I don't think there's anything wrong with cheating a little on one's income tax forms."
+\hypertarget{shyness-1}{%
+\subsubsection{Shyness}\label{shyness-1}}
 
-### Shyness
+Shyness captures whether people prefer to spend their time alone or in
+company. We measured shyness with 4 items of the inverted extraversion
+subscale gregariousness ({\textbf{???}}). An example item is "I shy away
+from crowds of people.\}
 
-Shyness captures whether people prefer to spend their time alone or in company.
-We measured shyness with 4 items of the inverted extraversion subscale gregariousness [@Costa.1992].
-An example item is "I shy away from crowds of people.}
+\hypertarget{anxiety-1}{%
+\subsubsection{Anxiety}\label{anxiety-1}}
 
-### Anxiety
+Anxiety measures whether people are afraid of negative external
+influences. We measured anxiety with 4 items of the neuroticism subscale
+anxiety ({\textbf{???}}). An example item is "I am easily frightened.\}
 
-Anxiety measures whether people are afraid of negative external influences.
-We measured anxiety with 4 items of the neuroticism subscale anxiety [@Costa.1992].
-An example item is "I am easily frightened.}
+\hypertarget{risk-avoidance}{%
+\subsubsection{Risk avoidance}\label{risk-avoidance}}
 
-### Risk avoidance
+Risk avoidance captures whether people abstain from taking risks. We
+measured risk avoidance with 4 items of the conscientiousness subscale
+deliberation ({\textbf{???}}). An example item is "I think twice before
+I answer a question.\}
 
-Risk avoidance captures whether people abstain from taking risks.
-We measured risk avoidance with 4 items of the conscientiousness subscale deliberation [@Costa.1992].
-An example item is "I think twice before I answer a question.}
+\hypertarget{traditionalism}{%
+\subsubsection{Traditionalism}\label{traditionalism}}
 
-### Traditionalism
+Traditionalism measures whether people prefer to stick with their usual
+routines. We measured traditionalism with 4 items of the inverted
+openness to experiences subscale actions ({\textbf{???}}). An example
+item is "I'm pretty set in my ways.\}
 
-Traditionalism measures whether people prefer to stick with their usual routines.
-We measured traditionalism with 4 items of the inverted openness to experiences subscale actions [@Costa.1992].
-An example item is "I'm pretty set in my ways.}
+\hypertarget{data-analyses}{%
+\subsection{Data analyses}\label{data-analyses}}
 
-## Data analyses
+All hypotheses were tested with structural equation modeling (SEM). To
+assess the SEM assumption of multivariate normality, we computed a
+multivariate Shapiro-Wilk normality test. The results showed a violation
+of multivariate normality (\emph{W} = 0.90, \emph{p} \textless .001),
+which is why we used the more robust Satorra-Bentler scaled test
+statistic as estimator. We treated missing data with casewise deletion
+and tested all hypotheses with a two-tailed p \textless .050
+significance level; values between \emph{p} = .050 and \emph{p} = .010
+were considered trends toward significance. Regarding effect sizes, we
+classified regression coefficients with values exceeding \(\upbeta\) =
+.10 as small effects, \(\upbeta\) = .30 as medium effects, and
+\(\upbeta\) = .50 as large effects.
 
-All hypotheses were tested with structural equation modeling (SEM).
-To assess the SEM assumption of multivariate normality, we computed a multivariate Shapiro-Wilk normality test.
-The results showed a violation of multivariate normality (_W_ = 0.90, _p_ \textless .001), which is why we used the more robust Satorra-Bentler scaled test statistic as estimator.
-We treated missing data with casewise deletion and tested all hypotheses with a two-tailed p \textless .050 significance level; values between _p_ = .050 and _p_ = .010 were considered trends toward significance.
-Regarding effect sizes, we classified regression coefficients with values exceeding $\upbeta$ = .10 as small effects, $\upbeta$ = .30 as medium effects, and $\upbeta$ = .50 as large effects.
+Unfortunately, we did not determine sample size based on a priori power
+analyses. We decided against including social desirability as a control
+variable, because even though social desirability can affect answers to
+sensitive questions ({\textbf{???}}), it is more likely to reflect a
+true personality trait than false answering behavior ({\textbf{???}}).
+Likewise, we did not include demographic control variables such as age
+or education, because we used a typical student sample with little
+demographic variance. We used R (Version 3.5.1; R Core Team, 2018) for
+all our analyses.
 
-Unfortunately, we did not determine sample size based on a priori power analyses.
-We decided against including social desirability as a control variable, because even though social desirability can affect answers to sensitive questions [@deJong.2012], it is more likely to reflect a true personality trait than false answering behavior [@deVries.2014].
-Likewise, we did not include demographic control variables such as age or education, because we used a typical student sample with little demographic variance.
-We used `r cite_r("..\bibliography\r-references.bib")` for all our analyses.
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-# Results
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
-# Discussion
+The results of Study 1 showed that integrity relates to several
+dimensions of desire for privacy: People who reported being of lower
+integrity desired more privacy from government and more anonymity. In
+other words, people who agreed that there would be nothing wrong with
+cheating a little or lying occasionally were also more likely to agree
+that the government should not invade peoples' privacy, even if that
+could help to prevent terrorist attacks. Likewise, people who said, for
+example, that they would feel tempted to take things that do not belong
+to them were also more likely to avoid situations in which they were
+identifiable.
 
-The results of Study 1 showed that integrity relates to several dimensions of desire for privacy: People who reported being of lower integrity desired more privacy from government and more anonymity.
-In other words, people who agreed that there would be nothing wrong with cheating a little or lying occasionally were also more likely to agree that the government should not invade peoples' privacy, even if that could help to prevent terrorist attacks.
-Likewise, people who said, for example, that they would feel tempted to take things that do not belong to them were also more likely to avoid situations in which they were identifiable.
+In addition, desire for privacy was predicted also by other (neutral)
+personality facets: People who were more shy, more risk averse, and less
+anxious also desired more privacy. This implies that next to lack of
+integrity there are various other personality-related aspects that
+predict desire for privacy.
 
-In addition, desire for privacy was predicted also by other (neutral) personality facets: People who were more shy, more risk averse, and less anxious also desired more privacy.
-This implies that next to lack of integrity there are various other personality-related aspects that predict desire for privacy.
+People who are more shy, more risk averse, or less anxious also desire
+more privacy. For example, people who are less anxious are less likely
+to accept government surveillance (arguably because they are less afraid
+of terrorist attacks). When looking at the bigger implications of the
+results, this shows the importance to make differentiated claims on why
+people desire privacy: Indeed, the results suggest that some people
+desire privacy because they might have something to hide. However,
+putting everyone who desires privacy under a general suspicion is wrong
+given that shy, risk averse, and less anxious people are also more
+likely to desire privacy.
 
-People who are more shy, more risk averse, or less anxious also desire more privacy.
-For example, people who are less anxious are less likely to accept government surveillance (arguably because they are less afraid of terrorist attacks).
-When looking at the bigger implications of the results, this shows the importance to make differentiated claims on why people desire privacy: Indeed, the results suggest that some people desire privacy because they might have something to hide.
-However, putting everyone who desires privacy under a general suspicion is wrong given that shy, risk averse, and less anxious people are also more likely to desire privacy.
+In conclusion, our results follow ({\textbf{???}}), who reasoned that if
+exposure of information is risky it is likely that people will use more
+mechanisms to strengthen their social boundaries and increase their
+desired level of privacy. This study thus aligns with Altman's privacy
+regulation theory by showing that, in several contexts, people with
+lower integrity had a higher level of desired privacy.
 
-In conclusion, our results follow @Altman.1976, who reasoned that if exposure of information is risky it is likely that people will use more mechanisms to strengthen their social boundaries and increase their desired level of privacy.
-This study thus aligns with Altman's privacy regulation theory by showing that, in several contexts, people with lower integrity had a higher level of desired privacy.
+\hypertarget{limitations-and-future-perspective}{%
+\subsection{Limitations and future
+perspective}\label{limitations-and-future-perspective}}
 
-## Limitations and future perspective
+In our analysis of predictors of privacy, we followed the recommendation
+by Paunonen and Ashton (2001) and did not analyze broad factors of
+personality (e.g., neuroticism); instead, we focused on more specific
+personality facets (e.g., fearfulness). For future research, we suggest
+going one step further by analyzing predictors that are even more
+specified. For example, it seems possible that people who hold
+dissenting political beliefs could also have a higher desire for privacy
+from the government. Similarly, it would be interesting to focus on
+different minority groups. For example, it seems plausible that people
+from a LGBT background might desire more privacy from government
+(because it is potentially repressive or unfriendly toward LGBTs).
+Finally, in this study we focused mostly on escapist motives for why
+people desire privacy (e.g., shyness, risk aversion). Interestingly,
+({\textbf{???}}) were able to show that when predicting engagement in
+solitary activities, it is less preferable to measure how strongly
+people want to escape society (avoidance oriented), but rather how much
+they seek solitude (approach oriented). Hence, future studies might want
+to include predictors that are more approach oriented (e.g., peoples'
+desire for contemplation).
 
-In our analysis of predictors of privacy, we followed the recommendation by @Paunonen.2001 and did not analyze broad factors of personality (e.g., neuroticism); instead, we focused on more specific personality facets (e.g., fearfulness).
-For future research, we suggest going one step further by analyzing predictors that are even more specified.
-For example, it seems possible that people who hold dissenting political beliefs could also have a higher desire for privacy from the government.
-Similarly, it would be interesting to focus on different minority groups.
-For example, it seems plausible that people from a LGBT background might desire more privacy from government (because it is potentially repressive or unfriendly toward LGBTs).
-Finally, in this study we focused mostly on escapist motives for why people desire privacy (e.g., shyness, risk aversion).
-Interestingly, @Leary.2003 were able to show that when predicting engagement in solitary activities, it is less preferable to measure how strongly people want to escape society (avoidance oriented), but rather how much they seek solitude (approach oriented).
-Hence, future studies might want to include predictors that are more approach oriented (e.g., peoples' desire for contemplation).
+From a methodological perspective, future research should continue to
+improve the instruments we used, given that factorial validity of some
+scales was only moderate. Similarly, we recommend elaborating on the
+general understanding of integrity as a theoretical concept. To date,
+there is not one overarching concept of integrity that incorporates all
+the different aspects of integrity, yet it would be valuable to examine
+how other aspects of integrity (e.g., authenticity, trustworthiness, or
+consistency) relate to privacy desires.
 
-From a methodological perspective, future research should continue to improve the instruments we used, given that factorial validity of some scales was only moderate.
-Similarly, we recommend elaborating on the general understanding of integrity as a theoretical concept.
-To date, there is not one overarching concept of integrity that incorporates all the different aspects of integrity, yet it would be valuable to examine how other aspects of integrity (e.g., authenticity, trustworthiness, or consistency) relate to privacy desires.
+Power analyses showed that future research should use samples above
+\emph{N} \(\approx\) 260 in order to test hypotheses with the
+recommended power of at least .80 (Cohen, 1992).
 
-Power analyses showed that future research should use samples above _N_ $\approx$ 260 in order to test hypotheses with the recommended power of at least .80 (Cohen, 1992).
+In general, the question arises whether it is possible, or even socially
+desirable, to measure a person's integrity. On the one hand, integrity
+implies absolute criteria: Stealing is bad and forbidden, whereas
+helping is good and encouraged. On the other hand, integrity implies
+relative criteria: Whereas some cultures disapprove of lying whatever
+the context, others consider lying okay---for example \enquote{white
+lies} in order to save face or to avoid hurting someone's feelings
+({\textbf{???}}). Thus, ranking behaviors, opinions, and character
+traits with regard to integrity is a moral dilemma. As a result,
+throughout the entire study we have understood integrity as a
+transgression of social norms that is strong and that most societies
+would agree upon (for example, most societies would consider stealing as
+a sign of low integrity).
 
-In general, the question arises whether it is possible, or even socially desirable, to measure a person's integrity.
-On the one hand, integrity implies absolute criteria: Stealing is bad and forbidden, whereas helping is good and encouraged.
-On the other hand, integrity implies relative criteria: Whereas some cultures disapprove of lying whatever the context, others consider lying okay---for example "white lies" in order to save face or to avoid hurting someone's feelings [@Altman.1977].
-Thus, ranking behaviors, opinions, and character traits with regard to integrity is a moral dilemma.
-As a result, throughout the entire study we have understood integrity as a transgression of social norms that is strong and that most societies would agree upon (for example, most societies would consider stealing as a sign of low integrity).
+As a final note, we measured integrity based on self-ratings. One can
+criticize this approach by saying it is not possible to measure
+integrity based on self-reports because of social desirability
+influences. However, self-reports of integrity can indeed predict
+malevolent behavior: In a meta-analysis with 665 correlation
+coefficients, integrity tests related to counterproductive behaviors
+with a coefficient of \emph{r} = .47 ({\textbf{???}}). Nonetheless,
+future research would benefit from including behavioral manifestations
+of integrity, such as concrete cheating behaviors. If concrete cheating
+behaviors also increase desires for privacy, this would strengthen the
+underlying premise of the nothing-to-hide argument.
 
-As a final note, we measured integrity based on self-ratings.
-One can criticize this approach by saying it is not possible to measure integrity based on self-reports because of social desirability influences.
-However, self-reports of integrity can indeed predict malevolent behavior: In a meta-analysis with 665 correlation coefficients, integrity tests related to counterproductive behaviors with a coefficient of _r_ = .47 [@Ones.1993].
-Nonetheless, future research would benefit from including behavioral manifestations of integrity, such as concrete cheating behaviors.
-If concrete cheating behaviors also increase desires for privacy, this would strengthen the underlying premise of the nothing-to-hide argument.
-
-## Conclusion
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
 
@@
 
-# References
-```{r create_r-references}
-r_refs(file = "../bibliography/r-references.bib")
-```
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
-<div id = "refs"></div>
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Dienlin.2014}{}%
+Dienlin, T. (2014). The privacy process model. In S. Garnett, S. Halft,
+M. Herz, \& J. M. Mönig (Eds.), \emph{Medien und Privatheit} (pp.
+105--122). Passau, Germany: Karl Stutz.
+
+\leavevmode\hypertarget{ref-Paunonen.2001}{}%
+Paunonen, S. V., \& Ashton, M. C. (2001). Big Five factors and facets
+and the prediction of behavior. \emph{Journal of Personality and Social
+Psychology}, \emph{81}(3), 524--539.
+doi:\href{https://doi.org/10.1037/0022-3514.81.3.524}{10.1037/0022-3514.81.3.524}
+
+\leavevmode\hypertarget{ref-Pedersen.1979}{}%
+Pedersen, D. M. (1979). Dimensions of privacy. \emph{Perceptual and
+Motor Skills}, \emph{48}(3), 1291--1297.
+doi:\href{https://doi.org/10.2466/pms.1979.48.3c.1291}{10.2466/pms.1979.48.3c.1291}
+
+\leavevmode\hypertarget{ref-Pedersen.1982}{}%
+Pedersen, D. M. (1982). Personality correlates of privacy. \emph{The
+Journal of Psychology}, \emph{112}(1), 11--14.
+doi:\href{https://doi.org/10.1080/00223980.1982.9923528}{10.1080/00223980.1982.9923528}
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2018). \emph{R: A language and environment for statistical
+computing}. Vienna, Austria: R Foundation for Statistical Computing.
+Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-Schwartz.1968}{}%
+Schwartz, B. (1968). The social psychology of privacy. \emph{American
+Journal of Sociology}, \emph{73}(6), 741--752.
+
+\leavevmode\hypertarget{ref-Westin.1967}{}%
+Westin, A. F. (1967). \emph{Privacy and freedom}. New York, NY:
+Atheneum.
+
 \endgroup
+
+\end{document}

### 2018-12-09 manuscript/manuscript.RmD
- major updates on everything:     - mostly finished the analyses     - rewritten the methods, results, and abstract

--- 2018-11-13 manuscript/manuscript.RmD
@@
 
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+abstract          : (ref:abstract)
+keywords          : "Privacy, personality, anonymity, integrity, SEM"
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+bibliography      : 
+  - "../bibliography/r-references.bib"
+  - "../bibliography/references.bib"
 
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["r-references.bib"]
-
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 output            : papaja::apa6_pdf
+# output            : papaja::apa6_word
+header-includes:
+  - \setlength{\parskip}{0em}
+  - \raggedbottom
 ---
-
-```{r setup, include = FALSE}
-library("papaja")
-```
 
@@
 set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed,
+                      fig.pos = 'h')
 ```
 
+```{r setup, include = FALSE}
+devtools::install_git("https://github.com/tdienlin/td")
+packages <- c("devtools", "ggplot2", "kableExtra", "lavaan", "magrittr", 
+              "papaja", "semPlot", "td")
+lapply(packages, library, character.only = TRUE)
+load("../data/workspace.RData")
+```
+
+(ref:abstract)
+In this study we analyzes how personality relates to peoples' need for privacy.
+For example, we analyze if the so-called "nothing-to-hide" argument is correct: Do people who lack integrity really desire more privacy?
+Moreover, we also analyze the relation between need for privacy and sociability, anxiety, risk aversion, and traditionality.
+Using an online questionnaire with _N_ = `r n_d` mostly student respondents, we found that it is possible to predict a considerable part of peoples' need for privacy on the basis of their personalities.
+For example, we indeed found that repondents who reported less integrity than others also desired more anonymity.
+Moreover, more traditional and more anxious respondents desired more privacy from the government, while more risk averse and less sociable respondents desired more privacy from other people.
+
+In his novel _The Circle_, @Eggers.2013 describes a dystopian society in which people are gradually forfeiting their privacy.
+One after another becomes "transparent": Carrying a small camera around the neck, people begin to broadcast their daily lives to the Internet.
+In the novel, this eventually causes a societal upheaval: "The pressure on those who hadn't gone transparent went from polite to oppressive.
+The question, from pundits and constituents, was obvious and loud: If you aren't transparent, what are you hiding?" [@Eggers.2013, p.
+129].
+
+With this study, we want to answer the following question.
+Why do people desire privacy?
+To date there is only little research on why people desire privacy and how the need for privacy can be predicted by aspects of personality.
+Why do some people not care whether government agencies such as the NSA are collecting their data [@Greenwald.2013], and why do others protest vehemently in order to protect their privacy?
+
+We think that finding an answer to this question is important: Given that government agencies are collecting large amounts of data hoping to reduce criminality and terrorism, and given that government agencies are collecting this data preemptively and without concrete suspicions, it seems relevant to find out whether this practice of mass surveillance can be justified based on the nothing-to-hide argument.
+As a result, the main question of this paper is: Do people who desire more privacy really have more to hide and, more generally, what are personality facets that determine peoples' overall need for privacy?
+
+## The Need for Privacy
+
+Privacy captures the extent of voluntary withdrawal from others [@Westin.1967].
+Several models suggest that privacy is a multi-dimensional concept: For example, in a theory-driven treatise @Burgoon.1982 argued that privacy has four dimensions: informational, social, psychological, and physical privacy.
+@Pedersen.1979, by contrast, did an empirical factor analysis (initially starting with 94 items) and suggested that privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity.
+In addition, @Schwartz.1968 differentiated between horizontal and vertical privacy: Whereas horizontal privacy captures withdrawal from peers, vertical privacy refers to withdrawal from superiors or institutions (e.g., government agencies).
+
+Next to being multi-dimensional, privacy is also contingent [@Dienlin.2014]: One can, for example, distinguish between the objective privacy context, the subsequent subjective perception of privacy, the psychological need for privacy (which is both a situational and dispositional need), and the resulting privacy behavior (as represented by self-disclosure).
+For the purpose of this study, we combine the aforementioned theories and focus on (a) vertical privacy with regard to the need for withdrawal from government surveillance, (b) horizontal privacy in terms of the need for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by the general need for anonymity.
+
+### Integrity
+
+Which specific aspects of personality help predict need for privacy?
+The so-called nothing-to-hide argument states that "If you have nothing to hide, you have nothing to fear." At its core, the nothing-to-hide argument implies that an important predictor of why people desire privacy is their _lack of integrity_.
+This becomes especially apparent when we consider the definition of Solove's (2007) nothing-to-hide argument (notably, Solove is a strong critic of the nothing-to-hide argument):
+
+> "The NSA surveillance, data mining, or other government information gathering programs will result in the disclosure of particular pieces of information to a few government officials, or perhaps only to government computers.
+This very limited disclosure of the particular information involved is not likely to be threatening to the privacy of law-abiding citizens.
+Only those who are engaged in illegal activities have a reason to hide this information." [@Solove.2007, p.
+753]
+
+This definition helps illustrate the link between lack of integrity and need for privacy: People who have "engaged in illegal activities" can be considered, by definition, to lack integrity [@Paunonen.2002], which is why they have a reason "to hide this information" (or, in other words, to desire more privacy).
+In terms of a scientific definition of integrity there is no real consensus, however most scholars agree that integrity "incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness" [@Connelly.2006, p.
+82].
+
+Several theoretical arguments exist why lack of integrity might correlate with need for privacy.
+In general, any self-disclosure is a potential risk because others might disagree, disapprove, or misuse the information in other contexts [@Petronio.2010].
+Privacy regulation theory showed that if self-disclosures are too risky, people raise their desired level of privacy, intensify their boundary regulation, and employ more mechanisms to seclude and protect themselves [@Altman.1976].
+In traditional contexts, this could range from moderate behaviors like closing doors, to extreme behaviors such as physically tossing someone out of the room [@Altman.1976].
+In modern contexts, protecting one's privacy can mean to avoid photographs or to deliberately shun public places that have surveillance cameras.
+People who have actually committed something bad, treacherous, or illegal become even more vulnerable and face a significant risk of self-disclosure, because others will surely disapprove of these activities [@Petronio.2010].
+Hence, the foregoing arguments illuminate an indirect link between integrity and need for privacy: By definition, people who participate in negative activities are considered to lack integrity [@Paunonen.2002].
+People who have engaged in negative activities have, by definition, more to hide, and disclosures concerning those activities pose a high risk.
+Because of this increased risk, people will arguably desire more privacy, as a means to mitigate their felt risk [@Altman.1976].
+In this way, the current research extends Altman's privacy regulation theory (1976) by suggesting that lack of integrity is an important yet unexamined factor that could increase peoples' desired level of privacy.
+
+A few studies can be found that imply a relation between privacy and integrity.
+For example, several studies found that surveillance reduces cheating behaviors [@Corcoran.1987, Covey.1989].
+@Covey.1989 asked students to solve an impossible maze.
+In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior.
+In the low surveillance condition, the experimenter stood behind the students, did not monitor their behavior, and visual dividers were used to block the experimenter's view of the students.
+Results showed that students were more likely to cheat in the low surveillance condition, suggesting that in situations of surveillance (i.e., less privacy), people show fewer cheating behaviors (i.e., more integrity).
+Similarly, people are more likely to prevent others from stealing when security cameras are visible [@vanBommel.2014], which is also a sign of higher integrity.
+Next, in a longitudinal sample with 457 respondents in Germany [@Trepte.2013a], people who reported needing more privacy were less satisfied with their lives (_r_ = -.47), had more (_r_ = .41) and less positive affect (_r_ = -.39).
+More importantly however, people who felt they needed more privacy were also less authentic on their SNSs profiles (_r_ = -.48) and less authentic in their personal relationships [_r_ = -.28; @Trepte.2013a].
+For example, people who agreed to items like "I do not talk about personal issues unless my conversation partner brings them up first" were more likely to report that their online profiles did not truly represent their personality.
+Given the argument that authenticity is a subset of integrity [@Sheldon.2004], we reason that the concept of integrity might relate to the desired level of privacy.
+Finally, @Pedersen.1982 showed that three dimensions of need for privacy related to self-esteem: In his study with _N_ = 70 undergraduate students, respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21) and preferred solitude (_r_ = .24).
+Granted, self-esteem and integrity are generally distinct concepts; however, Pedersen's specific operationalization of self-esteem integrated several aspects of integrity (e.g., by using items such as "moral, nice, fair, unselfish, good, honest, reputable, sane" to measure self-esteem).
+Thus, our overarching hypothesis is that people who lack integrity have a greater need for privacy.
+
+In accordance with the reasoning mentioned above, we suggest that people with less integrity feel a greater need for privacy.
+Specifically, we argue that integrity may relate to the need for privacy from (a) government surveillance, as governments have the legitimate power to prosecute illegal activities.
+Next, we hypothesize that integrity relates to the desire privacy for (b) anonymity.
+Anonymity makes it more difficult for both legal and social agents to identify and address potential wrongdoers, which is why people with less integrity will prefer situations in which they are anonymous.
+Finally, lack of integrity likely also relates to an increased need for privacy from (c) other people, as most other people will disapprove of immoral or illegal activities, and might reveal those activities to authorities.
+
+Hypothesis 1: People who feel lower in self-perceived integrity desire more privacy from government surveillance (H1a), more anonymity (H1b), and more privacy from other people (H1c).
+
+### Sociability
+
+Critics of the nothing-to-hide argument hold that people who desire privacy should not automatically be confronted with suspicion, and that privacy has several purposes that are not related to criminal behavior [@Marlinspike.2013].
+@Westin.1967, for example, defined four primary purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
+These are all important social factors for which people desire privacy.
+Hence, the argument is that people who desire privacy can have several legitimate reasons for doing so; reasons which are essential for psychosocial wellbeing and which relate to different factors of personality.
+Below, we thus explore other (neutral) aspects of personality that potentially predict need for privacy.
+In order to be more precise, we follow the advice by @Paunonen.2001 and, instead of using generic personality factors as predictors, refer to specific personality facets.
+
+First, we argue that people who are more reserved, who feel less comfortable in social situations, generally desire more anonymity and more interpersonal privacy.
+Given that privacy is, by definition, a voluntary withdrawal from society [@Westin.1967], we expect that people who are more reserved or more shy desire more privacy from others.
+Several empirical studies support this hypothesis: Extroverted people desire less privacy [@Morton.2013], people who describe themselves as introverted thinkers are more likely to prefer social isolation [@Pedersen.1982], and introverted people are more likely to report invasions of privacy [@Stone.1986].
+Finally, we did not find convincing theoretical and empirical arguments for why sociability should relate to an increased need for privacy from government surveillance, which is why we did not include a hypothesis on this relation.
+
+Hypothesis 2: People who are more sociable desire less anonymity (H2a) and less privacy from other people (H2b).
+
+### Anxiety
+
+Of course, there are also reasons why people might desire less privacy.
+Government agencies often curtail privacy with the aim to prevent crime: For example, the NSA's surveillance programs are often considered a direct response to the 9 / 11 terrorists attacks [@Greenwald.2013].
+It seems plausible that people who are more afraid of terrorist attacks are also more likely to consent to these surveillance programs, given that these programs promise to reduce the likelihood of future attacks.
+One can then argue that people who are afraid of terrorist attacks are also more afraid of threats overall, which is why we suggest that people who are, in general, more anxious desire less privacy from government surveillance and less anonymity.
+We did not include a hypothesis on the potential relation between anxiety and need for interpersonal privacy.
+On the one hand, one could argue that people who are more anxious are more reserved, given that social interactions can pose significant risks [especially with strangers or weak ties; @Granovetter.1973].
+At the same time, one could suggest that especially those people who are more anxious desire less privacy from others (and especially their strong ties), in order to cope better with their daily challenges.
+At the end, given that we measure interpersonal privacy on a general level (and do not distinguish between need for privacy from (a) weak ties and (b) strong ties), it seems plausible that both effects could cancel each other out.
+
+Hypothesis 3: People who are more anxious desire less privacy from government surveillance (H3a) and more anonymity (H3b).
+
+### Risk aversion
+
+Disclosing personal information always poses a certain risk, given that others can misuse self-disclosed personal information in different contexts, which can lead to severe consequences [@Altman.1976].
+Not everyone will feel intimidated by this hypothetical threat---except those who have a general tendency to avoid taking unnecessary risks.
+The most cautious strategy to minimize risks of personal self-disclosures would be, arguably, to keep as much information as possible private.
+Hence, we suggest that people who are, in general, more risk averse have a good reason to desire more privacy in all three aforementioned contexts.
+
+Hypothesis 4: People who are more risk averse desire more privacy from government surveillance (H4a), more anonymity (H4b), and more privacy from other people (H4c).
+
+### Traditionality
+
+The personal computer and the Internet have rendered the world increasingly digitized: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.
+Given the features of digital information [i.e., information is persistent, searchable, reproducible, and scalable; @boyd.2008c], this allows for unprecedented ways and degrees of surveillance.
+Mark Zuckerberg famously observed that privacy is no longer a "social norm," rather that people share personal information [@Johnson.2010].
+Hence, in order to be part of contemporary life (e.g., by using SNSs), it seems necessary to give up some privacy.
+However, arguably not everyone is willing to pay that price, and especially people who are more conservative might prefer to stick to their usual routines and decide against giving up their privacy.
+This is supported by empirical research: Older people, who are generally less open and more traditional [@Donnellan.2008], are more concerned about their privacy than younger people [@Fife.2012].
+Taken together, we suggest that people who are more traditional also desire more privacy in all three aforementioned contexts.
+
+Hypothesis 5: People who are more traditional desire more privacy from government surveillance (H5a), more anonymity (H5b), and more privacy from other people (H5c).
+
+### Sociodemographic variables
+
+(Dear Miriam, I would like to add a short paragraph on how sociodemographics relate to privacy.
+Relevant studies I can think of are @Park.2015, @Tifferet.2019, @Weinberger.2017b, @Trepte.2013a.
+I haven't yet managed to write it, maybe you have time?)
+
 # Methods
+
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
 
-## Participants
+## Open science
 
-## Material
+The following information can be found in the online supplementary material (OSM): the data, the study material, the syntax, unabridged results, additional analyses, and a reproducible version of the manuscript.
+Next to the variables reported here, we also collected additional ones, which can be found in the OSM.
+We invite everyone to for example rerun our analyses or to investigate novel research questions.
+It is also possible to suggest changes and/or corrections to the manuscript.
+The OSM can be found here: https://github.com/tdienlin/need_for_privacy/.
 
-## Procedure
+## Data analyses
 
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+All hypotheses were tested with a two-tailed significance level of 5%.
+Regarding effect sizes, we classified regression coefficients with values exceeding $\upbeta$ = .10 as small effects, $\upbeta$ = .30 as medium effects, and $\upbeta$ = .50 as large effects.
+In that vein, our smallest effect size of interest [SESOI; @Lakens.2018] was $\upbeta$ = .10.
+Effects below the SESOI are considered too small to be theoretically relevant.
+
+We removed participants with peculiar response patterns (e.g., straight-linining, missing of inverted items).
+As criterion, we used the Guttman value, which allows to identify respondents with peculiar response patterns [@Meijer.2016].
+We individually inspected respondents whose reponses were most extreme (5% quantile).
+Indeed, these reponses showed either obvious response patterns, which is why these 5% were excluded from the analyses.
+Next, we excluded one participant who provided an illogical age (i.e., 9 years).
+We also excluded all respondents who anwered less than 50% of all questions.
+The remaining missing responses were imputed using predictive mean matching.
+No respondents needed to be exluded due to "speeding" (i.e., < 5 minutes answer time).
+
+The factorial validity of the measures and the hypotheses were tested with structural equation modeling (SEM).
+Mardia's test showed that the assumption of multivariate normality was violated, _p_(skewness) `r mult_norm[mult_norm$Test == "Mardia Skewness", ]$"p value" %>% my_round("p")`, _p_(kurtosis) `r mult_norm[mult_norm$Test == "Mardia Kurtosis", ]$"p value" %>% my_round("p")`.
+As a result, we used the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator.
+Fit was assessed using the conventional measures and criteria as proposed by @Kline.2016.
+
+First, by running confirmatory factor analyses we tested the factorial validity of the variables we collected.
+In a first step, we ran exploratory factor analyses to assess the underlying factor structure.
+If more than one factor was found, we ran exploratory factor analyses looking for a bifactor model solution.
+Bifactor models implement one factor that explains the variance in all items (the so-called general factor or g-factor).
+Next, at least two more additional factors are implemented that explain the variance in a subset of the items.
+The general factor and the specific factors are orthogonal.
+Bifactor models are nested within hierachical models and are in general more liberal than hierachical models.
+For more information on bifactor models, see @Kline.2016.
+If the bifactor model did not show sufficient factorial validity, we proceeded by deleting items with low loadings on the general factor and/or the specific factors.
+If no bifactor solution could be found, using a subset of the items we then aimed to extract a single factor with sufficient factorial validity.
+
+To test our hypotheses, we regressed the dependent variable need for privacy unto the predictor variables.
+To increase parsimonity, the predictor variables were not modelled as latent factors.
+Instead, using the model predicted values of the CFAs we computed factor score for each respondent.
+If the CFAs showed a single-factor solution, we used the model predicted values for this latent factor; if the CFAs produced a bifactor solution, we used the model predicted values for the general latent factor.
+
+The criterion, need for privacy, was measured as latent construct.
+In general, combining the information of several items into a general latent construct helps reduce and combine information, which allows for more robust and precise inferences.
+At the same time, there are several degrees of freedom regarding how to exactly specify general latent constructs.
+In light of our not having preregistered the analyses, in order to provide the complete picture we hence also report how the independent variables predicted each item measuring need for privacy individually (see Figure \@ref(fig:results-items)).
+
+We used `r cite_r("../bibliography/r-references.bib", withhold = FALSE, pkgs = c("ggplot2", "lavaan", "mice", "MKV", "papaja", "psych", "pwr", "semPlot", "semTools", "tidyverse"))` for all our analyses.
+
+## Procedure and participants
+
+Participants were students from a university in the western U.S.
+who received course credit for taking part in the study.
+The initial sample consisted of _N_ = `r n_d_all` respondents.
+After the removing of the defective data, the final sample consisted of _N_ = `r n_d` respondents.
+The age ranged from `r min(d$age, na.rm = TRUE)` to `r max(d$age, na.rm = TRUE)` years (_M_ = 20 years), with `r mean(d$male, na.rm = TRUE) %>% round(2) * 100`% of the respondents being male.
+The median participation time was `r as.numeric(d$time) %>% min(na.rm = TRUE) %>% divide_by(60)`min.
+
+The study was run in 2015.
+At the time we were not yet aware of the importance to run a-priori power analyses to determine sample size.
+It was our aim to collect a large number of participants (i.e., _N_ = 300).
+The final sample size allowed to find effects with a size of $\upbeta$ = `r sensitivity_95` in 95% of all cases.
+We had a power to detect small effects (i.e., $\upbeta$ = .10) in `r power_small`% of all cases.
+
+## Measures
+
+In what follows we present how we operationalized our constructs.
+First, it was possible to model all variables with at least acceptable fit.
+Note that all items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).
+For an overview of the items' psychometrics, factorial validity, and reliability, see Table \@ref(tab:psychometrics).
+The data, all items (including deleted ones), results of CFAs, item statistics, and distribution plots can be found in the OSM.
+
+```{r psychometrics, results="asis"}
+apa_table(t_psyc, font_size = "footnotesize",
+          caption="Psychometrics of Variables Used.",
+          note = "All items were measured on 7-point scales with Likert response options.
+Alpha = Cronbach's alpha (internal consistency); omega = Raykov's omega (composite reliability); ave = average variance extracted."
+          )
+```
+
+### Need for privacy
+
+As main variable of interest, we collected several items to measure the need for privacy.
+First, we collected 4 items capturing the need for _informational privacy_ using the scale by @Trepte.2017d.
+One example items was "I prefer it when other people do not know much about me."
+
+Second, we measured the need for privacy on a _societal_ level using 9 self-designed items.
+The first subdimension was _government surveillance_, which represents the extent to which people want the government to abstain from collecting information about their personal life.
+One example item is "I feel the need to protect my privacy from government agencies." The second dimension was _anonymity_, which measures the extent to which people feel the need to avoid identification ("I prefer not to carry my ID with me all the time to preserve my privacy").
+
+Third, we measured the need for privacy on a _interpersonal_ level using 9 self-designed items.
+The first subdimension measured the need for privacy from other people in _online contexts_.
+One example items was "I don’t feel the need to be able to communicate about very personal things with others online".
+The second subdimension measured the need for privacy from other people in _offline contexts_.
+One example item was "I don’t feel the need to tell my friends all my secrets".
+
+Exploratory and confirmatory factor analyses finally revealed a well-fitting bifactor model, which consisted of one general factor measuring a general need for privacy and three specific ones measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity.
+For a list of all items, see Table \@ref(tab:need-for-privacy-items).
+For an overview of the items' loadings in the final bifactor model, see Figure \@ref(fig:need-for-privacy-loadings).
+
+```{r need-for-privacy-loadings, fig.cap="Overview of the bifactor model for the need for privacy"}
+plot(p_pri_nee)
+```
+
+\newpage
+
+```{r need-for-privacy-items}
+kable(t_pri_nee, "latex", booktabs = TRUE, linesep = "",
+      caption = "Overview of the Items Measuring the Need for Privacy") %>% 
+  column_spec(3, width = "10cm") %>% 
+  kable_styling(latex_options="scale_down", font_size = 7)
+```
+
+### Integrity
+
+Integrity measures the extent to which people comply with culturally established norms and values.
+In order to measure lack of integrity, we used the subscale _integrity_ of the Supernumerary Personality Inventory [@Paunonen.2002], which consists of 8 items.
+In addition, we self-designed another three items.
+An example item is "I don't think there's anything wrong with cheating a little on one's income tax forms." Analyses revealed that a bifactor model based on a subset of 9 items showed good fit to the data.
+
+### Sociability
+
+Sociability captures whether people prefer to spend their time alone or in company.
+We measured sociability with the extraversion subscale _gregariousness_ [@John.1999], which consists of 8 items.
+An example item is "I shy away from crowds of people." Analyses revealed that a bifactor model based on a subset of 6 items showed good fit to the data.
+
+### Anxiety
+
+Anxiety measures whether people are afraid of negative external influences.
+We measured anxiety with the neuroticism subscale _anxiety_ [@John.1999], which consists of 8 items.
+An example item is "I am easily frightened." Analyses revealed that a bifactor model using all 8 items showed good fit to the data.
+
+### Risk avoidance
+
+Risk avoidance captures whether people abstain from taking risks.
+We measured risk avoidance with the conscientiousness subscale _deliberation_ [@John.1999], which consists of 8 items.
+An example item is "I think twice before I answer a question." Analyses revealed that a bifactor model using all 8 items showed good fit to the data.
+
+### Traditionalism
+
+Traditionalism measures whether people prefer to stick with their usual routines.
+We measured traditionalism with the (inverted) openness to experiences subscale _actions_ [@John.1999], which consists of 8 items.
+An example item is "I'm pretty set in my ways." Analyses revealed that a model with a single factor based on a subset of 5 items showed good fit to the data.
 
@@
 
+In what follows, we present the verbatim result.
+For the exact statistical results, see Table \@ref(tab:results).
+For visualization of the results by means of confidence intervals, see Figure \@ref(fig:results-factor).
+
+```{r results, results="asis"}
+apa_table(dplyr::select(t_results, -Outcome),
+          font_size = "scriptsize",
+          align = c("l", rep("r", 5)), 
+          stub_indents = list("Privacy need general" = c(1:8),
+                              "Privcacy need government" = c(9:16),
+                              "Privacy need interpersonal" = c(17:24),
+                              "Privacy need anonymity" = c(25:32)),
+          caption = "Results of the main factorial model."
+)
+```
+
+```{r results-factor, fig.cap="Overview of results. Shows the 95% confidence intervals of standardized coefficients.", fig.height=3}
+plot(p_main)
+```
+
+To begin with, we found that the final model we estimated to test our hypotheses fit the data moderately well, `r fit_txt(main_fit, scaled = TRUE)`.
+Our first hypothesis stated that people reporting more integrity than others would need less privacy.
+Indeed, the results showed that respondents who reported more integrity than others desired moderately less anonymity.
+The relation with general privacy showed the same relation; however, it was marginally not significant.
+Interestingly, respondents who reported more integrity desired _more_ privacy from other people.
+No significant relation with the need for privacy from the government was found.
+
+Respondents who reported being more sociable than other desired less privacy from other people. The effect was of a considerable size. No other significant relations were found.
+
+Next, we found that respondents who indicated being more anxious than others also desired less privacy from the government.
+The effect size was moderate to considerable.
+No other significnat relations were found.
+
+Respondents who reported being more risk avoidant than others desired moderately more privacy from other people. No further significant effects were found.
+
+Next, respondents who indicated being more traditional than others also desired more privacy from the government.
+The effect was substantial.
+More traditional respondents also desired moderately more privacy from other people.
+No significant relations with the overall level of privacy and the need for anonymity were found.
+
+Finally, regarding sociodemographic variables, we found that respondents who were older also desired more privacy. The effect was small.
+
+In sum, the predictors could explained `r inspect(main_fit, 'r2')["pri_nee_gen"] * 100 %>% round(0)`% of the variance in the general need for privacy, `r inspect(main_fit, 'r2')["pri_nee_gov"] * 100 %>% round(0)`% of the variance in the need for privacy from the government, `r inspect(main_fit, 'r2')["pri_nee_int"] * 100 %>% round(0)`% of the variance in the need for privacy from other people, and `r inspect(main_fit, 'r2')["pri_nee_ano"] * 100 %>% round(0)`% of the variance in the need for anonymity.
+
+As stated above, we also calculated the relation between the predictor variables and the individual privacy need items.
+Several significant relations were found.
+For a visualization, see Figure \@ref(fig:results-items).
+
+```{r results-items, fig.cap="Overview of results. Shows the 95% confidence intervals of standardized coefficients."}
+plot(p_main_items)
+```
+
 # Discussion
+
+This study analyzed how the need for privacy can be predicted by means of personality.
+In a study with `r n_d` students from a large US university, we measured the need for privacy with 22 items.
+Fifteen items formed a well-fitting bifactor model, with one factor measuring the general desire for privacy, and three specific factors measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity.
+The factor solution we found is in line with privacy theory, which subsumes a vertical level (here, privacy from the government) and a horizontal level (here, privacy from other people).
+The third dimension, need for anonymity, can be argued to exist on the diagonal, as one can be anonymous both from the government and from other people.
+
+The results showed that the need for privacy can be predicted considerably well by means of personality.
+Specifically, integrity relates to several dimensions of need for privacy: People who reported being of lower integrity desired more anonymity and slightly less privacy from other people.
+Respondents who said, for example, that they would feel tempted to take things that do not belong to them were also more likely to avoid situations in which they were identifiable.
+
+In conclusion, our results follow @Altman.1976, who reasoned that if exposure of information is risky it is likely that people will use more mechanisms to strengthen their social boundaries and increase their desired level of privacy.
+This study thus aligns with Altman's privacy regulation theory by showing that, in several contexts, people with lower integrity had a higher level of desired privacy.
+
+<!-- In other words, people who agreed that there would be nothing wrong with cheating a little or lying occasionally were also more likely to agree that surveillance on public places is not a good idea.
+-->
+
+In addition, need for privacy was predicted also by other (neutral) personality facets: People who were less sociable, more risk averse, and less anxious also desired more privacy.
+This implies that various personality-related aspects can predict need for privacy.
+
+People who are more shy, more risk averse, or less anxious also desire more privacy.
+For example, people who are more anxious are more likely to accept government surveillance (arguably because they are less afraid of terrorist attacks).
+When looking at the bigger implications of the results, this shows the importance to make differentiated claims on why people desire privacy: Indeed, the results suggest that some people desire privacy because they might have something to hide.
+However, putting everyone who desires privacy under a general suspicion is wrong given that less sociable, risk averse, and less anxious people are also more likely to desire privacy.
+
+As a side note, despite the fact that we mostly used well-established scales, confirmatory factor analyses (CFAs) showed that some of the original items had to be deleted in order to achieve adequate factorial validity.
+This resembles the finding by @Hussey.2018, who reported that several widely used scales in psychological research actually do not show high factorial validity.
+We would like to point out that by using bifactor models it is possible to at least partially alleviate the problem, as the bifactor models are less strict than the routinely used unidimensional or hierarchical models, which are more conservative.
+
+## Limitations and future perspective
+
+Power analyses showed that future research should use samples above _N_ $\approx$ 260 in order to test hypotheses with the recommended power of at least .80 (@Cohen.1992).
+
+In general, the question arises whether it is possible, or even socially desirable, to measure a person's integrity.
+On the one hand, integrity implies absolute criteria: Stealing is bad and forbidden, whereas helping is good and encouraged.
+On the other hand, integrity implies relative criteria: Whereas some cultures disapprove of lying whatever the context, others consider lying okay---for example "white lies" in order to save face or to avoid hurting someone's feelings [@Altman.1977].
+Thus, ranking behaviors, opinions, and character traits with regard to integrity is a moral dilemma.
+As a result, throughout the entire study we have understood integrity as a transgression of social norms that is strong and that most societies would agree upon (for example, most societies would consider stealing as a sign of low integrity).
+
+Next, the question arises whether it is possible to measure integrity based on self-reports.
+Interestingly, integrity tests using self-reports have been shown to work successfully, given that they can predict unwanted professional workplace behavior sufficiently [e.g., theft, drug and alcohol problems, or absenteeism; @Ones.1993].
+In a meta-analysis with 665 correlation coefficients, integrity tests related to counterproductive behaviors with a coefficient of _r_ = .47 [@Ones.1993].
+Nonetheless, future research would benefit from including behavioral manifestations of integrity, such as concrete cheating behaviors.
+If concrete cheating behaviors also increase desires for privacy, this would strengthen the underlying premise of the nothing-to-hide argument.
+
+In that vein, we decided against including social desirability as a control variable, because even though social desirability can affect answers to sensitive questions [@deJong.2012], it is arguably more likely to reflect a true personality trait than false answering behavior [@deVries.2014].
+
+By focusing on _specific facets_ of personality (e.g., fearfulness), we followed the recommendation by @Paunonen.2001 to not analyze _general factors_ of personality (e.g., neuroticism).
+For future research, we suggest going one step further by analyzing predictors that are even more specified.
+For example, it seems possible that people who hold dissenting political beliefs could also have a higher need for privacy from the government.
+Similarly, it would be interesting to focus on different minority groups.
+For example, it seems plausible that people from a LGBT background might desire more privacy from government (because it is potentially repressive or unfriendly toward LGBTs).
+Finally, in this study we focused mostly on escapist motives for why people desire privacy (e.g., sociability, risk aversion).
+Interestingly, @Leary.2003 were able to show that when predicting engagement in solitary activities, it is less preferable to measure how strongly people want to escape society (avoidance oriented), but rather how much they seek solitude (approach oriented).
+Hence, future studies might want to include predictors that are more approach oriented (e.g., peoples' need for contemplation).
+
+From a methodological perspective, future research should continue to improve the instruments we used, given that factorial validity of some scales was only moderate.
+Similarly, we recommend elaborating on the general understanding of integrity as a theoretical concept.
+To date, there is not one overarching concept of integrity that incorporates all the different aspects of integrity, yet it would be valuable to examine how other aspects of integrity (e.g., authenticity, trustworthiness, or consistency) relate to privacy desires.
+
+Optimizing the variables' factorial validity might introduce problems of overfitting.
+In other words, although we might now have a sharper knife, we also use it less situations.
+First, we think that by using bifactor models we were able to retain a large number of items, rendering our results more robust.
+In addition, also when looking at the items individually one can see that the results are not dependent on inclusion of specific items.
+
+## Conclusion
 

### 2018-12-09 manuscript/manuscript.tex
- major updates on everything:     - mostly finished the analyses     - rewritten the methods, results, and abstract

--- 2018-11-13 manuscript/manuscript.RmD
@@
----
-title             : "Who Needs Privacy?"
-shorttitle        : "Who Needs Privacy?"
+\documentclass[man,floatsintext]{apa6}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Who Needs Privacy?},
+            pdfauthor={Tobias Dienlin~\& Miriam Metzger},
+            pdfkeywords={Privacy, personality, anonymity, integrity, SEM},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-author: 
-  - name          : "Tobias Dienlin"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "University of Hohenheim, Department of Media Psychology (540F)"
-    email         : "tobias.dienlin@uni-hohenheim.de"
-  - name          : "Miriam Metzger"
-    affiliation   : "1,2"
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-affiliation:
-  - id            : "1"
-    institution   : "University of Hohenheim"
-  - id            : "2"
-    institution   : "University of California, Santa Barbara"
+  \title{Who Needs Privacy?}
+    \author{Tobias Dienlin\textsuperscript{1}~\& Miriam Metzger\textsuperscript{1,2}}
+    \date{}
 
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+\shorttitle{Who Needs Privacy?}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} University of Hohenheim\\\textsuperscript{2} University of California, Santa Barbara}
+\keywords{Privacy, personality, anonymity, integrity, SEM}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+\usepackage{lineno}
+
+\linenumbers
+\setlength{\parskip}{0em}
+\raggedbottom
+
+\authornote{Add complete departmental
+affiliations for each author here. Each new line herein must be
+indented, like this line.
 
@@
 
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+Correspondence concerning this article should be addressed to Tobias
+Dienlin, University of Hohenheim, Department of Media Psychology (540F).
+E-mail:
+\href{mailto:tobias.dienlin@uni-hohenheim.de}{\nolinkurl{tobias.dienlin@uni-hohenheim.de}}}
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+\abstract{
+In this study we analyzes how personality relates to
+peoples' need for privacy. For example, we analyze if the so-called
+\enquote{nothing-to-hide} argument is correct: Do people who lack
+integrity really desire more privacy? Moreover, we also analyze the
+relation between need for privacy and sociability, anxiety, risk
+aversion, and traditionality. Using an online questionnaire with
+\emph{N} = 261 mostly student respondents, we found that it is possible
+to predict a considerable part of peoples' need for privacy on the basis
+of their personalities. For example, we indeed found that repondents who
+reported less integrity than others also desired more anonymity.
+Moreover, more traditional and more anxious respondents desired more
+privacy from the government, while more risk averse and less sociable
+respondents desired more privacy from other people. 
+}
 
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
+\theoremstyle{definition}
+\newtheorem{example}{Example}[section]
+\theoremstyle{definition}
+\newtheorem{exercise}{Exercise}[section]
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\newtheorem*{solution}{Solution}
+\begin{document}
+\maketitle
 
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+In his novel \emph{The Circle}, Eggers (2013) describes a dystopian
+society in which people are gradually forfeiting their privacy. One
+after another becomes \enquote{transparent}: Carrying a small camera
+around the neck, people begin to broadcast their daily lives to the
+Internet. In the novel, this eventually causes a societal upheaval:
+\enquote{The pressure on those who hadn't gone transparent went from
+polite to oppressive. The question, from pundits and constituents, was
+obvious and loud: If you aren't transparent, what are you hiding?}
+(Eggers, 2013, p. 129).
 
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+With this study, we want to answer the following question. Why do people
+desire privacy? To date there is only little research on why people
+desire privacy and how the need for privacy can be predicted by aspects
+of personality. Why do some people not care whether government agencies
+such as the NSA are collecting their data (Greenwald, n.d.), and why do
+others protest vehemently in order to protect their privacy?
 
-  One or two sentences to put the results into a more **general context**.
+We think that finding an answer to this question is important: Given
+that government agencies are collecting large amounts of data hoping to
+reduce criminality and terrorism, and given that government agencies are
+collecting this data preemptively and without concrete suspicions, it
+seems relevant to find out whether this practice of mass surveillance
+can be justified based on the nothing-to-hide argument. As a result, the
+main question of this paper is: Do people who desire more privacy really
+have more to hide and, more generally, what are personality facets that
+determine peoples' overall need for privacy?
 
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+\hypertarget{the-need-for-privacy}{%
+\subsection{The Need for Privacy}\label{the-need-for-privacy}}
 
-  <!-- https://tinyurl.com/ybremelq -->
+Privacy captures the extent of voluntary withdrawal from others (Westin,
+1967). Several models suggest that privacy is a multi-dimensional
+concept: For example, in a theory-driven treatise Burgoon (1982) argued
+that privacy has four dimensions: informational, social, psychological,
+and physical privacy. Pedersen (1979), by contrast, did an empirical
+factor analysis (initially starting with 94 items) and suggested that
+privacy exists on six dimensions: reserve, isolation, solitude, intimacy
+with friends, intimacy with family, and anonymity. In addition, Schwartz
+(1968) differentiated between horizontal and vertical privacy: Whereas
+horizontal privacy captures withdrawal from peers, vertical privacy
+refers to withdrawal from superiors or institutions (e.g., government
+agencies).
 
-keywords          : "keywords"
-wordcount         : "X"
+Next to being multi-dimensional, privacy is also contingent (Dienlin,
+2014): One can, for example, distinguish between the objective privacy
+context, the subsequent subjective perception of privacy, the
+psychological need for privacy (which is both a situational and
+dispositional need), and the resulting privacy behavior (as represented
+by self-disclosure). For the purpose of this study, we combine the
+aforementioned theories and focus on (a) vertical privacy with regard to
+the need for withdrawal from government surveillance, (b) horizontal
+privacy in terms of the need for withdrawal from peers, friends, or
+acquaintances, and (c) both horizontal and vertical privacy as captured
+by the general need for anonymity.
 
-bibliography      : ["r-references.bib"]
+\hypertarget{integrity}{%
+\subsubsection{Integrity}\label{integrity}}
 
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
+Which specific aspects of personality help predict need for privacy? The
+so-called nothing-to-hide argument states that \enquote{If you have
+nothing to hide, you have nothing to fear.} At its core, the
+nothing-to-hide argument implies that an important predictor of why
+people desire privacy is their \emph{lack of integrity}. This becomes
+especially apparent when we consider the definition of Solove's (2007)
+nothing-to-hide argument (notably, Solove is a strong critic of the
+nothing-to-hide argument):
 
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
----
+\begin{quote}
+\enquote{The NSA surveillance, data mining, or other government
+information gathering programs will result in the disclosure of
+particular pieces of information to a few government officials, or
+perhaps only to government computers. This very limited disclosure of
+the particular information involved is not likely to be threatening to
+the privacy of law-abiding citizens. Only those who are engaged in
+illegal activities have a reason to hide this information.} (Solove,
+2007, p. 753)
+\end{quote}
 
-```{r setup, include = FALSE}
-library("papaja")
-```
+This definition helps illustrate the link between lack of integrity and
+need for privacy: People who have \enquote{engaged in illegal
+activities} can be considered, by definition, to lack integrity
+(Paunonen, 2002), which is why they have a reason \enquote{to hide this
+information} (or, in other words, to desire more privacy). In terms of a
+scientific definition of integrity there is no real consensus, however
+most scholars agree that integrity \enquote{incorporates a tendency to
+comply with social norms, avoid deviant behavior, and embrace a sense of
+justice, truthfulness, and fairness} (Connelly, Lilienfeld, \& Schmeelk,
+2006, p. 82).
 
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
+Several theoretical arguments exist why lack of integrity might
+correlate with need for privacy. In general, any self-disclosure is a
+potential risk because others might disagree, disapprove, or misuse the
+information in other contexts (Petronio, 2010). Privacy regulation
+theory showed that if self-disclosures are too risky, people raise their
+desired level of privacy, intensify their boundary regulation, and
+employ more mechanisms to seclude and protect themselves (Altman, 1976).
+In traditional contexts, this could range from moderate behaviors like
+closing doors, to extreme behaviors such as physically tossing someone
+out of the room (Altman, 1976). In modern contexts, protecting one's
+privacy can mean to avoid photographs or to deliberately shun public
+places that have surveillance cameras. People who have actually
+committed something bad, treacherous, or illegal become even more
+vulnerable and face a significant risk of self-disclosure, because
+others will surely disapprove of these activities (Petronio, 2010).
+Hence, the foregoing arguments illuminate an indirect link between
+integrity and need for privacy: By definition, people who participate in
+negative activities are considered to lack integrity (Paunonen, 2002).
+People who have engaged in negative activities have, by definition, more
+to hide, and disclosures concerning those activities pose a high risk.
+Because of this increased risk, people will arguably desire more
+privacy, as a means to mitigate their felt risk (Altman, 1976). In this
+way, the current research extends Altman's privacy regulation theory
+(1976) by suggesting that lack of integrity is an important yet
+unexamined factor that could increase peoples' desired level of privacy.
 
-# Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+A few studies can be found that imply a relation between privacy and
+integrity. For example, several studies found that surveillance reduces
+cheating behaviors (Corcoran \& Rotter, 1987, Covey.1989). Covey,
+Saladin, and Killen (1989) asked students to solve an impossible maze.
+In the high surveillance condition, the experimenter stood in front of
+the students and closely monitored their behavior. In the low
+surveillance condition, the experimenter stood behind the students, did
+not monitor their behavior, and visual dividers were used to block the
+experimenter's view of the students. Results showed that students were
+more likely to cheat in the low surveillance condition, suggesting that
+in situations of surveillance (i.e., less privacy), people show fewer
+cheating behaviors (i.e., more integrity). Similarly, people are more
+likely to prevent others from stealing when security cameras are visible
+(van Bommel, van Prooijen, Elffers, \& van Lange, 2014), which is also a
+sign of higher integrity. Next, in a longitudinal sample with 457
+respondents in Germany (Trepte, Dienlin, \& Reinecke, 2013), people who
+reported needing more privacy were less satisfied with their lives
+(\emph{r} = -.47), had more (\emph{r} = .41) and less positive affect
+(\emph{r} = -.39). More importantly however, people who felt they needed
+more privacy were also less authentic on their SNSs profiles (\emph{r} =
+-.48) and less authentic in their personal relationships (\emph{r} =
+-.28; Trepte et al., 2013). For example, people who agreed to items like
+\enquote{I do not talk about personal issues unless my conversation
+partner brings them up first} were more likely to report that their
+online profiles did not truly represent their personality. Given the
+argument that authenticity is a subset of integrity (Sheldon, 2004), we
+reason that the concept of integrity might relate to the desired level
+of privacy. Finally, Pedersen (1982) showed that three dimensions of
+need for privacy related to self-esteem: In his study with \emph{N} = 70
+undergraduate students, respondents who held a lower self-esteem were
+more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21)
+and preferred solitude (\emph{r} = .24). Granted, self-esteem and
+integrity are generally distinct concepts; however, Pedersen's specific
+operationalization of self-esteem integrated several aspects of
+integrity (e.g., by using items such as \enquote{moral, nice, fair,
+unselfish, good, honest, reputable, sane} to measure self-esteem). Thus,
+our overarching hypothesis is that people who lack integrity have a
+greater need for privacy.
 
-## Participants
+In accordance with the reasoning mentioned above, we suggest that people
+with less integrity feel a greater need for privacy. Specifically, we
+argue that integrity may relate to the need for privacy from (a)
+government surveillance, as governments have the legitimate power to
+prosecute illegal activities. Next, we hypothesize that integrity
+relates to the desire privacy for (b) anonymity. Anonymity makes it more
+difficult for both legal and social agents to identify and address
+potential wrongdoers, which is why people with less integrity will
+prefer situations in which they are anonymous. Finally, lack of
+integrity likely also relates to an increased need for privacy from (c)
+other people, as most other people will disapprove of immoral or illegal
+activities, and might reveal those activities to authorities.
 
-## Material
+Hypothesis 1: People who feel lower in self-perceived integrity desire
+more privacy from government surveillance (H1a), more anonymity (H1b),
+and more privacy from other people (H1c).
 
-## Procedure
+\hypertarget{sociability}{%
+\subsubsection{Sociability}\label{sociability}}
 
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+Critics of the nothing-to-hide argument hold that people who desire
+privacy should not automatically be confronted with suspicion, and that
+privacy has several purposes that are not related to criminal behavior
+(Marlinspike, n.d.). Westin (1967), for example, defined four primary
+purposes of privacy: (1) self-development (i.e., the integration of
+experiences into meaningful patterns), (2) autonomy (i.e., the desire to
+avoid being manipulated and dominated), (3) emotional release (i.e., the
+release of tension from social role demands), and (4) protected
+communication (i.e., the ability to foster intimate relationships).
+These are all important social factors for which people desire privacy.
+Hence, the argument is that people who desire privacy can have several
+legitimate reasons for doing so; reasons which are essential for
+psychosocial wellbeing and which relate to different factors of
+personality. Below, we thus explore other (neutral) aspects of
+personality that potentially predict need for privacy. In order to be
+more precise, we follow the advice by Paunonen and Ashton (2001) and,
+instead of using generic personality factors as predictors, refer to
+specific personality facets.
 
-# Results
+First, we argue that people who are more reserved, who feel less
+comfortable in social situations, generally desire more anonymity and
+more interpersonal privacy. Given that privacy is, by definition, a
+voluntary withdrawal from society (Westin, 1967), we expect that people
+who are more reserved or more shy desire more privacy from others.
+Several empirical studies support this hypothesis: Extroverted people
+desire less privacy (Morton, 2013), people who describe themselves as
+introverted thinkers are more likely to prefer social isolation
+(Pedersen, 1982), and introverted people are more likely to report
+invasions of privacy (Stone, 1986). Finally, we did not find convincing
+theoretical and empirical arguments for why sociability should relate to
+an increased need for privacy from government surveillance, which is why
+we did not include a hypothesis on this relation.
 
-# Discussion
+Hypothesis 2: People who are more sociable desire less anonymity (H2a)
+and less privacy from other people (H2b).
+
+\hypertarget{anxiety}{%
+\subsubsection{Anxiety}\label{anxiety}}
+
+Of course, there are also reasons why people might desire less privacy.
+Government agencies often curtail privacy with the aim to prevent crime:
+For example, the NSA's surveillance programs are often considered a
+direct response to the 9 / 11 terrorists attacks (Greenwald, n.d.). It
+seems plausible that people who are more afraid of terrorist attacks are
+also more likely to consent to these surveillance programs, given that
+these programs promise to reduce the likelihood of future attacks. One
+can then argue that people who are afraid of terrorist attacks are also
+more afraid of threats overall, which is why we suggest that people who
+are, in general, more anxious desire less privacy from government
+surveillance and less anonymity. We did not include a hypothesis on the
+potential relation between anxiety and need for interpersonal privacy.
+On the one hand, one could argue that people who are more anxious are
+more reserved, given that social interactions can pose significant risks
+(especially with strangers or weak ties; Granovetter, 1973). At the same
+time, one could suggest that especially those people who are more
+anxious desire less privacy from others (and especially their strong
+ties), in order to cope better with their daily challenges. At the end,
+given that we measure interpersonal privacy on a general level (and do
+not distinguish between need for privacy from (a) weak ties and (b)
+strong ties), it seems plausible that both effects could cancel each
+other out.
+
+Hypothesis 3: People who are more anxious desire less privacy from
+government surveillance (H3a) and more anonymity (H3b).
+
+\hypertarget{risk-aversion}{%
+\subsubsection{Risk aversion}\label{risk-aversion}}
+
+Disclosing personal information always poses a certain risk, given that
+others can misuse self-disclosed personal information in different
+contexts, which can lead to severe consequences (Altman, 1976). Not
+everyone will feel intimidated by this hypothetical threat---except
+those who have a general tendency to avoid taking unnecessary risks. The
+most cautious strategy to minimize risks of personal self-disclosures
+would be, arguably, to keep as much information as possible private.
+Hence, we suggest that people who are, in general, more risk averse have
+a good reason to desire more privacy in all three aforementioned
+contexts.
+
+Hypothesis 4: People who are more risk averse desire more privacy from
+government surveillance (H4a), more anonymity (H4b), and more privacy
+from other people (H4c).
+
+\hypertarget{traditionality}{%
+\subsubsection{Traditionality}\label{traditionality}}
+
+The personal computer and the Internet have rendered the world
+increasingly digitized: Social interactions, purchases, and medical
+treatments nowadays all produce digital traces, which can be combined
+into accurate latent user profiles. Given the features of digital
+information (i.e., information is persistent, searchable, reproducible,
+and scalable; boyd, 2008), this allows for unprecedented ways and
+degrees of surveillance. Mark Zuckerberg famously observed that privacy
+is no longer a \enquote{social norm,} rather that people share personal
+information (Johnson, n.d.). Hence, in order to be part of contemporary
+life (e.g., by using SNSs), it seems necessary to give up some privacy.
+However, arguably not everyone is willing to pay that price, and
+especially people who are more conservative might prefer to stick to
+their usual routines and decide against giving up their privacy. This is
+supported by empirical research: Older people, who are generally less
+open and more traditional (Donnellan \& Lucas, 2008), are more concerned
+about their privacy than younger people (Fife \& Orjuel, 2012). Taken
+together, we suggest that people who are more traditional also desire
+more privacy in all three aforementioned contexts.
+
+Hypothesis 5: People who are more traditional desire more privacy from
+government surveillance (H5a), more anonymity (H5b), and more privacy
+from other people (H5c).
+
+\hypertarget{sociodemographic-variables}{%
+\subsubsection{Sociodemographic
+variables}\label{sociodemographic-variables}}
+
+(Dear Miriam, I would like to add a short paragraph on how
+sociodemographics relate to privacy. Relevant studies I can think of are
+Park (2015), Tifferet (2019), Weinberger, Zhitomirsky-Geffet, and
+Bouhnik (2017), Trepte et al. (2013). I haven't yet managed to write it,
+maybe you have time?)
+
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
+
+We report how we determined our sample size, all data exclusions (if
+any), all manipulations, and all measures in the study.
+
+\hypertarget{open-science}{%
+\subsection{Open science}\label{open-science}}
+
+The following information can be found in the online supplementary
+material (OSM): the data, the study material, the syntax, unabridged
+results, additional analyses, and a reproducible version of the
+manuscript. Next to the variables reported here, we also collected
+additional ones, which can be found in the OSM. We invite everyone to
+for example rerun our analyses or to investigate novel research
+questions. It is also possible to suggest changes and/or corrections to
+the manuscript. The OSM can be found here:
+\url{https://github.com/tdienlin/need_for_privacy/}.
+
+\hypertarget{data-analyses}{%
+\subsection{Data analyses}\label{data-analyses}}
+
+All hypotheses were tested with a two-tailed significance level of 5\%.
+Regarding effect sizes, we classified regression coefficients with
+values exceeding \(\upbeta\) = .10 as small effects, \(\upbeta\) = .30
+as medium effects, and \(\upbeta\) = .50 as large effects. In that vein,
+our smallest effect size of interest (SESOI; Lakens, Scheel, \& Isager,
+2018) was \(\upbeta\) = .10. Effects below the SESOI are considered too
+small to be theoretically relevant.
+
+We removed participants with peculiar response patterns (e.g.,
+straight-linining, missing of inverted items). As criterion, we used the
+Guttman value, which allows to identify respondents with peculiar
+response patterns (Meijer, Niessen, \& Tendeiro, 2016). We individually
+inspected respondents whose reponses were most extreme (5\% quantile).
+Indeed, these reponses showed either obvious response patterns, which is
+why these 5\% were excluded from the analyses. Next, we excluded one
+participant who provided an illogical age (i.e., 9 years). We also
+excluded all respondents who anwered less than 50\% of all questions.
+The remaining missing responses were imputed using predictive mean
+matching. No respondents needed to be exluded due to \enquote{speeding}
+(i.e., \textless{} 5 minutes answer time).
+
+The factorial validity of the measures and the hypotheses were tested
+with structural equation modeling (SEM). Mardia's test showed that the
+assumption of multivariate normality was violated, \emph{p}(skewness)
+\textless{} .001, \emph{p}(kurtosis) \textless{} .001. As a result, we
+used the more robust Satorra-Bentler scaled and mean-adjusted test
+statistic (MLM) as estimator. Fit was assessed using the conventional
+measures and criteria as proposed by Kline (2016).
+
+First, by running confirmatory factor analyses we tested the factorial
+validity of the variables we collected. In a first step, we ran
+exploratory factor analyses to assess the underlying factor structure.
+If more than one factor was found, we ran exploratory factor analyses
+looking for a bifactor model solution. Bifactor models implement one
+factor that explains the variance in all items (the so-called general
+factor or g-factor). Next, at least two more additional factors are
+implemented that explain the variance in a subset of the items. The
+general factor and the specific factors are orthogonal. Bifactor models
+are nested within hierachical models and are in general more liberal
+than hierachical models. For more information on bifactor models, see
+Kline (2016). If the bifactor model did not show sufficient factorial
+validity, we proceeded by deleting items with low loadings on the
+general factor and/or the specific factors. If no bifactor solution
+could be found, using a subset of the items we then aimed to extract a
+single factor with sufficient factorial validity.
+
+To test our hypotheses, we regressed the dependent variable need for
+privacy unto the predictor variables. To increase parsimonity, the
+predictor variables were not modelled as latent factors. Instead, using
+the model predicted values of the CFAs we computed factor score for each
+respondent. If the CFAs showed a single-factor solution, we used the
+model predicted values for this latent factor; if the CFAs produced a
+bifactor solution, we used the model predicted values for the general
+latent factor.
+
+The criterion, need for privacy, was measured as latent construct. In
+general, combining the information of several items into a general
+latent construct helps reduce and combine information, which allows for
+more robust and precise inferences. At the same time, there are several
+degrees of freedom regarding how to exactly specify general latent
+constructs. In light of our not having preregistered the analyses, in
+order to provide the complete picture we hence also report how the
+independent variables predicted each item measuring need for privacy
+individually (see Figure \ref{fig:results-items}).
+
+We used R (Version 3.5.1; R Core Team, 2018) and the R-packages
+\emph{ggplot2} (Version 3.1.0; Wickham, 2016), \emph{lavaan} (Version
+0.6.3; Rosseel, 2012), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth,
+2018), \emph{semPlot} (Version 1.1; Epskamp \& Simon Stuber, 2017), and
+\emph{tidyverse} (Version 1.2.1; Wickham, 2017) for all our analyses.
+
+\hypertarget{procedure-and-participants}{%
+\subsection{Procedure and
+participants}\label{procedure-and-participants}}
+
+Participants were students from a university in the western U.S. who
+received course credit for taking part in the study. The initial sample
+consisted of \emph{N} = 296 respondents. After the removing of the
+defective data, the final sample consisted of \emph{N} = 261
+respondents. The age ranged from 18 to 56 years (\emph{M} = 20 years),
+with 27\% of the respondents being male. The median participation time
+was 5.22min.
+
+The study was run in 2015. At the time we were not yet aware of the
+importance to run a-priori power analyses to determine sample size. It
+was our aim to collect a large number of participants (i.e., \emph{N} =
+300). The final sample size allowed to find effects with a size of
+\(\upbeta\) = 0.22 in 95\% of all cases. We had a power to detect small
+effects (i.e., \(\upbeta\) = .10) in 36\% of all cases.
+
+\hypertarget{measures}{%
+\subsection{Measures}\label{measures}}
+
+In what follows we present how we operationalized our constructs. First,
+it was possible to model all variables with at least acceptable fit.
+Note that all items were answered on a 7-point Likert scale ranging from
+1 (\emph{strongly disagree}) to 7 (\emph{strongly agree}). For an
+overview of the items' psychometrics, factorial validity, and
+reliability, see Table \ref{tab:psychometrics}. The data, all items
+(including deleted ones), results of CFAs, item statistics, and
+distribution plots can be found in the OSM.
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:psychometrics}Psychometrics of Variables Used.}
+\footnotesize{
+\begin{tabular}{lllllllllllll}
+\toprule
+ & \multicolumn{1}{c}{m} & \multicolumn{1}{c}{sd} & \multicolumn{1}{c}{chisq} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{pvalue} & \multicolumn{1}{c}{cfi} & \multicolumn{1}{c}{tli} & \multicolumn{1}{c}{rmsea} & \multicolumn{1}{c}{srmr} & \multicolumn{1}{c}{omega} & \multicolumn{1}{c}{alpha} & \multicolumn{1}{c}{ave}\\
+\midrule
+Privacy need & 4.17 & 1.61 & 107.36 & 62.00 & < .001 & .95 & .93 & .05 & .05 & .84 & .89 & .47\\
+Integrity & 4.56 & 1.81 & 50.81 & 23.00 & < .001 & .95 & .92 & .07 & .05 & .79 & .82 & .40\\
+Sociability & 4.67 & 1.48 & 12.77 & 3.00 & .005 & .97 & .85 & .11 & .04 & .78 & .83 & .51\\
+Anxiety & 4.40 & 1.50 & 29.60 & 16.00 & .020 & .97 & .94 & .06 & .04 & .80 & .83 & .44\\
+Risk aversion & 4.34 & 1.51 & 33.13 & 16.00 & .007 & .95 & .91 & .06 & .05 & .74 & .80 & .42\\
+Traditionality & 3.89 & 1.57 & 13.73 & 5.00 & .017 & .95 & .91 & .08 & .04 & .73 & .73 & .35\\
+\bottomrule
+\addlinespace
+\end{tabular}
+}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} All items were measured on 7-point scales with Likert response options.
+Alpha = Cronbach's alpha (internal consistency); omega = Raykov's omega (composite reliability); ave = average variance extracted.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\hypertarget{need-for-privacy}{%
+\subsubsection{Need for privacy}\label{need-for-privacy}}
+
+As main variable of interest, we collected several items to measure the
+need for privacy. First, we collected 4 items capturing the need for
+\emph{informational privacy} using the scale by Trepte and Masur (2017).
+One example items was \enquote{I prefer it when other people do not know
+much about me.}
+
+Second, we measured the need for privacy on a \emph{societal} level
+using 9 self-designed items. The first subdimension was \emph{government
+surveillance}, which represents the extent to which people want the
+government to abstain from collecting information about their personal
+life. One example item is \enquote{I feel the need to protect my privacy
+from government agencies.} The second dimension was \emph{anonymity},
+which measures the extent to which people feel the need to avoid
+identification (\enquote{I prefer not to carry my ID with me all the
+time to preserve my privacy}).
+
+Third, we measured the need for privacy on a \emph{interpersonal} level
+using 9 self-designed items. The first subdimension measured the need
+for privacy from other people in \emph{online contexts}. One example
+items was \enquote{I don't feel the need to be able to communicate about
+very personal things with others online}. The second subdimension
+measured the need for privacy from other people in \emph{offline
+contexts}. One example item was \enquote{I don't feel the need to tell
+my friends all my secrets}.
+
+Exploratory and confirmatory factor analyses finally revealed a
+well-fitting bifactor model, which consisted of one general factor
+measuring a general need for privacy and three specific ones measuring
+the need for privacy from the government, the need for privacy from
+other people, and the need for anonymity. For a list of all items, see
+Table \ref{tab:need-for-privacy-items}. For an overview of the items'
+loadings in the final bifactor model, see Figure
+\ref{fig:need-for-privacy-loadings}.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/need-for-privacy-loadings-1.pdf}
+\caption{\label{fig:need-for-privacy-loadings}Overview of the bifactor model
+for the need for privacy}
+\end{figure}
 
@@
 
-# References
-```{r create_r-references}
-r_refs(file = "r-references.bib")
-```
+\begin{table}
+
+\caption{\label{tab:need-for-privacy-items}Overview of the Items Measuring the Need for Privacy}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{7}{9}\selectfont
+\begin{tabular}[t]{ll>{\raggedright\arraybackslash}p{10cm}}
+\toprule
+Name & No. & Content\\
+\midrule
+N4P.SOC\_1 & 1 & I need government agencies to respect my privacy, even if that hinders a greater societal cause.\\
+N4P.SOC\_2 & 2 & I need the information that companies (e.g., Amazon, Facebook, or Google) have about me to stay private so that the government can never access it.\\
+N4P.SOC\_3 & 3 & I don’t want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.\\
+N4P.SOC\_4 & 4 & I don’t want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.\\
+N4P.SOC\_5 & -- & I need to be able to surf online anonymously.\\
+N4P.SOC\_6 & 6 & I need to be able to use a fake name on social network sites to preserve my privacy.\\
+N4P.SOC\_7 & 7 & I feel the need to avoid places with video surveillance.\\
+N4P.SOC\_8 & 8 & I prefer not to carry my ID with me all the time to preserve my privacy.\\
+N4P.SOC\_9 & 5 & I feel the need to protect my privacy from government agencies.\\
+N4P.INT\_1 & -- & I feel the need to disclose personal information about me on social network sites.\\
+N4P.INT\_2 & 9 & My need for privacy is so strong that it prevents me from using Facebook actively.\\
+N4P.INT\_3 & -- & I don’t feel the need to be able to communicate about very personal things with others online.\\
+N4P.INT\_4 & 12 & I need to know that my boss or future employers cannot find information about me online that they might disapprove of.\\
+N4P.INT\_5 & -- & I always need a person to talk about personal things.\\
+N4P.INT\_6 & -- & I don’t need to know a lot of things about people I interact with, as that might cause problems.\\
+N4P.INT\_7 & 13 & I don’t feel the need to tell my friends all my secrets.\\
+N4P.INT\_8 & -- & I sometimes feel the need to share my personal point of view with someone I don’t know that well.\\
+N4P.INT\_9 & 14 & I feel the need to protect my privacy from other people.\\
+N4P.BOT\_1 & 10 & I prefer it when other people do not know much about me.\\
+N4P.BOT\_2 & -- & When given the chance, I prefer being incognito.\\
+N4P.BOT\_3 & 11 & I don’t want personal information about me being publicly available.\\
+N4P.BOT\_4 & -- & Not everybody needs to know everything about me.\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+\hypertarget{integrity-1}{%
+\subsubsection{Integrity}\label{integrity-1}}
+
+Integrity measures the extent to which people comply with culturally
+established norms and values. In order to measure lack of integrity, we
+used the subscale \emph{integrity} of the Supernumerary Personality
+Inventory (Paunonen, 2002), which consists of 8 items. In addition, we
+self-designed another three items. An example item is \enquote{I don't
+think there's anything wrong with cheating a little on one's income tax
+forms.} Analyses revealed that a bifactor model based on a subset of 9
+items showed good fit to the data.
+
+\hypertarget{sociability-1}{%
+\subsubsection{Sociability}\label{sociability-1}}
+
+Sociability captures whether people prefer to spend their time alone or
+in company. We measured sociability with the extraversion subscale
+\emph{gregariousness} (John \& Srivastava, 1999), which consists of 8
+items. An example item is \enquote{I shy away from crowds of people.}
+Analyses revealed that a bifactor model based on a subset of 6 items
+showed good fit to the data.
+
+\hypertarget{anxiety-1}{%
+\subsubsection{Anxiety}\label{anxiety-1}}
+
+Anxiety measures whether people are afraid of negative external
+influences. We measured anxiety with the neuroticism subscale
+\emph{anxiety} (John \& Srivastava, 1999), which consists of 8 items. An
+example item is \enquote{I am easily frightened.} Analyses revealed that
+a bifactor model using all 8 items showed good fit to the data.
+
+\hypertarget{risk-avoidance}{%
+\subsubsection{Risk avoidance}\label{risk-avoidance}}
+
+Risk avoidance captures whether people abstain from taking risks. We
+measured risk avoidance with the conscientiousness subscale
+\emph{deliberation} (John \& Srivastava, 1999), which consists of 8
+items. An example item is \enquote{I think twice before I answer a
+question.} Analyses revealed that a bifactor model using all 8 items
+showed good fit to the data.
+
+\hypertarget{traditionalism}{%
+\subsubsection{Traditionalism}\label{traditionalism}}
+
+Traditionalism measures whether people prefer to stick with their usual
+routines. We measured traditionalism with the (inverted) openness to
+experiences subscale \emph{actions} (John \& Srivastava, 1999), which
+consists of 8 items. An example item is \enquote{I'm pretty set in my
+ways.} Analyses revealed that a model with a single factor based on a
+subset of 5 items showed good fit to the data.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+In what follows, we present the verbatim result. For the exact
+statistical results, see Table \ref{tab:results}. For visualization of
+the results by means of confidence intervals, see Figure
+\ref{fig:results-factor}.
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:results}Results of the main factorial model.}
+\scriptsize{
+\begin{tabular}{lrrrrr}
+\toprule
+Predictor & \multicolumn{1}{c}{b} & \multicolumn{1}{c}{ll} & \multicolumn{1}{c}{ul} & \multicolumn{1}{c}{beta} & \multicolumn{1}{c}{p}\\
+\midrule
+Privacy need general &  &  &  &  & \\
+\ \ \ Integrity & -0.24 & -0.48 & 0.01 & -.15 & .062\\
+\ \ \ Sociability & -0.16 & -0.44 & 0.13 & -.09 & .289\\
+\ \ \ Anxiety & -0.01 & -0.20 & 0.18 & -.01 & .897\\
+\ \ \ Traditionalism & -0.12 & -0.30 & 0.06 & -.12 & .190\\
+\ \ \ Risk avoidance & 0.77 & -0.19 & 1.73 & .14 & .117\\
+\ \ \ Male & 0.18 & -0.12 & 0.48 & .10 & .233\\
+\ \ \ Age & 0.04 & 0.01 & 0.07 & .14 & .006\\
+\ \ \ Income & 0.04 & -0.08 & 0.17 & .05 & .495\\
+Privcacy need government &  &  &  &  & \\
+\ \ \ Integrity & 0.16 & -0.15 & 0.47 & .10 & .316\\
+\ \ \ Sociability & -0.15 & -0.55 & 0.24 & -.09 & .440\\
+\ \ \ Anxiety & -0.27 & -0.49 & -0.04 & -.26 & .019\\
+\ \ \ Traditionalism & 0.42 & 0.14 & 0.69 & .43 & .003\\
+\ \ \ Risk avoidance & -0.06 & -1.16 & 1.04 & -.01 & .920\\
+\ \ \ Male & 0.03 & -0.34 & 0.40 & .02 & .881\\
+\ \ \ Age & -0.02 & -0.06 & 0.01 & -.08 & .174\\
+\ \ \ Income & -0.01 & -0.16 & 0.14 & -.01 & .891\\
+Privacy need interpersonal &  &  &  &  & \\
+\ \ \ Integrity & 0.24 & 0.01 & 0.48 & .15 & .039\\
+\ \ \ Sociability & -0.62 & -0.90 & -0.34 & -.34 & < .001\\
+\ \ \ Anxiety & 0.01 & -0.16 & 0.17 & .01 & .938\\
+\ \ \ Traditionalism & 0.25 & 0.05 & 0.44 & .23 & .012\\
+\ \ \ Risk avoidance & 1.01 & 0.06 & 1.96 & .17 & .038\\
+\ \ \ Male & -0.02 & -0.30 & 0.26 & -.01 & .899\\
+\ \ \ Age & < 0.01 & -0.03 & 0.04 & .02 & .764\\
+\ \ \ Income & -0.03 & -0.16 & 0.10 & -.04 & .621\\
+Privacy need anonymity &  &  &  &  & \\
+\ \ \ Integrity & -0.19 & -0.38 & 0.01 & -.23 & .061\\
+\ \ \ Sociability & -0.08 & -0.28 & 0.12 & -.10 & .423\\
+\ \ \ Anxiety & -0.04 & -0.14 & 0.06 & -.08 & .448\\
+\ \ \ Traditionalism & 0.03 & -0.09 & 0.15 & .05 & .654\\
+\ \ \ Risk avoidance & -0.29 & -0.89 & 0.31 & -.10 & .351\\
+\ \ \ Male & 0.13 & -0.07 & 0.33 & .15 & .193\\
+\ \ \ Age & -0.01 & -0.04 & 0.02 & -.04 & .673\\
+\ \ \ Income & 0.07 & -0.03 & 0.18 & .18 & .149\\
+\bottomrule
+\end{tabular}
+}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/results-factor-1.pdf}
+\caption{\label{fig:results-factor}Overview of results. Shows the 95\%
+confidence intervals of standardized coefficients.}
+\end{figure}
+
+To begin with, we found that the final model we estimated to test our
+hypotheses fit the data moderately well, \(\chi^2\)(142) = 233.64,
+\textit{p} \textless{} .001, cfi = .92, rmsea = .05, 90\% CI {[}.04,
+.06{]}, srmr = .05. Our first hypothesis stated that people reporting
+more integrity than others would need less privacy. Indeed, the results
+showed that respondents who reported more integrity than others desired
+moderately less anonymity. The relation with general privacy showed the
+same relation; however, it was marginally not significant.
+Interestingly, respondents who reported more integrity desired
+\emph{more} privacy from other people. No significant relation with the
+need for privacy from the government was found.
+
+Respondents who reported being more sociable than other desired less
+privacy from other people. The effect was of a considerable size. No
+other significant relations were found.
+
+Next, we found that respondents who indicated being more anxious than
+others also desired less privacy from the government. The effect size
+was moderate to considerable. No other significnat relations were found.
+
+Respondents who reported being more risk avoidant than others desired
+moderately more privacy from other people. No further significant
+effects were found.
+
+Next, respondents who indicated being more traditional than others also
+desired more privacy from the government. The effect was substantial.
+More traditional respondents also desired moderately more privacy from
+other people. No significant relations with the overall level of privacy
+and the need for anonymity were found.
+
+Finally, regarding sociodemographic variables, we found that respondents
+who were older also desired more privacy. The effect was small.
+
+In sum, the predictors could explained 8.82\% of the variance in the
+general need for privacy, 23.06\% of the variance in the need for
+privacy from the government, 29.71\% of the variance in the need for
+privacy from other people, and 15.52\% of the variance in the need for
+anonymity.
+
+As stated above, we also calculated the relation between the predictor
+variables and the individual privacy need items. Several significant
+relations were found. For a visualization, see Figure
+\ref{fig:results-items}.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/results-items-1.pdf}
+\caption{\label{fig:results-items}Overview of results. Shows the 95\%
+confidence intervals of standardized coefficients.}
+\end{figure}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+This study analyzed how the need for privacy can be predicted by means
+of personality. In a study with 261 students from a large US university,
+we measured the need for privacy with 22 items. Fifteen items formed a
+well-fitting bifactor model, with one factor measuring the general
+desire for privacy, and three specific factors measuring the need for
+privacy from the government, the need for privacy from other people, and
+the need for anonymity. The factor solution we found is in line with
+privacy theory, which subsumes a vertical level (here, privacy from the
+government) and a horizontal level (here, privacy from other people).
+The third dimension, need for anonymity, can be argued to exist on the
+diagonal, as one can be anonymous both from the government and from
+other people.
+
+The results showed that the need for privacy can be predicted
+considerably well by means of personality. Specifically, integrity
+relates to several dimensions of need for privacy: People who reported
+being of lower integrity desired more anonymity and slightly less
+privacy from other people. Respondents who said, for example, that they
+would feel tempted to take things that do not belong to them were also
+more likely to avoid situations in which they were identifiable.
+
+In conclusion, our results follow Altman (1976), who reasoned that if
+exposure of information is risky it is likely that people will use more
+mechanisms to strengthen their social boundaries and increase their
+desired level of privacy. This study thus aligns with Altman's privacy
+regulation theory by showing that, in several contexts, people with
+lower integrity had a higher level of desired privacy.
+
+In addition, need for privacy was predicted also by other (neutral)
+personality facets: People who were less sociable, more risk averse, and
+less anxious also desired more privacy. This implies that various
+personality-related aspects can predict need for privacy.
+
+People who are more shy, more risk averse, or less anxious also desire
+more privacy. For example, people who are more anxious are more likely
+to accept government surveillance (arguably because they are less afraid
+of terrorist attacks). When looking at the bigger implications of the
+results, this shows the importance to make differentiated claims on why
+people desire privacy: Indeed, the results suggest that some people
+desire privacy because they might have something to hide. However,
+putting everyone who desires privacy under a general suspicion is wrong
+given that less sociable, risk averse, and less anxious people are also
+more likely to desire privacy.
+
+As a side note, despite the fact that we mostly used well-established
+scales, confirmatory factor analyses (CFAs) showed that some of the
+original items had to be deleted in order to achieve adequate factorial
+validity. This resembles the finding by Hussey and Hughes (2018), who
+reported that several widely used scales in psychological research
+actually do not show high factorial validity. We would like to point out
+that by using bifactor models it is possible to at least partially
+alleviate the problem, as the bifactor models are less strict than the
+routinely used unidimensional or hierarchical models, which are more
+conservative.
+
+\hypertarget{limitations-and-future-perspective}{%
+\subsection{Limitations and future
+perspective}\label{limitations-and-future-perspective}}
+
+Power analyses showed that future research should use samples above
+\emph{N} \(\approx\) 260 in order to test hypotheses with the
+recommended power of at least .80 (Cohen (1992)).
+
+In general, the question arises whether it is possible, or even socially
+desirable, to measure a person's integrity. On the one hand, integrity
+implies absolute criteria: Stealing is bad and forbidden, whereas
+helping is good and encouraged. On the other hand, integrity implies
+relative criteria: Whereas some cultures disapprove of lying whatever
+the context, others consider lying okay---for example \enquote{white
+lies} in order to save face or to avoid hurting someone's feelings
+(Altman, 1977). Thus, ranking behaviors, opinions, and character traits
+with regard to integrity is a moral dilemma. As a result, throughout the
+entire study we have understood integrity as a transgression of social
+norms that is strong and that most societies would agree upon (for
+example, most societies would consider stealing as a sign of low
+integrity).
+
+Next, the question arises whether it is possible to measure integrity
+based on self-reports. Interestingly, integrity tests using self-reports
+have been shown to work successfully, given that they can predict
+unwanted professional workplace behavior sufficiently (e.g., theft, drug
+and alcohol problems, or absenteeism; Ones, Viswesvaran, \& Schmidt,
+1993). In a meta-analysis with 665 correlation coefficients, integrity
+tests related to counterproductive behaviors with a coefficient of
+\emph{r} = .47 (Ones et al., 1993). Nonetheless, future research would
+benefit from including behavioral manifestations of integrity, such as
+concrete cheating behaviors. If concrete cheating behaviors also
+increase desires for privacy, this would strengthen the underlying
+premise of the nothing-to-hide argument.
+
+In that vein, we decided against including social desirability as a
+control variable, because even though social desirability can affect
+answers to sensitive questions (de Jong, Pieters, \& Stremersch, 2012),
+it is arguably more likely to reflect a true personality trait than
+false answering behavior (de Vries, Zettler, \& Hilbig, 2014).
+
+By focusing on \emph{specific facets} of personality (e.g.,
+fearfulness), we followed the recommendation by Paunonen and Ashton
+(2001) to not analyze \emph{general factors} of personality (e.g.,
+neuroticism). For future research, we suggest going one step further by
+analyzing predictors that are even more specified. For example, it seems
+possible that people who hold dissenting political beliefs could also
+have a higher need for privacy from the government. Similarly, it would
+be interesting to focus on different minority groups. For example, it
+seems plausible that people from a LGBT background might desire more
+privacy from government (because it is potentially repressive or
+unfriendly toward LGBTs). Finally, in this study we focused mostly on
+escapist motives for why people desire privacy (e.g., sociability, risk
+aversion). Interestingly, Leary, Herbst, and McCrary (2003) were able to
+show that when predicting engagement in solitary activities, it is less
+preferable to measure how strongly people want to escape society
+(avoidance oriented), but rather how much they seek solitude (approach
+oriented). Hence, future studies might want to include predictors that
+are more approach oriented (e.g., peoples' need for contemplation).
+
+From a methodological perspective, future research should continue to
+improve the instruments we used, given that factorial validity of some
+scales was only moderate. Similarly, we recommend elaborating on the
+general understanding of integrity as a theoretical concept. To date,
+there is not one overarching concept of integrity that incorporates all
+the different aspects of integrity, yet it would be valuable to examine
+how other aspects of integrity (e.g., authenticity, trustworthiness, or
+consistency) relate to privacy desires.
+
+Optimizing the variables' factorial validity might introduce problems of
+overfitting. In other words, although we might now have a sharper knife,
+we also use it less situations. First, we think that by using bifactor
+models we were able to retain a large number of items, rendering our
+results more robust. In addition, also when looking at the items
+individually one can see that the results are not dependent on inclusion
+of specific items.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
+
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
-<div id = "refs"></div>
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Altman.1976}{}%
+Altman, I. (1976). Privacy: A conceptual analysis. \emph{Environment and
+Behavior}, \emph{8}(1), 7--29.
+doi:\href{https://doi.org/10.1177/001391657600800102}{10.1177/001391657600800102}
+
+\leavevmode\hypertarget{ref-Altman.1977}{}%
+Altman, I. (1977). Privacy regulation: Culturally universal or
+culturally specific? \emph{Journal of Social Issues}, \emph{33}(3),
+66--84.
+doi:\href{https://doi.org/10.1111/j.1540-4560.1977.tb01883.x}{10.1111/j.1540-4560.1977.tb01883.x}
+
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with
+R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-boyd.2008c}{}%
+boyd, danah m. (2008). \emph{Taken out of context. American teen
+sociality in networked publics: Doctoral dissertation}. Berkeley, CA:
+University of California.
+
+\leavevmode\hypertarget{ref-Burgoon.1982}{}%
+Burgoon, J. K. (1982). Privacy and communication. \emph{Annals of the
+International Communication Association}, \emph{1}, 206--249.
+
+\leavevmode\hypertarget{ref-Cohen.1992}{}%
+Cohen, J. (1992). A power primer. \emph{Psychological Bulletin},
+\emph{112}(1), 155--159.
+doi:\href{https://doi.org/10.1037/0033-2909.112.1.155}{10.1037/0033-2909.112.1.155}
+
+\leavevmode\hypertarget{ref-Connelly.2006}{}%
+Connelly, S., Lilienfeld, S. O., \& Schmeelk, K. M. (2006). Integrity
+tests and morality: Associations with ego development, moral reasoning,
+and psychopathic personality. \emph{International Journal of Selection
+and Assessment}, \emph{14}(1), 82--86.
+doi:\href{https://doi.org/10.1111/j.1468-2389.2006.00335.x}{10.1111/j.1468-2389.2006.00335.x}
+
+\leavevmode\hypertarget{ref-Corcoran.1987}{}%
+Corcoran, K. J., \& Rotter, J. B. (1987). Morality-conscience guilt
+scale as a predictor of ethical behavior in a cheating situation among
+college females. \emph{The Journal of General Psychology},
+\emph{114}(2), 117--123.
+doi:\href{https://doi.org/10.1080/00221309.1987.9711061}{10.1080/00221309.1987.9711061}
+
+\leavevmode\hypertarget{ref-Covey.1989}{}%
+Covey, M. K., Saladin, S., \& Killen, P. J. (1989). Self-monitoring,
+surveillance, and incentive effects on cheating. \emph{The Journal of
+Social Psychology}, \emph{129}(5), 673--679.
+doi:\href{https://doi.org/10.1080/00224545.1989.9713784}{10.1080/00224545.1989.9713784}
+
+\leavevmode\hypertarget{ref-deJong.2012}{}%
+de Jong, M. G., Pieters, R., \& Stremersch, S. (2012). Analysis of
+sensitive questions across cultures: An application of multigroup item
+randomized response theory to sexual attitudes and behavior.
+\emph{Journal of Personality and Social Psychology}, \emph{103}(3),
+543--564. doi:\href{https://doi.org/10.1037/a0029394}{10.1037/a0029394}
+
+\leavevmode\hypertarget{ref-deVries.2014}{}%
+de Vries, R. E., Zettler, I., \& Hilbig, B. E. (2014). Rethinking trait
+conceptions of social desirability scales: Impression management as an
+expression of honesty-humility. \emph{Assessment}, \emph{21}(3),
+286--299.
+doi:\href{https://doi.org/10.1177/1073191113504619}{10.1177/1073191113504619}
+
+\leavevmode\hypertarget{ref-Dienlin.2014}{}%
+Dienlin, T. (2014). The privacy process model. In S. Garnett, S. Halft,
+M. Herz, \& J. M. Mönig (Eds.), \emph{Medien und Privatheit} (pp.
+105--122). Passau, Germany: Karl Stutz.
+
+\leavevmode\hypertarget{ref-Donnellan.2008}{}%
+Donnellan, M. B., \& Lucas, R. E. (2008). Age differences in the Big
+Five across the life span: Evidence from two national samples.
+\emph{Psychology and Aging}, \emph{23}(3), 558--566.
+doi:\href{https://doi.org/10.1037/a0012897}{10.1037/a0012897}
+
+\leavevmode\hypertarget{ref-Eggers.2013}{}%
+Eggers, D. (2013). \emph{The circle}. New York, NY: Knopf Publishing
+Group.
+
+\leavevmode\hypertarget{ref-R-semPlot}{}%
+Epskamp, S., \& Simon Stuber. (2017). \emph{SemPlot: Path diagrams and
+visual analysis of various sem packages' output}. Retrieved from
+\url{https://CRAN.R-project.org/package=semPlot}
+
+\leavevmode\hypertarget{ref-Fife.2012}{}%
+Fife, E., \& Orjuel, J. (2012). The privacy calculus: Mobile apps and
+user perceptions of privacy and security. \emph{International Journal of
+Engineering Business Management}, \emph{4}, 1--10.
+doi:\href{https://doi.org/10.5772/51645}{10.5772/51645}
+
+\leavevmode\hypertarget{ref-Granovetter.1973}{}%
+Granovetter, M. S. (1973). The strength of weak ties. \emph{American
+Journal of Sociology}, \emph{78}(6), 1360--1380.
+
+\leavevmode\hypertarget{ref-Greenwald.2013}{}%
+Greenwald, G. (n.d.). NSA collecting phone records of millions of
+Verizon customers daily. \emph{The Guardian}. Retrieved from
+\url{www.theguardian.com}
+
+\leavevmode\hypertarget{ref-Hussey.2018}{}%
+Hussey, I., \& Hughes, S. (2018). Hidden invalidity among fifteen
+commonly used measures in social and personality psychology.
+doi:\href{https://doi.org/10.31234/osf.io/7rbfp}{10.31234/osf.io/7rbfp}
+
+\leavevmode\hypertarget{ref-John.1999}{}%
+John, O. P., \& Srivastava, S. (1999). The big five trait taxonomy:
+History, measurement, and theoretical perspectives. In L. A. Pervin \&
+O. P. John (Eds.), \emph{Handbook of personality} (pp. 102--138). New
+York, NY: Guilford Press.
+
+\leavevmode\hypertarget{ref-Johnson.2010}{}%
+Johnson, B. (n.d.). Privacy no longer a social norm, says Facebook
+founder. \emph{The Guardian}. Retrieved from \url{www.theguardian.com}
+
+\leavevmode\hypertarget{ref-Kline.2016}{}%
+Kline, R. B. (2016). \emph{Principles and practice of structural
+equation modeling} (4th ed.). New York, NY: The Guilford Press.
+
+\leavevmode\hypertarget{ref-Lakens.2018}{}%
+Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence testing
+for psychological research: A tutorial. \emph{Advances in Methods and
+Practices in Psychological Science}, \emph{1}(2), 259--269.
+doi:\href{https://doi.org/10.1177/2515245918770963}{10.1177/2515245918770963}
+
+\leavevmode\hypertarget{ref-Leary.2003}{}%
+Leary, M. R., Herbst, K. C., \& McCrary, F. (2003). Finding pleasure in
+solitary activities: Desire for aloneness or disinterest in social
+contact? \emph{Personality and Individual Differences}, \emph{35}(1),
+59--68.
+doi:\href{https://doi.org/10.1016/S0191-8869(02)00141-1}{10.1016/S0191-8869(02)00141-1}
+
+\leavevmode\hypertarget{ref-Marlinspike.2013}{}%
+Marlinspike, M. (n.d.). Why 'I have nothing to hide' is the wrong way to
+think about surveillance. Retrieved from \url{www.wired.com}
+
+\leavevmode\hypertarget{ref-Meijer.2016}{}%
+Meijer, R. R., Niessen, A. S. M., \& Tendeiro, J. N. (2016). A practical
+guide to check the consistency of item response patterns in clinical
+research through person-fit statistics: Examples and a computer Program.
+\emph{Assessment}, \emph{23}(1), 52--62.
+doi:\href{https://doi.org/10.1177/1073191115577800}{10.1177/1073191115577800}
+
+\leavevmode\hypertarget{ref-Morton.2013}{}%
+Morton, A. (2013). Measuring inherent privacy concern and desire for
+privacy - A pilot survey study of an instrument to measure dispositional
+privacy concern. In \emph{International Conference on Social Computing
+(SocialCom)} (pp. 468--477).
+doi:\href{https://doi.org/10.1109/SocialCom.2013.73}{10.1109/SocialCom.2013.73}
+
+\leavevmode\hypertarget{ref-Ones.1993}{}%
+Ones, D. S., Viswesvaran, C., \& Schmidt, F. L. (1993). Comprehensive
+meta-analysis of integrity test validities: Findings and implications
+for personnel selection and theories of job performance. \emph{Journal
+of Applied Psychology}, \emph{78}(4), 679--703.
+doi:\href{https://doi.org/10.1037/0021-9010.78.4.679}{10.1037/0021-9010.78.4.679}
+
+\leavevmode\hypertarget{ref-Park.2015}{}%
+Park, Y. J. (2015). Do men and women differ in privacy? Gendered privacy
+and (in)equality in the Internet. \emph{Computers in Human Behavior},
+\emph{50}, 252--258.
+doi:\href{https://doi.org/10.1016/j.chb.2015.04.011}{10.1016/j.chb.2015.04.011}
+
+\leavevmode\hypertarget{ref-Paunonen.2002}{}%
+Paunonen, S. V. (2002). Design and construction of the Supernumerary
+Personality Inventory. London, Canada: University of Western Ontario.
+
+\leavevmode\hypertarget{ref-Paunonen.2001}{}%
+Paunonen, S. V., \& Ashton, M. C. (2001). Big Five factors and facets
+and the prediction of behavior. \emph{Journal of Personality and Social
+Psychology}, \emph{81}(3), 524--539.
+doi:\href{https://doi.org/10.1037/0022-3514.81.3.524}{10.1037/0022-3514.81.3.524}
+
+\leavevmode\hypertarget{ref-Pedersen.1979}{}%
+Pedersen, D. M. (1979). Dimensions of privacy. \emph{Perceptual and
+Motor Skills}, \emph{48}(3), 1291--1297.
+doi:\href{https://doi.org/10.2466/pms.1979.48.3c.1291}{10.2466/pms.1979.48.3c.1291}
+
+\leavevmode\hypertarget{ref-Pedersen.1982}{}%
+Pedersen, D. M. (1982). Personality correlates of privacy. \emph{The
+Journal of Psychology}, \emph{112}(1), 11--14.
+doi:\href{https://doi.org/10.1080/00223980.1982.9923528}{10.1080/00223980.1982.9923528}
+
+\leavevmode\hypertarget{ref-Petronio.2010}{}%
+Petronio, S. (2010). Communication privacy management theory: What do we
+know about family privacy regulation? \emph{Journal of Family Theory \&
+Review}, \emph{2}(3), 175--196.
+doi:\href{https://doi.org/10.1111/j.1756-2589.2010.00052.x}{10.1111/j.1756-2589.2010.00052.x}
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2018). \emph{R: A language and environment for statistical
+computing}. Vienna, Austria: R Foundation for Statistical Computing.
+Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-R-lavaan}{}%
+Rosseel, Y. (2012). lavaan: An R package for structural equation
+modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36.
+Retrieved from \url{http://www.jstatsoft.org/v48/i02/}
+
+\leavevmode\hypertarget{ref-Schwartz.1968}{}%
+Schwartz, B. (1968). The social psychology of privacy. \emph{American
+Journal of Sociology}, \emph{73}(6), 741--752.
+
+\leavevmode\hypertarget{ref-Sheldon.2004}{}%
+Sheldon, K. M. (2004). Integrity {[}authenticity, honesty{]}. In C.
+Peterson \& Seligman, M. E. P. (Eds.), \emph{Character strengths and
+virtues: A handbook and classification} (pp. 249--271). Oxford, UK:
+Oxford University Press.
+
+\leavevmode\hypertarget{ref-Solove.2007}{}%
+Solove, D. J. (2007). 'I've got nothing to hide' and other
+misunderstandings of privacy. \emph{San Diego Law Review}, \emph{44},
+745--772.
+
+\leavevmode\hypertarget{ref-Stone.1986}{}%
+Stone, D. L. (1986). Relationship between introversion/extraversion,
+values regarding control over information, and perceptions of invasion
+of privacy. \emph{Perceptual and Motor Skills}, \emph{62}(2), 371--376.
+doi:\href{https://doi.org/10.2466/pms.1986.62.2.371}{10.2466/pms.1986.62.2.371}
+
+\leavevmode\hypertarget{ref-Tifferet.2019}{}%
+Tifferet, S. (2019). Gender differences in privacy tendencies on social
+network sites: A meta-analysis. \emph{Computers in Human Behavior},
+\emph{93}, 1--12.
+doi:\href{https://doi.org/10.1016/j.chb.2018.11.046}{10.1016/j.chb.2018.11.046}
+
+\leavevmode\hypertarget{ref-Trepte.2013a}{}%
+Trepte, S., Dienlin, T., \& Reinecke, L. (2013). Privacy,
+self-disclosure, social support, and social network site use. Research
+report of a three-year panel study. Retrieved from
+\url{http://opus.uni-hohenheim.de/volltexte/2013/889/}
+
+\leavevmode\hypertarget{ref-Trepte.2017d}{}%
+Trepte, S., \& Masur, P. K. (2017). Need for privacy. In V. Zeigler-Hill
+\& T. K. Shackelford (Eds.), \emph{Encyclopedia of Personality and
+Individual Differences} (Vol. 94, pp. 1--4). Cham: Springer
+International Publishing.
+doi:\href{https://doi.org/10.1007/978-3-319-28099-8_540-1}{10.1007/978-3-319-28099-8\_540-1}
+
+\leavevmode\hypertarget{ref-vanBommel.2014}{}%
+van Bommel, M., van Prooijen, J.-W., Elffers, H., \& van Lange, P. A. M.
+(2014). Intervene to be seen: The power of a camera in attenuating the
+bystander effect. \emph{Social Psychological and Personality Science},
+\emph{5}(4), 459--466.
+doi:\href{https://doi.org/10.1177/1948550613507958}{10.1177/1948550613507958}
+
+\leavevmode\hypertarget{ref-Weinberger.2017b}{}%
+Weinberger, M., Zhitomirsky-Geffet, M., \& Bouhnik, D. (2017). Sex
+differences in attitudes towards online privacy and anonymity among
+Israeli students with different technical backgrounds, \emph{22}(4).
+Retrieved from \url{http://InformationR.net/ir/22-4/paper777.html}
+
+\leavevmode\hypertarget{ref-Westin.1967}{}%
+Westin, A. F. (1967). \emph{Privacy and freedom}. New York, NY:
+Atheneum.
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
+Springer-Verlag New York. Retrieved from \url{http://ggplot2.org}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H. (2017). \emph{Tidyverse: Easily install and load the
+'tidyverse'}. Retrieved from
+\url{https://CRAN.R-project.org/package=tidyverse}
+
 \endgroup
+
+\end{document}

### 2018-12-09 results/analyses.RmD
- major updates on everything:     - mostly finished the analyses     - rewritten the methods, results, and abstract

---
title: "Who Needs Privacy?"
subtitle: "Analyses"
toc: TRUE
output:
  pdf_document: default
---

```{r knitr-setup, include=F}
set.seed(21)
knitr::opts_chunk$set(warning=F, echo=F, error=F, message=F,
                      cache.extra = knitr::rand_seed,
                      fig.pos = 'h')
options(digits = 3)
```

```{r r-setup, include=F}
# list packages to be used
packages <- c("corrplot", "devtools", "ggplot2", "influence.SEM", 
              "lavaan", "MBESS", "magrittr", "mice", "MVN", "PerFit", "psych", 
              "pwr", "semPlot", "tidyverse")

# install packages
install <- FALSE  # change to TRUE to install packages
if(isTRUE(install)) (
  lapply(packages, install.packages, repos = 'http://cran.us.r-project.org')
)
devtools::install_git("https://github.com/tdienlin/td")

# load packages
lapply(packages, library, character.only = TRUE)
library(td)
```

```{r data-wrangling, include=F}
# read data
# note: a bit complicated, as second row contains variable attributes
d <- read_csv("../data/data.csv", skip = 2, col_names = FALSE) %>% 
  set_names(colnames(read_csv("../data/data.csv", n_max = 1)))

# prepare table with item content
items <- data.frame(
  name = colnames(read_csv("../data/data.csv", n_max = 1)),  # extract item names
  content = colnames(read_csv("../data/data.csv", skip = 1, n_max = 2))  # extract item content
) %>% 
  mutate(content = gsub("To what extent do you agree or disagree with the following / statements[?][-]", "", content)) %>% 
  mutate(content = gsub("To what extent do you agree or disagree with the / following statements[?][-]", "", content)) %>% 
  mutate(content_breaks = sapply(content, string_break, 30))

# filter pretest data
d <- d[-(1:11), ]

# edit variables
d %<>% 
  mutate(
    male = 2 - SES.SEX,
    time = V9 - V8,
    id = 1:nrow(.)
    ) %>% 
  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.))) %>% 
  rename(
    age = SES.AGE,
    inc = SES.JOB_2
  )

# select items
d %<>% dplyr::select(
  id, male, age, inc, time,
  starts_with("N4P"),
  starts_with("INT_"),
  SOC_1 : SOC_8,
  starts_with("FEA_"),
  TRA_1 : TRA_8,
  RIT_1 : RIT_8,
  BFI_1 : BFI_10
)

# count no of missing responses
d$miss_per <- apply(d, 1, function(x) (sum(is.na(x)))) %>% 
  divide_by(ncol(d))
```

\newpage
# Data wrangling
## Filter defective data
### Empty/missing data

```{r}
d_all <- d
n_d_all <- nrow(d_all)
table(d$miss_per) %>% round(2)

# delete respondents with more than 50% missing data
d <- d[d$miss_per < .5, ]
n_d_empty <- n_d_all - nrow(d)

# impute missing data
init <- mice(d, maxit = 0) 
vars_excl <- c("id", "time", "miss_per")
pred_ma <- init$predictorMatrix
pred_ma[, vars_excl] <- 0
d_imp_multi <- mice(d, method = "pmm", m = 1, predictorMatrix = pred_ma)
d <- mice::complete(d_imp_multi)
```

Shows that most people answered all questions. There were 15 empty data sets, and some with more than 50% missing data. These were deleted.

### Speeder

```{r speeder, warning=F}
# plot reponse times
qplot(d$time)
```

Shows that some participants took very long to answer. Inspect regular times.

```{r}
qplot(d$time[d$time < 5000])
```

Distribution looks okay (no early peak). Also no answers faster than 5 mins.

### Response patterns

```{r}
# make backup with data including suspicious patterns
d_incl_susp <- d

# run guttman tests
d$guttman <- Gpoly(dplyr::select(d, N4P.BOT_1:RIT_8) - 1, 7) %$% 
  PFscores %>% 
  unlist()

# inspect cases with susceptive data
guttman_crit <- quantile(d$guttman, probs = .95)
d_suspicious <- d[d$guttman > guttman_crit, ] %>% 
  arrange(desc(guttman))

# remove cases
d <- d[d$guttman < guttman_crit, ]
n_d_defect <- n_d_all - n_d_empty - nrow(d)
n_d <- nrow(d)
d %<>%  filter(age != 9 | is.na(age))  # filter participant with illogial age
```

All of the 5% cases indeed show extreme response patterns and/or illogical data. Will be filtered.

\newpage
# Power Analyses

```{r}
(power_analysis <- pwr.r.test(n = n_d, r = .1, sig.level = .05))
power_small <- power_analysis$power %>% multiply_by(100) %>% round(0)

(sensitivity_analysis <- pwr.r.test(n = n_d, sig.level = .05, power = .95))
sensitivity_95 <- sensitivity_analysis$r %>% round(2)
```

\newpage
# Multivariate normal distribution

```{r}
d_tmp <- dplyr::select(d, -id, -male, -age, -inc, -time, -miss_per, -guttman, -starts_with("BFI"))
(mult_norm <- mvn(data = d_tmp, mvnTest = "mardia")$multivariateNormality %>% 
    as.data.frame() %>% 
    mutate_at(vars(Statistic, "p value"), funs(as.numeric(levels(.))[.])) %>% 
    filter(Test != "MVN")
  )
```

\newpage
# Measures
## Need for Privacy

```{r, fig.height=15, fig.width=12}
d_tmp <- dplyr::select(d, starts_with("N4P"))
name_tmp <- "pri_nee"
recoded_tmp <- c("N4P.INT_1", "N4P.INT_5", "N4P.INT_8")
```

### Items

```{r, fig.height=15, fig.width=12}
ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]

# new selection bc of recoding
d_tmp <- dplyr::select(d, starts_with("N4P"))

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc) 
```

\newpage
### Correlation table

```{r, fig.height=15, fig.width=12}
corr_tmp <- cor(d_tmp)
corrplot(corr_tmp, type = "upper", method = "color",
         tl.col = "black")
```

Shows that the inverted items `r recoded_tmp` do not always correlate positively and in general only weakly with the regular items. Will not be included.

\newpage
### Parallel analysis

```{r}
d_tmp <- dplyr::select(d_tmp, -one_of(recoded_tmp))
fa.parallel(d_tmp)
```

\newpage
### EFA

```{r}
tmp <- omega(d_tmp, nfactors = 3, fm = "ml")
```

Shows several items with negative or low loadings, which will be excluded in updated version.

\newpage

```{r}
tmp <- omega(dplyr::select(d_tmp,
                    -N4P.BOT_4 #, -N4P.BOT_3, -N4P.INT_3, -N4P.BOT_2 #, -N4P.INT_7, -N4P.INT_4
                    ),
             nfactors = 3, fm = "ml")
```

Produces a fitting solution.

\newpage

```{r}
tmp$schmid$sl
```

Interpretation

* factor 1 measures need for privacy from the government (vertical)
* factor 2 measures need for anonymity (combined)
* factor 3 measures need for privacy from other people (horizontal)

\newpage
### CFA

```{r}
model <- '
  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2 + N4P.BOT_1
  pri_nee_int =~ N4P.BOT_1 + N4P.BOT_3 + N4P.INT_4 + N4P.INT_7 + N4P.INT_9
  pri_nee_gen =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9 + N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.BOT_1 + N4P.BOT_3 + N4P.INT_4 + N4P.INT_7 + N4P.INT_9 + N4P.INT_2
  pri_nee_gen ~~ 0*pri_nee_gov + 0*pri_nee_int + 0*pri_nee_ano
  pri_nee_gov ~~ 0*pri_nee_int + 0*pri_nee_ano
  pri_nee_int ~~ 0*pri_nee_ano
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
```

### Table

```{r}

```

\newpage
## Integrity

```{r, fig.height=8, fig.width=12}
d_tmp <- dplyr::select(d, starts_with("INT_"))
name_tmp <- "int"
recoded_tmp <- c("INT_1", "INT_2", "INT_5", "INT_6", "INT_7", 
                 "INT_8", "INT_9", "INT_10", "INT_11")
```

### Items

```{r, fig.height=8, fig.width=12}
ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]

# new selection bc of recoding
d_tmp <- dplyr::select(d, starts_with("INT_"))

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc)
```

\newpage
### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

\newpage
### EFA

```{r}
tmp <- omega(d_tmp, fm = "ml", nfactors = 2)
```

Shows solution for two factors. Delete items INT_4 and INT_3 for not loading on general factor

\newpage

```{r}
tmp <- omega(dplyr::select(d_tmp, -INT_3, -INT_4), fm = "ml", nfactors = 2)
```

\newpage
### CFA

```{r}
model <- '
  int_1 =~ INT_1 + a*INT_5 + a*INT_6 + a*INT_2 + a*INT_7 + INT_8
  int_2 =~ b*INT_9 + b*INT_10 + b*INT_11 + b* INT_8
  int_gen =~ INT_1 + INT_2 + INT_5 + INT_6 + INT_7 + INT_8 + INT_9 + INT_10 + INT_11
  int_gen ~~ 0*int_1 + 0*int_2
  int_1 ~~ 0*int_2
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

\newpage
## Sociability
### Items

```{r, fig.height=8, fig.width=12}
d_tmp <- dplyr::select(d, SOC_1 : SOC_8)
name_tmp <- "soc"
recoded_tmp <- c("SOC_1", "SOC_3", "SOC_5", "SOC_7")

p_int <- ggplot(d_tmp %>% 
                  gather(name, value) %>% 
                  left_join(items, "name"),
                  aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)
p_int

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]

# new selection bc of recoding
d_tmp <- dplyr::select(d, SOC_1 : SOC_8)

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc)
```

\newpage
### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

\newpage
### EFA

```{r}
tmp <- omega(d_tmp, fm = "ml", nfactors = 3)
```

Shows no clear solution for three factors.

\newpage

```{r}
tmp <- omega(d_tmp, fm = "ml", nfactors = 2)
```

Shows solution for two factors. Differentiates between inverted and regular items. Delete Soc_6 and Soc_4

\newpage

```{r}
tmp <- omega(dplyr::select(d_tmp, -SOC_4, - SOC_6), fm = "ml", nfactors = 2)
```

\newpage
### CFA

```{r}
model <- '
  soc_1 =~ a*SOC_1 + SOC_3 + SOC_5 + a*SOC_7
  soc_2 =~ b*SOC_2 + b*SOC_8 + SOC_1 + SOC_7
  soc_gen =~ SOC_1 + SOC_2 + SOC_3 + SOC_5 + SOC_7 + SOC_8
  soc_gen ~~ 0*soc_1 + 0*soc_2
  soc_1 ~~ 0*soc_2
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

\newpage
## Anxiety
### Items

```{r}
d_tmp <- dplyr::select(d, starts_with("FEA_"))
name_tmp <- "fea"
recoded_tmp <- c("FEA_1", "FEA_3", "FEA_5", "FEA_7")

ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]

# new selection bc of recoding
d_tmp <- dplyr::select(d, starts_with("FEA_"))

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc) 
```

### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

\newpage
### EFA

```{r}
tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
```

Produces a fitting solution.

\newpage
### CFA

```{r}
model <- '
  fea_1 =~ a*FEA_2 + a*FEA_4 + a*FEA_6 + FEA_8
  fea_2 =~ FEA_1 + b*FEA_3 + b*FEA_5 + b*FEA_7
  fea_gen =~ FEA_2 + FEA_4 + FEA_7 + FEA_8 + FEA_1 + FEA_3 + FEA_5 + FEA_6

  fea_gen ~~ 0*fea_1 + 0*fea_2
  fea_1 ~~ 0*fea_2
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

\newpage
## Risk Avoidance
### Items

```{r}
d_tmp <- dplyr::select(d, RIT_1 : RIT_8)
name_tmp <- "rit"
recoded_tmp <- c("RIT_1", "RIT_3", "RIT_5")

ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]

# new selection bc of recoding
d_tmp <- dplyr::select(d, RIT_1 : RIT_8)

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc)
```

\newpage
### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

\newpage
### EFA

```{r}
tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
```

Produces a fitting solution.

\newpage
### CFA

```{r}
model <- '
  rit_1 =~ a*RIT_2 + a*RIT_4 + a*RIT_5 + a*RIT_7 + a*RIT_8
  rit_2 =~ RIT_1 + RIT_3 + RIT_5
  rit_gen =~ RIT_1 + RIT_2 + RIT_3 + RIT_4 + RIT_5 + RIT_6 + RIT_7 + RIT_8

  rit_gen ~~ 0*rit_1 + 0*rit_2
  rit_1 ~~ 0*rit_2
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

\newpage 
## Traditionalism
### Items

```{r}
d_tmp <- dplyr::select(d, TRA_1 : TRA_8)
name_tmp <- "tra"
recoded_tmp <- c("TRA_2", "TRA_4", "TRA_6")

ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]

# new selection bc of recoding
d_tmp <- dplyr::select(d, TRA_1 : TRA_8)

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc)
```

\newpage
### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

\newpage
### EFA

```{r}
tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
```

Need to delete item TRA_7, TRA_6, and TRA_4.

\newpage

```{r}
tmp <- omega(dplyr::select(d_tmp, -TRA_4, -TRA_7, -TRA_6, ), nfactors = 2, fm = "ml")
```

\newpage
### CFA

```{r}
model <- '
  tra_1 =~ a*TRA_1 + a*TRA_5 + a*TRA_3 + a*TRA_8 + a*TRA_7
  tra_2 =~ b*TRA_2 + b*TRA_4 + b*TRA_6
  tra_gen =~ TRA_1 + TRA_2 + TRA_3 + TRA_4 + TRA_5 + TRA_6 + TRA_7 + TRA_8

  tra_gen ~~ 0*tra_1 + 0*tra_2
  tra_1 ~~ 0*tra_2
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

\newpage

```{r}
model <- '
  tra_gen =~ TRA_1 + TRA_5 + TRA_3 + TRA_8 + TRA_7
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

\newpage
# Results

```{r}
d <- cbind(d, int_gen, soc_gen, fea_gen, tra_gen, rit_gen)
```

## Factor solution

```{r}
name_tmp <- "main"

# new
model <- '
  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2 + N4P.BOT_1
  pri_nee_int =~ N4P.BOT_1 + N4P.BOT_3 + N4P.INT_4 + N4P.INT_7 + N4P.INT_9
  pri_nee_gen =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9 + N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.BOT_1 + N4P.BOT_3 + N4P.INT_4 + N4P.INT_7 + N4P.INT_9 + N4P.INT_2

  pri_nee_gen ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
  pri_nee_gov ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
  pri_nee_int ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
  pri_nee_ano ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc

  int_gen ~~ soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
  soc_gen ~~ fea_gen + tra_gen + rit_gen + male + age + inc
  fea_gen ~~ tra_gen + rit_gen + male + age + inc
  tra_gen ~~ rit_gen + male + age + inc
  rit_gen ~~ male + age + inc
  male ~~ age + inc
  age ~~ inc

  pri_nee_gen ~~ 0*pri_nee_gov + 0*pri_nee_int + 0*pri_nee_ano
  pri_nee_gov ~~ 0*pri_nee_int + 0*pri_nee_ano
  pri_nee_int ~~ 0*pri_nee_ano
'
fit <- sem(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE, rsquare = TRUE)
assign(paste0(name_tmp, "_fit"), fit)

# fit_rem_outlier <- sem(model, filter(d, cooks_dist < 3), estimator = "MLR")
# summary(fit_rem_outlier, fit = TRUE, std = TRUE)
# d$cooks_dist <- cooks_dist
# genCookDist(model, d, estimator = "MLR")
```

\newpage
## Individual items

```{r}
name_tmp <- "main_items"
model <- '
  N4P.BOT_1 + N4P.BOT_2 + N4P.BOT_3 + N4P.BOT_4 + N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_5 + N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.SOC_9 + N4P.INT_1 + N4P.INT_2 + N4P.INT_3 + N4P.INT_4 + N4P.INT_5 + N4P.INT_6 + N4P.INT_7 + N4P.INT_8 + N4P.INT_9 ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc

  int_gen ~~ soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
  soc_gen ~~ fea_gen + tra_gen + rit_gen + male + age + inc
  fea_gen ~~ tra_gen + rit_gen + male + age + inc
  tra_gen ~~ rit_gen + male + age + inc
  rit_gen ~~ male + age + inc
  male ~~ age + inc
  age ~~ inc
'
fit <- sem(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), sem(model, d))
```

\newpage
# Tables
## Items

```{r}
t_pri_nee <- items %>% 
  filter(grepl("N4P", name)) %>% 
  mutate(name = factor(name, c(paste0("N4P.BOT_", rep(4:1)),
                             paste0("N4P.INT_", rep(9:1)),
                             paste0("N4P.SOC_", rep(9:1))))) %>% 
  arrange(desc(as.numeric(name))) %>% 
  mutate(no. = c(1:4, "--", 6:8, 5, "--", 9, 
         "--", 12, "--", "--", 13, "--", 14, 10, "--", 11, "--")) %>% 
    dplyr::select(Name = name, No. = no., Content = content)
knitr::kable(t_pri_nee) %>% 
  kableExtra::column_spec(3, width = "10cm") %>% 
  kableExtra::kable_styling(latex_options="scale_down", font_size = 7)
```

\newpage
## Psychometrics

```{r}
t_facval <- rbind(
  "Privacy need" = fit_tab(pri_nee_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Integrity" = fit_tab(int_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Sociability" = fit_tab(soc_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Anxiety" = fit_tab(fea_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Risk aversion" = fit_tab(rit_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Traditionality" = fit_tab(tra_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE)
)

t_desc <- rbind(
  pri_nee_desc, int_desc, soc_desc, fea_desc, rit_desc, tra_desc
)

(t_psyc <- cbind(t_desc, t_facval))
```

\newpage
## Results main model

```{r results}
(t_results <- coeffs_tab(main_fit, as_text = TRUE) %>% 
   mutate(Outcome = recode(Outcome, 
         `pri_nee_gen` = "Privacy need general", 
         `pri_nee_gov` = "Privacy need government",
         `pri_nee_int` = "Privacy need interpersonal",
         `pri_nee_ano` = "Privacy need anonymity")) %>% 
  mutate(Predictor = recode(Predictor,
         `int_gen` = "Integrity",
         `soc_gen` = "Sociability",
         `fea_gen` = "Anxiety",
         `rit_gen` = "Risk avoidance",
         `tra_gen` = "Traditionalism",
         `inc` = "Income",
         `age` = "Age",
         `male` = "Male")))
```

\newpage
# Figures
## Bifactor model privacy needs

```{r}
p_pri_nee <- semPaths(
  pri_nee_fit,
  bifactor = "pri_nee_gen",
  layout = "tree3",
  whatLabels = "std",
  intercepts = FALSE,
  residuals = FALSE, 
  thresholds = FALSE,
  nodeLabels = c(1:14, 
           "Privacy\nneed\ngovernment", "Privacy\nneed\nanonymity", "Privacy\nneed\ninterpersonal",
           "Privacy\nneed\ngeneral"),
  reorder = FALSE,
  edge.label.position = .61,
  fixedStyle = 1,
  exoCov = FALSE,
  sizeMan = 4,
  sizeLat = 12,
  label.prop = .95,
  edge.label.cex = .8,
  mar = c(3, 1, 3, 1),
  label.scale.equal = TRUE
  )
```

\newpage
## Model bifactor

```{r}
# calculate CI for standardized effect 
# option 1: proper option, calculates extract bootstrapped coefficients for standardized solution
# CURRENTLY DOESN'T WORK
# d_effects <- bootstrapLavaan(main_fit)

# option 2: use SEs of standardized solution
d_main <- standardizedsolution(main_fit) %>% 
  as.data.frame() %>% 
  filter(op == "~") %>% 
  mutate(lhs = factor(lhs, c("pri_nee_ano", "pri_nee_int", "pri_nee_gov", "pri_nee_gen"))) %>%  # reorder for plot
  mutate(rhs = factor(rhs, c("int_gen", "soc_gen", "fea_gen", "rit_gen", "tra_gen", "male", "age", "inc"))) %>%  # reorder for plot
  mutate(lhs = recode(lhs, 
         `pri_nee_gen` = "Privacy need\ngeneral", 
         `pri_nee_gov` = "Privacy need\ngovernment",
         `pri_nee_int` = "Privacy need\ninterpersonal",
         `pri_nee_ano` = "Privacy need\nanonymity")) %>% 
  mutate(rhs = recode(rhs,
         `int_gen` = "Integrity",
         `soc_gen` = "Sociability",
         `fea_gen` = "Anxiety",
         `tra_gen` = "Traditio-\nnalism",
         `rit_gen` = "Risk\navoidance",
         `inc` = "Income",
         `age` = "Age",
         `male` = "Male")) %>% 
  rename(beta = est.std)

(p_main <- ggplot(d_main, aes(x = beta, y = lhs)) +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -0.1, linetype = "dashed", color = "grey") +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper, height = .2)) + 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_x_continuous(breaks = seq(-.7, .7, .2)) +
  coord_cartesian(xlim = c(-.5, .5)) +
  facet_grid(~ rhs))
```

\newpage
## Model items

```{r}
# calculate CI for standardized effect 
# option 1: proper option, calculates extract bootstrapped coefficients for standardized solution
# CURRENTLY DOESN'T WORK
# d_effects <- bootstrapLavaan(main_fit)

# option 2: use SEs of standardized solution
d_main_items <- standardizedsolution(main_items_fit) %>% 
  as.data.frame() %>% 
  filter(op == "~") %>% 
  mutate(rhs = factor(rhs, c("int_gen", "soc_gen", "fea_gen", "rit_gen", "tra_gen", "male", "age", "inc"))) %>%  # reorder for plot
  mutate(lhs = factor(lhs, c(paste0("N4P.BOT_", rep(4:1)),
                             paste0("N4P.INT_", rep(9:1)),
                             paste0("N4P.SOC_", rep(9:1))))) %>%  # reorder for plot
  mutate(rhs = recode(rhs,
         `int_gen` = "Integrity",
         `soc_gen` = "Sociability",
         `fea_gen` = "Anxiety",
         `tra_gen` = "Traditio-\nnalism",
         `rit_gen` = "Risk\navoidance",
         `inc` = "Income",
         `age` = "Age",
         `male` = "Male")) %>% 
  rename(beta = est.std)

(p_main_items <- ggplot(d_main_items, aes(x = beta, y = lhs)) +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -0.1, linetype = "dashed", color = "grey") +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper, height = .2)) + 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_x_continuous(breaks = seq(-.7, .7, .2)) +
  facet_grid(~ rhs))
```

\newpage
# Additional analyses
## Big five

```{r}
d_tmp <- dplyr::select(d, BFI_1 : BFI_10)
name_tmp <- "BFI"

ggplot(d_tmp %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)
```

\newpage
### Correlations

```{r}
cor(d_tmp, use = "pairwise.complete.obs")
```

The dimensions show low correlations; as a result, we will use only 1 item (the one which is not inverted), to measure each dimension. This includes the following items:

* BFI_2, BFI_3, BFI_5, BFI_8, BFI_9

```{r save-workspace}
# remove large objects
remove(d_imp_multi, d_incl_susp, fit, init)
# save workspace so that manuscript can be reproduced without rerunning analyses
save.image("../data/workspace.RData")
```

### 2018-12-09 results/archive/analyses_2018-11-21_before filtering.RmD
- major updates on everything:     - mostly finished the analyses     - rewritten the methods, results, and abstract

--- 2018-11-13 src/analyses.RmD
@@
 # list packages to be used
-packages <- c("devtools", "lavaan", "MBESS", "magrittr", "psych", "semPlot", "tidyverse")
+packages <- c("devtools", "ggplot2", "influence.SEM", "lavaan", "MBESS", 
+              "magrittr", "PerFit", "psych", "semPlot", "tidyverse")
 
@@
 
-# recode
-d <- d %>% 
-  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.)))
+# edit variables
+d %<>% 
+  mutate(
+    male = 2 - SES.SEX,
+    time = V9 - V8,
+    id = 1:nrow(.)
+    ) %>% 
+  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.))) %>% 
+  rename(
+    age = SES.AGE,
+    inc = SES.JOB_2
+  )
+
+# select items
+d %<>% dplyr::select(
+  id, male, age, inc, time,
+  starts_with("N4P"),
+  starts_with("INT_"),
+  SOC_1 : SOC_8,
+  starts_with("FEA_"),
+  TRA_1 : TRA_8,
+  RIT_1 : RIT_8,
+  BFI_1 : BFI_10
+)
+items <- names(d)
+```
+
+# Data wrangling
+## Delete defective data
+
+First, we checked response times to delete inconceivably fast respondents.
+
+```{r}
+# plot reponse times
+qplot(d$time)
+
+# filter speeders (i.e., t < 180s)
+d_all <- d
+d <- d[d$time > 120, ]
+
+# filter defective data
+lzpoly <- lzpoly(dplyr::select(d, N4P.BOT_1:RIT_8) - 1, 7)
+gpoly <- Gnormed.poly(dplyr::select(d, N4P.BOT_1:RIT_8) - 1, 7) %$% 
+  PFscores %>% 
+  mutate(id = d$id) %>% 
+  arrange(PFscores)
+
+# inspect cases with susceptive data
+d[PFscores > .30, ]
 ```
@@
 ```{r, fig.height=15, fig.width=12}
-d_tmp <- select(d, starts_with("N4P"))
+d_tmp <- dplyr::select(d, starts_with("N4P"))
 name_tmp <- "pri_nee"
@@
 d[recoded_tmp] <- 8 - d[recoded_tmp]
-d_tmp <- select(d, starts_with("N4P"))  # new selection bc of recoding
+d_tmp <- dplyr::select(d, starts_with("N4P"))  # new selection bc of recoding
 ```
@@
 ```{r}
-tmp <- omega(select(d_tmp, 
+tmp <- omega(dplyr::select(d_tmp, 
                     -N4P.BOT_4, -N4P.BOT_3, -N4P.SOC_7, -N4P.INT_5, -N4P.INT_3), 
@@
 ```{r}
-tmp <- omega(select(d_tmp,
+tmp <- omega(dplyr::select(d_tmp,
                     -N4P.BOT_4, -N4P.BOT_3, -N4P.INT_5, -N4P.INT_3, -N4P.INT_7, -N4P.INT_4), 
@@
 ```{r, fig.height=8, fig.width=12}
-d_tmp <- select(d, starts_with("INT_"))
+d_tmp <- dplyr::select(d, starts_with("INT_"))
 name_tmp <- "int"
@@
 
-# recode
-d[recoded_tmp] <- 8 - d[recoded_tmp]
-d_tmp <- select(d, starts_with("INT_"))  # new selection bc of recoding
+d[recoded_tmp] <- 8 - d[recoded_tmp]  # recode
+d_tmp <- dplyr::select(d, starts_with("INT_"))  # new selection bc of recoding
 ```
@@
 ```{r}
-tmp <- omega(select(d_tmp, -INT_3, -INT_4), fm = "ml", nfactors = 2)
+tmp <- omega(dplyr::select(d_tmp, -INT_3, -INT_4), fm = "ml", nfactors = 2)
 ```
@@
 assign(paste0(name_tmp, "_gen"), 
-       select(as.data.frame(predict(fit)), ends_with("_gen")))
+       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
 ```
@@
 ```{r, fig.height=8, fig.width=12}
-d_tmp <- select(d, SOC_1 : SOC_8)
+d_tmp <- dplyr::select(d, SOC_1 : SOC_8)
 name_tmp <- "soc"
@@
 d[recoded_tmp] <- 8 - d[recoded_tmp]
-d_tmp <- select(d, SOC_1 : SOC_8)  # new selection bc of recoding
+d_tmp <- dplyr::select(d, SOC_1 : SOC_8)  # new selection bc of recoding
 ```
@@
 ```{r}
-d_tmp <- select(d, starts_with("FEA_"))
+d_tmp <- dplyr::select(d, starts_with("FEA_"))
 name_tmp <- "fea"
@@
 d[recoded_tmp] <- 8 - d[recoded_tmp]
-d_tmp <- select(d, starts_with("FEA_"))  # new selection bc of recoding
+d_tmp <- dplyr::select(d, starts_with("FEA_"))  # new selection bc of recoding
 ```
@@
 ```{r}
-d_tmp <- select(d, TRA_1 : TRA_8)
+d_tmp <- dplyr::select(d, TRA_1 : TRA_8)
 name_tmp <- "tra"
@@
 d[recoded_tmp] <- 8 - d[recoded_tmp]
-d_tmp <- select(d, TRA_1 : TRA_8)  # new selection bc of recoding
+d_tmp <- dplyr::select(d, TRA_1 : TRA_8)  # new selection bc of recoding
 ```
@@
 ```{r}
-d_tmp <- select(d, RIT_1 : RIT_8)
+d_tmp <- dplyr::select(d, RIT_1 : RIT_8)
 name_tmp <- "rit"
@@
 d[recoded_tmp] <- 8 - d[recoded_tmp]
-d_tmp <- select(d, RIT_1 : RIT_8)  # new selection bc of recoding
+d_tmp <- dplyr::select(d, RIT_1 : RIT_8)  # new selection bc of recoding
 ```
@@
 ```{r}
-d_tmp <- select(d, BFI_1 : BFI_10)
+d_tmp <- dplyr::select(d, BFI_1 : BFI_10)
 name_tmp <- "BFI"
@@
 
-  pri_nee_gen ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen
-  pri_nee_ver ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen
-  pri_nee_ide ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen
-  pri_nee_hor ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen
+  pri_nee_gen ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
+  pri_nee_ver ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
+  pri_nee_ide ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
+  pri_nee_hor ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
 
@@
 '
-fit <- sem(model, d, missing = "ml")
+fit <- sem(model, d, estimator = "MLR")
 summary(fit, fit = TRUE, std = TRUE)
+fit_rem_outlier <- sem(model, filter(d, cooks_dist < 3), estimator = "MLR")
+summary(fit_rem_outlier, fit = TRUE, std = TRUE)
 assign(paste0(name_tmp, "_fit"), cfa(model, d))
+d$cooks_dist <- cooks_dist
+genCookDist(model, d, estimator = "MLR")
 ```
 
+# Visualization
+
+```{r}
+# calculate CI for standardized effect 
+# option 1: proper option, calculates extract bootstrapped coefficients for standardized solution
+# CURRENTLY DOESN'T WORK
+# d_effects <- bootstrapLavaan(main_fit)
+
+# option 2: use SEs of standardized solution
+d_effects <- standardizedsolution(main_fit) %>% 
+  as.data.frame() %>% 
+  filter(op == "~") %>% 
+  mutate(lhs = factor(lhs, c("pri_nee_gen", "pri_nee_ver", "pri_nee_hor", "pri_nee_ide"))) %>%  # reorder for plot
+  mutate(rhs = factor(rhs, c("inc", "age", "male", "rit_gen", "tra_gen", "fea_gen", "soc_gen", "int_gen"))) %>%  # reorder for plot
+  mutate(lhs = recode(lhs, 
+         `pri_nee_gen` = "Privacy need\ngeneral", 
+         `pri_nee_ver` = "Privacy need\ngovernment",
+         `pri_nee_hor` = "Privacy need\ninterpersonal",
+         `pri_nee_ide` = "Privacy need\nanonymity")) %>% 
+  mutate(rhs = recode(rhs,
+         `int_gen` = "Integrity",
+         `soc_gen` = "Sociability",
+         `fea_gen` = "Anxiety",
+         `tra_gen` = "Traditionalism",
+         `rit_gen` = "Risk avoidance",
+         `inc` = "Income",
+         `age` = "Age",
+         `male` = "Male")) %>% 
+  rename(beta = est.std)
+
+# prior solution
+# d_effects <- coeffs_tab(main_fit) %>%
+#   mutate(sig = ifelse(p < .05, "1", "0"))
+
+(p_effects <- ggplot(d_effects, aes(x = beta, y = rhs)) +
+  geom_point() +
+  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper, height = .2)) + 
+#  scale_color_manual(values = c("#000000", "#FF0000")) +
+  geom_vline(xintercept = 0) +
+  geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +
+  geom_vline(xintercept = -0.1, linetype = "dashed", color = "grey") +
+  theme_bw() + 
+  theme(axis.title = element_blank()) +
+  scale_x_continuous(breaks = seq(-.7, .7, .2)) +
+  facet_grid(~ lhs))
+```
+
+# Additional Analyses
 ## With big five
@@
 ```
-
-# Visualization
-
-```{r}
-d_effects <- coeffs_tab(main_fit) %>%
-  mutate(sig = ifelse(p < .05, "1", "0"))
-
-std_ci <- ci.src(beta.k = d_effects$beta, b.k = d_effects$b, 
-                 N = 400, conf.level = .95, SE.b.k = .10, s.Y = sqrt(.955), )
-
-p_effects <- ggplot(d_effects, aes(x = beta)) +
-  geom_point(aes(y = Predictor, color = sig)) +
-  scale_color_manual(values = c("#000000", "#FF0000")) +
-  geom_vline(xintercept = 0) +
-  geom_vline(xintercept = 0.1, linetype = "dashed") +
-  geom_vline(xintercept = -0.1, linetype = "dashed") +
-  theme_bw() + 
-  facet_grid(~ Outcome)
-```

### 2018-12-19 results/analyses.RmD
- slight changes

@@
 d %<>% 
+  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.))) %>% 
+  mutate_at(vars(V8, V9), funs(parse_datetime(., c("%d.%m.%Y %H:%M")))) %>% 
   mutate(
@@
     ) %>% 
-  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.))) %>% 
   rename(

### 2019-02-12 analyses/analyses.RmD
- Major changes regarding everything: analyses (e.g., inclusion of bifactor models), ms, etc.

---
title: "Who Needs Privacy?"
subtitle: "Analyses"
output:
  pdf_document: 
    toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=F, error=F, message=F, # cache = T, 
                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
options(digits = 3, width = 100)
```

```{r r-setup, include=F}
# define packages
packages <- c("corrplot", "devtools", "GGally", "ggplot2", "kableExtra", "knitr", 
              "lavaan", "magrittr", "mice", "MVN", "PerFit", "psych", 
              "pwr", "semPlot", "semTools", "tidyverse", "td")

# install packages
# devtools::install_github("https://github.com/tdienlin/td")

# load packages
lapply(packages, library, character.only = TRUE)
```

```{r data-wrangling, include=F}
# read data
# note: a bit complicated, as second row contains variable attributes
d <- read_csv("../data/data.csv", skip = 2, col_names = FALSE) %>% 
  set_names(colnames(read_csv("../data/data.csv", n_max = 1)))

# prepare table with item content
items <- data.frame(
  name = colnames(read_csv("../data/data.csv", n_max = 1)),  # extract item names
  content = colnames(read_csv("../data/data.csv", skip = 1, n_max = 2))  # extract item content
) %>% 
  mutate(content = gsub("To what extent do you agree or disagree with the following / statements[?][-]", "", content)) %>% 
  mutate(content = gsub("To what extent do you agree or disagree with the / following statements[?][-]", "", content)) %>% 
  mutate(content_breaks = sapply(content, string_break, 30))

# edit variables
d %<>% 
  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.))) %>% 
  mutate_at(vars(V8, V9), funs(parse_datetime(., c("%d.%m.%Y %H:%M")))) %>% 
  mutate(
    male = 2 - SES.SEX,
    time = V9 - V8,
    id = 1:nrow(.)
    ) %>% 
  rename(
    age = SES.AGE,
    inc = SES.JOB_2
  )

# select items
d %<>% dplyr::select(
  id, male, age, inc, time,
  starts_with("N4P"),
  starts_with("INT_"),
  SOC_1 : SOC_8,
  starts_with("FEA_"),
  TRA_1 : TRA_8,
  RIT_1 : RIT_8,
  BFI_1 : BFI_10
)

# count no of missing responses
d$miss_per <- apply(d, 1, function(x) (sum(is.na(x)))) %>% 
  divide_by(ncol(d))

# recode inverted items
# make dataframe of not inverted items (needed for plotting distributions)
d_noninvert <- d

# define inverted items
recoded <- c("N4P.INT_1", "N4P.INT_5", "N4P.INT_8",
             "INT_1", "INT_2", "INT_5", "INT_6", "INT_7", 
                 "INT_8", "INT_9", "INT_10", "INT_11",
             "SOC_1", "SOC_3", "SOC_5", "SOC_7",
             "FEA_1", "FEA_3", "FEA_5", "FEA_7",
             "RIT_1", "RIT_3", "RIT_5",
             "TRA_2", "TRA_4", "TRA_6")

# recode items
d[recoded] <- 8 - d[recoded]
```

\newpage
# Data wrangling
## Filter defective data
### Empty/missing data

```{r}
n_d_all <- nrow(d)

# show percentage of missing data
table(d$miss_per) %>% round(2)

# delete respondents with more than 50% missing data
d_missing <- d[d$miss_per > .5, ]
n_d_missing <- nrow(d_missing)
d <- d[!(d$id %in% d_missing$id), ]

# filter participant with illogial age
d %<>% filter(age != 9 | is.na(age))

# estimate overall percentage of missing data
na_perc <- mean(d$miss_per)

# impute missing data
init <- mice(d, maxit = 0) 
vars_excl <- c("id", "time", "miss_per")
pred_ma <- init$predictorMatrix
pred_ma[, vars_excl] <- 0
d_imp <- mice(d, method = "pmm", m = 1, maxit = 30, predictorMatrix = pred_ma, 
              seed = 180719, print = FALSE)
d <- mice::complete(d_imp)
```

Shows that most people answered all questions. There were 15 empty data sets, and some with more than 50% missing data. These were deleted. Overall, there was just `r na_perc` missing data.

### Speeder

```{r speeder, warning=F}
# plot reponse times
qplot(d$time)
```

Shows that some participants took very long to answer. Inspect regular times.

```{r}
qplot(d$time[d$time < 5000])
```

Distribution looks okay (no early peak). Also no answers faster than 5 mins.

### Response Styles

```{r}
# make backup with data including suspicious patterns
d_incl_susp <- d

# make matrixes of variables
d_pri_nee <- dplyr::select(d, starts_with("N4P"))
d_pri_nee_noninvert <- dplyr::select(d_noninvert, starts_with("N4P"))
d_int <- dplyr::select(d, starts_with("INT_"))
d_int_noninvert <- dplyr::select(d_noninvert, starts_with("INT_"))
d_soc <- dplyr::select(d, SOC_1 : SOC_8)
d_soc_noninvert <- dplyr::select(d_noninvert, SOC_1 : SOC_8)
d_fea <- dplyr::select(d, starts_with("FEA_"))
d_fea_noninvert <- dplyr::select(d_noninvert, starts_with("FEA_"))
d_rit <- dplyr::select(d, RIT_1 : RIT_8)
d_rit_noninvert <- dplyr::select(d_noninvert, RIT_1 : RIT_8)
d_tra <- dplyr::select(d, TRA_1 : TRA_8)
d_tra_noninvert <- dplyr::select(d_noninvert, TRA_1 : TRA_8)

# run guttman tests
d_vars <- list(d_pri_nee, d_int, d_soc, d_fea, d_rit, d_tra)
d_guttman_scores <- lapply(d_vars, function(x) Gnormed.poly(x - 1, 7) %$% 
  PFscores %>% 
  unlist()) %>% 
  as.data.frame() %>% 
  mutate(mean = apply(., 1, mean))
d$guttman <- d_guttman_scores$mean
ggplot(d_guttman_scores, aes(x = mean)) + 
  geom_histogram()

# inspect cases with susceptive data
# guttman_crit <- quantile(d$guttman, probs = .95)  # relative 5% criterion
guttman_crit <- .30  # absolute .25 criterion (cf. histogram)
d_suspicious <- d[d$guttman > guttman_crit, ] %>% 
  arrange(desc(guttman))

# remove cases
d <- d[d$guttman < guttman_crit, ]

# count cases
n_d_suspicious <- nrow(d_suspicious)
n_d_defect <- n_d_all - n_d_empty - nrow(d)
n_d <- nrow(d)

# make matrixes of variables (bc. of removed participants)
d_pri_nee <- dplyr::select(d, starts_with("N4P"))
d_pri_nee_noninvert <- dplyr::select(d_noninvert, starts_with("N4P"))
d_int <- dplyr::select(d, starts_with("INT_"))
d_int_noninvert <- dplyr::select(d_noninvert, starts_with("INT_"))
d_soc <- dplyr::select(d, SOC_1 : SOC_8)
d_soc_noninvert <- dplyr::select(d_noninvert, SOC_1 : SOC_8)
d_fea <- dplyr::select(d, starts_with("FEA_"))
d_fea_noninvert <- dplyr::select(d_noninvert, starts_with("FEA_"))
d_rit <- dplyr::select(d, RIT_1 : RIT_8)
d_rit_noninvert <- dplyr::select(d_noninvert, RIT_1 : RIT_8)
d_tra <- dplyr::select(d, TRA_1 : TRA_8)
d_tra_noninvert <- dplyr::select(d_noninvert, TRA_1 : TRA_8)
```

Only few participants seem to have particularly atypical data. Will filter respondents with m > .30. All of the 5% cases indeed show extreme response patterns and/or illogical data. Will be filtered.

\newpage
# Power Analyses

```{r}
(power_analysis <- pwr.r.test(n = n_d, r = .1, sig.level = .05))
power_small <- power_analysis$power %>% multiply_by(100) %>% round(0)

(power_analysis <- pwr.r.test(n = n_d, r = .2, sig.level = .05))
power_smallmoderate <- power_analysis$power %>% multiply_by(100) %>% round(0)

(sensitivity_analysis <- pwr.r.test(n = n_d, sig.level = .05, power = .95))
sensitivity_95 <- sensitivity_analysis$r %>% round(2)

(sample_analysis <- pwr.r.test(sig.level = .05, power = .95, r = .1))
sample_95 <-  sample_analysis$n %>% round(0)
```

\newpage
# Multivariate normal distribution

```{r}
d_tmp <- dplyr::select(d, -id, -male, -age, -inc, -time, -miss_per, -starts_with("BFI"))
(mult_norm <- mvn(data = d_tmp, mvnTest = "mardia")$multivariateNormality %>% 
    as.data.frame() %>% 
    mutate_at(vars(Statistic, "p value"), funs(as.numeric(levels(.))[.])) %>% 
    filter(Test != "MVN")
  )
```

\newpage
# Measures
## Need for Privacy

```{r, fig.height=15, fig.width=12}
d_tmp <- d_pri_nee
d_tmp_noninvert <- d_pri_nee_noninvert
name_tmp <- "pri_nee"
```

### Items

```{r, fig.height=15, fig.width=12}
ggplot(d_tmp_noninvert %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc) 
```

\newpage
### Correlation table

```{r, fig.height=15, fig.width=12}
corr_tmp <- cor(d_tmp)
corrplot(corr_tmp, type = "upper", method = "color",
         tl.col = "black")
```

### Kaiser-Meyer-Oltkin criterion

The Kaiser-Meyer-Oltkin criterion measures the extent to which items are suitable for being combined as a single factor.

```{r}
(kmo <- KMO(d_tmp))
items_excl <- names(kmo$MSAi[kmo$MSAi < .65])
```

On the basis of the KMO, the following items should be exluded: `r names(kmo$MSAi[kmo$MSAi < .7])`.

\newpage
### Parallel analysis

```{r}
d_tmp <- dplyr::select(d_tmp, -items_excl)
fa.parallel(d_tmp)
```

\newpage
### EFA

```{r}
fa(r = d_tmp, nfactors = 3, fm = "oblimin")
```

Three latent factors emerge:

- factor 1 measures need for privacy from the government (vertical)
- factor 2 measures need for privacy from other people (horizontal)
- factor 3 can be described as desire for anonymity (combined)

The following items overall contribute little:

- Communalities reveal that item INT_4 and INT_8 don't load sufficiently strong on latent factors. Should be excluded.
- Item INT_1 only loads negative on factor 3 -- little positive contribution

The following items show double-loadings:

- BOT_3, BOT_4, INT_2, INT_6. Will be difficult to decide whether to maintain or delete.

\newpage

```{r}
d_tmp <- dplyr::select(d_tmp, -c("N4P.INT_1", "N4P.INT_4", "N4P.INT_8")) # -N4P.INT_2 -N4P.INT_6, -N4P.INT_7, -N4P.BOT_2, -N4P.INT_4
fa(r = d_tmp, nfactors = 3, fm = "oblimin")
```

\newpage
### CFA 1

```{r}
model <- '
  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_5 + N4P.SOC_9
  pri_nee_int =~ N4P.BOT_1 + N4P.BOT_2 + N4P.BOT_3 + N4P.BOT_4 + N4P.INT_2 + N4P.INT_3 + N4P.INT_6 + N4P.INT_7 + N4P.INT_9
  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2 + N4P.INT_6
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
```

Does not yield good results. Inspect modification indices.

```{r}
modificationindices(fit, minimum.value = 10, sort. = TRUE)
```

As expected, items BOT_2, BOT_3, & BOT_4 cause trouble. Will delete.

\newpage
### CFA 2

```{r}
model <- '
  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_5 + N4P.SOC_9
  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_3 + N4P.INT_6 + N4P.INT_7 + N4P.INT_9
  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2 + N4P.INT_6
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
```

Shows acceptable fit. Problem is, we don't want to exclude too many items and to overfit the data. Let's inspect modification indices once more to see if there's a theoretically plausible adaption.

```{r}
modificationindices(fit, minimum.value = 10, sort. = TRUE)
```

Item INT_3 is a troublemaker. As it's an inverted item, we have a good reason to delete it. Also, item INT_6 doesn't really have anything to do with anonymity; we can delete it. Likewise, item SOC_5 loads on government, while it also measure anonymity. Maybe delete.

\newpage
### CFA 3

```{r}
model <- '
  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9
  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_lat"), as.data.frame(predict(fit)))
```

Shows a satisfactory, but not ideal solution. Try bifactor next.

\newpage
### CFA bifactor

```{r}
model <- '
  pri_nee_gen =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9 + N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9 + N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9
  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
'
fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_bifactor_fit"), fit)
```

Bifactor-solution fits the data best.

\newpage
### CFA privacy need government

```{r}
model <- '
  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
  '
fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_gov_fit"), fit)
```

\newpage
### CFA privacy need interpersonal

```{r}
model <- '
  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9
'
fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_int_fit"), fit)
```

\newpage
### CFA privacy need anonymity

```{r}
model <- '
  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
'
fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_ano_fit"), fit)
```

\newpage
## Sociability

```{r}
d_tmp <- d_soc
d_tmp_noninvert <- d_soc_noninvert
name_tmp <- "soc"
```

### Items

```{r, fig.height=8, fig.width=12}
p_int <- ggplot(d_tmp_noninvert %>% 
                  gather(name, value) %>% 
                  left_join(items, "name"),
                  aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)
p_int

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc)
```

\newpage
### Parallel analysis

```{r}
fa.parallel(d_tmp, fm = "ml")
```

\newpage
### EFA 1

```{r}
fa(d_tmp, fm = "ml", nfactors = 3)
```

\newpage
### EFA 2

```{r}
fa(d_tmp, fm = "ml", nfactors = 2)
```

\newpage
### CFA 1

```{r}
model <- '
  soc_1 =~ a*SOC_1 + a*SOC_3 + a*SOC_5 + a*SOC_7
  soc_2 =~ b*SOC_1 + b*SOC_2 + b*SOC_4 + b*SOC_6 + b*SOC_7 + b*SOC_8
  soc_gen =~ SOC_1 + SOC_2 + SOC_3 + SOC_4 + SOC_5 + SOC_6 + SOC_7 + SOC_8
'
fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
summary(fit, fit = TRUE, std = TRUE)
```

Shows no solution for two factors.

\newpage
### CFA 2

```{r}
model <- '
  soc_gen =~ SOC_1 + SOC_2 + SOC_4 + SOC_6 + SOC_7 + SOC_8
'
fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
summary(fit, fit = TRUE, std = TRUE)
```

Uni-dimensional solution with 6 items not feasible; need to reduce to 4.

\newpage
### CFA 3

```{r}
model <- '
  soc_gen =~ SOC_1 + SOC_2 + SOC_7 + SOC_8
'
fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

Shows adequate fit.

```{r}
# Extract error variance
rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
err_var <- (1 - rel) * var
assign(paste0(name_tmp, "_err_var"), err_var)
```

\newpage
## Anxiety

```{r}
d_tmp <- d_fea
d_tmp_noninvert <- d_fea_noninvert
name_tmp <- "fea"
```

### Items

```{r}
ggplot(d_tmp_noninvert %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc) 
```

### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

Implies one dimension.

\newpage
### CFA 1

```{r}
model <- '
  fea_gen =~ FEA_2 + FEA_4 + FEA_7 + FEA_8 + FEA_1 + FEA_3 + FEA_5 + FEA_6
'
fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
summary(fit, fit = TRUE, std = TRUE)
```

Doesn't fit. Instead, try two dimensions.

\newpage
### EFA

```{r}
fa(d_tmp, nfactors = 2, fm = "ml")
tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
```

Seems appropriate.

\newpage
### CFA 2

```{r}
model <- '
  fea_1 =~ a*FEA_2 + a*FEA_4 + a*FEA_6 + a*FEA_8
  fea_2 =~ b*FEA_1 + b*FEA_3 + b*FEA_5 + b*FEA_7
  fea_gen =~ FEA_2 + FEA_4 + FEA_7 + FEA_8 + FEA_1 + FEA_3 + FEA_5 + FEA_6
'
fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

Shows an adequate solution.

```{r}
# Extract error variance
rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
err_var <- (1 - rel) * var
assign(paste0(name_tmp, "_err_var"), err_var)
```

\newpage
## Risk Avoidance

```{r}
d_tmp <- d_rit
d_tmp_noninvert <- d_rit_noninvert
name_tmp <- "rit"
```

### Items

```{r}
ggplot(d_tmp_noninvert %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc)
```

\newpage
### Parallel analysis

```{r}
fa.parallel(d_tmp)
```

\newpage
### EFA

```{r}
fa(d_tmp, nfactors = 2, fm = "ml")
tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
```

Produces a fitting solution.

\newpage
### CFA 1

```{r}
model <- '
  rit_1 =~ a*RIT_2 + a*RIT_4 + RIT_5 + a*RIT_6 + a*RIT_7 + a*RIT_8
  rit_2 =~ RIT_1 + RIT_3 + RIT_5
  rit_gen =~ RIT_1 + RIT_2 + RIT_3 + RIT_4 + RIT_5 + RIT_6 + RIT_7 + RIT_8
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

Does not produce a good-fitting model.

\newpage
### CFA 2

```{r}
model <- '
  rit_gen =~ RIT_2 + RIT_4 + RIT_6 + RIT_7 + RIT_8
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

```{r}
# Extract error variance
rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
err_var <- (1 - rel) * var
assign(paste0(name_tmp, "_err_var"), err_var)
```

\newpage 
## Traditionalism

```{r}
d_tmp <- d_tra
d_tmp_noninvert <- d_tra_noninvert
name_tmp <- "tra"
```

### Items

```{r}
ggplot(d_tmp_noninvert %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc)
```

\newpage
### Parallel analysis

```{r}
fa.parallel(d_tmp, fm = "ml")
```

\newpage
### EFA

```{r}
fa(d_tmp, nfactors = 2, fm = "ml")
tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
```

Implies a single dimension, as on factor 2 there is only one significant loading.

\newpage
### CFA

```{r}
model <- '
  tra_gen =~ TRA_1 + TRA_5 + TRA_3 + TRA_8 + TRA_7
'
fit <- cfa(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

Shows adequate fit.

```{r}
# Extract error variance
rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
err_var <- (1 - rel) * var
assign(paste0(name_tmp, "_err_var"), err_var)
```

\newpage
## Integrity

```{r, fig.height=8, fig.width=12}
d_tmp <- d_int
d_tmp_noninvert <- d_int_noninvert
name_tmp <- "int"
```

### Items

```{r, fig.height=8, fig.width=12}
ggplot(d_tmp_noninvert %>% 
         gather(name, value) %>% 
         left_join(items, "name"),
         aes(x = value)) +
  geom_bar() +
  facet_wrap(~content_breaks)

# extract mean and sd
desc <- data.frame(
  m = mean(unlist(d_tmp), na.rm = TRUE),
  sd = sd(unlist(d_tmp), na.rm = TRUE)
)
assign(paste0(name_tmp, "_desc"), desc)
```

\newpage
### Parallel analysis

```{r}
fa.parallel(d_tmp, fm = "ml")
```

\newpage
### EFA

```{r}
fa(d_tmp, nfactors = 3, fm = "ml")
```

Two factors don't really convince, as factor 3 consists of one item only. Will try two-factor solution.

```{r}
fa(d_tmp, nfactors = 2, fm = "ml")
```

Implies that item 3 and item 4 should be dropped.

\newpage
### CFA

```{r}
model <- '
  int_1 =~ a*INT_1 + a*INT_2 + a*INT_5 + a*INT_6 + a*INT_7 + a*INT_8
  int_2 =~ b*INT_8 + b*INT_9 + b*INT_10 + b*INT_11
  int_gen =~ INT_1 + INT_2 + INT_5 + INT_6 + INT_7 + INT_8 + INT_9 + INT_10 + INT_11
'
fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
assign(paste0(name_tmp, "_gen"), as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
```

Bifactor model fits the date well.

```{r}
# Extract error variance
# For the models testing the hypotheses, we next calculate the measures' error variance. The error variance will be included in the final model, enabling a better estimation of the effects.
rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
err_var <- (1 - rel) * var
assign(paste0(name_tmp, "_err_var"), err_var)
```

\newpage
# Results

```{r}
# combine model predicted values with regular data
d_lat <- cbind(soc_gen, int_gen, fea_gen, rit_gen, tra_gen, pri_nee_lat)
d <- cbind(d, d_lat)

# combine error variances in table
err_vars <- cbind(int_err_var, soc_err_var, fea_err_var, tra_err_var, rit_err_var)

# define and run model
name_tmp <- "results_threefactors"
model <- '
  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9
  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
  soc =~ soc_gen
  fea =~ fea_gen
  tra =~ tra_gen
  rit =~ rit_gen
  int =~ int_gen

  pri_nee_gov ~ soc + int + fea + tra + rit + male + age + inc
  pri_nee_int ~ soc + int + fea + tra + rit + male + age + inc
  pri_nee_ano ~ soc + int + fea + tra + rit + male + age + inc

  soc_gen ~~ .177 * soc_gen
  int_gen ~~ .104 * int_gen
  fea_gen ~~ .106 * fea_gen
  tra_gen ~~ .169 * tra_gen
  rit_gen ~~ .118 * rit_gen
'
fit <- sem(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
```

\newpage
# Tables
## Items measuring need for privacy

```{r}
# fig.pos="h"
# get names of included items
items_incl <- colnames(inspect(results_threefactors_fit, 'sampstat')$cov)
pri_nee_gov_items <- parameterestimates(results_threefactors_fit) %>% 
  filter(lhs == "pri_nee_gov", op == "=~") %>% 
  select(rhs) %>% 
  unlist()
pri_nee_int_items <- parameterestimates(results_threefactors_fit) %>% 
  filter(lhs == "pri_nee_int", op == "=~") %>% 
  select(rhs) %>% 
  unlist()
pri_nee_ano_items <- parameterestimates(results_threefactors_fit) %>% 
  filter(lhs == "pri_nee_ano", op == "=~") %>% 
  select(rhs) %>% 
  unlist()

t_pri_nee <- items %>% 
  filter(grepl("N4P", name)) %>% 
  mutate(name = factor(name, c(paste0("N4P.BOT_", rep(4:1)),
                             paste0("N4P.INT_", rep(9:1)),
                             paste0("N4P.SOC_", rep(9:1))))) %>% 
  mutate(included = ifelse(name %in% items_incl, "yes", "no")) %>% 
  arrange(desc(as.numeric(name))) %>% 
  dplyr::select(name, included, content)

knitr::kable(t_pri_nee) %>% 
  kableExtra::column_spec(3, width = "10cm") %>% 
  kableExtra::kable_styling(latex_options="scale_down", font_size = 7)
```

\newpage
## Psychometrics

```{r}
t_facval <- rbind(
  "(Combined)" = fit_tab(pri_nee_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Government" = fit_tab(pri_nee_gov_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Interpersonal" = fit_tab(pri_nee_int_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Anonymity" = fit_tab(pri_nee_ano_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Sociability" = fit_tab(soc_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Integrity" = fit_tab(int_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Anxiety" = fit_tab(fea_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Risk aversion" = fit_tab(rit_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
  "Traditionality" = fit_tab(tra_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE)
)

pri_nee_gov_desc <- c(mean = mean(as.matrix(d[pri_nee_gov_items])),
                      sd = sd(as.matrix(d[pri_nee_gov_items])))
pri_nee_int_desc <- c(mean = mean(as.matrix(d[pri_nee_int_items])),
                      sd = sd(as.matrix(d[pri_nee_int_items])))
pri_nee_ano_desc <- c(mean = mean(as.matrix(d[pri_nee_ano_items])),
                      sd = sd(as.matrix(d[pri_nee_ano_items])))

t_desc <- rbind(pri_nee_desc, pri_nee_gov_desc, pri_nee_int_desc, pri_nee_ano_desc,
                soc_desc, int_desc, fea_desc, rit_desc, tra_desc)

t_psyc <- cbind(t_desc, t_facval)
kable(t_psyc)
```

\newpage
## Results

```{r}
t_results_threefactors <- coeffs_tab(results_threefactors_fit, as_text = TRUE) %>% 
   mutate(Outcome = recode(Outcome, 
         `pri_nee_gov` = "Privacy need government",
         `pri_nee_int` = "Privacy need interpersonal",
         `pri_nee_ano` = "Privacy need anonymity")) %>% 
  mutate(Predictor = recode(Predictor,
         `int` = "Integrity",
         `soc` = "Sociability",
         `fea` = "Anxiety",
         `rit` = "Risk avoidance",
         `tra` = "Traditionalism",
         `inc` = "Income",
         `age` = "Age",
         `male` = "Male"))
kable(t_results_threefactors)
```

\newpage
# Figures
## Bivariate relations

```{r eval = F}
d_lat %<>% set_names("Sociability", "Integrity", "Anxiety", "Risk\navoidance", "Traditio-\nnalism", "Privacy need\ngovernment", "Privacy need\ninterpersonal", "Privacy need\nanonymity")

p_bivar <- ggpairs(
  d_lat,
  upper = list(continuous = "cor"),
  lower = list(continuous = scat_plot)) +
  theme_bw()
print(p_bivar)
```

## Results

```{r}
# calculate CI for standardized effect 
d_results_threefactors <- standardizedsolution(results_threefactors_fit) %>% 
  as.data.frame() %>% 
  filter(op == "~") %>% 
  mutate(lhs = factor(lhs, c("pri_nee_ano", "pri_nee_int", "pri_nee_gov"))) %>%  # reorder for plot
  mutate(rhs = factor(rhs, c("int", "soc", "fea", "rit", "tra", "male", "age", "inc"))) %>%  # reorder for plot
  mutate(lhs = recode(lhs, 
         `pri_nee_gov` = "Privacy need\ngovernment",
         `pri_nee_int` = "Privacy need\ninterpersonal",
         `pri_nee_ano` = "Privacy need\nanonymity")) %>% 
  mutate(rhs = recode(rhs,
         `int` = "Integrity",
         `soc` = "Sociability",
         `fea` = "Anxiety",
         `tra` = "Traditio-\nnalism",
         `rit` = "Risk\navoidance",
         `inc` = "Income",
         `age` = "Age",
         `male` = "Male")) %>% 
  rename(beta = est.std)

(p_results_threefactors <- ggplot(d_results_threefactors, aes(x = beta, y = lhs)) +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -0.1, linetype = "dashed", color = "grey") +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper, height = .2)) + 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_x_continuous(breaks = c(-.4, -.2, 0, .2, .4)) +
  coord_cartesian(xlim = c(-.5, .5)) +
  facet_grid(~ rhs))
```

\newpage
# Additional analyses
## Bi-Factor

```{r}
name_tmp <- "results_bifactor"
model <- '
  pri_nee_gen =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9 + N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9 + N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9
  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2

  int =~ int_gen
  soc =~ soc_gen
  fea =~ fea_gen
  tra =~ tra_gen
  rit =~ rit_gen

  pri_nee_gen ~ int + soc + fea + tra + rit + male + age + inc
  pri_nee_gov ~ int + soc + fea + tra + rit + male + age + inc
  pri_nee_int ~ int + soc + fea + tra + rit + male + age + inc
  pri_nee_ano ~ int + soc + fea + tra + rit + male + age + inc

  pri_nee_gen ~~ 0*pri_nee_gov + 0*pri_nee_int + 0*pri_nee_ano
  pri_nee_gov ~~ 0*pri_nee_int + 0*pri_nee_ano
  pri_nee_int ~~ 0*pri_nee_ano

  int_gen ~~ .104 * int_gen
  soc_gen ~~ .177 * soc_gen
  fea_gen ~~ .106 * fea_gen
  tra_gen ~~ .169 * tra_gen
  rit_gen ~~ .118 * rit_gen
'
fit <- sem(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE, rsquare = TRUE)
assign(paste0(name_tmp, "_fit"), fit)
```

\newpage

```{r}
# calculate CI for standardized effect
d_results_bifactor <- standardizedsolution(results_bifactor_fit) %>%
  as.data.frame() %>%
  filter(op == "~") %>%
  mutate(lhs = factor(lhs, c("pri_nee_ano", "pri_nee_int", "pri_nee_gov", "pri_nee_gen"))) %>%  # reorder for plot
  mutate(rhs = factor(rhs, c("int", "soc", "fea", "rit", "tra", "male", "age", "inc"))) %>%  # reorder for plot
  mutate(lhs = recode(lhs,
         `pri_nee_gen` = "Privacy need\ngeneral",
         `pri_nee_gov` = "Privacy need\ngovernment",
         `pri_nee_int` = "Privacy need\ninterpersonal",
         `pri_nee_ano` = "Privacy need\nanonymity")) %>%
  mutate(rhs = recode(rhs,
         `int` = "Integrity",
         `soc` = "Sociability",
         `fea` = "Anxiety",
         `tra` = "Traditio-\nnalism",
         `rit` = "Risk\navoidance",
         `inc` = "Income",
         `age` = "Age",
         `male` = "Male")) %>%
  rename(beta = est.std)

(p_results_bifactor <- ggplot(d_results_bifactor, aes(x = beta, y = lhs)) +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -0.1, linetype = "dashed", color = "grey") +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper, height = .2)) +
  theme_bw() +
  theme(axis.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_x_continuous(breaks = c(-.4, -.2, 0, .2, .4)) +
  coord_cartesian(xlim = c(-.5, .5)) +
  facet_grid(~ rhs))
```

\newpage
## Individual items

```{r}
name_tmp <- "results_items"
model <- '
  N4P.BOT_1 + N4P.BOT_2 + N4P.BOT_3 + N4P.BOT_4 + N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_5 + N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.SOC_9 + N4P.INT_1 + N4P.INT_2 + N4P.INT_3 + N4P.INT_4 + N4P.INT_5 + N4P.INT_6 + N4P.INT_7 + N4P.INT_8 + N4P.INT_9 ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc

  int_gen ~~ soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
  soc_gen ~~ fea_gen + tra_gen + rit_gen + male + age + inc
  fea_gen ~~ tra_gen + rit_gen + male + age + inc
  tra_gen ~~ rit_gen + male + age + inc
  rit_gen ~~ male + age + inc
  male ~~ age + inc
  age ~~ inc
'
fit <- sem(model, d, estimator = "MLM")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), sem(model, d))
```

\newpage

```{r}
# calculate CI for standardized effect 
d_results_items <- standardizedsolution(results_items_fit) %>% 
  as.data.frame() %>% 
  filter(op == "~") %>% 
  mutate(rhs = factor(rhs, c("int_gen", "soc_gen", "fea_gen", "rit_gen", "tra_gen", 
                             "male", "age", "inc"))) %>%  # reorder for plot
  mutate(lhs = factor(lhs, c(paste0("N4P.BOT_", rep(4:1)),
                             paste0("N4P.INT_", rep(9:1)),
                             paste0("N4P.SOC_", rep(9:1))))) %>%  # reorder for plot
  mutate(rhs = recode(rhs,
         `int_gen` = "Integrity",
         `soc_gen` = "Sociability",
         `fea_gen` = "Anxiety",
         `tra_gen` = "Traditio-\nnalism",
         `rit_gen` = "Risk\navoidance",
         `inc` = "Income",
         `age` = "Age",
         `male` = "Male")) %>% 
  rename(beta = est.std)

(p_results_items <- ggplot(d_results_items, aes(x = beta, y = lhs)) +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -0.1, linetype = "dashed", color = "grey") +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper, height = .2)) + 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_x_continuous(breaks = seq(-.7, .7, .2)) +
  facet_grid(~ rhs))
```

```{r save-workspace}
# remove large objects
remove(d_imp, d_incl_susp, fit)

# save workspace so that manuscript can be reproduced without rerunning analyses
save.image("../data/workspace.RData")
```

### 2019-02-12 manuscript/archive/manuscript_2019-02-07.RmD
- Major changes regarding everything: analyses (e.g., inclusion of bifactor models), ms, etc.

--- 2018-12-09 manuscript/manuscript.RmD
@@
 (ref:abstract)
-In this study we analyzes how personality relates to peoples' need for privacy.
-For example, we analyze if the so-called "nothing-to-hide" argument is correct: Do people who lack integrity really desire more privacy?
-Moreover, we also analyze the relation between need for privacy and sociability, anxiety, risk aversion, and traditionality.
-Using an online questionnaire with _N_ = `r n_d` mostly student respondents, we found that it is possible to predict a considerable part of peoples' need for privacy on the basis of their personalities.
-For example, we indeed found that repondents who reported less integrity than others also desired more anonymity.
+The logic underpinning the so-called “nothing-to-hide” argument in the privacy literature posits that people who lack integrity desire more privacy.
+This study analyzes how integrity and, in addition, four other personality traits relate to peoples’ need for privacy along three dimensions: (a) need for anonymity, (b) need for privacy from other individuals, and (b) need for privacy from government surveillance.
+Specifically, we analyze the relation between need for privacy and integrity, sociability, anxiety, risk aversion, and traditionality.
+Using an online questionnaire with `r n_d` student respondents, we found that it is possible to predict a considerable part of peoples’ need for privacy on the basis of personality.
+For example, we indeed found that respondents who reported less integrity desired more anonymity.
 Moreover, more traditional and more anxious respondents desired more privacy from the government, while more risk averse and less sociable respondents desired more privacy from other people.
@@
 ```{r need-for-privacy-items}
-kable(t_pri_nee, "latex", booktabs = TRUE, linesep = "",
-      caption = "Overview of the Items Measuring the Need for Privacy") %>% 
-  column_spec(3, width = "10cm") %>% 
-  kable_styling(latex_options="scale_down", font_size = 7)
+d_t_items <- rbind(
+  t_pri_nee %>% filter(name %in% pri_nee_gov_items),
+  t_pri_nee %>% filter(name %in% pri_nee_int_items),
+  t_pri_nee %>% filter(name %in% pri_nee_ano_items)) %>% 
+  select(content)
+kable(d_t_items, "latex", booktabs = TRUE, linesep = "",
+      caption = "Overview of the Items Measuring Need for Privacy") %>% 
+  # column_spec(3, width = "10cm") %>% 
+  kable_styling(latex_options="scale_down", font_size = 10) %>% 
+  group_rows("Privacy need government", 1, 5) %>%
+  group_rows("Privacy need interpersonal", 6, 9) %>%
+  group_rows("Privacy need anonymity", 10, 13)
 ```
@@
 In a study with `r n_d` students from a large US university, we measured the need for privacy with 22 items.
-Fifteen items formed a well-fitting bifactor model, with one factor measuring the general desire for privacy, and three specific factors measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity.
+Fifteen items formed a well-fitting bifactor model, with one factor measuring the general need for privacy, and three specific factors measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity.
 The factor solution we found is in line with privacy theory, which subsumes a vertical level (here, privacy from the government) and a horizontal level (here, privacy from other people).

### 2019-02-12 manuscript/archive/manuscript_2019-02-08.RmD
- Major changes regarding everything: analyses (e.g., inclusion of bifactor models), ms, etc.

--- 2018-12-09 manuscript/manuscript.RmD
@@
     affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "University of Hohenheim, Department of Media Psychology (540F)"
+    corresponding : yes
+    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
     email         : "tobias.dienlin@uni-hohenheim.de"
   - name          : "Miriam Metzger"
-    affiliation   : "1,2"
+    affiliation   : "2"
+    email         : "metzger@ucsb.edu"
 
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
+  Tobias Dienlin, Department of Media Psychology, University of Hohenheim, Germany; Miriam Metzger, Department of Communication, University of California, Santa Barbara, United States of America.
 
 abstract          : (ref:abstract)
-keywords          : "Privacy, personality, anonymity, integrity, SEM"
+keywords          : "Privacy, need for privacy, personality, anonymity, integrity, SEM"
 
@@
 packages <- c("devtools", "ggplot2", "kableExtra", "lavaan", "magrittr", 
-              "papaja", "semPlot", "td")
+              "papaja", "semPlot", "td", "tidyverse")
 lapply(packages, library, character.only = TRUE)
@@
 (ref:abstract)
-In this study we analyzes how personality relates to peoples' need for privacy.
-For example, we analyze if the so-called "nothing-to-hide" argument is correct: Do people who lack integrity really desire more privacy?
-Moreover, we also analyze the relation between need for privacy and sociability, anxiety, risk aversion, and traditionality.
-Using an online questionnaire with _N_ = `r n_d` mostly student respondents, we found that it is possible to predict a considerable part of peoples' need for privacy on the basis of their personalities.
-For example, we indeed found that repondents who reported less integrity than others also desired more anonymity.
-Moreover, more traditional and more anxious respondents desired more privacy from the government, while more risk averse and less sociable respondents desired more privacy from other people.
+This study analyzes how personality traits relate to peoples’ need for privacy.
+We focus on three dimensions: (a) need for privacy from government surveillance, (b) need for privacy from other individuals, and (c) need for anonymity.
+Using an online questionnaire with `r n_d` student respondents, several relationships were found.
+For example, results showed that people who reported less integrity desired more anonymity.
+Less sociable people desired considerably more privacy on all three dimensions.
+While anxious people desired less privacy from government surveillance, risk avoidant people desired more privacy from other people.
+Traditionalism did not relate to need for privacy.
+Together, the results have several interesting impliciations.
+For example, they shed some light on the nothing-to-hide argument: A person who desires more anonymity might indeed be of less integrity.
+However, it is equally plausible that this person is just a little less gregarious.
 
-In his novel _The Circle_, @Eggers.2013 describes a dystopian society in which people are gradually forfeiting their privacy.
-One after another becomes "transparent": Carrying a small camera around the neck, people begin to broadcast their daily lives to the Internet.
-In the novel, this eventually causes a societal upheaval: "The pressure on those who hadn't gone transparent went from polite to oppressive.
-The question, from pundits and constituents, was obvious and loud: If you aren't transparent, what are you hiding?" [@Eggers.2013, p.
-129].
+Whereas some people protest the fact that government agencies such as the NSA are collecting large amounts of person-related data, others do not care [@Greenwald.2013].
+Whereas some are happy to tell a friend a personal secret, others refrain from doing so.
+Whereas some people use pseudonyms to communicate online, again, others do not.
+Why do some people need more privacy than others, and how do they differ from one another?
 
-With this study, we want to answer the following question.
-Why do people desire privacy?
-To date there is only little research on why people desire privacy and how the need for privacy can be predicted by aspects of personality.
-Why do some people not care whether government agencies such as the NSA are collecting their data [@Greenwald.2013], and why do others protest vehemently in order to protect their privacy?
-
-We think that finding an answer to this question is important: Given that government agencies are collecting large amounts of data hoping to reduce criminality and terrorism, and given that government agencies are collecting this data preemptively and without concrete suspicions, it seems relevant to find out whether this practice of mass surveillance can be justified based on the nothing-to-hide argument.
-As a result, the main question of this paper is: Do people who desire more privacy really have more to hide and, more generally, what are personality facets that determine peoples' overall need for privacy?
+In light of the increasing digitization of everyday life, which has led to the commodification and monetization of personal information [@Sevignani.2017], privacy has become one of the most important topics of the day.
+To date, however, we still know suprisingly little about who needs privacy and who does not, and how the need for privacy can be predicted by aspects of personality.
+As a result, the main question of this paper is: What are personality facets that determine peoples' overall need for privacy?
 
@@
           note = "All items were measured on 7-point scales with Likert response options.
-Alpha = Cronbach's alpha (internal consistency); omega = Raykov's omega (composite reliability); ave = average variance extracted."
-          )
+Alpha = Cronbach's alpha (internal consistency); omega = Raykov's omega (composite reliability); ave = average variance extracted.",
+          stub_indents = list("Privacy need" = c(1:4)))
 ```
@@
 For a list of all items, see Table \@ref(tab:need-for-privacy-items).
-For an overview of the items' loadings in the final bifactor model, see Figure \@ref(fig:need-for-privacy-loadings).
-
-```{r need-for-privacy-loadings, fig.cap="Overview of the bifactor model for the need for privacy"}
-plot(p_pri_nee)
-```
 
@@
 ```{r need-for-privacy-items}
-kable(t_pri_nee, "latex", booktabs = TRUE, linesep = "",
-      caption = "Overview of the Items Measuring the Need for Privacy") %>% 
-  column_spec(3, width = "10cm") %>% 
-  kable_styling(latex_options="scale_down", font_size = 7)
+d_t_items <- rbind(
+  t_pri_nee %>% filter(name %in% pri_nee_gov_items),
+  t_pri_nee %>% filter(name %in% pri_nee_int_items),
+  t_pri_nee %>% filter(name %in% pri_nee_ano_items)) %>% 
+  select("Item content" = content) %>% 
+  mutate_all(linebreak)
+kable(d_t_items, "latex", booktabs = TRUE, linesep = "",
+      caption = "Overview of Items Measuring Need for Privacy") %>% 
+  # column_spec(1, width = "16cm") %>% 
+  kable_styling(latex_options="scale_down") %>% 
+  group_rows("Privacy need government", 1, 5) %>%
+  group_rows("Privacy need interpersonal", 6, 9) %>%
+  group_rows("Privacy need anonymity", 10, 13)
 ```
@@
 ```{r results, results="asis"}
-apa_table(dplyr::select(t_results, -Outcome),
-          font_size = "scriptsize",
+apa_table(dplyr::select(t_results_threefactors, -Outcome),
+          font_size = "footnotesize",
           align = c("l", rep("r", 5)), 
-          stub_indents = list("Privacy need general" = c(1:8),
-                              "Privcacy need government" = c(9:16),
-                              "Privacy need interpersonal" = c(17:24),
-                              "Privacy need anonymity" = c(25:32)),
+          stub_indents = list("Privcacy need government" = c(1:8),
+                              "Privacy need interpersonal" = c(9:16),
+                              "Privacy need anonymity" = c(17:24)),
           caption = "Results of the main factorial model."
@@
 ```{r results-factor, fig.cap="Overview of results. Shows the 95% confidence intervals of standardized coefficients.", fig.height=3}
-plot(p_main)
+plot(p_results_threefactors)
 ```
 
-To begin with, we found that the final model we estimated to test our hypotheses fit the data moderately well, `r fit_txt(main_fit, scaled = TRUE)`.
+To begin with, we found that the final model we estimated to test our hypotheses fit the data moderately well, `r fit_txt(results_threefactors_fit, scaled = TRUE)`.
 Our first hypothesis stated that people reporting more integrity than others would need less privacy.
@@
 
-In sum, the predictors could explained `r inspect(main_fit, 'r2')["pri_nee_gen"] * 100 %>% round(0)`% of the variance in the general need for privacy, `r inspect(main_fit, 'r2')["pri_nee_gov"] * 100 %>% round(0)`% of the variance in the need for privacy from the government, `r inspect(main_fit, 'r2')["pri_nee_int"] * 100 %>% round(0)`% of the variance in the need for privacy from other people, and `r inspect(main_fit, 'r2')["pri_nee_ano"] * 100 %>% round(0)`% of the variance in the need for anonymity.
+In sum, the predictors could explained `r inspect(results_threefactors_fit, 'r2')["pri_nee_gen"] * 100 %>% round(0)`% of the variance in the general need for privacy, `r inspect(results_threefactors_fit, 'r2')["pri_nee_gov"] * 100 %>% round(0)`% of the variance in the need for privacy from the government, `r inspect(results_threefactors_fit, 'r2')["pri_nee_int"] * 100 %>% round(0)`% of the variance in the need for privacy from other people, and `r inspect(results_threefactors_fit, 'r2')["pri_nee_ano"] * 100 %>% round(0)`% of the variance in the need for anonymity.
 
@@
 
-```{r results-items, fig.cap="Overview of results. Shows the 95% confidence intervals of standardized coefficients."}
-plot(p_main_items)
-```
-
 # Discussion
 
+With this study, we want to answer the following question. Why do people desire privacy?
 This study analyzed how the need for privacy can be predicted by means of personality.
 In a study with `r n_d` students from a large US university, we measured the need for privacy with 22 items.
-Fifteen items formed a well-fitting bifactor model, with one factor measuring the general desire for privacy, and three specific factors measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity.
+Fifteen items formed a well-fitting bifactor model, with one factor measuring the general need for privacy, and three specific factors measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity.
 The factor solution we found is in line with privacy theory, which subsumes a vertical level (here, privacy from the government) and a horizontal level (here, privacy from other people).
@@
 
+In his novel _The Circle_, @Eggers.2013 describes a dystopian society in which people are gradually forfeiting their privacy.
+One after another becomes "transparent": Carrying a small camera around the neck, people begin to broadcast their daily lives to the Internet.
+In the novel, this eventually causes a societal upheaval: "The pressure on those who hadn't gone transparent went from polite to oppressive.
+The question, from pundits and constituents, was obvious and loud: If you aren't transparent, what are you hiding?" [@Eggers.2013, p.
+129].
+
 \newpage
@@
 \endgroup
+
+# Contributions
+
+- Contributed to conception and design: TD, MM
+- Contributed to acquisition of data: MM
+- Contributed to analysis and interpretation of data: TD, MM
+- Drafted and/or revised the article: TD, MM
+- Approved the submitted version for publication: TD, MM
+
+# Funding Information
+
+During the conception and data collection of the study, TD was funded by The German Academic Scholarship Foundation (German: Studienstiftung des deutschen Volkes), which financially supported TD's research stay at UCSB.
+During the writing of the article, TD was funded by the Volkswagen Foundation (German: Volkswagenstiftung), grant "Transformations of Privacy".
+
+MM is funded by a regular and tenured full professorship at UCSB.
+
+# Competing Interests
+
+We declare no competing interests.
+
+# Data accessibility statement
+
+All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found on this paper’s project page on the open science framework (https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f).
+In addition, we invite everyone to suggest changes/improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/tree/master).

### 2019-02-12 manuscript/manuscript.RmD
- Major changes regarding everything: analyses (e.g., inclusion of bifactor models), ms, etc.

--- 2018-11-13 manuscript/manuscript.RmD
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+  Tobias Dienlin, Department of Media Psychology, University of Hohenheim, Germany; Miriam Metzger, Department of Communication, University of California, Santa Barbara, United States of America.
 
-  Enter author note here.
+abstract          : "This study analyzes how personality traits relate to need for privacy.
+We focus on three dimensions: (a) need for privacy from government surveillance, (b) need for privacy from other individuals, and (c) need for anonymity.
+Using an online questionnaire with 271 student respondents, several significant relationships were found.
+For example, results showed that less sociable people desired considerably more privacy on all three dimensions.
+Somewhat more controversially, people who reported less integrity also desired noticeably more anonymity.
+While anxious people desired slightly less privacy from government surveillance, risk avoidant people desired considerably more privacy from other people.
+Traditionalism did not relate to need for privacy.
+Together, the results have several implications.
+For example, they shed some light on the nothing-to-hide argument: A person who desires more anonymity might indeed be of less integrity.
+However, it is equally plausible that this person is just a little less sociable."
+keywords          : "Privacy, need for privacy, personality, anonymity, integrity, SEM"
 
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+bibliography      : 
+  - "../bibliography/r-references.bib"
+  - "../bibliography/references.bib"
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["r-references.bib"]
-
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed,
+                      fig.pos = 'h')
 ```
 
+```{r setup, include = FALSE}
+# devtools::install_git("https://github.com/tdienlin/td")
+packages <- c("devtools", "english", "ggplot2", "kableExtra", "lavaan", "magrittr", 
+              "papaja", "semPlot", "td", "tidyverse")
+lapply(packages, library, character.only = TRUE)
+load("../data/workspace.RData")
+
+# export references
+r_refs(file = "../bibliography/r-references.bib")
+```
+
+In light of the increasing digitization of everyday life, which has led to several sweeping societal changes such as the commodification and monetization of personal information [@Sevignani.2016], privacy has become a major topic of interest.
+Despite its importance, however, we still know surprisingly little about the relation between privacy and personality [e.g., @Masur.2018, p.
+155].
+Why do some people need more privacy than others, and how do these people differ from one another?
+We think that a better understanding of the relation between personality and privacy is crucial: Several theories argue that personality determines privacy behaviors [e.g., @Masur.2018], however, to date there is almost no empirical research that can be used to deduct well-informed hypotheses.
+As a result, the main question of this paper is as follows: What are personality facets that can be used to best explain peoples' need for privacy?
+
+## The Need for Privacy
+
+Privacy as a theoretical concept is both complicated and contested [@Nissenbaum.2010, p.
+71].
+Hence, we begin by outlining our own understanding of privacy.
+First and foremost, privacy captures the extent of voluntary withdrawal from others [@Westin.1967].
+Several models suggest that privacy is multi-dimensional.
+For example, in a theory-driven treatise @Burgoon.1982 argued that privacy has four dimensions: informational, social, psychological, and physical privacy.
+@Pedersen.1979, by contrast, did an empirical factor analysis (initially starting with 94 items) and suggested that privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity.
+In addition, @Schwartz.1968 differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies).
+Finally, one can also distinguish between the objective privacy context, the subjective privacy perception, the psychological need for privacy (which is both a situational and dispositional need), and the resulting privacy behavior (often represented by self-disclosure) [@Dienlin.2014].
+
+For the purpose of this study, we combine the aforementioned notions and focus on (a) vertical privacy with regard to the need for withdrawal from government surveillance, (b) horizontal privacy in terms of the need for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by the general need for anonymity.
+
+In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually need privacy.
+@Westin.1967 defined four primary positive purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
+Not least, privacy facilitates self-disclosure [@Dienlin.2014], which is vital for attaining social support, initiating relationships, and getting close to one another [@Omarzu.2000].
+
+On the other hand, however, too much privacy can also be problematic.
+Because human beings are inherently social, being overly cut-off from others can impede flourishing, nurture deviant behavior, or introduce power asymmetries [@Altman.1975].
+"[T]he feminist critique rightfully argued that for men, the private sphere can be a shielded sphere in which female suppression is not sanctioned." [@DeCew.1997, p.
+81, as cited by Masur, 2018, p.
+38].
+Next, and as mentioned above, privacy fosters self-disclosure.
+However, any self-disclosure is also always a potential risk because others might disagree, disapprove, or misuse the information in other contexts [@Petronio.2010].
+
+## Predicting the Need for Privacy
+
+In what follows we now explore several personality aspects that we think might predict the need for privacy.
+As there is no established theory that dovetails privacy and personality, it is difficult to deduct precise and well-informed hypotheses.
+The rationales that we outline below should hence considered to be tentative suggestions.
+Also, please note that we elaborate only on those dimensions of need for privacy for which plausible rationales could be found.
+
+The general underlying theoretical framework that guided our selection process was the big five approach [e.g.,@John.1999].
+Note that privacy concerns, a variable conceptually close to need for privacy, shows only negligible relations with the big five factors [@Bansal.2010; @Junglas.2008].
+In order to be more precise, we hence follow the advice by @Paunonen.2001 and refer to specific personality facets instead of generic personality factors.
+To illustrate, instead of dwelling on the general factor of _extraversion_, we instead focused on the facet _gregariousness_, which we consider to be more pertinent.
+
+Our reasoning was guided by another central theoretical thought.
+As implied above, privacy can be either positive or negative.
+Similarly, other people, the government, and anonymity can be considered either a _resource_ or a _threat_.
+Having information about a person's personality can inform us whether he or she is more likely to think of others as a resource or a threat.
+It follows that if other people are considered a threat it seems to be more likely that a person will desire more privacy from others, and vice versa [@Altman.1976].
+
+### Sociability
+
+First, we argue that need for privacy should be closely related to a person's sociability or gregariousness [which is a subdimension of extraversion, @John.1999].
+Sociability captures whether people prefer to spend their time alone or with company.
+It seems plausible that people who are more sociable are also more likely to think of other people as a resource, which is why they should generally desire less interpersonal privacy and less anonymity [e.g., @Buss.2001].
+Put differently, given that privacy is a voluntary withdrawal from society [@Westin.1967], we expect that people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.
+
+This rationale is supported by several empirical studies: Extroverted people desire less privacy [@Morton.2013], people who describe themselves as introverted thinkers are more likely to prefer social isolation [@Pedersen.1982], and introverted people are more likely to report invasions of privacy [@Stone.1986].
+
+### Integrity
+
+More controversially, it has been argued that people need privacy because they have something to hide.
+The so-called nothing-to-hide argument states that “If you have nothing to hide, you have nothing to fear.” As described by Solove, the nothing-to-hide argument says that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens.
+Only those who are engaged in illegal activities have a reason to hide this information” [@Solove.2007, p.
+753].
+Hence, another potential predictor of why people need privacy could also be a so-called "lack of integrity".
+
+Because integrity is a delicate concept, let us first try to define it conceptually.
+Although in terms of a scientific definition there is no consensus, most scholars seem to agree that integrity “incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness” [@Connelly.2006, p.
+82].
+In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow @Paunonen.2002 and adopt a lowest common denominator approach, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.
+
+It is indeed possible to think of theoretical arguments for why lack of integrity might correlate positively with need for privacy.
+People who have actually committed crimes evidently face even greater risk from self-disclosure compared to others, because government agencies and people sould surely disapprove of their activities [@Petronio.2010].
+Hence, the government and other people are more likely to be a threat, which should render anonymity rather a resource.
+As a consequence, people with lower integrity might desire more privacy as a means to mitigate their felt risk [@Altman.1976].
+
+There are also a few empirical studies that imply---at least indirectly---a relation between privacy and integrity.
+For example, studies have found that surveillance can reduce cheating behaviors [@Corcoran.1987; @Covey.1989].
+@Covey.1989 for example asked students to solve an impossible maze.
+In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior.
+In the low surveillance condition, the experimenter remained behind the students where he or she could not see the students.
+Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more integrity (i.e., fewer cheating behaviors).
+Next, in a longitudinal sample with 457 respondents in Germany [@Trepte.2013a], people who felt they needed more privacy were also less authentic on their SNSs profiles (_r_ = -.48) and less authentic in their personal relationships (_r_ = -.28).
+Given the argument that authenticity is a subset of integrity [@Sheldon.2004], one could hence reason that also the concept of integrity might relate to a person’s need for privacy.
+Somewhat related, it has been found that people who are more agreeable are also moderately less concerned about their privacy [@Junglas.2008].
+Finally, @Pedersen.1982 showed that three dimensions of need for privacy relate to self-esteem: Respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21), and preferred solitude (_r_ = .24).
+While self-esteem and integrity are distinct concepts, Pedersen’s specific operationalization of self-esteem integrated several aspects of integrity by using items such as “moral, nice, fair, unselfish, good, honest, reputable, sane”..
+
+In conclusion, we could imagine that lack of integrity may indeed relate to an increased need for privacy from government surveillance, as governments have the legitimate power to prosecute illegal activities.
+Next, it seems plausible that lack of integrity relates to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers.
+Finally, lack of integrity may also relate to an increased need for privacy from other people, as most other people will disapprove of immoral or illegal activities, and could even reveal those activities to authorities.
+
+### Anxiety
+
+Next, it seems possible that the need for privacy is also related to people's level of general anxiety [which is a subdimension of neuroticism, @John.1999].
+General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened.
+With regard to interpersonal privacy, one could argue that people who are anxious are more likely to feel that social interactions pose a greater risk and threat [especially with strangers or weak ties; @Granovetter.1973], which is why anxious people might desire more privacy.
+Somewhat related, prior empirical research has shown that people who are more concerned about their privacy are also more likely to withdraw online, for example by deleting posts or untagging themselves from linked content [@Dienlin.2016a].
+On the other hand, one could argue in favor of the opposite: People who are more anxious may desire _less_ privacy from others (especially their strong ties), as a means to cope better with their daily challenges.
+
+Concerning the need for privacy from government surveillance, we could imagine that people who are more anxious desire less privacy.
+Despite the fact that only 18% of all US-Americans trust their government "to do what is right" [@PewResearchCenter.2017], almost everyone agrees that "it's the government's job to keep the country safe", with most people also being satisfied with the government's job [@PewResearchCenter.2015c].
+Hence, when being anxious, the government should rather be seen as a resource than a threat.
+It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that these programs promise to prevent crime or to reduce the likelihood of terrorist attacks [@Greenwald.2013], implying that people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.
+
+### Risk aversion
+
+Similarly, it could be that need for privacy is related to the general tendency to avoid risks, to deliberate, and to plan carefully [deliberation is a subdimension of conscientiousness, @John.1999].
+Risk avoidance captures the degree to which people prefer to abstain from taking risks.
+If other people are considered a threat, people who are risk averse should desire more interpersonal privacy, because they may feel greater risk associated with disclosure of personal information.
+The most cautious strategy to minimize risks of information disclosure would be, arguably, to keep as much information as possible private.
+Somewhat related, empirical studies report that people who think that their privacy is at risk are less likely to disclose information online [e.g., @Bol.2018].
+Moreover, research suggests that conscientious people are slightly more concerned about their privacy [@Junglas.2008].
+But again, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, in order for the government to be able to avert potential threats.
+
+### Traditionality
+
+Next, it seems plausible that need for privacy is also related to traditionality [which is a subdimension of openness to experience, @John.1999].
+Traditionalism measures whether people prefer to stick with their usual routines.
+The computers and the Internet have rendered the world increasingly knowable: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.
+Given that digital information is persistent, searchable, reproducible, and scalable [@boyd.2008c], this allows for unprecedented means and degrees of surveillance.
+Mark Zuckerberg famously observed that privacy is no longer a social norm, rather the norm is that people share personal information [@Johnson.2010].
+Hence, in order to be part of contemporary life, it seems necessary to give up some privacy.
+However, people may not be equally willing to pay that price, and especially people who are more traditional might decide against giving up their privacy.
+
+Empirical research does find that older people, who are generally less open and more traditional [@Donnellan.2008], are more concerned about their privacy [@Fife.2012].
+On the other hand, @Junglas.2008 report that openness to experience is positively related to privacy concern, which would argue in favor of the exact opposite.
+Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three aforementioned contexts.
+
+### Socio-demographic variables
+
+Finally, it has often been shown that socio-demographic variables such as sex, age, and affluence can relate to the need for privacy [@Park.2015; @Tifferet.2019; @Weinberger.2017b; @Trepte.2013a].
+Although these variables do not specifically address our research question at hand they will be included---not least as their omission could lead to spurious results or an inflation of false positives.
+
 # Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
 
-## Participants
+This section describes how we determined the sample size, data exclusions, the analyses, and all measures in the study.
 
-## Material
+## Sample
 
-## Procedure
+Participants were students from an IRB-approved subject pool at a university in the western U.S.
+All students received course credit for participating in the study.
+The initial sample consisted of `r n_d_all` respondents.
+We removed `r as.english(n_d_suspicious)` cases with problematic response patterns (e.g., straight-lining, missing of inverted items), which we identified using the Guttman value [@Meijer.2016].
+Next, we excluded one participant who provided an illogical age (i.e., 9 years).
+We also excluded `r n_d_missing` respondents because they answered less than 50% of all questions.
+The remaining missing responses (`r round(na_perc * 100, 2)`%) were imputed using predictive mean matching.
+Analyses showed no respondents needed to be excluded due to “speeding” (i.e., < 5 min answer time).
+The final sample consisted of `r n_d` respondents.
 
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+Age of participants ranged from `r min(d$age, na.rm = TRUE)` to `r max(d$age, na.rm = TRUE)` years (_M_ = 20 years), with `r mean(d$male, na.rm = TRUE) %>% round(2) * 100`% of the respondents being male.
+The median participation time was `r as.numeric(d$time) %>% median(na.rm = TRUE) %>% divide_by(60)` min.
+
+The data were collected in 2015.
+While we aimed to collect a large number of participants (i.e., _N_ > 300), at the time we were not yet aware of the importance to run a-priori power analyses to determine sample size.
+A post-hoc power analysis shows that the final sample size allowed to find effects with a size of $\upbeta$ = `r sensitivity_95 %>% my_round("beta")` in 95% of all cases, and that we had power to detect small effects (i.e., $\upbeta$ = .10) in `r power_small`% of all cases.
+
+## Data Analyses
+
+All hypotheses were tested using a two-tailed significance level of 5%.
+Because all predictors were chosen on the basis of a-priori reasoning we did not control for alpha error inflation.
+We classified regression coefficients with values exceeding |$\upbeta$| = .10 as small effects, |$\upbeta$| = .30 as medium effects, and |$\upbeta$| = .50 as large effects.
+Our smallest effect size of interest [SESOI; @Lakens.2018] was |$\upbeta$| = .10.
+Effects below the SESOI were considered too small to be theoretically relevant.
+
+The factorial validity of the measures and the hypotheses were tested with structural equation modeling (SEM).
+Mardia’s test showed that the assumption of multivariate normality was violated, _p_(skewness) `r mult_norm[mult_norm$Test == "Mardia Skewness", ]$"p value" %>% my_round("p")`, _p_(kurtosis) `r mult_norm[mult_norm$Test == "Mardia Kurtosis", ]$"p value" %>% my_round("p")`.
+As a result, we used the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator.
+Fit was assessed using the conventional measures and criteria as proposed by @Kline.2016.
+
+First, we tested the factorial validity of the variables we collected.
+In a first step, we ran confirmatory factor analyses (CFAs) to determine whether the variables were uni-dimensional.
+If fit was not adequate, we then ran exploratory factor analyses (EFAs) to assess the actual underlying factor structure.
+If more than one factor was revealed, we tried to find a bifactor model solution.[^1] This way we were able to attain a general measure of the predictors, instead of needing to further complicate our analyses by including subdimensions of the predictors.[^2] If no adequate bifactor model could be found, we proceeded by deleting items with low loadings on the general factor and/or the specific factors.
+If also after deletion of individual items no bifactor solution emerged, using a subset of the items we then aimed to extract a single factor with sufficient factorial validity.
+
+[^1]: Bifactor models implement one factor that explains the variance in all items (the so-called general factor or g-factor).
+In addition, at least another two more factors are implemented that explain the variance in a subset of the items.
+The general factor and the specific factors are orthogonal.
+Bifactor models are nested within hierarchical models.
+For more information on bifactor models, see @Kline.2016, p.
+319.
+
+[^2]: Note that we did not specify a bifactor model of need for privacy, because we were explicitly interested in the relations between the personality facets and the three dimensions of need for privacy.
+
+To anwers our research question, we first had a look at the variables' bivariate relations (see Figure \@ref(fig:bivar-fig)).
+To better assess the variables' potential causal relations, we next ran a multivariate structural regression model.
+Because we were interested in a complex model (overall, eight predictors and three outcomes) but the sample was comparatively small, we simplified the model.
+To this end, instead of a fully latent structural regression model we conducted a partially latent structural regression model, in which the predictor variables were modelled as single indicators while controlling for measurement error [@Kline.2016, p.
+214].
+To get high-quality single indicators of the predictors, we computed the average of the model predicted values / latent factor scores, which we extracted from the CFAs.
+If the CFAs showed a single-factor solution, we used the model predicted values for this latent factor; if the CFAs produced a bifactor solution, we used the model predicted values for the general latent factor.
+As main variable of interest, the outcome need for privacy was measured as a three-dimensional latent factor consisting of overall 12 items (see below).
+
+Finally, combining the information of several items into a latent factors helps to reduce and combine information.
+At the same time, however, this approach also introduces several researcher degrees of freedom.
+We hence emphasize that we deleted items only in order to achieve satisfactory factorial validity and not in order to cherry-pick significant material.
+In light of our not having preregistered the analyses and in order to provide the complete picture, in the online supplementary material (OSM) we hence also report how the independent variables predicted each item individually.
+
+`r cite_r("../bibliography/r-references.bib", withhold = FALSE, pkgs = c("GGally", "ggplot2", "knitr", "lavaan", "mice", "MVN", "papaja", "PerFit", "psych", "pwr", "semTools", "tidyverse"))` was used for the analyses.
+
+## Measures
+
+In this section we present how we operationalized our constructs.
+All items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).
+The results of the CFAs showed that it was possible to model all variables with at least acceptable fit.
+For an overview of the items’ psychometrics, factorial validity, and reliability, see Table \@ref(tab:psychometrics).
+A list of all the items that were used (including deleted ones), results of CFAs/EFAs, as well as item statistics and their distribution plots can be found in the OSM.
+
+```{r psychometrics, results="asis"}
+apa_table(t_psyc, font_size = "footnotesize",
+          caption="Psychometrics of Variables Used.",
+          note = "All items were measured on 7-point scales with Likert response options.
+Alpha = Cronbach's alpha (internal consistency); omega = Raykov's omega (composite reliability); ave = average variance extracted.",
+          stub_indents = list("Privacy need" = c(1:4)))
+```
+
+### Need for privacy
+
+As the main variable of interest, we collected several items to measure need for privacy.
+First, we collected four items capturing the need for informational privacy using the scale developed by @Trepte.2017d.
+Second, we measured need for privacy on a societal level using nine self-designed items.
+The first subdimension was government surveillance, which represents the extent to which people want the government to abstain from collecting information about them.
+The second dimension was anonymity, which captures the extent to which people feel the need to avoid identification.
+Third, we measured need for privacy on an interpersonal level using nine self-designed items.
+The first subdimension measures need for privacy from other people in online contexts.
+The second subdimension measures need for privacy from other people in offline contexts.
+
+EFAs and CFAs revealed a well-fitting model with 12 items (one double-loading), which consisted of the three dimensions (a) need for privacy from the government, (b) need for privacy from other people, and (c) need for anonymity.
+For a list of all items, see Table \@ref(tab:need-for-privacy-items).
+
+```{r need-for-privacy-items}
+d_t_items <- rbind(
+  t_pri_nee %>% filter(name %in% pri_nee_gov_items),
+  t_pri_nee %>% filter(name %in% pri_nee_int_items),
+  t_pri_nee %>% filter(name %in% pri_nee_ano_items)) %>% 
+  select("Item content" = content) %>% 
+  mutate_all(linebreak)
+kable(d_t_items, "latex", booktabs = TRUE, linesep = "",
+      caption = "Overview of Items Measuring Need for Privacy") %>% 
+  # column_spec(1, width = "16cm") %>% 
+  kable_styling(latex_options="scale_down") %>% 
+  group_rows("Privacy need government", 1, 5) %>%
+  group_rows("Privacy need interpersonal", 6, 9) %>%
+  group_rows("Privacy need anonymity", 10, 13)
+```
+
+### Sociability
+
+Sociability was measured with the extraversion subscale _gregariousness_ [@John.1999], which consists of eight items.
+An example item is “I shy away from crowds of people.” Analyses revealed that a bifactor model based on a subset of six items showed good fit to the data.
+
+### Integrity
+
+In order to measure integrity, we used the subscale _integrity_ of the Supernumerary Personality Inventory [@Paunonen.2002], which consists of eight items.
+In addition, we designed another three items.
+An example item is “I don’t think there’s anything wrong with cheating a little on one’s income tax forms.” Analyses revealed that a bifactor model based on a subset of nine items showed good fit to the data.
+
+### Anxiety
+
+Anxiety was measured with the neuroticism subscale _anxiety_ [@John.1999], which consists of eight items.
+An example item is “I am easily frightened.” Analyses revealed that a bifactor model using all eight items showed good fit to the data.
+
+### Risk avoidance
+
+Risk avoidance was measured with the conscientiousness subscale _deliberation_ [@John.1999], which consists of eight items.
+An example item is “I plan ahead carefully when I go on a trip.” Analyses revealed that a bifactor model using all eight items showed good fit to the data.
+
+### Traditionalism
+
+Traditionalism was measured with the (inverted) openness to experiences subscale _actions_ [@John.1999], which consists of eight items.
+An example item is “I’m pretty set in my ways.” Analyses revealed that a model with a single factor based on a subset of five items showed good fit to the data.
 
@@
 
+For an overview of the results of the bivariate relations, see Figure \@ref(fig:bivar-fig).
+For the statistical results of the SEM, see Table \@ref(tab:sem-tab), and for a graphical visualization, Figure \@ref(fig:sem-fig).
+Note that the final structural regression model that was estimated fit the data comparatively well, `r fit_txt(results_threefactors_fit, scaled = TRUE)`.
+
+```{r bivar-fig, fig.cap="Results of the bivariate relations.
+Above diagonal: zero-order correlation matrix; diagonal: density plots for each variable; below diagonal: bivariate scatter plots for zero-order correlations.
+Solid regression lines represent linear regressions, dashed regression lines represent quadratic regressions.
+Calculated with the variables’ latent factor scores.", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
+suppressWarnings(print(p_bivar))
+```
+
+```{r sem-fig, fig.cap="Graphical overview of the results of Structural Equation Model.
+Shows the 95% confidence intervals of standardized coefficients.
+Dashed lines indicate the SESOI of |.10|.", fig.height=2.5}
+plot(p_results_threefactors)
+```
+
+The bivariate correlations revealed that respondents who were more sociable than others also needed considerably less privacy from other people.
+In addition, they also needed slightly less privacy from the government and less anonymity.
+Also when analyzed in the multivariate structural regression model holding all other predictors constant, sociability was related to a reduced need for privacy on all three dimensions.
+
+Next, both the bivariate and the SEM results showed that respondents who reported less integrity compared to others desired considerably more anonymity.
+No significant relations existed with the need for privacy from the government and the need for anonymity.
+
+For anxiety, both analyses showed that respondents who indicated being more anxious indeed desired less privacy from the government.
+The effect size was small to moderate.
+Whereas the bivariate analyses revealed a small significant relation between anxiety and need for anonymity, this relation disappeared when analyzed in the SEM keeping all other predictors constant.
+No significant relationship with need for privacy from other people emerged.
+
+Both analyses showed that respondents who reported being more risk avoidant than others desired considerably more privacy from other people.
+The bivariate analyses showed a small and positive association between risk avoidance and need for privacy from government surveillance, which ceased to exist in the SEM.
+No significant relation with need for anonymity was found.
+
+```{r sem-tab, results="asis"}
+apa_table(dplyr::select(t_results_threefactors, -Outcome),
+          font_size = "footnotesize",
+          align = c("l", rep("r", 5)), 
+          stub_indents = list("Privacy need government" = c(1:8),
+                              "Privacy need interpersonal" = c(9:16),
+                              "Privacy need anonymity" = c(17:24)),
+          caption = "Results of Structural Equation Model.")
+```
+
+Next, the bivariate analyses showed that respondents who scored higher on traditionalism also reported increased levels of need for privacy from government surveillance and other people.
+However, both relations disappeared in the SEM.
+No significant relation with need for anonymity was found.
+
+Finally, regarding socio-demographic variables, the SEM showed that respondents who were older also desired slightly more anonymity.
+Male respondents desired more privacy from the government and more anonymity.
+Respondents with a higher income did not exhibit different levels of need for privacy.
+
+Summarizing across the results, the predictors explained `r inspect(results_threefactors_fit, 'r2')["pri_nee_gov"] * 100 %>% round(0)`% of the variance in need for privacy from the government, `r inspect(results_threefactors_fit, 'r2')["pri_nee_int"] * 100 %>% round(0)`% of the variance in need for privacy from other people, and `r inspect(results_threefactors_fit, 'r2')["pri_nee_ano"] * 100 %>% round(0)`% of the variance in need for anonymity.
+
 # Discussion
+
+This study analyzed the extent to which the need for privacy can be predicted and explained by personality traits.
+First, the results of the bivariate analyses showed that the need for privacy can be predicted surprisingly well by means of specific personality facets.
+Second, also when analyzed together in a structural regression model alongside additional socio-demographic variables, most personality variables remained significant, supporting the robustness of the relations.
+
+Most prominently, we find that sociability was negatively related to all three dimensions of need for privacy.
+This does not come to much surprise as privacy captures the withdrawal from others and is hence already from a conceptual point of view closely related to sociability.
+Nonetheless, it is interesting to see that the relation is indeed thus proximal---especially in light of prior studies not having found a significant relation between extraversion and concern for privacy [@Junglas.2008], which are both related variables.
+
+Next, and more controversial, our results also showed that the desire for anonymity is related substantially with measures of integrity.
+People who self-reported lower integrity desired more anonymity.
+Respondents who said, for example, that they would feel tempted to take things that do not belong to them were also more likely to avoid situations in which they were identifiable.
+This finding hence supports the logic behind the “nothing to hide” argument.
+It also follows Altman’s privacy regulation theory (1976), which states that if exposure of information is risky it is likely that people will use more mechanisms to strengthen their social boundaries and increase their desired level of privacy.	Importantly, however, integrity was not related to need for privacy from other people or to need for privacy from government surveillance, which hence limits the generalisability of the nothing-to-hide argument.
+In addition, note that the items measuring need for anonymity were very difficult (the mean was much lower compared to the other dimensions; see Table \@ref(tab:psychometrics))---hence, the relationship between integrity and need for privacy might show only in very specific domains, for example, when it comes to avoiding places with video surveillance.
+In conclusion, the relation between integrity and need for privacy seems to be limited to certain aspects of need for privacy only.
+It should hence not be overly generalized.
+
+Interestingly, the data showed that people who were more anxious were also more willing to accept government surveillance.
+This might be explained by the fact that governments are explicitly commissioned to help prevent crime or terrorist attacks, which are things more anxious people are more likely to dread.
+
+People who were more risk averse desired more privacy from other people.
+Specifically, people who try to avoid risks are less inclined to share secrets with friends.
+This finding makes sense and can be aligned with prospect theory [@Kahneman.1979]: The risks of a secret being publicly disclosed seem to outweigh the potential benefits of sharing it with confidants.
+
+Finally, in the SEM no significant relations between need for privacy and traditionality were found.
+The results imply that independent from being more open to change or not, people desire the same level of privacy.
+Taken further, this finding might illustrate that a modern way of living does not necessarily imply a reduced need for privacy.
+
+At a larger level, the results of this study highlight the importance of making differentiated claims on why people need privacy.
+Indeed, while the results suggest that some people might need anonymity because they may have something to hide, they also show that putting everyone who exhibits an increased need for privacy under suspicion is outright wrong.
+People who are less sociable, more risk averse, and less anxious are also more likely to need a bit more privacy.
+This implies that various personality-related aspects can predict need for privacy in different ways and for different reasons.
+
+Another contribution this study makes to the privacy literature is that it is one of the first to explicitly distinguish different types of privacy needs.
+Specifically, we found that need for privacy consists of three separate dimensions, with factors measuring need for privacy from the government, need for privacy from other people, and need for anonymity.
+This factor solution is in line with privacy theory, which subsumes a vertical level (here, privacy from the government) and a horizontal level (here, privacy from other people) [e.g., @Schwartz.1968].
+The third dimension, need for anonymity, can be argued to exist on the diagonal, as one can be anonymous both from the government and from other people.
+The results of our study demonstrate the importance of differentiating these types of need for privacy, as relationships were not consistent across the various privacy needs and the five personality traits.
+
+## Limitations and Future Research
+
+One can of course raise the question of whether it is possible or even socially desirable to measure a person’s integrity.
+On the one hand, integrity implies absolute criteria in relation to social norms: Stealing is bad and forbidden, whereas helping is good and encouraged.
+On the other hand, integrity implies relative criteria: Whereas some cultures disapprove of lying whatever the context, others consider lying okay (for example, “white lies” in order to avoid hurting someone’s feelings) [@Altman.1977].
+Thus, ranking behaviors, opinions, and character traits with regard to integrity presents a moral dilemma.
+As a result, throughout our study we have employed a conservative approach and understood and measured integrity as an explicit transgression of social norms that is strong and that most societies would arguably agree upon (for example, most societies would consider stealing as a sign of low integrity).
+Nonetheless, we recommend that future research should further elaborate on the general understanding of integrity as a theoretical concept.
+To date, there is not one overarching concept of integrity that incorporates all of the different aspects of this variable, and yet it would be valuable to examine how other aspects of integrity (e.g., authenticity, trustworthiness, or consistency) relate to need for privacy.
+
+Worth nothing, integrity tests using self-reports have been shown to work surprisingly well, given that they can predict unwanted professional workplace behavior successfully (e.g., theft, drug and alcohol problems, or absenteeism) [@Ones.1993].
+In a meta-analysis with 665 correlation coefficients, self-reported integrity tests were associated with counterproductive behaviors with an average correlation coefficient of _r_ = .47 [@Ones.1993].
+Nonetheless, future research would evidently benefit from including behavioral manifestations of integrity, such as concrete cheating behaviors.
+
+In what follows, we present some methodological points of criticism.
+Despite the fact that we used mostly well-established scales, confirmatory factor analyses showed that some of the original items had to be deleted to achieve adequate factorial validity.
+This resembles the finding by @Hussey.2018, who reported that several widely-used scales in psychological research actually do not show satisfactory factorial validity.
+By using bifactor models, however, it was possible to at least partially alleviate the problem.
+Next, in order to achieve sufficient factorial validity we needed to adapt the scales (for example by deleting items), which introduces problems of overfitting, which in turn potentially impedes the generalisability of the results [see, e.g., @Yarkoni.2017].
+However, by using bifactor models we explicitly tried to retain the largest possible number of items, which should render our results more robust.
+In addition, also when looking at the items individually (see OSM) one can see that the results are not overly dependent on inclusion of specific items.
+Another methodological improvement for future studies concerns the sample, which was comparatively small, leading to a reduced power to detect also small effects.
+Nonetheless, we are still confident that the results should be reliable, because we deliberately selected specific predictors that should exhibit at lest small to moderate relations with need for privacy (i.e., _r_ = .20).
+For small to moderate relations, the current study still had a convincing power of `r power_smallmoderate`%.
+Granted, when aiming to find also small effects (i.e., _r_ = .10) with a probability of 95%, future studies would need to collect the answers of `r sample_95` respondents [@Cohen.1992].
+Finally, generalisability is limited, as our sample was predominantly young, female, highly educated, and collected only in one single country.
+
+Next, future research might consider analyzing predictors of privacy needs that are even more specified.
+For example, it is possible that people who hold dissenting political beliefs could also have a higher need for privacy from the government.
+In this study we focused mostly on escapist motives for why people desire privacy (e.g., sociability, risk aversion).
+Interestingly, @Leary.2003 showed that when predicting engagement in solitary activities, it is less preferable to measure how strongly people want to escape society (avoidance oriented), but rather how much they seek solitude (approach oriented).
+Hence, future studies might want to include predictors such as need for contemplation or trust [see, e.g., @Metzger.2004; @Wheeless.1977].
+Finally, it would be interesting to focus on need for privacy within different minority groups.
+For example, it seems plausible that people with a LGBT background might report needing more privacy from government (because it is potentially repressive or unfriendly toward LGBTs) or other people (especially weaker ties in their social networks who might not approve of their sexual identity).
+
+## Conclusion
+
+In his novel _The Circle_, @Eggers.2013 describes a dystopian society in which people are gradually forfeiting their privacy.
+One after another becomes "transparent": Carrying a small camera around the neck, people begin to broadcast their daily lives to the Internet.
+In the novel, this eventually causes a societal upheaval: "The pressure on those who hadn't gone transparent went from polite to oppressive.
+The question, from pundits and constituents, was obvious and loud: If you aren't transparent, what are you hiding?" [@Eggers.2013, p.
+129].
+
+The results of this study suggest that there might be some truth to the nothing-to-hide argument.
+However, the applicability seems to be limited to (very specific) aspects of anonymity (e.g., avoiding places with video surveillance or leaving one's ID at home).
+In general, the need for privacy seems to be related more closely to other aspects of personality.
 
@@
 # References
-```{r create_r-references}
-r_refs(file = "r-references.bib")
-```
 
@@
 \setlength{\leftskip}{0.5in}
-
 <div id = "refs"></div>
 \endgroup
+
+\newpage
+# Contributions
+
+- Contributed to conception and design: TD, MM
+- Contributed to acquisition of data: MM, TD
+- Contributed to analysis and interpretation of data: TD, MM
+- Drafted and/or revised the article: TD, MM
+- Approved the submitted version for publication: TD, MM
+
+# Funding Information
+
+During the conception and data collection of the study, TD was funded by The German Academic Scholarship Foundation (German: Studienstiftung des deutschen Volkes), which financially supported TD's research stay at UCSB.
+During the writing of the article, TD was funded by the Volkswagen Foundation (German: Volkswagenstiftung), grant "Transformations of Privacy".
+
+MM is funded by a regular and tenured full professorship at UCSB.
+
+# Competing Interests
+
+We declare no competing interests.
+
+# Data Accessibility Statement
+
+All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found on this paper’s project page on the open science framework (https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f).
+In addition, we invite everyone to suggest changes and improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/tree/master).

### 2019-02-12 manuscript/manuscript.tex
- Major changes regarding everything: analyses (e.g., inclusion of bifactor models), ms, etc.

--- 2018-11-14 manuscript/manuscript.tex
@@
-\documentclass[man]{apa6}
+\documentclass[man,floatsintext]{apa6}
 \usepackage{lmodern}
@@
             pdfauthor={Tobias Dienlin~\& Miriam Metzger},
-            pdfkeywords={keywords},
+            pdfkeywords={Privacy, need for privacy, personality, anonymity, integrity, SEM},
             pdfborder={0 0 0},
@@
   \title{Who Needs Privacy?}
-    \author{Tobias Dienlin\textsuperscript{1}~\& Miriam Metzger\textsuperscript{1,2}}
+    \author{Tobias Dienlin\textsuperscript{1}~\& Miriam Metzger\textsuperscript{2}}
     \date{}
@@
 \textsuperscript{1} University of Hohenheim\\\textsuperscript{2} University of California, Santa Barbara}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{Privacy, need for privacy, personality, anonymity, integrity, SEM}
 \usepackage{csquotes}
@@
 
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{lineno}
@@
 
-\authornote{Add complete departmental affiliations for each
-author here. Each new line herein must be indented, like this line.
+\authornote{Tobias Dienlin, Department of Media Psychology, University of Hohenheim, Germany; Miriam Metzger, Department of Communication, University of California, Santa Barbara, United States of America.
 
-Enter author note here.
-
-Correspondence concerning this article should be addressed to Tobias
-Dienlin, University of Hohenheim, Department of Media Psychology (540F).
-E-mail:
-\href{mailto:tobias.dienlin@uni-hohenheim.de}{\nolinkurl{tobias.dienlin@uni-hohenheim.de}}}
+Correspondence concerning this article should be addressed to Tobias Dienlin, University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany.
+E-mail: \href{mailto:tobias.dienlin@uni-hohenheim.de}{\nolinkurl{tobias.dienlin@uni-hohenheim.de}}}
 
 \abstract{
-Objective: This study analyzes how personality relates to peoples'
-desire for privacy. Specifically, we investigated whether the syllogism
-``I don't mind surveillance because I have nothing to hide'' is correct:
-Do people who lack integrity (given they have something to hide) indeed
-desire more privacy?
-
-Method: Study 1 featured an online questionnaire (\emph{N} = 268,
-\emph{M}\textsubscript{age} = 20 years, 72\% female) and Study 2 a
-laboratory experiment (\emph{N} = 87, \emph{M}\textsubscript{age} = 20
-years, 51\% female), where participants wrote an essay about past
-negative, positive, or neutral behaviors to analyze effects on desire
-for privacy.
-
-Results: Study 1 showed that respondents who are more shy, less anxious,
-and more risk averse desired more privacy. Respondents who self-reported
-lacking integrity reported desiring more privacy from government and
-more anonymity. Study 2 replicated these results and showed a
-statistical trend (\emph{p} = .052) that writing about negative past
-behaviors increased desire for interpersonal privacy. Moreover, the
-integrity IAT showed significant relations with desire for privacy from
-government.
-
-Conclusion: It is possible to predict peoples' desire for privacy based
-on their lack of integrity. However, other neutral personality facets
-also explain desire for privacy. Hence, putting everyone who desires
-privacy under general suspicion would be incorrect.
+This study analyzes how personality traits relate to need for privacy.
+We focus on three dimensions: (a) need for privacy from government surveillance, (b) need for privacy from other individuals, and (c) need for anonymity.
+Using an online questionnaire with 271 student respondents, several significant relationships were found.
+For example, results showed that less sociable people desired considerably more privacy on all three dimensions.
+Somewhat more controversially, people who reported less integrity also desired noticeably more anonymity.
+While anxious people desired slightly less privacy from government surveillance, risk avoidant people desired considerably more privacy from other people.
+Traditionalism did not relate to need for privacy.
+Together, the results have several implications.
+For example, they shed some light on the nothing-to-hide argument: A person who desires more anonymity might indeed be of less integrity.
+However, it is equally plausible that this person is just a little less sociable.
 
@@
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\theoremstyle{definition}
-\newtheorem{example}{Example}[section]
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[section]
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
@@
 
-In his novel \emph{The Circle}, ({\textbf{???}}) describes a dystopian
-society in which people are gradually forfeiting their privacy. People
-decide to become \enquote{transparent}, which means that they start
-carrying a small camera around the neck in order to broadcast their
-daily lives to the Internet. Eventually, this causes a societal
-upheaval: \enquote{The pressure on those who hadn't gone transparent
-went from polite to oppressive. The question, from pundits and
-constituents, was obvious and loud: If you aren't transparent, what are
-you hiding?} ({\textbf{???}}). The main argument being offered to
-justify the surveillance is: \enquote{If you have nothing to hide, you
-have nothing to fear.} This syllogism is familiar, given that it
-commonly appears in also nonfictional conversations ({\textbf{???}}).
-Consider, for example, the following tweet: \enquote{I don't download
-illegally. I don't have anything on my comp{[}uter{]} to hide. Hell, I'm
-sure the \#NSA gave up on me years ago.} ({\textbf{???}}).
+In light of the increasing digitization of everyday life, which has led to several sweeping societal changes such as the commodification and monetization of personal information (Sevignani, 2016), privacy has become a major topic of interest.
+Despite its importance, however, we still know surprisingly little about the relation between privacy and personality (e.g., Masur, 2018, p.
+155).
+Why do some people need more privacy than others, and how do these people differ from one another?
+We think that a better understanding of the relation between personality and privacy is crucial: Several theories argue that personality determines privacy behaviors (e.g., Masur, 2018), however, to date there is almost no empirical research that can be used to deduct well-informed hypotheses.
+As a result, the main question of this paper is as follows: What are personality facets that can be used to best explain peoples' need for privacy?
 
-Why do people desire privacy? To date there is only little research on
-why people desire privacy and how the desire for privacy can be
-predicted by aspects of personality. For example, and to the best of our
-knowledge, so far no study exists that has analyzed the nothing-to-hide
-argument from a scientific and empirical perspective. Why do some people
-not care whether government agencies such as the NSA are collecting
-their data ({\textbf{???}}), and why do others protest vehemently in
-order to protect their privacy?
+\hypertarget{the-need-for-privacy}{%
+\subsection{The Need for Privacy}\label{the-need-for-privacy}}
 
-Answering this question is important: Given that government agencies are
-collecting large amounts of data hoping to reduce criminality and
-terrorism, and given that government agencies are collecting this data
-preemptively and without concrete suspicions, it is relevant to find out
-whether this practice of mass surveillance can be justified based on the
-nothing-to-hide argument. As a result, the main question of this paper
-is: Do people who desire more privacy really have more to hide and, more
-generally, what are personality facets that determine peoples' overall
-desire for privacy?
+Privacy as a theoretical concept is both complicated and contested (Nissenbaum, 2010, p.
+71).
+Hence, we begin by outlining our own understanding of privacy.
+First and foremost, privacy captures the extent of voluntary withdrawal from others (Westin, 1967).
+Several models suggest that privacy is multi-dimensional.
+For example, in a theory-driven treatise Burgoon (1982) argued that privacy has four dimensions: informational, social, psychological, and physical privacy.
+Pedersen (1979), by contrast, did an empirical factor analysis (initially starting with 94 items) and suggested that privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity.
+In addition, Schwartz (1968) differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies).
+Finally, one can also distinguish between the objective privacy context, the subjective privacy perception, the psychological need for privacy (which is both a situational and dispositional need), and the resulting privacy behavior (often represented by self-disclosure) (Dienlin, 2014).
 
-\hypertarget{desire-for-privacy}{%
-\subsection{Desire for Privacy}\label{desire-for-privacy}}
+For the purpose of this study, we combine the aforementioned notions and focus on (a) vertical privacy with regard to the need for withdrawal from government surveillance, (b) horizontal privacy in terms of the need for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by the general need for anonymity.
 
-Privacy captures the extent of voluntary withdrawal from others (Westin,
-1967). Several models suggest that privacy is a multi-dimensional
-concept: For example, in a theory-driven treatise ({\textbf{???}})
-argued that privacy has four dimensions: informational, social,
-psychological, and physical privacy. Pedersen (1979), by contrast, did
-an empirical factor analysis (initially starting with 94 items) and
-suggested that privacy exists on six dimensions: reserve, isolation,
-solitude, intimacy with friends, intimacy with family, and anonymity. In
-addition, Schwartz (1968) differentiated between horizontal and vertical
-privacy: Whereas horizontal privacy captures withdrawal from peers,
-vertical privacy refers to withdrawal from superiors or institutions
-(e.g., government agencies). Next to being multi-dimensional, privacy is
-also contingent (Dienlin, 2014): One can, for example, distinguish
-between the objective privacy context, the subsequent subjective
-perception of privacy, the psychological desire for privacy (which is
-both a situational and dispositional need), and the resulting privacy
-behavior (as represented by self-disclosure). For the purpose of this
-study, we combine the aforementioned theories and focus on (a) vertical
-privacy with regard to the desire for withdrawal from government
-surveillance, (b) horizontal privacy in terms of the desire for
-withdrawal from peers, friends, or acquaintances, and (c) both
-horizontal and vertical privacy as captured by the general desire for
-anonymity.
+In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually need privacy.
+Westin (1967) defined four primary positive purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
+Not least, privacy facilitates self-disclosure (Dienlin, 2014), which is vital for attaining social support, initiating relationships, and getting close to one another (Omarzu, 2000).
 
-\hypertarget{the-relation-between-integrity-and-desire-for-privacy}{%
-\subsubsection{The relation between integrity and desire for
-privacy}\label{the-relation-between-integrity-and-desire-for-privacy}}
+On the other hand, however, too much privacy can also be problematic.
+Because human beings are inherently social, being overly cut-off from others can impede flourishing, nurture deviant behavior, or introduce power asymmetries (Altman, 1975).
+\enquote{{[}T{]}he feminist critique rightfully argued that for men, the private sphere can be a shielded sphere in which female suppression is not sanctioned.} (DeCew, 1997, p.
+81, as cited by Masur, 2018, p.~38).
+Next, and as mentioned above, privacy fosters self-disclosure.
+However, any self-disclosure is also always a potential risk because others might disagree, disapprove, or misuse the information in other contexts (Petronio, 2010).
 
-Which specific aspects of personality help predict desire for privacy?
-At its core, the nothing-to-hide argument implies that lack of integrity
-is an important predictor of why people desire privacy. This becomes
-especially apparent when we consider the definition of Solove's (2007)
-nothing-to-hide argument (notably, Solove is a strong critic of the
-nothing-to-hide argument):
+\hypertarget{predicting-the-need-for-privacy}{%
+\subsection{Predicting the Need for Privacy}\label{predicting-the-need-for-privacy}}
 
-The NSA surveillance, data mining, or other government information
-gathering programs will result in the disclosure of particular pieces of
-information to a few government officials, or perhaps only to government
-computers. This very limited disclosure of the particular information
-involved is not likely to be threatening to the privacy of law-abiding
-citizens. Only those who are engaged in illegal activities have a reason
-to hide this information. {[}({\textbf{???}}); p.~753{]}
+In what follows we now explore several personality aspects that we think might predict the need for privacy.
+As there is no established theory that dovetails privacy and personality, it is difficult to deduct precise and well-informed hypotheses.
+The rationales that we outline below should hence considered to be tentative suggestions.
+Also, please note that we elaborate only on those dimensions of need for privacy for which plausible rationales could be found.
 
-This definition helps illustrate the link between lack of integrity and
-desire for privacy: People who have \enquote{engaged in illegal
-activities} can be considered, by definition, to lack integrity
-({\textbf{???}}), which is why they have a reason \enquote{to hide this
-information} (or, in other words, to desire more privacy). In terms of a
-scientific definition of integrity there is no real consensus, however
-most scholars agree that integrity \enquote{incorporates a tendency to
-comply with social norms, avoid deviant behavior, and embrace a sense of
-justice, truthfulness, and fairness} {[}({\textbf{???}}); p.~82{]}.
+The general underlying theoretical framework that guided our selection process was the big five approach (e.g., John \& Srivastava, 1999).
+Note that privacy concerns, a variable conceptually close to need for privacy, shows only negligible relations with the big five factors (Bansal, Zahedi, \& Gefen, 2010; Junglas, Johnson, \& Spitzmüller, 2008).
+In order to be more precise, we hence follow the advice by Paunonen and Ashton (2001) and refer to specific personality facets instead of generic personality factors.
+To illustrate, instead of dwelling on the general factor of \emph{extraversion}, we instead focused on the facet \emph{gregariousness}, which we consider to be more pertinent.
 
-Several theoretical arguments exist why lack of integrity might
-correlate with desire for privacy. In general, any self-disclosure is a
-potential risk because others might disagree, disapprove, or misuse the
-information in other contexts ({\textbf{???}}). Privacy regulation
-theory showed that if self-disclosures are too risky, people raise their
-desired level of privacy, intensify their boundary regulation, and
-employ more mechanisms to seclude and protect themselves
-({\textbf{???}}). In traditional contexts, this could range from
-moderate behaviors like closing doors, to extreme behaviors such as
-physically tossing someone out of the room ({\textbf{???}}). In modern
-contexts, protecting one's privacy can mean to avoid photographs or to
-deliberately shun public places that have surveillance cameras. People
-who have actually committed something bad, treacherous, or illegal
-become even more vulnerable and face a significant risk of
-self-disclosure, because others will surely disapprove of these
-activities ({\textbf{???}}). Hence, the foregoing arguments illuminate
-an indirect link between integrity and desire for privacy: By
-definition, people who participate in negative activities are considered
-to lack integrity ({\textbf{???}}). People who have engaged in negative
-activities have, by definition, more to hide, and disclosures concerning
-those activities pose a high risk. Because of this increased risk,
-people will arguably desire more privacy, as a means to mitigate their
-felt risk ({\textbf{???}}). In this way, the current research extends
-Altman's privacy regulation theory (1976) by suggesting that lack of
-integrity is an important yet unexamined factor that could increase
-peoples' desired level of privacy.
+Our reasoning was guided by another central theoretical thought.
+As implied above, privacy can be either positive or negative.
+Similarly, other people, the government, and anonymity can be considered either a \emph{resource} or a \emph{threat}.
+Having information about a person's personality can inform us whether he or she is more likely to think of others as a resource or a threat.
+It follows that if other people are considered a threat it seems to be more likely that a person will desire more privacy from others, and vice versa (Altman, 1976).
 
-A few studies can be found that imply a relation between privacy and
-integrity. For example, several studies found that surveillance reduces
-cheating behaviors ({\textbf{???}}, Covey.1989). ({\textbf{???}}) asked
-students to solve an impossible maze. In the high surveillance
-condition, the experimenter stood in front of the students and closely
-monitored their behavior. In the low surveillance condition, the
-experimenter stood behind the students, did not monitor their behavior,
-and visual dividers were used to block the experimenter's view of the
-students. Results showed that students were more likely to cheat in the
-low surveillance condition, suggesting that in situations of
-surveillance (i.e., less privacy), people show fewer cheating behaviors
-(i.e., more integrity). Similarly, people are more likely to prevent
-others from stealing when security cameras are visible ({\textbf{???}}),
-which is also a sign of higher integrity. Next, in a longitudinal sample
-with 457 respondents in Germany ({\textbf{???}}), people who reported
-needing more privacy were less satisfied with their lives (\emph{r} =
--.47), had more (\emph{r} = .41) and less positive affect (\emph{r} =
--.39). More importantly however, people who felt they needed more
-privacy were also less authentic on their SNSs profiles (\emph{r} =
--.48) and less authentic in their personal relationships (\emph{r} =
--.28; {\textbf{???}}). For example, people who agreed to items like
-\enquote{I do not talk about personal issues unless my conversation
-partner brings them up first} were more likely to report that their
-online profiles did not truly represent their personality. Given the
-argument that authenticity is a subset of integrity ({\textbf{???}}), we
-reason that the concept of integrity might relate to the desired level
-of privacy. Finally, Pedersen (1982) showed that three dimensions of
-need for privacy related to self-esteem: In his study with \emph{N} = 70
-undergraduate students, respondents who held a lower self-esteem were
-more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21)
-and preferred solitude (\emph{r} = .24). Granted, self-esteem and
-integrity are generally distinct concepts; however, Pedersen's specific
-operationalization of self-esteem integrated several aspects of
-integrity (e.g., by using items such as \enquote{moral, nice, fair,
-unselfish, good, honest, reputable, sane} to measure self-esteem). Thus,
-our overarching hypothesis is that people who lack integrity have a
-greater desire for privacy.
+\hypertarget{sociability}{%
+\subsubsection{Sociability}\label{sociability}}
 
-In Study 1, we used a questionnaire-based design to analyze how lack of
-integrity and other personality facets relate to desire for privacy. In
-accordance with the reasoning mentioned above, we suggest that people
-with less integrity feel a greater desire for privacy. Specifically, we
-argue that integrity may relate to the desire for privacy from (a)
-government surveillance, as governments have the legitimate power to
-prosecute illegal activities. Next, we hypothesize that integrity
-relates to the desire privacy for (b) anonymity. Anonymity makes it more
-difficult for both legal and social agents to identify and address
-potential wrongdoers, which is why people with less integrity will
-prefer situations in which they are anonymous. Finally, lack of
-integrity likely also relates to an increased desire for privacy from
-(c) other people, as most other people will disapprove of immoral or
-illegal activities, and might reveal those activities to authorities.
+First, we argue that need for privacy should be closely related to a person's sociability or gregariousness (which is a subdimension of extraversion, John \& Srivastava, 1999).
+Sociability captures whether people prefer to spend their time alone or with company.
+It seems plausible that people who are more sociable are also more likely to think of other people as a resource, which is why they should generally desire less interpersonal privacy and less anonymity (e.g., Buss, 2001).
+Put differently, given that privacy is a voluntary withdrawal from society (Westin, 1967), we expect that people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.
 
-Hypothesis 1: People who feel lower in self-perceived integrity desire
-more privacy from government surveillance (H1a), more anonymity (H1b),
-and more privacy from other persons (H1c).
+This rationale is supported by several empirical studies: Extroverted people desire less privacy (Morton, 2013), people who describe themselves as introverted thinkers are more likely to prefer social isolation (Pedersen, 1982), and introverted people are more likely to report invasions of privacy (Stone, 1986).
 
-\hypertarget{shyness}{%
-\subsubsection{Shyness}\label{shyness}}
+\hypertarget{integrity}{%
+\subsubsection{Integrity}\label{integrity}}
 
-Critics of the nothing-to-hide argument hold that people who desire
-privacy should not automatically be confronted with suspicion, and that
-privacy has several purposes that are not related to criminal behavior
-({\textbf{???}}). Westin (1967), for example, defined four primary
-purposes of privacy: (1) self-development (i.e., the integration of
-experiences into meaningful patterns), (2) autonomy (i.e., the desire to
-avoid being manipulated and dominated), (3) emotional release (i.e., the
-release of tension from social role demands), and (4) protected
-communication (i.e., the ability to foster intimate relationships).
-These are all important social factors for which people desire privacy.
-Hence, the argument is that people who desire privacy can have several
-legitimate reasons for doing so; reasons which are essential for
-psychosocial wellbeing and which relate to different factors of
-personality. Below, we thus explore other (neutral) aspects of
-personality that potentially predict desire for privacy. In order to be
-more precise, we follow the advice by Paunonen and Ashton (2001) and,
-instead of using generic personality factors as predictors, refer to
-specific personality facets.
+More controversially, it has been argued that people need privacy because they have something to hide.
+The so-called nothing-to-hide argument states that \enquote{If you have nothing to hide, you have nothing to fear.} As described by Solove, the nothing-to-hide argument says that data mining and surveillance by government entities \enquote{is not likely to be threatening to the privacy of law-abiding citizens.
+Only those who are engaged in illegal activities have a reason to hide this information} (Solove, 2007, p.
+753).
+Hence, another potential predictor of why people need privacy could also be a so-called \enquote{lack of integrity}.
 
-First, we argue that people who are more reserved, who feel less
-comfortable in social situations, generally desire more anonymity and
-more interpersonal privacy. Given that privacy is, by definition, a
-voluntary withdrawal from society (Westin, 1967), we expect that people
-who are more reserved or more shy desire more privacy from others.
-Several empirical studies support this hypothesis: Extroverted people
-desire less privacy ({\textbf{???}}), people who describe themselves as
-introverted thinkers are more likely to prefer social isolation
-(Pedersen, 1982), and introverted people are more likely to report
-invasions of privacy ({\textbf{???}}). Finally, we did not find
-convincing theoretical and empirical arguments for why shyness should
-relate to an increased desire for privacy from government surveillance,
-which is why we did not include a hypothesis on this relation.
+Because integrity is a delicate concept, let us first try to define it conceptually.
+Although in terms of a scientific definition there is no consensus, most scholars seem to agree that integrity \enquote{incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness} (Connelly, Lilienfeld, \& Schmeelk, 2006, p.
+82).
+In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow Paunonen (2002) and adopt a lowest common denominator approach, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.
 
-Hypothesis 2: People who are more shy desire more anonymity (H2a) and
-more privacy from other persons (H2b).
+It is indeed possible to think of theoretical arguments for why lack of integrity might correlate positively with need for privacy.
+People who have actually committed crimes evidently face even greater risk from self-disclosure compared to others, because government agencies and people sould surely disapprove of their activities (Petronio, 2010).
+Hence, the government and other people are more likely to be a threat, which should render anonymity rather a resource.
+As a consequence, people with lower integrity might desire more privacy as a means to mitigate their felt risk (Altman, 1976).
+
+There are also a few empirical studies that imply---at least indirectly---a relation between privacy and integrity.
+For example, studies have found that surveillance can reduce cheating behaviors (Corcoran \& Rotter, 1987; Covey, Saladin, \& Killen, 1989).
+Covey et al.
+(1989) for example asked students to solve an impossible maze.
+In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior.
+In the low surveillance condition, the experimenter remained behind the students where he or she could not see the students.
+Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more integrity (i.e., fewer cheating behaviors).
+Next, in a longitudinal sample with 457 respondents in Germany (Trepte, Dienlin, \& Reinecke, 2013), people who felt they needed more privacy were also less authentic on their SNSs profiles (\emph{r} = -.48) and less authentic in their personal relationships (\emph{r} = -.28).
+Given the argument that authenticity is a subset of integrity (Sheldon, 2004), one could hence reason that also the concept of integrity might relate to a person's need for privacy.
+Somewhat related, it has been found that people who are more agreeable are also moderately less concerned about their privacy (Junglas et al., 2008).
+Finally, Pedersen (1982) showed that three dimensions of need for privacy relate to self-esteem: Respondents who held a lower self-esteem were more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21), and preferred solitude (\emph{r} = .24).
+While self-esteem and integrity are distinct concepts, Pedersen's specific operationalization of self-esteem integrated several aspects of integrity by using items such as \enquote{moral, nice, fair, unselfish, good, honest, reputable, sane}..
+
+In conclusion, we could imagine that lack of integrity may indeed relate to an increased need for privacy from government surveillance, as governments have the legitimate power to prosecute illegal activities.
+Next, it seems plausible that lack of integrity relates to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers.
+Finally, lack of integrity may also relate to an increased need for privacy from other people, as most other people will disapprove of immoral or illegal activities, and could even reveal those activities to authorities.
 
@@
 
-Of course, there are also reasons why people might desire less privacy.
-Government agencies often curtail privacy with the aim to prevent crime:
-For example, the NSA's surveillance programs are often considered a
-direct response to the 9 / 11 terrorists attacks ({\textbf{???}}). It
-seems plausible that people who are more afraid of terrorist attacks are
-also more likely to consent to these surveillance programs, given that
-these programs promise to reduce the likelihood of future attacks. One
-can then argue that people who are afraid of terrorist attacks are also
-more afraid of threats overall, which is why we suggest that people who
-are, in general, more anxious desire less privacy from government
-surveillance and less anonymity. We did not include a hypothesis on the
-potential relation between anxiety and desire for interpersonal privacy.
-On the one hand, one could argue that people who are more anxious are
-more reserved, given that social interactions can pose significant risks
-(especially with strangers or weak ties; {\textbf{???}}). At the same
-time, one could suggest that especially those people who are more
-anxious desire less privacy from others (and especially their strong
-ties), in order to cope better with their daily challenges. At the end,
-given that we measure interpersonal privacy on a general level (and do
-not distinguish between desire for privacy from (a) weak ties and (b)
-strong ties), it seems plausible that both effects could cancel each
-other out.
+Next, it seems possible that the need for privacy is also related to people's level of general anxiety (which is a subdimension of neuroticism, John \& Srivastava, 1999).
+General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened.
+With regard to interpersonal privacy, one could argue that people who are anxious are more likely to feel that social interactions pose a greater risk and threat (especially with strangers or weak ties; Granovetter, 1973), which is why anxious people might desire more privacy.
+Somewhat related, prior empirical research has shown that people who are more concerned about their privacy are also more likely to withdraw online, for example by deleting posts or untagging themselves from linked content (Dienlin \& Metzger, 2016).
+On the other hand, one could argue in favor of the opposite: People who are more anxious may desire \emph{less} privacy from others (especially their strong ties), as a means to cope better with their daily challenges.
 
-Hypothesis 3: People who are more anxious desire less privacy from
-government surveillance (H3a) and more anonymity (H3b).
+Concerning the need for privacy from government surveillance, we could imagine that people who are more anxious desire less privacy.
+Despite the fact that only 18\% of all US-Americans trust their government \enquote{to do what is right} (Pew Research Center, 2017), almost everyone agrees that \enquote{it's the government's job to keep the country safe}, with most people also being satisfied with the government's job (Pew Research Center, 2015).
+Hence, when being anxious, the government should rather be seen as a resource than a threat.
+It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that these programs promise to prevent crime or to reduce the likelihood of terrorist attacks (Greenwald, 2013), implying that people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.
 
@@
 
-Disclosing personal information always poses a certain risk, given that
-others can misuse self-disclosed personal information in different
-contexts, which can lead to severe consequences ({\textbf{???}}). Not
-everyone will feel intimidated by this hypothetical threat---except
-those who have a general tendency to avoid taking unnecessary risks. The
-most cautious strategy to minimize risks of personal self-disclosures
-would be, arguably, to keep as much information as possible private.
-Hence, we suggest that people who are, in general, more risk averse have
-a good reason to desire more privacy in all three aforementioned
-contexts.
-
-Hypothesis 4: People who are more risk averse desire more privacy from
-government surveillance (H4a), more anonymity (H4b), and more privacy
-from other persons (H4c).
+Similarly, it could be that need for privacy is related to the general tendency to avoid risks, to deliberate, and to plan carefully (deliberation is a subdimension of conscientiousness, John \& Srivastava, 1999).
+Risk avoidance captures the degree to which people prefer to abstain from taking risks.
+If other people are considered a threat, people who are risk averse should desire more interpersonal privacy, because they may feel greater risk associated with disclosure of personal information.
+The most cautious strategy to minimize risks of information disclosure would be, arguably, to keep as much information as possible private.
+Somewhat related, empirical studies report that people who think that their privacy is at risk are less likely to disclose information online (e.g., Bol et al., 2018).
+Moreover, research suggests that conscientious people are slightly more concerned about their privacy (Junglas et al., 2008).
+But again, especially with regard to privacy from government surveillance, risk averse people could also desire \emph{less} privacy, in order for the government to be able to avert potential threats.
 
@@
 
-The personal computer and the Internet have rendered the world
-increasingly digitized: Social interactions, purchases, and medical
-treatments nowadays all produce digital traces, which can be combined
-into accurate latent user profiles. Given the features of digital
-information (i.e., information is persistent, searchable, reproducible,
-and scalable; {\textbf{???}}), this allows for unprecedented ways and
-degrees of surveillance. Mark Zuckerberg famously observed that privacy
-is no longer a \enquote{social norm,} rather that people share personal
-information ({\textbf{???}}). Hence, in order to be part of contemporary
-life (e.g., by using SNSs), it seems necessary to give up some privacy.
-However, arguably not everyone is willing to pay that price, and
-especially people who are more conservative might prefer to stick to
-their usual routines and decide against giving up their privacy. This is
-supported by empirical research: Older people, who are generally less
-open and more traditional ({\textbf{???}}), are more concerned about
-their privacy than younger people ({\textbf{???}}). Taken together, we
-suggest that people who are more traditional also desire more privacy in
-all three aforementioned contexts.
+Next, it seems plausible that need for privacy is also related to traditionality (which is a subdimension of openness to experience, John \& Srivastava, 1999).
+Traditionalism measures whether people prefer to stick with their usual routines.
+The computers and the Internet have rendered the world increasingly knowable: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.
+Given that digital information is persistent, searchable, reproducible, and scalable (boyd, 2008), this allows for unprecedented means and degrees of surveillance.
+Mark Zuckerberg famously observed that privacy is no longer a social norm, rather the norm is that people share personal information (Johnson, 2010).
+Hence, in order to be part of contemporary life, it seems necessary to give up some privacy.
+However, people may not be equally willing to pay that price, and especially people who are more traditional might decide against giving up their privacy.
 
-Hypothesis 5: People who are more traditional desire more privacy from
-government surveillance (H5a), more anonymity (H5b), and more privacy
-from other persons (H5c).
+Empirical research does find that older people, who are generally less open and more traditional (Donnellan \& Lucas, 2008), are more concerned about their privacy (Fife \& Orjuel, 2012).
+On the other hand, Junglas et al.
+(2008) report that openness to experience is positively related to privacy concern, which would argue in favor of the exact opposite.
+Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three aforementioned contexts.
+
+\hypertarget{socio-demographic-variables}{%
+\subsubsection{Socio-demographic variables}\label{socio-demographic-variables}}
+
+Finally, it has often been shown that socio-demographic variables such as sex, age, and affluence can relate to the need for privacy (Park, 2015; Tifferet, 2019; Trepte et al., 2013; Weinberger, Zhitomirsky-Geffet, \& Bouhnik, 2017).
+Although these variables do not specifically address our research question at hand they will be included---not least as their omission could lead to spurious results or an inflation of false positives.
 
@@
 
-We report how we determined our sample size, all data exclusions (if
-any), all manipulations, and all measures in the study.
+This section describes how we determined the sample size, data exclusions, the analyses, and all measures in the study.
 
-\hypertarget{procedure-and-participants}{%
-\subsection{Procedure and
-participants}\label{procedure-and-participants}}
+\hypertarget{sample}{%
+\subsection{Sample}\label{sample}}
 
-Participants were students from a university in the western U.S. who
-received course credit for taking part in the study. The sample
-consisted of \emph{N} = 296 respondents, with an age that ranged from 18
-to 56 years (\emph{M} = 20 years). 72\% of the respondents were female.
-The median participation time was 24 minutes. Regarding ethnicity, 37\%
-of the respondents were Non-Hispanic White / Caucasian, 4\% Black /
-African American, 21\% Hispanic / Latino, 24\% Asian / Pacific Islander,
-0\% Native American, 5\% others, and 8\% nonresponse.
+Participants were students from an IRB-approved subject pool at a university in the western U.S.
+All students received course credit for participating in the study.
+The initial sample consisted of 296 respondents.
+We removed three cases with problematic response patterns (e.g., straight-lining, missing of inverted items), which we identified using the Guttman value (Meijer, Niessen, \& Tendeiro, 2016).
+Next, we excluded one participant who provided an illogical age (i.e., 9 years).
+We also excluded 21 respondents because they answered less than 50\% of all questions.
+The remaining missing responses (0.21\%) were imputed using predictive mean matching.
+Analyses showed no respondents needed to be excluded due to \enquote{speeding} (i.e., \textless{} 5 min answer time).
+The final sample consisted of 271 respondents.
+
+Age of participants ranged from 18 to 56 years (\emph{M} = 20 years), with 27\% of the respondents being male. The median participation time was 25 min.
+
+The data were collected in 2015.
+While we aimed to collect a large number of participants (i.e., \emph{N} \textgreater{} 300), at the time we were not yet aware of the importance to run a-priori power analyses to determine sample size.
+A post-hoc power analysis shows that the final sample size allowed to find effects with a size of \(\upbeta\) = .22 in 95\% of all cases, and that we had power to detect small effects (i.e., \(\upbeta\) = .10) in 38\% of all cases.
+
+\hypertarget{data-analyses}{%
+\subsection{Data Analyses}\label{data-analyses}}
+
+All hypotheses were tested using a two-tailed significance level of 5\%.
+Because all predictors were chosen on the basis of a-priori reasoning we did not control for alpha error inflation.
+We classified regression coefficients with values exceeding \textbar{}\(\upbeta\)\textbar{} = .10 as small effects, \textbar{}\(\upbeta\)\textbar{} = .30 as medium effects, and \textbar{}\(\upbeta\)\textbar{} = .50 as large effects.
+Our smallest effect size of interest (SESOI; Lakens, Scheel, \& Isager, 2018) was \textbar{}\(\upbeta\)\textbar{} = .10.
+Effects below the SESOI were considered too small to be theoretically relevant.
+
+The factorial validity of the measures and the hypotheses were tested with structural equation modeling (SEM).
+Mardia's test showed that the assumption of multivariate normality was violated, \emph{p}(skewness) \textless{} .001, \emph{p}(kurtosis) \textless{} .001.
+As a result, we used the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator.
+Fit was assessed using the conventional measures and criteria as proposed by Kline (2016).
+
+First, we tested the factorial validity of the variables we collected.
+In a first step, we ran confirmatory factor analyses (CFAs) to determine whether the variables were uni-dimensional.
+If fit was not adequate, we then ran exploratory factor analyses (EFAs) to assess the actual underlying factor structure.
+If more than one factor was revealed, we tried to find a bifactor model solution.\footnote{Bifactor models implement one factor that explains the variance in all items (the so-called general factor or g-factor).
+In addition, at least another two more factors are implemented that explain the variance in a subset of the items.
+The general factor and the specific factors are orthogonal.
+Bifactor models are nested within hierarchical models.
+For more information on bifactor models, see Kline (2016), p.~319.} This way we were able to attain a general measure of the predictors, instead of needing to further complicate our analyses by including subdimensions of the predictors.\footnote{Note that we did not specify a bifactor model of need for privacy, because we were explicitly interested in the relations between the personality facets and the three dimensions of need for privacy.} If no adequate bifactor model could be found, we proceeded by deleting items with low loadings on the general factor and/or the specific factors.
+If also after deletion of individual items no bifactor solution emerged, using a subset of the items we then aimed to extract a single factor with sufficient factorial validity.
+
+To anwers our research question, we first had a look at the variables' bivariate relations (see Figure \ref{fig:bivar-fig}).
+To better assess the variables' potential causal relations, we next ran a multivariate structural regression model.
+Because we were interested in a complex model (overall, eight predictors and three outcomes) but the sample was comparatively small, we simplified the model.
+To this end, instead of a fully latent structural regression model we conducted a partially latent structural regression model, in which the predictor variables were modelled as single indicators while controlling for measurement error (Kline, 2016, p.
+214).
+To get high-quality single indicators of the predictors, we computed the average of the model predicted values / latent factor scores, which we extracted from the CFAs.
+If the CFAs showed a single-factor solution, we used the model predicted values for this latent factor; if the CFAs produced a bifactor solution, we used the model predicted values for the general latent factor.
+As main variable of interest, the outcome need for privacy was measured as a three-dimensional latent factor consisting of overall 12 items (see below).
+
+Finally, combining the information of several items into a latent factors helps to reduce and combine information.
+At the same time, however, this approach also introduces several researcher degrees of freedom.
+We hence emphasize that we deleted items only in order to achieve satisfactory factorial validity and not in order to cherry-pick significant material.
+In light of our not having preregistered the analyses and in order to provide the complete picture, in the online supplementary material (OSM) we hence also report how the independent variables predicted each item individually.
+
+R (Version 3.5.1; R Core Team, 2018) and the R-packages \emph{GGally} (Version 1.4.0; Schloerke et al., 2018), \emph{ggplot2} (Version 3.1.0; Wickham, 2016), \emph{knitr} (Version 1.21; Xie, 2015), \emph{lavaan} (Version 0.6.3; Rosseel, 2012), \emph{mice} (Version 3.3.0; van Buuren \& Groothuis-Oudshoorn, 2011), \emph{MVN} (Version 5.5; Korkmaz, Goksuluk, \& Zararsiz, 2014), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{PerFit} (Version 1.4.3; Tendeiro, Meijer, \& Niessen, 2016), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{pwr} (Version 1.2.2; Champely, 2018), \emph{semTools} (Version 0.5.1; Jorgensen et al., 2018), and \emph{tidyverse} (Version 1.2.1; Wickham, 2017) was used for the analyses.
 
@@
 
-Despite the fact that we mostly used well-established scales,
-confirmatory factor analyses (CFAs) showed that some of the original
-items had to be deleted in order to achieve adequate factorial validity.
-The final scales showed acceptable fit (CFI \textgreater .90, TLI
-\textgreater .90, RMSEA \textless .10, SRMR \textless .10), good
-composite reliability (REL(\(\upomega\)) \textgreater .60), and adequate
-convergent factorial validity (AVE \textgreater .50; see Table
-\ref{tab:DIS_Study_4_Table_1}). Respondents answered all items on a
-7-point Likert scale ranging from 1 (\emph{strongly disagree}) to 7
-(\emph{strongly agree}).
+In this section we present how we operationalized our constructs.
+All items were answered on a 7-point Likert scale ranging from 1 (\emph{strongly disagree}) to 7 (\emph{strongly agree}).
+The results of the CFAs showed that it was possible to model all variables with at least acceptable fit.
+For an overview of the items' psychometrics, factorial validity, and reliability, see Table \ref{tab:psychometrics}.
+A list of all the items that were used (including deleted ones), results of CFAs/EFAs, as well as item statistics and their distribution plots can be found in the OSM.
 
-The data, all items (including deleted ones), results of CFAs, item
-statistics, and distribution plots can be found in the online
-supplementary material.\footnote{\url{https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f}\}\}}
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:psychometrics}Psychometrics of Variables Used.}
+\footnotesize{
+\begin{tabular}{lllllllllllll}
+\toprule
+ & \multicolumn{1}{c}{m} & \multicolumn{1}{c}{sd} & \multicolumn{1}{c}{chisq} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{pvalue} & \multicolumn{1}{c}{cfi} & \multicolumn{1}{c}{tli} & \multicolumn{1}{c}{rmsea} & \multicolumn{1}{c}{srmr} & \multicolumn{1}{c}{omega} & \multicolumn{1}{c}{alpha} & \multicolumn{1}{c}{ave}\\
+\midrule
+Privacy need &  &  &  &  &  &  &  &  &  &  &  & \\
+\ \ \ (Combined) & 4.17 & 1.62 & 97.74 & 50.00 & < .001 & .95 & .93 & .06 & .06 & .84 & .88 & .46\\
+\ \ \ Government & 4.12 & 1.49 & 6.39 & 5.00 & .270 & 1.00 & .99 & .03 & .02 & .87 & .87 & .57\\
+\ \ \ Interpersonal & 4.21 & 1.59 & 10.61 & 2.00 & .005 & .92 & .76 & .13 & .05 & .61 & .62 & .30\\
+\ \ \ Anonymity & 2.90 & 1.50 & 3.11 & 2.00 & .212 & .99 & .98 & .05 & .03 & .69 & .69 & .36\\
+Sociability & 4.70 & 1.50 & 5.94 & 2.00 & .051 & .98 & .95 & .09 & .03 & .79 & .79 & .49\\
+Integrity & 4.56 & 1.83 & 47.93 & 25.00 & .004 & .96 & .94 & .06 & .04 & .79 & .82 & .40\\
+Anxiety & 4.42 & 1.52 & 38.05 & 18.00 & .004 & .95 & .93 & .06 & .04 & .80 & .82 & .41\\
+Risk aversion & 4.32 & 1.55 & 5.16 & 5.00 & .397 & 1.00 & 1.00 & .01 & .02 & .78 & .78 & .42\\
+Traditionality & 3.90 & 1.60 & 10.71 & 5.00 & .058 & .98 & .95 & .06 & .03 & .74 & .74 & .37\\
+\bottomrule
+\addlinespace
+\end{tabular}
+}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} All items were measured on 7-point scales with Likert response options.
+Alpha = Cronbach's alpha (internal consistency); omega = Raykov's omega (composite reliability); ave = average variance extracted.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
 
-\hypertarget{desire-for-privacy-1}{%
-\subsubsection{Desire for privacy}\label{desire-for-privacy-1}}
+\hypertarget{need-for-privacy}{%
+\subsubsection{Need for privacy}\label{need-for-privacy}}
 
-We measured desire for privacy on three dimensions: (a) Desire for
-privacy from government surveillance, which represents the extent to
-which people want the government to abstain from collecting information
-about their personal life. One example item is \enquote{I feel the need
-to protect my privacy from government agencies.} (b) Desire for
-anonymity, which measures the extent to which people feel the need to
-avoid identification(\enquote{I need to be able to use a fake name on
-social network sites to preserve my privacy\}). (c) Desire for privacy
-from other people, which measures the extent to which people want to
-withhold personal information from others(}I don't feel the need to tell
-my friends all my secrets\}). For each dimension, we used 3
-self-developed items that build on prior studies ({\textbf{???}}).
+As the main variable of interest, we collected several items to measure need for privacy.
+First, we collected four items capturing the need for informational privacy using the scale developed by Trepte and Masur (2017).
+Second, we measured need for privacy on a societal level using nine self-designed items.
+The first subdimension was government surveillance, which represents the extent to which people want the government to abstain from collecting information about them.
+The second dimension was anonymity, which captures the extent to which people feel the need to avoid identification.
+Third, we measured need for privacy on an interpersonal level using nine self-designed items.
+The first subdimension measures need for privacy from other people in online contexts.
+The second subdimension measures need for privacy from other people in offline contexts.
 
-\hypertarget{integrity}{%
-\subsubsection{Integrity}\label{integrity}}
+EFAs and CFAs revealed a well-fitting model with 12 items (one double-loading), which consisted of the three dimensions (a) need for privacy from the government, (b) need for privacy from other people, and (c) need for anonymity.
+For a list of all items, see Table \ref{tab:need-for-privacy-items}.
 
-Integrity measures the extent to which people comply with social norms
-and values. When measuring integrity, the question arises whether it is
-possible to measure integrity based on self-reports. Interestingly,
-integrity tests that are based on self-reports have been shown to work
-successfully, given that they can predict unwanted professional
-workplace behavior sufficiently (e.g., theft, drug and alcohol problems,
-or absenteeism; {\textbf{???}}). In order to measure lack of integrity,
-we thus used 4 items of the subscale integrity of the Supernumerary
-Personality Inventory ({\textbf{???}}). An example item is \enquote{I
-don't think there's anything wrong with cheating a little on one's
-income tax forms.}
+\begin{table}[t]
 
-\hypertarget{shyness-1}{%
-\subsubsection{Shyness}\label{shyness-1}}
+\caption{\label{tab:need-for-privacy-items}Overview of Items Measuring Need for Privacy}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}{l}
+\toprule
+Item content\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{1}{l}{\textbf{Privacy need government}}\\
+\hspace{1em}I need government agencies to respect my privacy, even if that hinders a greater societal cause.\\
+\hspace{1em}I need the information that companies (e.g., Amazon, Facebook, or Google) have about me to stay private so that the government can never access it.\\
+\hspace{1em}I don't want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.\\
+\hspace{1em}I don't want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.\\
+\hspace{1em}I feel the need to protect my privacy from government agencies.\\
+\addlinespace[0.3em]
+\multicolumn{1}{l}{\textbf{Privacy need interpersonal}}\\
+\hspace{1em}My need for privacy is so strong that it prevents me from using Facebook \vphantom{1} actively.\\
+\hspace{1em}I don't feel the need to tell my friends all my secrets.\\
+\hspace{1em}I feel the need to protect my privacy from other people.\\
+\hspace{1em}I prefer it when other people do not know much about me.\\
+\addlinespace[0.3em]
+\multicolumn{1}{l}{\textbf{Privacy need anonymity}}\\
+\hspace{1em}I need to be able to use a fake name on social network sites to preserve my privacy.\\
+\hspace{1em}I feel the need to avoid places with video surveillance.\\
+\hspace{1em}I prefer not to carry my ID with me all the time to preserve my privacy.\\
+\hspace{1em}My need for privacy is so strong that it prevents me from using Facebook actively.\\
+\bottomrule
+\end{tabular}}
+\end{table}
 
-Shyness captures whether people prefer to spend their time alone or in
-company. We measured shyness with 4 items of the inverted extraversion
-subscale gregariousness ({\textbf{???}}). An example item is "I shy away
-from crowds of people.\}
+\hypertarget{sociability-1}{%
+\subsubsection{Sociability}\label{sociability-1}}
+
+Sociability was measured with the extraversion subscale \emph{gregariousness} (John \& Srivastava, 1999), which consists of eight items.
+An example item is \enquote{I shy away from crowds of people.} Analyses revealed that a bifactor model based on a subset of six items showed good fit to the data.
+
+\hypertarget{integrity-1}{%
+\subsubsection{Integrity}\label{integrity-1}}
+
+In order to measure integrity, we used the subscale \emph{integrity} of the Supernumerary Personality Inventory (Paunonen, 2002), which consists of eight items.
+In addition, we designed another three items.
+An example item is \enquote{I don't think there's anything wrong with cheating a little on one's income tax forms.} Analyses revealed that a bifactor model based on a subset of nine items showed good fit to the data.
 
@@
 
-Anxiety measures whether people are afraid of negative external
-influences. We measured anxiety with 4 items of the neuroticism subscale
-anxiety ({\textbf{???}}). An example item is "I am easily frightened.\}
+Anxiety was measured with the neuroticism subscale \emph{anxiety} (John \& Srivastava, 1999), which consists of eight items.
+An example item is \enquote{I am easily frightened.} Analyses revealed that a bifactor model using all eight items showed good fit to the data.
 
@@
 
-Risk avoidance captures whether people abstain from taking risks. We
-measured risk avoidance with 4 items of the conscientiousness subscale
-deliberation ({\textbf{???}}). An example item is "I think twice before
-I answer a question.\}
+Risk avoidance was measured with the conscientiousness subscale \emph{deliberation} (John \& Srivastava, 1999), which consists of eight items.
+An example item is \enquote{I plan ahead carefully when I go on a trip.} Analyses revealed that a bifactor model using all eight items showed good fit to the data.
 
@@
 
-Traditionalism measures whether people prefer to stick with their usual
-routines. We measured traditionalism with 4 items of the inverted
-openness to experiences subscale actions ({\textbf{???}}). An example
-item is "I'm pretty set in my ways.\}
-
-\hypertarget{data-analyses}{%
-\subsection{Data analyses}\label{data-analyses}}
-
-All hypotheses were tested with structural equation modeling (SEM). To
-assess the SEM assumption of multivariate normality, we computed a
-multivariate Shapiro-Wilk normality test. The results showed a violation
-of multivariate normality (\emph{W} = 0.90, \emph{p} \textless .001),
-which is why we used the more robust Satorra-Bentler scaled test
-statistic as estimator. We treated missing data with casewise deletion
-and tested all hypotheses with a two-tailed p \textless .050
-significance level; values between \emph{p} = .050 and \emph{p} = .010
-were considered trends toward significance. Regarding effect sizes, we
-classified regression coefficients with values exceeding \(\upbeta\) =
-.10 as small effects, \(\upbeta\) = .30 as medium effects, and
-\(\upbeta\) = .50 as large effects.
-
-Unfortunately, we did not determine sample size based on a priori power
-analyses. We decided against including social desirability as a control
-variable, because even though social desirability can affect answers to
-sensitive questions ({\textbf{???}}), it is more likely to reflect a
-true personality trait than false answering behavior ({\textbf{???}}).
-Likewise, we did not include demographic control variables such as age
-or education, because we used a typical student sample with little
-demographic variance. We used R (Version 3.5.1; R Core Team, 2018) for
-all our analyses.
+Traditionalism was measured with the (inverted) openness to experiences subscale \emph{actions} (John \& Srivastava, 1999), which consists of eight items.
+An example item is \enquote{I'm pretty set in my ways.} Analyses revealed that a model with a single factor based on a subset of five items showed good fit to the data.
 
@@
 
+For an overview of the results of the bivariate relations, see Figure \ref{fig:bivar-fig}.
+For the statistical results of the SEM, see Table \ref{tab:sem-tab}, and for a graphical visualization, Figure \ref{fig:sem-fig}.
+Note that the final structural regression model that was estimated fit the data comparatively well, \(\chi^2\)(137) = 218.68, \textit{p} \textless{} .001, cfi = .93, rmsea = .05, 90\% CI {[}.04, .06{]}, srmr = .06.
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=.9\textwidth]{manuscript_files/figure-latex/bivar-fig-1}
+
+}
+
+\caption{Results of the bivariate relations.
+Above diagonal: zero-order correlation matrix; diagonal: density plots for each variable; below diagonal: bivariate scatter plots for zero-order correlations.
+Solid regression lines represent linear regressions, dashed regression lines represent quadratic regressions.
+Calculated with the variables’ latent factor scores.}\label{fig:bivar-fig}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/sem-fig-1.pdf}
+\caption{\label{fig:sem-fig}Graphical overview of the results of Structural Equation Model.
+Shows the 95\% confidence intervals of standardized coefficients.
+Dashed lines indicate the SESOI of \textbar{}.10\textbar{}.}
+\end{figure}
+
+The bivariate correlations revealed that respondents who were more sociable than others also needed considerably less privacy from other people.
+In addition, they also needed slightly less privacy from the government and less anonymity.
+Also when analyzed in the multivariate structural regression model holding all other predictors constant, sociability was related to a reduced need for privacy on all three dimensions.
+
+Next, both the bivariate and the SEM results showed that respondents who reported less integrity compared to others desired considerably more anonymity.
+No significant relations existed with the need for privacy from the government and the need for anonymity.
+
+For anxiety, both analyses showed that respondents who indicated being more anxious indeed desired less privacy from the government.
+The effect size was small to moderate.
+Whereas the bivariate analyses revealed a small significant relation between anxiety and need for anonymity, this relation disappeared when analyzed in the SEM keeping all other predictors constant.
+No significant relationship with need for privacy from other people emerged.
+
+Both analyses showed that respondents who reported being more risk avoidant than others desired considerably more privacy from other people.
+The bivariate analyses showed a small and positive association between risk avoidance and need for privacy from government surveillance, which ceased to exist in the SEM.
+No significant relation with need for anonymity was found.
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:sem-tab}Results of Structural Equation Model.}
+\footnotesize{
+\begin{tabular}{lrrrrr}
+\toprule
+Predictor & \multicolumn{1}{c}{b} & \multicolumn{1}{c}{ll} & \multicolumn{1}{c}{ul} & \multicolumn{1}{c}{beta} & \multicolumn{1}{c}{p}\\
+\midrule
+Privacy need government &  &  &  &  & \\
+\ \ \ Sociability & -0.23 & -0.44 & -0.01 & -.17 & .037\\
+\ \ \ Integrity & -0.07 & -0.37 & 0.22 & -.04 & .622\\
+\ \ \ Anxiety & -0.31 & -0.58 & -0.03 & -.18 & .029\\
+\ \ \ Traditionalism & 0.16 & -0.12 & 0.44 & .10 & .257\\
+\ \ \ Risk avoidance & 0.20 & -0.10 & 0.51 & .12 & .197\\
+\ \ \ Male & 0.38 & 0.08 & 0.68 & .16 & .012\\
+\ \ \ Age & 0.03 & > -0.01 & 0.05 & .06 & .051\\
+\ \ \ Income & 0.07 & -0.06 & 0.20 & .07 & .276\\
+Privacy need interpersonal &  &  &  &  & \\
+\ \ \ Sociability & -0.39 & -0.58 & -0.19 & -.33 & < .001\\
+\ \ \ Integrity & 0.01 & -0.24 & 0.26 & .01 & .930\\
+\ \ \ Anxiety & > -0.01 & -0.24 & 0.24 & > -.01 & .991\\
+\ \ \ Traditionalism & 0.19 & -0.11 & 0.48 & .14 & .213\\
+\ \ \ Risk avoidance & 0.40 & 0.12 & 0.67 & .27 & .005\\
+\ \ \ Male & 0.28 & > -0.01 & 0.56 & .13 & .053\\
+\ \ \ Age & 0.02 & -0.01 & 0.04 & .05 & .208\\
+\ \ \ Income & 0.03 & -0.12 & 0.19 & .03 & .686\\
+Privacy need anonymity &  &  &  &  & \\
+\ \ \ Sociability & -0.22 & -0.40 & -0.04 & -.20 & .018\\
+\ \ \ Integrity & -0.40 & -0.67 & -0.14 & -.28 & .003\\
+\ \ \ Anxiety & -0.16 & -0.39 & 0.07 & -.11 & .167\\
+\ \ \ Traditionalism & -0.03 & -0.29 & 0.23 & -.02 & .814\\
+\ \ \ Risk avoidance & 0.04 & -0.21 & 0.28 & .03 & .770\\
+\ \ \ Male & 0.29 & 0.01 & 0.58 & .14 & .041\\
+\ \ \ Age & 0.03 & < 0.01 & 0.07 & .10 & .031\\
+\ \ \ Income & 0.14 & -0.01 & 0.28 & .15 & .065\\
+\bottomrule
+\end{tabular}
+}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+Next, the bivariate analyses showed that respondents who scored higher on traditionalism also reported increased levels of need for privacy from government surveillance and other people.
+However, both relations disappeared in the SEM.
+No significant relation with need for anonymity was found.
+
+Finally, regarding socio-demographic variables, the SEM showed that respondents who were older also desired slightly more anonymity.
+Male respondents desired more privacy from the government and more anonymity.
+Respondents with a higher income did not exhibit different levels of need for privacy.
+
+Summarizing across the results, the predictors explained 12.04\% of the variance in need for privacy from the government, 28.27\% of the variance in need for privacy from other people, and 18.59\% of the variance in need for anonymity.
+
 \hypertarget{discussion}{%
@@
 
-The results of Study 1 showed that integrity relates to several
-dimensions of desire for privacy: People who reported being of lower
-integrity desired more privacy from government and more anonymity. In
-other words, people who agreed that there would be nothing wrong with
-cheating a little or lying occasionally were also more likely to agree
-that the government should not invade peoples' privacy, even if that
-could help to prevent terrorist attacks. Likewise, people who said, for
-example, that they would feel tempted to take things that do not belong
-to them were also more likely to avoid situations in which they were
-identifiable.
+This study analyzed the extent to which the need for privacy can be predicted and explained by personality traits.
+First, the results of the bivariate analyses showed that the need for privacy can be predicted surprisingly well by means of specific personality facets.
+Second, also when analyzed together in a structural regression model alongside additional socio-demographic variables, most personality variables remained significant, supporting the robustness of the relations.
 
-In addition, desire for privacy was predicted also by other (neutral)
-personality facets: People who were more shy, more risk averse, and less
-anxious also desired more privacy. This implies that next to lack of
-integrity there are various other personality-related aspects that
-predict desire for privacy.
+Most prominently, we find that sociability was negatively related to all three dimensions of need for privacy.
+This does not come to much surprise as privacy captures the withdrawal from others and is hence already from a conceptual point of view closely related to sociability.
+Nonetheless, it is interesting to see that the relation is indeed thus proximal---especially in light of prior studies not having found a significant relation between extraversion and concern for privacy (Junglas et al., 2008), which are both related variables.
 
-People who are more shy, more risk averse, or less anxious also desire
-more privacy. For example, people who are less anxious are less likely
-to accept government surveillance (arguably because they are less afraid
-of terrorist attacks). When looking at the bigger implications of the
-results, this shows the importance to make differentiated claims on why
-people desire privacy: Indeed, the results suggest that some people
-desire privacy because they might have something to hide. However,
-putting everyone who desires privacy under a general suspicion is wrong
-given that shy, risk averse, and less anxious people are also more
-likely to desire privacy.
+Next, and more controversial, our results also showed that the desire for anonymity is related substantially with measures of integrity.
+People who self-reported lower integrity desired more anonymity.
+Respondents who said, for example, that they would feel tempted to take things that do not belong to them were also more likely to avoid situations in which they were identifiable.
+This finding hence supports the logic behind the \enquote{nothing to hide} argument.
+It also follows Altman's privacy regulation theory (1976), which states that if exposure of information is risky it is likely that people will use more mechanisms to strengthen their social boundaries and increase their desired level of privacy.
+Importantly, however, integrity was not related to need for privacy from other people or to need for privacy from government surveillance, which hence limits the generalisability of the nothing-to-hide argument.
+In addition, note that the items measuring need for anonymity were very difficult (the mean was much lower compared to the other dimensions; see Table \ref{tab:psychometrics})---hence, the relationship between integrity and need for privacy might show only in very specific domains, for example, when it comes to avoiding places with video surveillance.
+In conclusion, the relation between integrity and need for privacy seems to be limited to certain aspects of need for privacy only.
+It should hence not be overly generalized.
 
-In conclusion, our results follow ({\textbf{???}}), who reasoned that if
-exposure of information is risky it is likely that people will use more
-mechanisms to strengthen their social boundaries and increase their
-desired level of privacy. This study thus aligns with Altman's privacy
-regulation theory by showing that, in several contexts, people with
-lower integrity had a higher level of desired privacy.
+Interestingly, the data showed that people who were more anxious were also more willing to accept government surveillance.
+This might be explained by the fact that governments are explicitly commissioned to help prevent crime or terrorist attacks, which are things more anxious people are more likely to dread.
 
-\hypertarget{limitations-and-future-perspective}{%
-\subsection{Limitations and future
-perspective}\label{limitations-and-future-perspective}}
+People who were more risk averse desired more privacy from other people.
+Specifically, people who try to avoid risks are less inclined to share secrets with friends.
+This finding makes sense and can be aligned with prospect theory (Kahneman \& Tversky, 1979): The risks of a secret being publicly disclosed seem to outweigh the potential benefits of sharing it with confidants.
 
-In our analysis of predictors of privacy, we followed the recommendation
-by Paunonen and Ashton (2001) and did not analyze broad factors of
-personality (e.g., neuroticism); instead, we focused on more specific
-personality facets (e.g., fearfulness). For future research, we suggest
-going one step further by analyzing predictors that are even more
-specified. For example, it seems possible that people who hold
-dissenting political beliefs could also have a higher desire for privacy
-from the government. Similarly, it would be interesting to focus on
-different minority groups. For example, it seems plausible that people
-from a LGBT background might desire more privacy from government
-(because it is potentially repressive or unfriendly toward LGBTs).
-Finally, in this study we focused mostly on escapist motives for why
-people desire privacy (e.g., shyness, risk aversion). Interestingly,
-({\textbf{???}}) were able to show that when predicting engagement in
-solitary activities, it is less preferable to measure how strongly
-people want to escape society (avoidance oriented), but rather how much
-they seek solitude (approach oriented). Hence, future studies might want
-to include predictors that are more approach oriented (e.g., peoples'
-desire for contemplation).
+Finally, in the SEM no significant relations between need for privacy and traditionality were found.
+The results imply that independent from being more open to change or not, people desire the same level of privacy.
+Taken further, this finding might illustrate that a modern way of living does not necessarily imply a reduced need for privacy.
 
-From a methodological perspective, future research should continue to
-improve the instruments we used, given that factorial validity of some
-scales was only moderate. Similarly, we recommend elaborating on the
-general understanding of integrity as a theoretical concept. To date,
-there is not one overarching concept of integrity that incorporates all
-the different aspects of integrity, yet it would be valuable to examine
-how other aspects of integrity (e.g., authenticity, trustworthiness, or
-consistency) relate to privacy desires.
+At a larger level, the results of this study highlight the importance of making differentiated claims on why people need privacy.
+Indeed, while the results suggest that some people might need anonymity because they may have something to hide, they also show that putting everyone who exhibits an increased need for privacy under suspicion is outright wrong.
+People who are less sociable, more risk averse, and less anxious are also more likely to need a bit more privacy.
+This implies that various personality-related aspects can predict need for privacy in different ways and for different reasons.
 
-Power analyses showed that future research should use samples above
-\emph{N} \(\approx\) 260 in order to test hypotheses with the
-recommended power of at least .80 (Cohen, 1992).
+Another contribution this study makes to the privacy literature is that it is one of the first to explicitly distinguish different types of privacy needs.
+Specifically, we found that need for privacy consists of three separate dimensions, with factors measuring need for privacy from the government, need for privacy from other people, and need for anonymity.
+This factor solution is in line with privacy theory, which subsumes a vertical level (here, privacy from the government) and a horizontal level (here, privacy from other people) (e.g., Schwartz, 1968).
+The third dimension, need for anonymity, can be argued to exist on the diagonal, as one can be anonymous both from the government and from other people.
+The results of our study demonstrate the importance of differentiating these types of need for privacy, as relationships were not consistent across the various privacy needs and the five personality traits.
 
-In general, the question arises whether it is possible, or even socially
-desirable, to measure a person's integrity. On the one hand, integrity
-implies absolute criteria: Stealing is bad and forbidden, whereas
-helping is good and encouraged. On the other hand, integrity implies
-relative criteria: Whereas some cultures disapprove of lying whatever
-the context, others consider lying okay---for example \enquote{white
-lies} in order to save face or to avoid hurting someone's feelings
-({\textbf{???}}). Thus, ranking behaviors, opinions, and character
-traits with regard to integrity is a moral dilemma. As a result,
-throughout the entire study we have understood integrity as a
-transgression of social norms that is strong and that most societies
-would agree upon (for example, most societies would consider stealing as
-a sign of low integrity).
+\hypertarget{limitations-and-future-research}{%
+\subsection{Limitations and Future Research}\label{limitations-and-future-research}}
 
-As a final note, we measured integrity based on self-ratings. One can
-criticize this approach by saying it is not possible to measure
-integrity based on self-reports because of social desirability
-influences. However, self-reports of integrity can indeed predict
-malevolent behavior: In a meta-analysis with 665 correlation
-coefficients, integrity tests related to counterproductive behaviors
-with a coefficient of \emph{r} = .47 ({\textbf{???}}). Nonetheless,
-future research would benefit from including behavioral manifestations
-of integrity, such as concrete cheating behaviors. If concrete cheating
-behaviors also increase desires for privacy, this would strengthen the
-underlying premise of the nothing-to-hide argument.
+One can of course raise the question of whether it is possible or even socially desirable to measure a person's integrity.
+On the one hand, integrity implies absolute criteria in relation to social norms: Stealing is bad and forbidden, whereas helping is good and encouraged.
+On the other hand, integrity implies relative criteria: Whereas some cultures disapprove of lying whatever the context, others consider lying okay (for example, \enquote{white lies} in order to avoid hurting someone's feelings) (Altman, 1977).
+Thus, ranking behaviors, opinions, and character traits with regard to integrity presents a moral dilemma.
+As a result, throughout our study we have employed a conservative approach and understood and measured integrity as an explicit transgression of social norms that is strong and that most societies would arguably agree upon (for example, most societies would consider stealing as a sign of low integrity).
+Nonetheless, we recommend that future research should further elaborate on the general understanding of integrity as a theoretical concept.
+To date, there is not one overarching concept of integrity that incorporates all of the different aspects of this variable, and yet it would be valuable to examine how other aspects of integrity (e.g., authenticity, trustworthiness, or consistency) relate to need for privacy.
+
+Worth nothing, integrity tests using self-reports have been shown to work surprisingly well, given that they can predict unwanted professional workplace behavior successfully (e.g., theft, drug and alcohol problems, or absenteeism) (Ones, Viswesvaran, \& Schmidt, 1993).
+In a meta-analysis with 665 correlation coefficients, self-reported integrity tests were associated with counterproductive behaviors with an average correlation coefficient of \emph{r} = .47 (Ones et al., 1993).
+Nonetheless, future research would evidently benefit from including behavioral manifestations of integrity, such as concrete cheating behaviors.
+
+In what follows, we present some methodological points of criticism.
+Despite the fact that we used mostly well-established scales, confirmatory factor analyses showed that some of the original items had to be deleted to achieve adequate factorial validity.
+This resembles the finding by Hussey and Hughes (2018), who reported that several widely-used scales in psychological research actually do not show satisfactory factorial validity.
+By using bifactor models, however, it was possible to at least partially alleviate the problem.
+Next, in order to achieve sufficient factorial validity we needed to adapt the scales (for example by deleting items), which introduces problems of overfitting, which in turn potentially impedes the generalisability of the results (see, e.g., Yarkoni \& Westfall, 2017).
+However, by using bifactor models we explicitly tried to retain the largest possible number of items, which should render our results more robust.
+In addition, also when looking at the items individually (see OSM) one can see that the results are not overly dependent on inclusion of specific items.
+Another methodological improvement for future studies concerns the sample, which was comparatively small, leading to a reduced power to detect also small effects.
+Nonetheless, we are still confident that the results should be reliable, because we deliberately selected specific predictors that should exhibit at lest small to moderate relations with need for privacy (i.e., \emph{r} = .20).
+For small to moderate relations, the current study still had a convincing power of 91\%.
+Granted, when aiming to find also small effects (i.e., \emph{r} = .10) with a probability of 95\%, future studies would need to collect the answers of 1293 respondents (Cohen, 1992).
+Finally, generalisability is limited, as our sample was predominantly young, female, highly educated, and collected only in one single country.
+
+Next, future research might consider analyzing predictors of privacy needs that are even more specified.
+For example, it is possible that people who hold dissenting political beliefs could also have a higher need for privacy from the government.
+In this study we focused mostly on escapist motives for why people desire privacy (e.g., sociability, risk aversion).
+Interestingly, Leary, Herbst, and McCrary (2003) showed that when predicting engagement in solitary activities, it is less preferable to measure how strongly people want to escape society (avoidance oriented), but rather how much they seek solitude (approach oriented).
+Hence, future studies might want to include predictors such as need for contemplation or trust (see, e.g., Metzger, 2004; Wheeless \& Grotz, 1977).
+Finally, it would be interesting to focus on need for privacy within different minority groups.
+For example, it seems plausible that people with a LGBT background might report needing more privacy from government (because it is potentially repressive or unfriendly toward LGBTs) or other people (especially weaker ties in their social networks who might not approve of their sexual identity).
 
@@
 \subsection{Conclusion}\label{conclusion}}
+
+In his novel \emph{The Circle}, Eggers (2013) describes a dystopian society in which people are gradually forfeiting their privacy.
+One after another becomes \enquote{transparent}: Carrying a small camera around the neck, people begin to broadcast their daily lives to the Internet.
+In the novel, this eventually causes a societal upheaval: \enquote{The pressure on those who hadn't gone transparent went from polite to oppressive.
+The question, from pundits and constituents, was obvious and loud: If you aren't transparent, what are you hiding?} (Eggers, 2013, p.
+129).
+
+The results of this study suggest that there might be some truth to the nothing-to-hide argument.
+However, the applicability seems to be limited to (very specific) aspects of anonymity (e.g., avoiding places with video surveillance or leaving one's ID at home).
+In general, the need for privacy seems to be related more closely to other aspects of personality.
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Altman.1975}{}%
+Altman, I. (1975). \emph{The environment and social behavior}. Monterey, CA: Brooks Cole.
+
+\leavevmode\hypertarget{ref-Altman.1976}{}%
+Altman, I. (1976). Privacy: A conceptual analysis. \emph{Environment and Behavior}, \emph{8}(1), 7--29. doi:\href{https://doi.org/10.1177/001391657600800102}{10.1177/001391657600800102}
+
+\leavevmode\hypertarget{ref-Altman.1977}{}%
+Altman, I.
+(1977).
+Privacy regulation: Culturally universal or culturally specific?
+\emph{Journal of Social Issues}, \emph{33}(3), 66--84.
+doi:\href{https://doi.org/10.1111/j.1540-4560.1977.tb01883.x}{10.1111/j.1540-4560.1977.tb01883.x}
+
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-Bansal.2010}{}%
+Bansal, G., Zahedi, F.
+M., \& Gefen, D.
+(2010).
+The impact of personal dispositions on information sensitivity, privacy concern and trust in disclosing health information online.
+\emph{Decision Support Systems}, \emph{49}(2), 138--150.
+doi:\href{https://doi.org/10.1016/j.dss.2010.01.010}{10.1016/j.dss.2010.01.010}
+
+\leavevmode\hypertarget{ref-Bol.2018}{}%
+Bol, N., Dienlin, T., Kruikemeier, S., Sax, M., Boerman, S.
+C., Strycharz, J., \ldots{} Vreese, C.
+H.
+de.
+(2018).
+Understanding the effects of personalization as a privacy calculus: Analyzing self-disclosure across health, news, and commerce contexts.
+\emph{Journal of Computer-Mediated Communication}, \emph{23}(6), 370--388.
+doi:\href{https://doi.org/10.1093/jcmc/zmy020}{10.1093/jcmc/zmy020}
+
+\leavevmode\hypertarget{ref-boyd.2008c}{}%
+boyd, danah m. (2008). \emph{Taken out of context. American teen sociality in networked publics: Doctoral dissertation}. Berkeley, CA: University of California.
+
+\leavevmode\hypertarget{ref-Burgoon.1982}{}%
+Burgoon, J. K. (1982). Privacy and communication. \emph{Annals of the International Communication Association}, \emph{1}, 206--249.
+
+\leavevmode\hypertarget{ref-Buss.2001}{}%
+Buss, A. H. (2001). \emph{Psychological dimensions of the self}. Thousand Oaks; Calif: Sage Publications.
+
+\leavevmode\hypertarget{ref-R-pwr}{}%
+Champely, S. (2018). \emph{Pwr: Basic functions for power analysis}. Retrieved from \url{https://CRAN.R-project.org/package=pwr}
+
+\leavevmode\hypertarget{ref-Cohen.1992}{}%
+Cohen, J. (1992). A power primer. \emph{Psychological Bulletin}, \emph{112}(1), 155--159. doi:\href{https://doi.org/10.1037/0033-2909.112.1.155}{10.1037/0033-2909.112.1.155}
+
+\leavevmode\hypertarget{ref-Connelly.2006}{}%
+Connelly, S., Lilienfeld, S.
+O., \& Schmeelk, K.
+M.
+(2006).
+Integrity tests and morality: Associations with ego development, moral reasoning, and psychopathic personality.
+\emph{International Journal of Selection and Assessment}, \emph{14}(1), 82--86.
+doi:\href{https://doi.org/10.1111/j.1468-2389.2006.00335.x}{10.1111/j.1468-2389.2006.00335.x}
+
+\leavevmode\hypertarget{ref-Corcoran.1987}{}%
+Corcoran, K.
+J., \& Rotter, J.
+B.
+(1987).
+Morality-conscience guilt scale as a predictor of ethical behavior in a cheating situation among college females.
+\emph{The Journal of General Psychology}, \emph{114}(2), 117--123.
+doi:\href{https://doi.org/10.1080/00221309.1987.9711061}{10.1080/00221309.1987.9711061}
+
+\leavevmode\hypertarget{ref-Covey.1989}{}%
+Covey, M.
+K., Saladin, S., \& Killen, P.
+J.
+(1989).
+Self-monitoring, surveillance, and incentive effects on cheating.
+\emph{The Journal of Social Psychology}, \emph{129}(5), 673--679.
+doi:\href{https://doi.org/10.1080/00224545.1989.9713784}{10.1080/00224545.1989.9713784}
+
+\leavevmode\hypertarget{ref-DeCew.1997}{}%
+DeCew, J. W. (1997). \emph{In pursuit of privacy: Law, ethics, and the rise of technology}. Ithaca, NY: Cornell Univ. Press.
+
 \leavevmode\hypertarget{ref-Dienlin.2014}{}%
-Dienlin, T. (2014). The privacy process model. In S. Garnett, S. Halft,
-M. Herz, \& J. M. Mönig (Eds.), \emph{Medien und Privatheit} (pp.
-105--122). Passau, Germany: Karl Stutz.
+Dienlin, T. (2014). The privacy process model. In S. Garnett, S. Halft, M. Herz, \& J. M. Mönig (Eds.), \emph{Medien und Privatheit} (pp. 105--122). Passau, Germany: Karl Stutz.
+
+\leavevmode\hypertarget{ref-Dienlin.2016a}{}%
+Dienlin, T., \& Metzger, M.
+J.
+(2016).
+An extended privacy calculus model for SNSs---Analyzing self-disclosure and self-withdrawal in a representative U.S.
+sample.
+\emph{Journal of Computer-Mediated Communication}, \emph{21}(5), 368--383.
+doi:\href{https://doi.org/10.1111/jcc4.12163}{10.1111/jcc4.12163}
+
+\leavevmode\hypertarget{ref-Donnellan.2008}{}%
+Donnellan, M.
+B., \& Lucas, R.
+E.
+(2008).
+Age differences in the Big Five across the life span: Evidence from two national samples.
+\emph{Psychology and Aging}, \emph{23}(3), 558--566.
+doi:\href{https://doi.org/10.1037/a0012897}{10.1037/a0012897}
+
+\leavevmode\hypertarget{ref-Eggers.2013}{}%
+Eggers, D. (2013). \emph{The circle}. New York, NY: Knopf Publishing Group.
+
+\leavevmode\hypertarget{ref-Fife.2012}{}%
+Fife, E., \& Orjuel, J.
+(2012).
+The privacy calculus: Mobile apps and user perceptions of privacy and security.
+\emph{International Journal of Engineering Business Management}, \emph{4}, 1--10.
+doi:\href{https://doi.org/10.5772/51645}{10.5772/51645}
+
+\leavevmode\hypertarget{ref-Granovetter.1973}{}%
+Granovetter, M. S. (1973). The strength of weak ties. \emph{American Journal of Sociology}, \emph{78}(6), 1360--1380.
+
+\leavevmode\hypertarget{ref-Greenwald.2013}{}%
+Greenwald, G. (2013). NSA collecting phone records of millions of Verizon customers daily. \emph{The Guardian}. Retrieved from \url{www.theguardian.com}
+
+\leavevmode\hypertarget{ref-Hussey.2018}{}%
+Hussey, I., \& Hughes, S. (2018). Hidden invalidity among fifteen commonly used measures in social and personality psychology. doi:\href{https://doi.org/10.31234/osf.io/7rbfp}{10.31234/osf.io/7rbfp}
+
+\leavevmode\hypertarget{ref-John.1999}{}%
+John, O.
+P., \& Srivastava, S.
+(1999).
+The big five trait taxonomy: History, measurement, and theoretical perspectives.
+In L.
+A.
+Pervin \& O.
+P.
+John (Eds.), \emph{Handbook of personality} (pp.
+102--138).
+New York, NY: Guilford Press.
+
+\leavevmode\hypertarget{ref-Johnson.2010}{}%
+Johnson, B. (2010). Privacy no longer a social norm, says Facebook founder. \emph{The Guardian}. Retrieved from \url{www.theguardian.com}
+
+\leavevmode\hypertarget{ref-R-semTools}{}%
+Jorgensen, D., T., Pornprasertmanit, S., Schoemann, M., A., \ldots{} Y.
+(2018).
+\emph{semTools: Useful tools for structural equation modeling}.
+Retrieved from \url{https://CRAN.R-project.org/package=semTools}
+
+\leavevmode\hypertarget{ref-Junglas.2008}{}%
+Junglas, I.
+A., Johnson, N.
+A., \& Spitzmüller, C.
+(2008).
+Personality traits and concern for privacy: an empirical study in the context of location-based services.
+\emph{European Journal of Information Systems}, \emph{17}(4), 387--402.
+doi:\href{https://doi.org/10.1057/ejis.2008.29}{10.1057/ejis.2008.29}
+
+\leavevmode\hypertarget{ref-Kahneman.1979}{}%
+Kahneman, D., \& Tversky, A. (1979). Prospect theory: An analysis of decision under risk. \emph{Econometrica}, \emph{47}(2), 263. doi:\href{https://doi.org/10.2307/1914185}{10.2307/1914185}
+
+\leavevmode\hypertarget{ref-Kline.2016}{}%
+Kline, R. B. (2016). \emph{Principles and practice of structural equation modeling} (4th ed.). New York, NY: The Guilford Press.
+
+\leavevmode\hypertarget{ref-R-MVN}{}%
+Korkmaz, S., Goksuluk, D., \& Zararsiz, G.
+(2014).
+MVN: An r package for assessing multivariate normality.
+\emph{The R Journal}, \emph{6}(2), 151--162.
+Retrieved from \url{https://journal.r-project.org/archive/2014-2/korkmaz-goksuluk-zararsiz.pdf}
+
+\leavevmode\hypertarget{ref-Lakens.2018}{}%
+Lakens, D., Scheel, A.
+M., \& Isager, P.
+M.
+(2018).
+Equivalence testing for psychological research: A tutorial.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269.
+doi:\href{https://doi.org/10.1177/2515245918770963}{10.1177/2515245918770963}
+
+\leavevmode\hypertarget{ref-Leary.2003}{}%
+Leary, M.
+R., Herbst, K.
+C., \& McCrary, F.
+(2003).
+Finding pleasure in solitary activities: Desire for aloneness or disinterest in social contact?
+\emph{Personality and Individual Differences}, \emph{35}(1), 59--68.
+doi:\href{https://doi.org/10.1016/S0191-8869(02)00141-1}{10.1016/S0191-8869(02)00141-1}
+
+\leavevmode\hypertarget{ref-Masur.2018}{}%
+Masur, P. K. (2018). \emph{Situational privacy and self-disclosure: Communication processes in online environments}. Cham, Switzerland: Springer.
+
+\leavevmode\hypertarget{ref-Meijer.2016}{}%
+Meijer, R.
+R., Niessen, A.
+S.
+M., \& Tendeiro, J.
+N.
+(2016).
+A practical guide to check the consistency of item response patterns in clinical research through person-fit statistics: Examples and a computer Program.
+\emph{Assessment}, \emph{23}(1), 52--62.
+doi:\href{https://doi.org/10.1177/1073191115577800}{10.1177/1073191115577800}
+
+\leavevmode\hypertarget{ref-Metzger.2004}{}%
+Metzger, M.
+J.
+(2004).
+Privacy, trust, and disclosure: Exploring barriers to electronic commerce.
+\emph{Journal of Computer-Mediated Communication}, \emph{9}(4).
+doi:\href{https://doi.org/10.1111/j.1083-6101.2004.tb00292.x}{10.1111/j.1083-6101.2004.tb00292.x}
+
+\leavevmode\hypertarget{ref-Morton.2013}{}%
+Morton, A.
+(2013).
+Measuring inherent privacy concern and desire for privacy - A pilot survey study of an instrument to measure dispositional privacy concern.
+In \emph{International Conference on Social Computing (SocialCom)} (pp.
+468--477).
+doi:\href{https://doi.org/10.1109/SocialCom.2013.73}{10.1109/SocialCom.2013.73}
+
+\leavevmode\hypertarget{ref-Nissenbaum.2010}{}%
+Nissenbaum, H. (2010). \emph{Privacy in context: Technology, policy, and the integrity of social life}. Stanford, CA: Stanford University Press.
+
+\leavevmode\hypertarget{ref-Omarzu.2000}{}%
+Omarzu, J.
+(2000).
+A disclosure decision model: Determining how and when individuals will self-disclose.
+\emph{Personality and Social Psychology Review}, \emph{4}(2), 174--185.
+doi:\href{https://doi.org/10.1207/S15327957PSPR0402_5}{10.1207/S15327957PSPR0402\_5}
+
+\leavevmode\hypertarget{ref-Ones.1993}{}%
+Ones, D.
+S., Viswesvaran, C., \& Schmidt, F.
+L.
+(1993).
+Comprehensive meta-analysis of integrity test validities: Findings and implications for personnel selection and theories of job performance.
+\emph{Journal of Applied Psychology}, \emph{78}(4), 679--703.
+doi:\href{https://doi.org/10.1037/0021-9010.78.4.679}{10.1037/0021-9010.78.4.679}
+
+\leavevmode\hypertarget{ref-Park.2015}{}%
+Park, Y.
+J.
+(2015).
+Do men and women differ in privacy?
+Gendered privacy and (in)equality in the Internet.
+\emph{Computers in Human Behavior}, \emph{50}, 252--258.
+doi:\href{https://doi.org/10.1016/j.chb.2015.04.011}{10.1016/j.chb.2015.04.011}
+
+\leavevmode\hypertarget{ref-Paunonen.2002}{}%
+Paunonen, S. V. (2002). Design and construction of the Supernumerary Personality Inventory. London, Canada: University of Western Ontario.
 
 \leavevmode\hypertarget{ref-Paunonen.2001}{}%
-Paunonen, S. V., \& Ashton, M. C. (2001). Big Five factors and facets
-and the prediction of behavior. \emph{Journal of Personality and Social
-Psychology}, \emph{81}(3), 524--539.
+Paunonen, S.
+V., \& Ashton, M.
+C.
+(2001).
+Big Five factors and facets and the prediction of behavior.
+\emph{Journal of Personality and Social Psychology}, \emph{81}(3), 524--539.
 doi:\href{https://doi.org/10.1037/0022-3514.81.3.524}{10.1037/0022-3514.81.3.524}
@@
 \leavevmode\hypertarget{ref-Pedersen.1979}{}%
-Pedersen, D. M. (1979). Dimensions of privacy. \emph{Perceptual and
-Motor Skills}, \emph{48}(3), 1291--1297.
-doi:\href{https://doi.org/10.2466/pms.1979.48.3c.1291}{10.2466/pms.1979.48.3c.1291}
+Pedersen, D. M. (1979). Dimensions of privacy. \emph{Perceptual and Motor Skills}, \emph{48}(3), 1291--1297. doi:\href{https://doi.org/10.2466/pms.1979.48.3c.1291}{10.2466/pms.1979.48.3c.1291}
 
 \leavevmode\hypertarget{ref-Pedersen.1982}{}%
-Pedersen, D. M. (1982). Personality correlates of privacy. \emph{The
-Journal of Psychology}, \emph{112}(1), 11--14.
+Pedersen, D.
+M.
+(1982).
+Personality correlates of privacy.
+\emph{The Journal of Psychology}, \emph{112}(1), 11--14.
 doi:\href{https://doi.org/10.1080/00223980.1982.9923528}{10.1080/00223980.1982.9923528}
 
+\leavevmode\hypertarget{ref-Petronio.2010}{}%
+Petronio, S.
+(2010).
+Communication privacy management theory: What do we know about family privacy regulation?
+\emph{Journal of Family Theory \& Review}, \emph{2}(3), 175--196.
+doi:\href{https://doi.org/10.1111/j.1756-2589.2010.00052.x}{10.1111/j.1756-2589.2010.00052.x}
+
+\leavevmode\hypertarget{ref-PewResearchCenter.2015c}{}%
+Pew Research Center. (2015). Beyond distrust: How Americans view their government. Retrieved from \url{http://www.people-press.org/2015/11/23/beyond-distrust-how-americans-view-their-government/}
+
+\leavevmode\hypertarget{ref-PewResearchCenter.2017}{}%
+Pew Research Center. (2017). Public trust in government: 1958-2017. Retrieved from \url{http://www.people-press.org/2017/12/14/public-trust-in-government-1958-2017/}
+
 \leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2018). \emph{R: A language and environment for statistical
-computing}. Vienna, Austria: R Foundation for Statistical Computing.
-Retrieved from \url{https://www.R-project.org/}
+R Core Team. (2018). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-R-psych}{}%
+Revelle, W.
+(2018).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
+\leavevmode\hypertarget{ref-R-lavaan}{}%
+Rosseel, Y. (2012). lavaan: An R package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. Retrieved from \url{http://www.jstatsoft.org/v48/i02/}
+
+\leavevmode\hypertarget{ref-R-GGally}{}%
+Schloerke, B., Crowley, J., Cook, D., Briatte, F., Marbach, M., Thoen, E., \ldots{} Larmarange, J.
+(2018).
+\emph{GGally: Extension to 'ggplot2'}.
+Retrieved from \url{https://CRAN.R-project.org/package=GGally}
 
 \leavevmode\hypertarget{ref-Schwartz.1968}{}%
-Schwartz, B. (1968). The social psychology of privacy. \emph{American
-Journal of Sociology}, \emph{73}(6), 741--752.
+Schwartz, B. (1968). The social psychology of privacy. \emph{American Journal of Sociology}, \emph{73}(6), 741--752.
+
+\leavevmode\hypertarget{ref-Sevignani.2016}{}%
+Sevignani, S. (2016). \emph{Privacy and capitalism in the age of social media}. New York; London: Routledge Taylor \& Francis Group.
+
+\leavevmode\hypertarget{ref-Sheldon.2004}{}%
+Sheldon, K.
+M.
+(2004).
+Integrity {[}authenticity, honesty{]}.
+In C.
+Peterson \& Seligman, M.
+E.
+P.
+(Eds.), \emph{Character strengths and virtues: A handbook and classification} (pp.
+249--271).
+Oxford, UK: Oxford University Press.
+
+\leavevmode\hypertarget{ref-Solove.2007}{}%
+Solove, D. J. (2007). 'I've got nothing to hide' and other misunderstandings of privacy. \emph{San Diego Law Review}, \emph{44}, 745--772.
+
+\leavevmode\hypertarget{ref-Stone.1986}{}%
+Stone, D.
+L.
+(1986).
+Relationship between introversion/extraversion, values regarding control over information, and perceptions of invasion of privacy.
+\emph{Perceptual and Motor Skills}, \emph{62}(2), 371--376.
+doi:\href{https://doi.org/10.2466/pms.1986.62.2.371}{10.2466/pms.1986.62.2.371}
+
+\leavevmode\hypertarget{ref-R-PerFit}{}%
+Tendeiro, J.
+N., Meijer, R.
+R., \& Niessen, A.
+S.
+M.
+(2016).
+PerFit: An R package for person-fit analysis in IRT.
+\emph{Journal of Statistical Software}, \emph{74}(5), 1--27.
+doi:\href{https://doi.org/10.18637/jss.v074.i05}{10.18637/jss.v074.i05}
+
+\leavevmode\hypertarget{ref-Tifferet.2019}{}%
+Tifferet, S.
+(2019).
+Gender differences in privacy tendencies on social network sites: A meta-analysis.
+\emph{Computers in Human Behavior}, \emph{93}, 1--12.
+doi:\href{https://doi.org/10.1016/j.chb.2018.11.046}{10.1016/j.chb.2018.11.046}
+
+\leavevmode\hypertarget{ref-Trepte.2013a}{}%
+Trepte, S., Dienlin, T., \& Reinecke, L.
+(2013).
+Privacy, self-disclosure, social support, and social network site use.
+Research report of a three-year panel study.
+Retrieved from \url{http://opus.uni-hohenheim.de/volltexte/2013/889/}
+
+\leavevmode\hypertarget{ref-Trepte.2017d}{}%
+Trepte, S., \& Masur, P.
+K.
+(2017).
+Need for privacy.
+In V.
+Zeigler-Hill \& T.
+K.
+Shackelford (Eds.), \emph{Encyclopedia of Personality and Individual Differences} (Vol.
+94, pp.
+1--4).
+Cham: Springer International Publishing.
+doi:\href{https://doi.org/10.1007/978-3-319-28099-8_540-1}{10.1007/978-3-319-28099-8\_540-1}
+
+\leavevmode\hypertarget{ref-R-mice}{}%
+van Buuren, S., \& Groothuis-Oudshoorn, K.
+(2011).
+mice: Multivariate imputation by chained equations in r.
+\emph{Journal of Statistical Software}, \emph{45}(3), 1--67.
+Retrieved from \url{https://www.jstatsoft.org/v45/i03/}
+
+\leavevmode\hypertarget{ref-Weinberger.2017b}{}%
+Weinberger, M., Zhitomirsky-Geffet, M., \& Bouhnik, D.
+(2017).
+Sex differences in attitudes towards online privacy and anonymity among Israeli students with different technical backgrounds, \emph{22}(4).
+Retrieved from \url{http://InformationR.net/ir/22-4/paper777.html}
 
 \leavevmode\hypertarget{ref-Westin.1967}{}%
-Westin, A. F. (1967). \emph{Privacy and freedom}. New York, NY:
-Atheneum.
+Westin, A. F. (1967). \emph{Privacy and freedom}. New York, NY: Atheneum.
+
+\leavevmode\hypertarget{ref-Wheeless.1977}{}%
+Wheeless, L.
+R., \& Grotz, J.
+(1977).
+The measurement of trust and its relationship to self-disclosure.
+\emph{Human Communication Research}, \emph{3}(3), 250--257.
+doi:\href{https://doi.org/10.1111/j.1468-2958.1977.tb00523.x}{10.1111/j.1468-2958.1977.tb00523.x}
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{http://ggplot2.org}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}
+
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
+
+\leavevmode\hypertarget{ref-Yarkoni.2017}{}%
+Yarkoni, T., \& Westfall, J.
+(2017).
+Choosing prediction over explanation in psychology: Lessons from machine learning.
+\emph{Perspectives on psychological science : a journal of the Association for Psychological Science}, \emph{12}(6), 1100--1122.
+doi:\href{https://doi.org/10.1177/1745691617693393}{10.1177/1745691617693393}
 
@@
 
+\newpage
+
+\hypertarget{contributions}{%
+\section{Contributions}\label{contributions}}
+
+\begin{itemize}
+\tightlist
+\item
+  Contributed to conception and design: TD, MM
+\item
+  Contributed to acquisition of data: MM, TD
+\item
+  Contributed to analysis and interpretation of data: TD, MM
+\item
+  Drafted and/or revised the article: TD, MM
+\item
+  Approved the submitted version for publication: TD, MM
+\end{itemize}
+
+\hypertarget{funding-information}{%
+\section{Funding Information}\label{funding-information}}
+
+During the conception and data collection of the study, TD was funded by The German Academic Scholarship Foundation (German: Studienstiftung des deutschen Volkes), which financially supported TD's research stay at UCSB.
+During the writing of the article, TD was funded by the Volkswagen Foundation (German: Volkswagenstiftung), grant \enquote{Transformations of Privacy}.
+
+MM is funded by a regular and tenured full professorship at UCSB.
+
+\hypertarget{competing-interests}{%
+\section{Competing Interests}\label{competing-interests}}
+
+We declare no competing interests.
+
+\hypertarget{data-accessibility-statement}{%
+\section{Data Accessibility Statement}\label{data-accessibility-statement}}
+
+All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found on this paper's project page on the open science framework (\url{https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f}).
+In addition, we invite everyone to suggest changes and improvements to the manuscript via our github (\url{https://github.com/tdienlin/need_for_privacy/tree/master}).
+
 \end{document}

### 2019-02-12 manuscript/manuscript.RmD
- minor changes

@@
 Finally, @Pedersen.1982 showed that three dimensions of need for privacy relate to self-esteem: Respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21), and preferred solitude (_r_ = .24).
-While self-esteem and integrity are distinct concepts, Pedersen’s specific operationalization of self-esteem integrated several aspects of integrity by using items such as “moral, nice, fair, unselfish, good, honest, reputable, sane”..
+While self-esteem and integrity are distinct concepts, Pedersen’s specific operationalization of self-esteem integrated several aspects of integrity by using items such as “moral, nice, fair, unselfish, good, honest, reputable, sane”.
 

### 2019-02-12 manuscript/manuscript.tex
- minor changes

@@
 Finally, Pedersen (1982) showed that three dimensions of need for privacy relate to self-esteem: Respondents who held a lower self-esteem were more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21), and preferred solitude (\emph{r} = .24).
-While self-esteem and integrity are distinct concepts, Pedersen's specific operationalization of self-esteem integrated several aspects of integrity by using items such as \enquote{moral, nice, fair, unselfish, good, honest, reputable, sane}..
+While self-esteem and integrity are distinct concepts, Pedersen's specific operationalization of self-esteem integrated several aspects of integrity by using items such as \enquote{moral, nice, fair, unselfish, good, honest, reputable, sane}.
 

### 2019-02-26 analyses/analyses.RmD
Major updates on everything. Specifically, this includes updates on data, including MMs latest feedback, and getting things ready for submission.

@@
                       tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
-options(digits = 3, width = 100)
+options(digits = 3, width = 90)
 ```
@@
 # install packages
-# devtools::install_github("https://github.com/tdienlin/td")
+devtools::install_github("https://github.com/tdienlin/td")
 
@@
 ```
+
+\newpage
+# Items
+
+"To what extent do you agree or disagree with the following statements?"
+
+(-3) Strongly Disagree, (-2) Disagree, (-1) Slightly Disagree, (0) Neutral, (1) Slightly Agree (2) Agree, (3) Strongly Agree
+
+(Inverted items are labelled "*".)
+
+## Need for privacy
+### Informational
+
+1.	I prefer it when other people do not know much about me.
+2.	When given the chance, I prefer being incognito.
+3.	I don't want personal information about me being publicly available.
+4.	Not everybody needs to know everything about me.
+
+### Societal
+
+Government Surveillance
+
+1.	I need government agencies to respect my privacy, even if that hinders a greater societal cause.
+2.	I need the information that companies (e.g., Amazon, Facebook, or Google) have about me to stay private so that the government cannot access it.
+3.	I don't want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.
+4.	I don't want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.
+
+Anonymity
+
+5.	I need to be able to surf online anonymously.
+6.	I need to be able to use a fake name on social network sites to preserve my privacy.
+7.	I feel the need to avoid places with video surveillance.
+8.	I prefer not to carry my ID with me all the time to preserve my privacy
+
+Both
+
+9.	I feel the need to protect my privacy from government agencies.
+
+### Interpersonal
+
+Online
+
+1.	I feel the need to disclose personal information about me on social network sites.
+2.	My need for privacy is so strong that it prevents me from using Facebook actively.
+3.	I don’t feel the need to be able to communicate about very personal things with others online.
+4.	I need to know that my boss or future employers cannot find information about me online that they might disapprove of.
+
+Offline
+
+5.	I always need a person to talk about personal things.*
+6.	I don’t need to know a lot of things about people I interact with, as that might cause problems.
+7.	I don’t feel the need to tell my friends all my secrets.
+8.	I sometimes feel the need to share my personal point of view with someone I don’t know that well.*
+
+Both
+
+9.	I feel the need to protect my privacy from other people.
+
+## Sociability
+
+1.	I shy away from crowds of people.*
+2.	I like to have a lot of people around me.
+3.	I usually prefer to do things alone.*
+4.	I really feel the need for other people if I am by myself for long.
+5.	I prefer jobs that let me work alone without being bothered by other people.*
+6.	I’d rather vacation at a popular beach than an isolated cabin in the woods.
+7.	Social gatherings are usually boring to me.*
+8.	I enjoy parties with lots of people.
+
+## Integrity
+
+1.	I am often tempted to take things that do not belong to me.*
+2.	I don't think there's anything wrong with cheating a little on one's income tax forms.*
+3.	When traveling, I would always declare everything at customs.
+4.	If I found a wallet, I would not be tempted to keep any money.
+5.	If I could get away with it, I would leave a restaurant or bar without paying the bill.*
+6.	I would buy stolen merchandise if the price was right.*
+7.	I would mislead people when it comes to my academic achievements.*
+8.	I think that there are circumstances when people are justified in cheating.*
+
+Self-designed
+
+9.	I have cheated on an exam in school.*
+10.	I have watched movies or listened to music online for free, even though I knew doing so violated copyright law.*
+11.	Certain things that I have done would be considered illegal in some places.*
+
+## Anxiety
+
+1.	I am not a worrier.*
+2.	I am easily frightened.
+3.	I rarely feel fearful or anxious.*
+4.	I often feel tense and jittery.
+5.	I’m seldom apprehensive about the future.
+6.	I often worry about things that might go wrong.
+7.	I have fewer fears than most people.*
+8.	Frightening thoughts sometimes come into my head.
+
+## Risk avoidance
+
+1.	Over the years I’ve done some pretty stupid things.*
+2.	I think things through before coming to a decision.
+3.	Occasionally I act first and think later.*
+4.	I always consider the consequences before I take action.
+5.	I often do things on the spur of the moment.*
+6.	I rarely make hasty decisions.
+7.	I plan ahead carefully when I go on a trip.
+8.	I think twice before I answer a question.
+
+## Traditionalism
+
+1.	I'm pretty set in my ways.
+2.	I think it's interesting to learn and develop new hobbies.*
+3.	Once I find the right way to do something, I stick to it.
+4.	I often try new and foreign foods.*
+5.	I prefer to spend my time in familiar surroundings.
+6.	Sometimes I make changes around the house just to try something different.*
+7.	On a vacation, I prefer going back to a tried and true spot.
+8.	I follow the same route when I go someplace.
+
+\newpage
+# Sample
 
@@
   set_names(colnames(read_csv("../data/data.csv", n_max = 1)))
-
-# prepare table with item content
-items <- data.frame(
-  name = colnames(read_csv("../data/data.csv", n_max = 1)),  # extract item names
-  content = colnames(read_csv("../data/data.csv", skip = 1, n_max = 2))  # extract item content
-) %>% 
-  mutate(content = gsub("To what extent do you agree or disagree with the following / statements[?][-]", "", content)) %>% 
-  mutate(content = gsub("To what extent do you agree or disagree with the / following statements[?][-]", "", content)) %>% 
-  mutate(content_breaks = sapply(content, string_break, 30))
-
-# edit variables
-d %<>% 
-  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.))) %>% 
-  mutate_at(vars(V8, V9), funs(parse_datetime(., c("%d.%m.%Y %H:%M")))) %>% 
-  mutate(
-    male = 2 - SES.SEX,
-    time = V9 - V8,
-    id = 1:nrow(.)
-    ) %>% 
-  rename(
-    age = SES.AGE,
-    inc = SES.JOB_2
-  )
-
-# select items
-d %<>% dplyr::select(
-  id, male, age, inc, time,
-  starts_with("N4P"),
-  starts_with("INT_"),
-  SOC_1 : SOC_8,
-  starts_with("FEA_"),
-  TRA_1 : TRA_8,
-  RIT_1 : RIT_8,
-  BFI_1 : BFI_10
-)
+items <- read_csv("../data/items.csv")
 
@@
 # define inverted items
-recoded <- c("N4P.INT_1", "N4P.INT_5", "N4P.INT_8",
-             "INT_1", "INT_2", "INT_5", "INT_6", "INT_7", 
-                 "INT_8", "INT_9", "INT_10", "INT_11",
-             "SOC_1", "SOC_3", "SOC_5", "SOC_7",
-             "FEA_1", "FEA_3", "FEA_5", "FEA_7",
-             "RIT_1", "RIT_3", "RIT_5",
-             "TRA_2", "TRA_4", "TRA_6")
+recoded <- c("pri_nee_int_1", "pri_nee_int_5", "pri_nee_int_8",
+             "itg_1", "itg_2", "itg_5", "itg_6", "itg_7", 
+                 "itg_8", "itg_9", "itg_10", "itg_11",
+             "soc_1", "soc_3", "soc_5", "soc_7",
+             "anx_1", "anx_3", "anx_5", "anx_7",
+             "ria_1", "ria_3", "ria_5",
+             "tra_2", "tra_4", "tra_6")
 
@@
 
-\newpage
-# Data wrangling
-## Filter defective data
-### Empty/missing data
+## Missing values
+
+Inspect how much data is missing.
 
@@
 
-Shows that most people answered all questions. There were 15 empty data sets, and some with more than 50% missing data. These were deleted. Overall, there was just `r na_perc` missing data.
-
-### Speeder
+Shows that most people answered all questions. There were 15 empty data sets, and some with more than 50% missing data. These were deleted. In the final sample, there was `r na_perc` missing data.
+
+## Response time
+
+Inspect how long it took respondents to answer the questionnaire.
 
@@
 
-Distribution looks okay (no early peak). Also no answers faster than 5 mins.
-
-### Response Styles
+Distribution looks okay (no early peak). Also no answers faster than 5 mins. No respondents will be excluded.
+
+\newpage
+## Response patterns
+
+We inspect response patterns using the Guttman criterion. Cases with most extreme values will be excluded.
 
@@
 # make matrixes of variables
-d_pri_nee <- dplyr::select(d, starts_with("N4P"))
-d_pri_nee_noninvert <- dplyr::select(d_noninvert, starts_with("N4P"))
-d_int <- dplyr::select(d, starts_with("INT_"))
-d_int_noninvert <- dplyr::select(d_noninvert, starts_with("INT_"))
-d_soc <- dplyr::select(d, SOC_1 : SOC_8)
-d_soc_noninvert <- dplyr::select(d_noninvert, SOC_1 : SOC_8)
-d_fea <- dplyr::select(d, starts_with("FEA_"))
-d_fea_noninvert <- dplyr::select(d_noninvert, starts_with("FEA_"))
-d_rit <- dplyr::select(d, RIT_1 : RIT_8)
-d_rit_noninvert <- dplyr::select(d_noninvert, RIT_1 : RIT_8)
-d_tra <- dplyr::select(d, TRA_1 : TRA_8)
-d_tra_noninvert <- dplyr::select(d_noninvert, TRA_1 : TRA_8)
+d_pri_nee <- dplyr::select(d, starts_with("pri_nee"))
+d_pri_nee_noninvert <- dplyr::select(d_noninvert, starts_with("pri_nee"))
+d_itg <- dplyr::select(d, starts_with("itg_"))
+d_itg_noninvert <- dplyr::select(d_noninvert, starts_with("itg_"))
+d_soc <- dplyr::select(d, soc_1 : soc_8)
+d_soc_noninvert <- dplyr::select(d_noninvert, soc_1 : soc_8)
+d_anx <- dplyr::select(d, starts_with("anx_"))
+d_anx_noninvert <- dplyr::select(d_noninvert, starts_with("anx_"))
+d_ria <- dplyr::select(d, ria_1 : ria_8)
+d_ria_noninvert <- dplyr::select(d_noninvert, ria_1 : ria_8)
+d_tra <- dplyr::select(d, tra_1 : tra_8)
+d_tra_noninvert <- dplyr::select(d_noninvert, tra_1 : tra_8)
 
 # run guttman tests
-d_vars <- list(d_pri_nee, d_int, d_soc, d_fea, d_rit, d_tra)
+d_vars <- list(d_pri_nee, d_itg, d_soc, d_anx, d_ria, d_tra)
 d_guttman_scores <- lapply(d_vars, function(x) Gnormed.poly(x - 1, 7) %$% 
@@
 # inspect cases with susceptive data
-# guttman_crit <- quantile(d$guttman, probs = .95)  # relative 5% criterion
-guttman_crit <- .30  # absolute .25 criterion (cf. histogram)
-d_suspicious <- d[d$guttman > guttman_crit, ] %>% 
+guttman_crit_30 <- .30  # absolute .30 criterion (cf. histogram)
+guttman_crit_95 <- quantile(d$guttman, .95)  # relative 5% criterion; possible, but given the already small sample not recommended
+
+d_suspicious <- d[d$guttman > guttman_crit_30, ] %>% 
   arrange(desc(guttman))
+n_d_suspicious <- nrow(d_suspicious)
 
 # remove cases
-d <- d[d$guttman < guttman_crit, ]
+d <- d[d$guttman < guttman_crit_30, ]
+d_guttman_95 <- d[d$guttman < guttman_crit_95, ]
 
 # count cases
-n_d_suspicious <- nrow(d_suspicious)
-n_d_defect <- n_d_all - n_d_empty - nrow(d)
 n_d <- nrow(d)
@@
 # make matrixes of variables (bc. of removed participants)
-d_pri_nee <- dplyr::select(d, starts_with("N4P"))
-d_pri_nee_noninvert <- dplyr::select(d_noninvert, starts_with("N4P"))
-d_int <- dplyr::select(d, starts_with("INT_"))
-d_int_noninvert <- dplyr::select(d_noninvert, starts_with("INT_"))
-d_soc <- dplyr::select(d, SOC_1 : SOC_8)
-d_soc_noninvert <- dplyr::select(d_noninvert, SOC_1 : SOC_8)
-d_fea <- dplyr::select(d, starts_with("FEA_"))
-d_fea_noninvert <- dplyr::select(d_noninvert, starts_with("FEA_"))
-d_rit <- dplyr::select(d, RIT_1 : RIT_8)
-d_rit_noninvert <- dplyr::select(d_noninvert, RIT_1 : RIT_8)
-d_tra <- dplyr::select(d, TRA_1 : TRA_8)
-d_tra_noninvert <- dplyr::select(d_noninvert, TRA_1 : TRA_8)
-```
-
-Only few participants seem to have particularly atypical data. Will filter respondents with m > .30. All of the 5% cases indeed show extreme response patterns and/or illogical data. Will be filtered.
-
-\newpage
-# Power Analyses
+d_pri_nee <- dplyr::select(d, starts_with("pri_nee"))
+d_pri_nee_noninvert <- dplyr::select(d_noninvert, starts_with("pri_nee"))
+d_itg <- dplyr::select(d, starts_with("itg_"))
+d_itg_noninvert <- dplyr::select(d_noninvert, starts_with("itg_"))
+d_soc <- dplyr::select(d, soc_1 : soc_8)
+d_soc_noninvert <- dplyr::select(d_noninvert, soc_1 : soc_8)
+d_anx <- dplyr::select(d, starts_with("anx_"))
+d_anx_noninvert <- dplyr::select(d_noninvert, starts_with("anx_"))
+d_ria <- dplyr::select(d, ria_1 : ria_8)
+d_ria_noninvert <- dplyr::select(d_noninvert, ria_1 : ria_8)
+d_tra <- dplyr::select(d, tra_1 : tra_8)
+d_tra_noninvert <- dplyr::select(d_noninvert, tra_1 : tra_8)
+```
+
+Only few participants seem to have particularly atypical data. Will filter respondents with m > .30. Inspect those cases to see whether they indeed show irregular response patterns.
+
+\newpage
+
+```{r}
+d_suspicious
+```
+
+The cases indeed show extreme response patterns. Also, several inverted variables were not recognized (e.g., `r recoded`). These respondents will be deleted.
+
+\newpage
+# Power analyses
+
+Estimate achieved power for small effects.
 
@@
 power_small <- power_analysis$power %>% multiply_by(100) %>% round(0)
-
+```
+
+Estimate achieved power for small to moderate effects.
+
+```{r}
 (power_analysis <- pwr.r.test(n = n_d, r = .2, sig.level = .05))
 power_smallmoderate <- power_analysis$power %>% multiply_by(100) %>% round(0)
-
+```
+
+Estimate the size of effects that we were able to find with a probability of 95%.
+
+```{r}
 (sensitivity_analysis <- pwr.r.test(n = n_d, sig.level = .05, power = .95))
 sensitivity_95 <- sensitivity_analysis$r %>% round(2)
-
+```
+
+Estimate the sample size needed to find small effects with a probability of 95%.
+
+```{r}
 (sample_analysis <- pwr.r.test(sig.level = .05, power = .95, r = .1))
@@
 
-```{r}
-d_tmp <- dplyr::select(d, -id, -male, -age, -inc, -time, -miss_per, -starts_with("BFI"))
+We test for the assumption of multivariate normal distribution by running Mardia's test.
+
+```{r}
+d_tmp <- dplyr::select(d, -id, -male, -age, -inc, -time, -miss_per)
 (mult_norm <- mvn(data = d_tmp, mvnTest = "mardia")$multivariateNormality %>% 
@@
 
+Shows that the assumptions of multivariate normal distribution was violated. Will hence use robust estimator in the following analyses.
+
 \newpage
 # Measures
+
+In what follows, we present the measures we used.
+Specifically, we present each item's distribution and a confirmatory factor analysis (CFA) of the original scale.
+If the scale did not show sufficient fit, we first ran exploratory factor analyses (EFA) to better determine the underlying factor structure.
+In an iterative process, we then adapted the scales (e.g., by introducing subdimensions, trying bifactor solutions, or deleting items).
+
 ## Need for Privacy
 
-```{r, fig.height=15, fig.width=12}
+```{r}
 d_tmp <- d_pri_nee
@@
 \newpage
-### Correlation table
-
-```{r, fig.height=15, fig.width=12}
-corr_tmp <- cor(d_tmp)
-corrplot(corr_tmp, type = "upper", method = "color",
-         tl.col = "black")
-```
-
-### Kaiser-Meyer-Oltkin criterion
+### CFA 1
+
+We first analyze all dimensions separately to see how they do individually and as specified theoretically a priori.
+The general aim is, of course, to find the general structure of the items when analyzed together.
+
+#### Informational Privacy
+
+```{r}
+model <- '
+  pri_nee_gen =~ pri_nee_gen_1 + pri_nee_gen_2 + pri_nee_gen_3 + pri_nee_gen_4
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+Does not show adequate fit.
+
+\newpage
+#### Government
+
+```{r}
+model <- '
+  pri_nee_gov =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_5 + pri_nee_soc_9
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+Shows good fit, can be used individually for future research.
+
+\newpage
+#### Anonymity
+
+```{r}
+model <- '
+  pri_nee_ano =~ pri_nee_soc_5 + pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+Shows moderate fit.
+
+\newpage
+#### Interpersonal online
+
+```{r}
+model <- '
+  pri_nee_int_onl =~ pri_nee_int_1 + pri_nee_int_2 + pri_nee_int_3 + pri_nee_int_4 + pri_nee_int_9
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+Shows poor fit.
+
+\newpage
+#### Interpersonal offline
+
+```{r}
+model <- '
+  pri_nee_int_off =~ pri_nee_int_5 + pri_nee_int_6 + pri_nee_int_7 + pri_nee_int_8 + pri_nee_int_9
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+Does not show adequate fit.
+
+\newpage
+#### Combined
+
+```{r}
+model <- '
+  pri_nee_gen =~ pri_nee_gen_1 + pri_nee_gen_2 + pri_nee_gen_3 + pri_nee_gen_4
+  pri_nee_gov =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_5 + pri_nee_soc_9
+  pri_nee_ano =~ pri_nee_soc_5 + pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8
+  pri_nee_int_onl =~ pri_nee_int_1 + pri_nee_int_2 + pri_nee_int_3 + pri_nee_int_4 + pri_nee_int_9
+  pri_nee_int_off =~ pri_nee_int_5 + pri_nee_int_6 + pri_nee_int_7 + pri_nee_int_8 + pri_nee_int_9
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+The combined scale does not converge. Will need to be adapted thoroughly.
+
+\newpage
+### EFA 1
+
+In what follows, we now try to find what items need to be selected in order to attain a measure of need for privacy that includes as many items as possible.
+
+#### Kaiser-Meyer-Oltkin criterion
 
@@
 
-On the basis of the KMO, the following items should be exluded: `r names(kmo$MSAi[kmo$MSAi < .7])`.
-
-\newpage
-### Parallel analysis
+On the basis of the KMO, the following items should (and will) be exluded: `r names(kmo$MSAi[kmo$MSAi < .7])`.
+
+\newpage
+#### Parallel analysis
+
+Next, we run a parallel analysis to determine the underlying structure.
 
@@
 \newpage
-### EFA
-
-```{r}
-fa(r = d_tmp, nfactors = 3, fm = "oblimin")
+#### Factor analysis 1
+
+```{r}
+efa <- fa(r = d_tmp, nfactors = 3, fm = "oblimin")
+efa$loadings
 ```
@@
 
-The following items overall contribute little:
-
-- Communalities reveal that item INT_4 and INT_8 don't load sufficiently strong on latent factors. Should be excluded.
-- Item INT_1 only loads negative on factor 3 -- little positive contribution
+The following items will be exluded:
+
+- Communalities reveal that item itg_4 and itg_8 don't load sufficiently strong on latent factors.
+- Item itg_1 only loads negative on factor 3 -- little positive contribution.
 
@@
 
-- BOT_3, BOT_4, INT_2, INT_6. Will be difficult to decide whether to maintain or delete.
-
-\newpage
-
-```{r}
-d_tmp <- dplyr::select(d_tmp, -c("N4P.INT_1", "N4P.INT_4", "N4P.INT_8")) # -N4P.INT_2 -N4P.INT_6, -N4P.INT_7, -N4P.BOT_2, -N4P.INT_4
-fa(r = d_tmp, nfactors = 3, fm = "oblimin")
-```
-
-\newpage
-### CFA 1
-
-```{r}
-model <- '
-  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_5 + N4P.SOC_9
-  pri_nee_int =~ N4P.BOT_1 + N4P.BOT_2 + N4P.BOT_3 + N4P.BOT_4 + N4P.INT_2 + N4P.INT_3 + N4P.INT_6 + N4P.INT_7 + N4P.INT_9
-  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2 + N4P.INT_6
+- BOT_3, BOT_4, itg_2, itg_6. Will be difficult to decide whether to maintain or delete.
+
+Run novel factor analysis.
+
+\newpage
+#### Factor analysis 2
+
+```{r}
+d_tmp <- dplyr::select(d_tmp, -c("pri_nee_int_1", "pri_nee_int_4", "pri_nee_int_8"))
+efa <- fa(r = d_tmp, nfactors = 3, fm = "oblimin")
+efa$loadings
+```
+
+Looks better. Will now be tested in CFA.
+
+\newpage
+### CFA 2
+
+```{r}
+model <- '
+  pri_nee_gov =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_5 + pri_nee_soc_9
+  pri_nee_int =~ pri_nee_gen_1 + pri_nee_gen_2 + pri_nee_gen_3 + pri_nee_gen_4 + pri_nee_int_2 + pri_nee_int_3 + pri_nee_int_6 + pri_nee_int_7 + pri_nee_int_9
+  pri_nee_ano =~ pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8 + pri_nee_int_2 + pri_nee_int_6
 '
@@
 
-As expected, items BOT_2, BOT_3, & BOT_4 cause trouble. Will delete.
-
-\newpage
-### CFA 2
-
-```{r}
-model <- '
-  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_5 + N4P.SOC_9
-  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_3 + N4P.INT_6 + N4P.INT_7 + N4P.INT_9
-  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2 + N4P.INT_6
+As expected, items BOT_2, BOT_3, & BOT_4 cause trouble. Will be deleted.
+
+\newpage
+### CFA 3
+
+```{r}
+model <- '
+  pri_nee_gov =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_5 + pri_nee_soc_9
+  pri_nee_int =~ pri_nee_gen_1 + pri_nee_int_2 + pri_nee_int_3 + pri_nee_int_6 + pri_nee_int_7 + pri_nee_int_9
+  pri_nee_ano =~ pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8 + pri_nee_int_2 + pri_nee_int_6
 '
@@
 
-Shows acceptable fit. Problem is, we don't want to exclude too many items and to overfit the data. Let's inspect modification indices once more to see if there's a theoretically plausible adaption.
+Shows shows improved but still not really acceptable fit.
+Problem is, we don't want to exclude too many items and to overfit the data.
+Let's inspect modification indices once more to see if there's a theoretically plausible adaption.
 
@@
 
-Item INT_3 is a troublemaker.
+Item itg_3 is a troublemaker.
 As it's an inverted item, we have a good reason to delete it.
-Also, item INT_6 doesn't really have anything to do with anonymity; we can delete it.
-Likewise, item SOC_5 loads on government, while it also measure anonymity.
+Also, item itg_6 doesn't really have anything to do with anonymity; we can delete it.
+Likewise, item soc_5 loads on government, while it also measure anonymity.
 Maybe delete.
@@
 \newpage
-### CFA 3
-
-```{r}
-model <- '
-  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
-  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9
-  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
+### CFA 4
+
+```{r}
+model <- '
+  pri_nee_gov =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_9
+  pri_nee_int =~ pri_nee_gen_1 + pri_nee_int_2 + pri_nee_int_7 + pri_nee_int_9
+  pri_nee_ano =~ pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8 + pri_nee_int_2
 '
@@
 
-Shows a satisfactory, but not ideal solution. Try bifactor next.
-
-\newpage
-### CFA bifactor
-
-```{r}
-model <- '
-  pri_nee_gen =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9 + N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9 + N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
-  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
-  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9
-  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
+Although not ideal, shows a satisfactory solution. Will be used for analyses. In what follows, run specific CFAs for the dimensions, to get a better idea how they would work when used separately.
+
+\newpage
+#### CFA privacy need government
+
+```{r}
+model <- '
+  pri_nee_gov =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_9
   '
@@
 summary(fit, fit = TRUE, std = TRUE)
+assign(paste0(name_tmp, "_gov_fit"), fit)
+```
+
+\newpage
+#### CFA privacy need interpersonal
+
+```{r}
+model <- '
+  pri_nee_int =~ pri_nee_gen_1 + pri_nee_int_2 + pri_nee_int_7 + pri_nee_int_9
+'
+fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
+summary(fit, fit = TRUE, std = TRUE)
+assign(paste0(name_tmp, "_int_fit"), fit)
+```
+
+\newpage
+#### CFA privacy need anonymity
+
+```{r}
+model <- '
+  pri_nee_ano =~ pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8 + pri_nee_int_2
+'
+fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
+summary(fit, fit = TRUE, std = TRUE)
+assign(paste0(name_tmp, "_ano_fit"), fit)
+```
+
+\newpage
+#### CFA bifactor
+
+```{r}
+model <- '
+  pri_nee_gen =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_9 + pri_nee_gen_1 + pri_nee_int_2 + pri_nee_int_7 + pri_nee_int_9 + pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8 + pri_nee_int_2
+  pri_nee_gov =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_9
+  pri_nee_int =~ pri_nee_gen_1 + pri_nee_int_2 + pri_nee_int_7 + pri_nee_int_9
+  pri_nee_ano =~ pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8 + pri_nee_int_2
+'
+fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
+summary(fit, fit = TRUE, std = TRUE)
 assign(paste0(name_tmp, "_bifactor_fit"), fit)
@@
 
-Bifactor-solution fits the data best.
-
-\newpage
-### CFA privacy need government
-
-```{r}
-model <- '
-  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
-  '
-fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
-summary(fit, fit = TRUE, std = TRUE)
-assign(paste0(name_tmp, "_gov_fit"), fit)
-```
-
-\newpage
-### CFA privacy need interpersonal
-
-```{r}
-model <- '
-  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9
-'
-fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
-summary(fit, fit = TRUE, std = TRUE)
-assign(paste0(name_tmp, "_int_fit"), fit)
-```
-
-\newpage
-### CFA privacy need anonymity
-
-```{r}
-model <- '
-  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
-'
-fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
-summary(fit, fit = TRUE, std = TRUE)
-assign(paste0(name_tmp, "_ano_fit"), fit)
-```
+Bifactor-solution fits the data best. However, for theoretical reasons will not be used for the analyses.
 
@@
 name_tmp <- "soc"
-```
-
-### Items
-
-```{r, fig.height=8, fig.width=12}
-p_int <- ggplot(d_tmp_noninvert %>% 
-                  gather(name, value) %>% 
-                  left_join(items, "name"),
-                  aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~content_breaks)
-p_int
-
-# extract mean and sd
-desc <- data.frame(
-  m = mean(unlist(d_tmp), na.rm = TRUE),
-  sd = sd(unlist(d_tmp), na.rm = TRUE)
-)
-assign(paste0(name_tmp, "_desc"), desc)
-```
-
-\newpage
-### Parallel analysis
-
-```{r}
-fa.parallel(d_tmp, fm = "ml")
-```
-
-\newpage
-### EFA 1
-
-```{r}
-fa(d_tmp, fm = "ml", nfactors = 3)
-```
-
-\newpage
-### EFA 2
-
-```{r}
-fa(d_tmp, fm = "ml", nfactors = 2)
-```
-
-\newpage
-### CFA 1
-
-```{r}
-model <- '
-  soc_1 =~ a*SOC_1 + a*SOC_3 + a*SOC_5 + a*SOC_7
-  soc_2 =~ b*SOC_1 + b*SOC_2 + b*SOC_4 + b*SOC_6 + b*SOC_7 + b*SOC_8
-  soc_gen =~ SOC_1 + SOC_2 + SOC_3 + SOC_4 + SOC_5 + SOC_6 + SOC_7 + SOC_8
-'
-fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
-summary(fit, fit = TRUE, std = TRUE)
-```
-
-Shows no solution for two factors.
-
-\newpage
-### CFA 2
-
-```{r}
-model <- '
-  soc_gen =~ SOC_1 + SOC_2 + SOC_4 + SOC_6 + SOC_7 + SOC_8
-'
-fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
-summary(fit, fit = TRUE, std = TRUE)
-```
-
-Uni-dimensional solution with 6 items not feasible; need to reduce to 4.
-
-\newpage
-### CFA 3
-
-```{r}
-model <- '
-  soc_gen =~ SOC_1 + SOC_2 + SOC_7 + SOC_8
-'
-fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
-summary(fit, fit = TRUE, std = TRUE)
-assign(paste0(name_tmp, "_fit"), fit)
-assign(paste0(name_tmp, "_gen"), 
-       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
-```
-
-Shows adequate fit.
-
-```{r}
-# Extract error variance
-rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
-var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
-err_var <- (1 - rel) * var
-assign(paste0(name_tmp, "_err_var"), err_var)
-```
-
-\newpage
-## Anxiety
-
-```{r}
-d_tmp <- d_fea
-d_tmp_noninvert <- d_fea_noninvert
-name_tmp <- "fea"
-```
-
-### Items
-
-```{r}
-ggplot(d_tmp_noninvert %>% 
-         gather(name, value) %>% 
-         left_join(items, "name"),
-         aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~content_breaks)
-
-# extract mean and sd
-desc <- data.frame(
-  m = mean(unlist(d_tmp), na.rm = TRUE),
-  sd = sd(unlist(d_tmp), na.rm = TRUE)
-)
-assign(paste0(name_tmp, "_desc"), desc) 
-```
-
-### Parallel analysis
-
-```{r}
-fa.parallel(d_tmp)
-```
-
-Implies one dimension.
-
-\newpage
-### CFA 1
-
-```{r}
-model <- '
-  fea_gen =~ FEA_2 + FEA_4 + FEA_7 + FEA_8 + FEA_1 + FEA_3 + FEA_5 + FEA_6
-'
-fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
-summary(fit, fit = TRUE, std = TRUE)
-```
-
-Doesn't fit. Instead, try two dimensions.
-
-\newpage
-### EFA
-
-```{r}
-fa(d_tmp, nfactors = 2, fm = "ml")
-tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
-```
-
-Seems appropriate.
-
-\newpage
-### CFA 2
-
-```{r}
-model <- '
-  fea_1 =~ a*FEA_2 + a*FEA_4 + a*FEA_6 + a*FEA_8
-  fea_2 =~ b*FEA_1 + b*FEA_3 + b*FEA_5 + b*FEA_7
-  fea_gen =~ FEA_2 + FEA_4 + FEA_7 + FEA_8 + FEA_1 + FEA_3 + FEA_5 + FEA_6
-'
-fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
-summary(fit, fit = TRUE, std = TRUE)
-assign(paste0(name_tmp, "_fit"), fit)
-assign(paste0(name_tmp, "_gen"), 
-       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
-```
-
-Shows an adequate solution.
-
-```{r}
-# Extract error variance
-rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
-var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
-err_var <- (1 - rel) * var
-assign(paste0(name_tmp, "_err_var"), err_var)
-```
-
-\newpage
-## Risk Avoidance
-
-```{r}
-d_tmp <- d_rit
-d_tmp_noninvert <- d_rit_noninvert
-name_tmp <- "rit"
-```
-
-### Items
-
-```{r}
-ggplot(d_tmp_noninvert %>% 
-         gather(name, value) %>% 
-         left_join(items, "name"),
-         aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~content_breaks)
-
-# extract mean and sd
-desc <- data.frame(
-  m = mean(unlist(d_tmp), na.rm = TRUE),
-  sd = sd(unlist(d_tmp), na.rm = TRUE)
-)
-assign(paste0(name_tmp, "_desc"), desc)
-```
-
-\newpage
-### Parallel analysis
-
-```{r}
-fa.parallel(d_tmp)
-```
-
-\newpage
-### EFA
-
-```{r}
-fa(d_tmp, nfactors = 2, fm = "ml")
-tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
-```
-
-Produces a fitting solution.
-
-\newpage
-### CFA 1
-
-```{r}
-model <- '
-  rit_1 =~ a*RIT_2 + a*RIT_4 + RIT_5 + a*RIT_6 + a*RIT_7 + a*RIT_8
-  rit_2 =~ RIT_1 + RIT_3 + RIT_5
-  rit_gen =~ RIT_1 + RIT_2 + RIT_3 + RIT_4 + RIT_5 + RIT_6 + RIT_7 + RIT_8
-'
-fit <- cfa(model, d, estimator = "MLM")
-summary(fit, fit = TRUE, std = TRUE)
-assign(paste0(name_tmp, "_fit"), fit)
-assign(paste0(name_tmp, "_gen"), 
-       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
-```
-
-Does not produce a good-fitting model.
-
-\newpage
-### CFA 2
-
-```{r}
-model <- '
-  rit_gen =~ RIT_2 + RIT_4 + RIT_6 + RIT_7 + RIT_8
-'
-fit <- cfa(model, d, estimator = "MLM")
-summary(fit, fit = TRUE, std = TRUE)
-assign(paste0(name_tmp, "_fit"), fit)
-assign(paste0(name_tmp, "_gen"), 
-       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
-```
-
-```{r}
-# Extract error variance
-rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
-var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
-err_var <- (1 - rel) * var
-assign(paste0(name_tmp, "_err_var"), err_var)
-```
-
-\newpage 
-## Traditionalism
-
-```{r}
-d_tmp <- d_tra
-d_tmp_noninvert <- d_tra_noninvert
-name_tmp <- "tra"
-```
-
-### Items
-
-```{r}
-ggplot(d_tmp_noninvert %>% 
-         gather(name, value) %>% 
-         left_join(items, "name"),
-         aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~content_breaks)
-
-# extract mean and sd
-desc <- data.frame(
-  m = mean(unlist(d_tmp), na.rm = TRUE),
-  sd = sd(unlist(d_tmp), na.rm = TRUE)
-)
-assign(paste0(name_tmp, "_desc"), desc)
-```
-
-\newpage
-### Parallel analysis
-
-```{r}
-fa.parallel(d_tmp, fm = "ml")
-```
-
-\newpage
-### EFA
-
-```{r}
-fa(d_tmp, nfactors = 2, fm = "ml")
-tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
-```
-
-Implies a single dimension, as on factor 2 there is only one significant loading.
-
-\newpage
-### CFA
-
-```{r}
-model <- '
-  tra_gen =~ TRA_1 + TRA_5 + TRA_3 + TRA_8 + TRA_7
-'
-fit <- cfa(model, d, estimator = "MLM")
-summary(fit, fit = TRUE, std = TRUE)
-assign(paste0(name_tmp, "_fit"), fit)
-assign(paste0(name_tmp, "_gen"), 
-       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
-```
-
-Shows adequate fit.
-
-```{r}
-# Extract error variance
-rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
-var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
-err_var <- (1 - rel) * var
-assign(paste0(name_tmp, "_err_var"), err_var)
-```
-
-\newpage
-## Integrity
-
-```{r, fig.height=8, fig.width=12}
-d_tmp <- d_int
-d_tmp_noninvert <- d_int_noninvert
-name_tmp <- "int"
 ```
@@
 \newpage
-### Parallel analysis
+### CFA 1
+
+```{r}
+model <- '
+  soc =~ soc_1 + soc_2 + soc_3 + soc_4 + soc_5 + soc_6 + soc_7 + soc_8
+'
+fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+Does not show sufficient fit. Run EFAs to determine underlying factor structure.
+
+\newpage
+### EFA 1
+#### Parallel analysis
 
@@
 \newpage
-### EFA
-
-```{r}
-fa(d_tmp, nfactors = 3, fm = "ml")
-```
-
-Two factors don't really convince, as factor 3 consists of one item only. Will try two-factor solution.
-
-```{r}
-fa(d_tmp, nfactors = 2, fm = "ml")
-```
-
-Implies that item 3 and item 4 should be dropped.
-
-\newpage
-### CFA
-
-```{r}
-model <- '
-  int_1 =~ a*INT_1 + a*INT_2 + a*INT_5 + a*INT_6 + a*INT_7 + a*INT_8
-  int_2 =~ b*INT_8 + b*INT_9 + b*INT_10 + b*INT_11
-  int_gen =~ INT_1 + INT_2 + INT_5 + INT_6 + INT_7 + INT_8 + INT_9 + INT_10 + INT_11
+#### Factor analysis
+
+```{r}
+efa <- fa(d_tmp, fm = "ml", nfactors = 3)
+efa$loadings
+```
+
+The three factor solution does not show a coherent picture; for example, Factor 3 is determined by a single item.
+
+\newpage
+### EFA 2
+#### Factor analysis
+
+```{r}
+efa <- fa(d_tmp, fm = "ml", nfactors = 2)
+efa$loadings
+```
+
+Seems more plausible. Will be modelled as bifactor solution next.
+
+\newpage
+### CFA 2
+
+```{r}
+model <- '
+  soc_one =~ a*soc_1 + a*soc_3 + a*soc_5 + a*soc_7
+  soc_two =~ b*soc_1 + b*soc_2 + b*soc_4 + b*soc_6 + b*soc_7 + b*soc_8
+  soc_gen =~ soc_1 + soc_2 + soc_3 + soc_4 + soc_5 + soc_6 + soc_7 + soc_8
 '
@@
 summary(fit, fit = TRUE, std = TRUE)
+```
+
+Shows no solution for two factors. Single-dimension solution will be fitted next.
+
+\newpage
+### CFA 3
+
+```{r}
+model <- '
+  soc_gen =~ soc_1 + soc_2 + soc_4 + soc_6 + soc_7 + soc_8
+'
+fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+Uni-dimensional solution with 6 items not feasible; need to reduce to 4.
+
+\newpage
+### CFA 4
+
+```{r}
+model <- '
+  soc_gen =~ soc_1 + soc_2 + soc_7 + soc_8
+'
+fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
+summary(fit, fit = TRUE, std = TRUE)
 assign(paste0(name_tmp, "_fit"), fit)
-assign(paste0(name_tmp, "_gen"), as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
-```
-
-Bifactor model fits the date well.
+assign(paste0(name_tmp, "_gen"), 
+       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
+```
+
+Shows adequate fit.
 
@@
 # Extract error variance
-# For the models testing the hypotheses, we next calculate the measures' error variance. The error variance will be included in the final model, enabling a better estimation of the effects.
 rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
@@
 \newpage
+## Integrity
+
+```{r, fig.height=8, fig.width=12}
+d_tmp <- d_itg
+d_tmp_noninvert <- d_itg_noninvert
+name_tmp <- "itg"
+```
+
+### Items
+
+```{r, fig.height=8, fig.width=12}
+ggplot(d_tmp_noninvert %>% 
+         gather(name, value) %>% 
+         left_join(items, "name"),
+         aes(x = value)) +
+  geom_bar() +
+  facet_wrap(~content_breaks)
+
+# extract mean and sd
+desc <- data.frame(
+  m = mean(unlist(d_tmp), na.rm = TRUE),
+  sd = sd(unlist(d_tmp), na.rm = TRUE)
+)
+assign(paste0(name_tmp, "_desc"), desc)
+```
+
+Does not show adequate fit.
+
+\newpage
+### CFA 1
+
+```{r}
+model <- '
+  itg =~ itg_1 + itg_2 + itg_3 + itg_4 + itg_5 + itg_6 + itg_7 + itg_8 + itg_9 + itg_10 + itg_11
+'
+fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+\newpage
+### EFA 1
+#### Parallel analysis
+
+```{r}
+fa.parallel(d_tmp, fm = "ml")
+```
+
+\newpage
+#### Factor analysis 1
+
+```{r}
+efa <- fa(d_tmp, nfactors = 3, fm = "ml")
+efa$loadings
+```
+
+Two factors don't really convince, as factor 3 consists of one item only. Will try two-factor solution.
+
+\newpage
+#### Factor analysis 2
+
+```{r}
+efa <- fa(d_tmp, nfactors = 2, fm = "ml")
+efa$loadings
+```
+
+Suggests that item 3 and item 4 should be dropped.
+
+\newpage
+### CFA 2
+
+```{r}
+model <- '
+  int_1 =~ a*itg_1 + a*itg_2 + a*itg_5 + a*itg_6 + a*itg_7 + a*itg_8
+  int_2 =~ b*itg_8 + b*itg_9 + b*itg_10 + b*itg_11
+  itg_gen =~ itg_1 + itg_2 + itg_5 + itg_6 + itg_7 + itg_8 + itg_9 + itg_10 + itg_11
+'
+fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
+summary(fit, fit = TRUE, std = TRUE)
+assign(paste0(name_tmp, "_fit"), fit)
+assign(paste0(name_tmp, "_gen"), as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
+```
+
+The data fit a bifactor model well.
+
+```{r}
+# Extract error variance
+rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
+var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
+err_var <- (1 - rel) * var
+assign(paste0(name_tmp, "_err_var"), err_var)
+```
+
+\newpage
+## Anxiety
+
+```{r}
+d_tmp <- d_anx
+d_tmp_noninvert <- d_anx_noninvert
+name_tmp <- "anx"
+```
+
+### Items
+
+```{r}
+ggplot(d_tmp_noninvert %>% 
+         gather(name, value) %>% 
+         left_join(items, "name"),
+         aes(x = value)) +
+  geom_bar() +
+  facet_wrap(~content_breaks)
+
+# extract mean and sd
+desc <- data.frame(
+  m = mean(unlist(d_tmp), na.rm = TRUE),
+  sd = sd(unlist(d_tmp), na.rm = TRUE)
+)
+assign(paste0(name_tmp, "_desc"), desc) 
+```
+
+\newpage
+### CFA 1
+
+```{r}
+model <- '
+  anx =~ anx_1 + anx_2 + anx_3 + anx_4 + anx_5 + anx_6 + anx_7 + anx_8
+'
+fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+Does not show adequate fit.
+
+\newpage
+### EFA 1
+#### Parallel analysis
+
+```{r}
+fa.parallel(d_tmp)
+```
+
+Implies three dimension.
+
+\newpage
+#### Factor analysis
+
+```{r}
+efa <- fa(d_tmp, nfactors = 2, fm = "ml")
+efa$loadings
+```
+
+Seems appropriate. First, try bifactor solution.
+
+\newpage
+### CFA 2
+
+```{r}
+model <- '
+  anx_one =~ a*anx_2 + a*anx_4 + a*anx_6 + a*anx_8
+  anx_two =~ b*anx_1 + b*anx_3 + b*anx_5 + b*anx_7
+  anx_gen =~ anx_2 + anx_4 + anx_7 + anx_8 + anx_1 + anx_3 + anx_5 + anx_6
+'
+fit <- cfa(model, d, estimator = "MLM", orthogonal = TRUE)
+summary(fit, fit = TRUE, std = TRUE)
+assign(paste0(name_tmp, "_fit"), fit)
+assign(paste0(name_tmp, "_gen"), 
+       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
+```
+
+Shows an adequate solution.
+
+```{r}
+# Extract error variance
+rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
+var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
+err_var <- (1 - rel) * var
+assign(paste0(name_tmp, "_err_var"), err_var)
+```
+
+\newpage
+## Risk avoidance
+
+```{r}
+d_tmp <- d_ria
+d_tmp_noninvert <- d_ria_noninvert
+name_tmp <- "ria"
+```
+
+### Items
+
+```{r}
+ggplot(d_tmp_noninvert %>% 
+         gather(name, value) %>% 
+         left_join(items, "name"),
+         aes(x = value)) +
+  geom_bar() +
+  facet_wrap(~content_breaks)
+
+# extract mean and sd
+desc <- data.frame(
+  m = mean(unlist(d_tmp), na.rm = TRUE),
+  sd = sd(unlist(d_tmp), na.rm = TRUE)
+)
+assign(paste0(name_tmp, "_desc"), desc)
+```
+
+\newpage
+### CFA 1
+
+```{r}
+model <- '
+  ria =~ ria_1 + ria_2 + ria_3 + ria_4 + ria_5 + ria_6 + ria_7 + ria_8
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+assign(paste0(name_tmp, "_fit"), fit)
+assign(paste0(name_tmp, "_gen"), 
+       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
+```
+
+Does not show sufficient fit.
+
+\newpage
+### EFA 1
+#### Parallel analysis
+
+```{r}
+fa.parallel(d_tmp)
+```
+
+\newpage
+#### Factor analysis
+
+```{r}
+efa <- fa(d_tmp, nfactors = 2, fm = "ml")
+efa$loadings
+```
+
+Produces a plausible solution.
+
+\newpage
+### CFA 2
+
+```{r}
+model <- '
+  ria_one =~ a*ria_2 + a*ria_4 + ria_5 + a*ria_6 + a*ria_7 + a*ria_8
+  ria_two =~ ria_1 + ria_3 + ria_5
+  ria_gen =~ ria_1 + ria_2 + ria_3 + ria_4 + ria_5 + ria_6 + ria_7 + ria_8
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+assign(paste0(name_tmp, "_fit"), fit)
+assign(paste0(name_tmp, "_gen"), 
+       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
+```
+
+Does not produce a good-fitting model. Try single-dimension next.
+
+\newpage
+### CFA 3
+
+```{r}
+model <- '
+  ria_gen =~ ria_2 + ria_4 + ria_6 + ria_7 + ria_8
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+assign(paste0(name_tmp, "_fit"), fit)
+assign(paste0(name_tmp, "_gen"), 
+       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
+```
+
+Shows an adequate solution.
+
+```{r}
+# Extract error variance
+rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
+var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
+err_var <- (1 - rel) * var
+assign(paste0(name_tmp, "_err_var"), err_var)
+```
+
+\newpage 
+## Traditionalism
+
+```{r}
+d_tmp <- d_tra
+d_tmp_noninvert <- d_tra_noninvert
+name_tmp <- "tra"
+```
+
+### Items
+
+```{r}
+ggplot(d_tmp_noninvert %>% 
+         gather(name, value) %>% 
+         left_join(items, "name"),
+         aes(x = value)) +
+  geom_bar() +
+  facet_wrap(~content_breaks)
+
+# extract mean and sd
+desc <- data.frame(
+  m = mean(unlist(d_tmp), na.rm = TRUE),
+  sd = sd(unlist(d_tmp), na.rm = TRUE)
+)
+assign(paste0(name_tmp, "_desc"), desc)
+```
+
+\newpage
+### CFA 1
+
+```{r}
+model <- '
+  tra_gen =~ tra_1 + tra_2 + tra_3 + tra_4 + tra_5 + tra_6 + tra_7 + tra_8
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+```
+
+Data show poor fit to the model.
+
+\newpage
+### EFA 1
+#### Parallel analysis
+
+```{r}
+fa.parallel(d_tmp, fm = "ml")
+```
+
+\newpage
+#### Factor analysis
+
+```{r}
+efa <- fa(d_tmp, nfactors = 3, fm = "ml")
+efa$loadings
+# tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
+```
+
+Does not show a convincing solution.
+
+\newpage
+#### Factor analysis
+
+```{r}
+efa <- fa(d_tmp, nfactors = 2, fm = "ml")
+efa$loadings
+# tmp <- omega(d_tmp, nfactors = 2, fm = "ml")
+```
+
+Implies a single dimension, as on factor 2 there is only one significant loading.
+
+\newpage
+### CFA 2
+
+```{r}
+model <- '
+  tra_gen =~ tra_1 + tra_3 + tra_5 + tra_7 + tra_8
+'
+fit <- cfa(model, d, estimator = "MLM")
+summary(fit, fit = TRUE, std = TRUE)
+assign(paste0(name_tmp, "_fit"), fit)
+assign(paste0(name_tmp, "_gen"), 
+       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
+```
+
+Shows adequate fit.
+
+```{r}
+# Extract error variance
+rel <- reliability(fit)["alpha", paste0(name_tmp, "_gen")]
+var <- var(as.data.frame(predict(fit))[paste0(name_tmp, "_gen")])
+err_var <- (1 - rel) * var
+assign(paste0(name_tmp, "_err_var"), err_var)
+```
+
+\newpage
 # Results
+## Structural regression model
+
+In what follows, we present the results of the structural regression model, in which we predict the three dimensions of privacy on the basis of the aforementioned personality facets.
+The personality facets are modelled as latent factors with single indicators, in which the indicators' error variances are specified using the results from the CFAs.
 
@@
 # combine model predicted values with regular data
-d_lat <- cbind(soc_gen, int_gen, fea_gen, rit_gen, tra_gen, pri_nee_lat)
+d_lat <- cbind(soc_gen, itg_gen, anx_gen, ria_gen, tra_gen, pri_nee_lat)
 d <- cbind(d, d_lat)
@@
 # combine error variances in table
-err_vars <- cbind(int_err_var, soc_err_var, fea_err_var, tra_err_var, rit_err_var)
+err_vars <- cbind(itg_err_var, soc_err_var, anx_err_var, tra_err_var, ria_err_var)
 
@@
 model <- '
-  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
-  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9
-  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
+  pri_nee_gov =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_9
+  pri_nee_int =~ pri_nee_gen_1 + pri_nee_int_2 + pri_nee_int_7 + pri_nee_int_9
+  pri_nee_ano =~ pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8 + pri_nee_int_2
   soc =~ soc_gen
-  fea =~ fea_gen
+  anx =~ anx_gen
   tra =~ tra_gen
-  rit =~ rit_gen
-  int =~ int_gen
-
-  pri_nee_gov ~ soc + int + fea + tra + rit + male + age + inc
-  pri_nee_int ~ soc + int + fea + tra + rit + male + age + inc
-  pri_nee_ano ~ soc + int + fea + tra + rit + male + age + inc
+  ria =~ ria_gen
+  itg =~ itg_gen
+
+  pri_nee_gov ~ soc + itg + anx + tra + ria + male + age + inc
+  pri_nee_int ~ soc + itg + anx + tra + ria + male + age + inc
+  pri_nee_ano ~ soc + itg + anx + tra + ria + male + age + inc
 
   soc_gen ~~ .177 * soc_gen
-  int_gen ~~ .104 * int_gen
-  fea_gen ~~ .106 * fea_gen
+  itg_gen ~~ .104 * itg_gen
+  anx_gen ~~ .106 * anx_gen
   tra_gen ~~ .169 * tra_gen
-  rit_gen ~~ .118 * rit_gen
+  ria_gen ~~ .118 * ria_gen
 '
@@
 \newpage
-# Tables
-## Items measuring need for privacy
+## Tables
+### Final items measuring need for privacy
 
@@
 t_pri_nee <- items %>% 
-  filter(grepl("N4P", name)) %>% 
-  mutate(name = factor(name, c(paste0("N4P.BOT_", rep(4:1)),
-                             paste0("N4P.INT_", rep(9:1)),
-                             paste0("N4P.SOC_", rep(9:1))))) %>% 
+  filter(grepl("pri_nee", name)) %>% 
+  mutate(name = factor(name, c(paste0("pri_nee_gen_", rep(4:1)),
+                             paste0("pri_nee_int_", rep(9:1)),
+                             paste0("pri_nee_soc_", rep(9:1))))) %>% 
   mutate(included = ifelse(name %in% items_incl, "yes", "no")) %>% 
+  filter(included == "yes") %>%
   arrange(desc(as.numeric(name))) %>% 
-  dplyr::select(name, included, content)
+  dplyr::select(name, content)
 
 knitr::kable(t_pri_nee) %>% 
-  kableExtra::column_spec(3, width = "10cm") %>% 
-  kableExtra::kable_styling(latex_options="scale_down", font_size = 7)
-```
-
-\newpage
-## Psychometrics
+#  kableExtra::column_spec(2, width = "10cm") %>% 
+kableExtra::kable_styling(latex_options="scale_down", font_size = 10)
+```
+
+\newpage
+### Psychometrics
 
@@
   "Sociability" = fit_tab(soc_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
-  "Integrity" = fit_tab(int_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
-  "Anxiety" = fit_tab(fea_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
-  "Risk aversion" = fit_tab(rit_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
+  "Integrity" = fit_tab(itg_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
+  "Anxiety" = fit_tab(anx_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
+  "Risk avoidance" = fit_tab(ria_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE),
   "Traditionality" = fit_tab(tra_fit, as_text = TRUE, reliability = TRUE, scaled = TRUE)
@@
 t_desc <- rbind(pri_nee_desc, pri_nee_gov_desc, pri_nee_int_desc, pri_nee_ano_desc,
-                soc_desc, int_desc, fea_desc, rit_desc, tra_desc)
-
-t_psyc <- cbind(t_desc, t_facval)
+                soc_desc, itg_desc, anx_desc, ria_desc, tra_desc)
+
+t_psyc <- cbind(t_desc, t_facval) %>% 
+  mutate_at(vars(df), funs(as.integer(.))) %>% 
+  set_rownames(rownames(t_facval))
 kable(t_psyc)
@@
 \newpage
-## Results
+### Structural regression model
 
@@
   mutate(Predictor = recode(Predictor,
-         `int` = "Integrity",
          `soc` = "Sociability",
-         `fea` = "Anxiety",
-         `rit` = "Risk avoidance",
+         `itg` = "Integrity",
+         `anx` = "Anxiety",
+         `ria` = "Risk avoidance",
          `tra` = "Traditionalism",
@@
 \newpage
-# Figures
-## Bivariate relations
-
-```{r eval = F}
-d_lat %<>% set_names("Sociability", "Integrity", "Anxiety", "Risk\navoidance", "Traditio-\nnalism", "Privacy need\ngovernment", "Privacy need\ninterpersonal", "Privacy need\nanonymity")
+## Figures
+### Bivariate relations
+
+```{r fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center'}
+d_lat %<>% 
+  set_names("Sociability", "Integrity", "Anxiety", "Risk\navoidance", "Traditio-\nnalism", 
+            "Privacy need\ngovernment", "Privacy need\ninterpersonal", "Privacy need\nanonymity")
 
@@
 
-## Results
+\newpage
+### Structural regression model
+
+Confidence intervals estimated using lavaan's standardized solution.
 
@@
   mutate(lhs = factor(lhs, c("pri_nee_ano", "pri_nee_int", "pri_nee_gov"))) %>%  # reorder for plot
-  mutate(rhs = factor(rhs, c("int", "soc", "fea", "rit", "tra", "male", "age", "inc"))) %>%  # reorder for plot
+  mutate(rhs = factor(rhs, c("soc", "itg", "anx", "ria", "tra", "male", "age", "inc"))) %>%  # reorder for plot
   mutate(lhs = recode(lhs, 
@@
   mutate(rhs = recode(rhs,
-         `int` = "Integrity",
          `soc` = "Sociability",
-         `fea` = "Anxiety",
+         `itg` = "Integrity",
+         `anx` = "Anxiety",
          `tra` = "Traditio-\nnalism",
-         `rit` = "Risk\navoidance",
+         `ria` = "Risk\navoidance",
          `inc` = "Income",
@@
 (p_results_threefactors <- ggplot(d_results_threefactors, aes(x = beta, y = lhs)) +
-  geom_vline(xintercept = 0) +
+  geom_vline(xintercept = 0, color = "darkgrey") +
   geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +
@@
 \newpage
+
+Confidence intervals estimated using Bootstrap approach with 2000 draws.
+Note that the results differ slightly from the regular approach, which is why in the paper we present the results using lavaan's standardized solution.
+
+```{r cache = T}
+# CIs are calculated by means of bootstrapping
+RNGkind("L'Ecuyer-CMRG")  # needed in order to enable replication of bootstrap
+results_threefactors_boot <- bootstrapLavaan(results_threefactors_fit, 
+                                             R = 2000, type = "parametric", iseed = 170819)
+ci_boot <- results_threefactors_boot %>%
+  as.data.frame() %>%
+  select(starts_with("pri_nee_gov~"), starts_with("pri_nee_int~"), starts_with("pri_nee_ano~")) %>%
+  select(-contains("~~")) %>%
+  summarise_all(funs("ci_ll_boot" = quantile(., .025),
+                     "ci_ul_boot" = quantile(., .975),
+                     "beta_median" = median(.)))
+
+ci_ll_boot <- select(ci_boot, contains("_ll_")) %>% t()
+ci_ul_boot <- select(ci_boot, contains("_ul_")) %>% t()
+beta_median <- select(ci_boot, contains("beta_median")) %>% t()
+
+# calculate CI for standardized effect 
+d_results_threefactors %<>%
+  mutate(ci_ll_boot = ci_ll_boot,
+         ci_ul_boot = ci_ul_boot,
+         beta_median = beta_median)
+
+(p_results_threefactors_boot <- ggplot(d_results_threefactors, aes(x = beta_median, y = lhs)) +
+  geom_vline(xintercept = 0, color = "darkgrey") +
+  geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +
+  geom_vline(xintercept = -0.1, linetype = "dashed", color = "grey") +
+  geom_point() +
+  geom_errorbarh(aes(xmin = ci_ll_boot, xmax = ci_ul_boot, height = .2)) + 
+  theme_bw() + 
+  theme(axis.title = element_blank(),
+        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
+  scale_x_continuous(breaks = c(-.4, -.2, 0, .2, .4)) +
+  coord_cartesian(xlim = c(-.5, .5)) +
+  facet_grid(~ rhs))
+```
+
+\newpage
 # Additional analyses
-## Bi-Factor
+## Structural regression model with need for privacy measured as bifactor
+### Results
 
@@
 model <- '
-  pri_nee_gen =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9 + N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9 + N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
-  pri_nee_gov =~ N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_9
-  pri_nee_int =~ N4P.BOT_1 + N4P.INT_2 + N4P.INT_7 + N4P.INT_9
-  pri_nee_ano =~ N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.INT_2
-
-  int =~ int_gen
+  pri_nee_gen =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_9 + pri_nee_gen_1 + pri_nee_int_2 + pri_nee_int_7 + pri_nee_int_9 + pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8 + pri_nee_int_2
+  pri_nee_gov =~ pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_9
+  pri_nee_int =~ pri_nee_gen_1 + pri_nee_int_2 + pri_nee_int_7 + pri_nee_int_9
+  pri_nee_ano =~ pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8 + pri_nee_int_2
+
   soc =~ soc_gen
-  fea =~ fea_gen
+  itg =~ itg_gen
+  anx =~ anx_gen
+  ria =~ ria_gen
   tra =~ tra_gen
-  rit =~ rit_gen
-
-  pri_nee_gen ~ int + soc + fea + tra + rit + male + age + inc
-  pri_nee_gov ~ int + soc + fea + tra + rit + male + age + inc
-  pri_nee_int ~ int + soc + fea + tra + rit + male + age + inc
-  pri_nee_ano ~ int + soc + fea + tra + rit + male + age + inc
+
+  pri_nee_gen ~ soc + itg + anx + ria + tra + male + age + inc
+  pri_nee_gov ~ soc + itg + anx + ria + tra + male + age + inc
+  pri_nee_int ~ soc + itg + anx + ria + tra + male + age + inc
+  pri_nee_ano ~ soc + itg + anx + ria + tra + male + age + inc
 
@@
 
-  int_gen ~~ .104 * int_gen
   soc_gen ~~ .177 * soc_gen
-  fea_gen ~~ .106 * fea_gen
+  itg_gen ~~ .104 * itg_gen
+  anx_gen ~~ .106 * anx_gen
+  ria_gen ~~ .118 * ria_gen
   tra_gen ~~ .169 * tra_gen
-  rit_gen ~~ .118 * rit_gen
 '
@@
 \newpage
+### Visualization
 
@@
   mutate(lhs = factor(lhs, c("pri_nee_ano", "pri_nee_int", "pri_nee_gov", "pri_nee_gen"))) %>%  # reorder for plot
-  mutate(rhs = factor(rhs, c("int", "soc", "fea", "rit", "tra", "male", "age", "inc"))) %>%  # reorder for plot
+  mutate(rhs = factor(rhs, c("soc", "itg", "anx", "ria", "tra", "male", "age", "inc"))) %>%  # reorder for plot
   mutate(lhs = recode(lhs,
@@
   mutate(rhs = recode(rhs,
-         `int` = "Integrity",
          `soc` = "Sociability",
-         `fea` = "Anxiety",
+         `itg` = "Integrity",
+         `anx` = "Anxiety",
+         `ria` = "Risk\navoidance",
          `tra` = "Traditio-\nnalism",
-         `rit` = "Risk\navoidance",
          `inc` = "Income",
@@
 (p_results_bifactor <- ggplot(d_results_bifactor, aes(x = beta, y = lhs)) +
-  geom_vline(xintercept = 0) +
+  geom_vline(xintercept = 0, color = "darkgrey") +
   geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +
@@
 \newpage
-## Individual items
+## Structural regression model with individual items
 
@@
 model <- '
-  N4P.BOT_1 + N4P.BOT_2 + N4P.BOT_3 + N4P.BOT_4 + N4P.SOC_1 + N4P.SOC_2 + N4P.SOC_3 + N4P.SOC_4 + N4P.SOC_5 + N4P.SOC_6 + N4P.SOC_7 + N4P.SOC_8 + N4P.SOC_9 + N4P.INT_1 + N4P.INT_2 + N4P.INT_3 + N4P.INT_4 + N4P.INT_5 + N4P.INT_6 + N4P.INT_7 + N4P.INT_8 + N4P.INT_9 ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
-
-  int_gen ~~ soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
-  soc_gen ~~ fea_gen + tra_gen + rit_gen + male + age + inc
-  fea_gen ~~ tra_gen + rit_gen + male + age + inc
-  tra_gen ~~ rit_gen + male + age + inc
-  rit_gen ~~ male + age + inc
+  pri_nee_gen_1 + pri_nee_gen_2 + pri_nee_gen_3 + pri_nee_gen_4 + pri_nee_soc_1 + pri_nee_soc_2 + pri_nee_soc_3 + pri_nee_soc_4 + pri_nee_soc_5 + pri_nee_soc_6 + pri_nee_soc_7 + pri_nee_soc_8 + pri_nee_soc_9 + pri_nee_int_1 + pri_nee_int_2 + pri_nee_int_3 + pri_nee_int_4 + pri_nee_int_5 + pri_nee_int_6 + pri_nee_int_7 + pri_nee_int_8 + pri_nee_int_9 ~ itg_gen + soc_gen + anx_gen + tra_gen + ria_gen + male + age + inc
+
+  itg_gen ~~ soc_gen + anx_gen + tra_gen + ria_gen + male + age + inc
+  soc_gen ~~ anx_gen + tra_gen + ria_gen + male + age + inc
+  anx_gen ~~ tra_gen + ria_gen + male + age + inc
+  tra_gen ~~ ria_gen + male + age + inc
+  ria_gen ~~ male + age + inc
   male ~~ age + inc
@@
   filter(op == "~") %>% 
-  mutate(rhs = factor(rhs, c("int_gen", "soc_gen", "fea_gen", "rit_gen", "tra_gen", 
+  mutate(rhs = factor(rhs, c("soc_gen", "itg_gen", "anx_gen", "ria_gen", "tra_gen", 
                              "male", "age", "inc"))) %>%  # reorder for plot
-  mutate(lhs = factor(lhs, c(paste0("N4P.BOT_", rep(4:1)),
-                             paste0("N4P.INT_", rep(9:1)),
-                             paste0("N4P.SOC_", rep(9:1))))) %>%  # reorder for plot
+  mutate(lhs = factor(lhs, c(paste0("pri_nee_gen_", rep(4:1)),
+                             paste0("pri_nee_int_", rep(9:1)),
+                             paste0("pri_nee_soc_", rep(9:1))))) %>%  # reorder for plot
   mutate(rhs = recode(rhs,
-         `int_gen` = "Integrity",
          `soc_gen` = "Sociability",
-         `fea_gen` = "Anxiety",
+         `itg_gen` = "Integrity",
+         `anx_gen` = "Anxiety",
+         `ria_gen` = "Risk\navoidance",
          `tra_gen` = "Traditio-\nnalism",
-         `rit_gen` = "Risk\navoidance",
          `inc` = "Income",
@@
 (p_results_items <- ggplot(d_results_items, aes(x = beta, y = lhs)) +
-  geom_vline(xintercept = 0) +
+  geom_vline(xintercept = 0, color = "darkgrey") +
   geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +

### 2019-02-26 manuscript/manuscript.RmD
Major updates on everything. Specifically, this includes updates on data, including MMs latest feedback, and getting things ready for submission.

@@
 
-abstract          : "This study analyzes how personality traits relate to need for privacy.
+abstract          : 'This study analyzes how personality traits relate to need for privacy.
 We focus on three dimensions: (a) need for privacy from government surveillance, (b) need for privacy from other individuals, and (c) need for anonymity.
-Using an online questionnaire with 271 student respondents, several significant relationships were found.
+Using an online questionnaire with 273 student respondents, several significant relationships were found.
 For example, results showed that less sociable people desired considerably more privacy on all three dimensions.
-Somewhat more controversially, people who reported less integrity also desired noticeably more anonymity.
+Somewhat more controversially, people who reported less integrity also desired more anonymity.
 While anxious people desired slightly less privacy from government surveillance, risk avoidant people desired considerably more privacy from other people.
@@
 Together, the results have several implications.
-For example, they shed some light on the nothing-to-hide argument: A person who desires more anonymity might indeed be of less integrity.
-However, it is equally plausible that this person is just a little less sociable."
+For example, they shed light on the "nothing-to-hide argument": A person who desires more anonymity might indeed be of less integrity.
+The most important predictor of need for privacy, however, was sociability.
+In conclusion, this study is the first to show that if a person desires more privacy, it is most plausible that he or she is less sociable.'
 keywords          : "Privacy, need for privacy, personality, anonymity, integrity, SEM"
@@
 output            : papaja::apa6_pdf
-# output            : papaja::apa6_word
+\ output            : papaja::apa6_word
 header-includes:
@@
 ```{r setup, include = FALSE}
-# devtools::install_git("https://github.com/tdienlin/td")
-packages <- c("devtools", "english", "ggplot2", "kableExtra", "lavaan", "magrittr", 
-              "papaja", "semPlot", "td", "tidyverse")
+devtools::install_github("tdienlin/td@v.0.0.2.5")
+packages <- c("devtools", "english", "ggplot2", "kableExtra", "lavaan", 
+              "magrittr", "papaja", "semPlot", "td", "tidyverse")
 lapply(packages, library, character.only = TRUE)
@@
 
-In light of the increasing digitization of everyday life, which has led to several sweeping societal changes such as the commodification and monetization of personal information [@Sevignani.2016], privacy has become a major topic of interest.
+In light of the increasing digitization of everyday life, which has led to several sweeping societal changes such as the commodification and monetization of personal information [@Sevignani.2016], privacy has become a major topic of societal interest.
 Despite its importance, however, we still know surprisingly little about the relation between privacy and personality [e.g., @Masur.2018, p.
 155].
-Why do some people need more privacy than others, and how do these people differ from one another?
-We think that a better understanding of the relation between personality and privacy is crucial: Several theories argue that personality determines privacy behaviors [e.g., @Masur.2018], however, to date there is almost no empirical research that can be used to deduct well-informed hypotheses.
-As a result, the main question of this paper is as follows: What are personality facets that can be used to best explain peoples' need for privacy?
+Why do some people feel they need or desire more privacy than others do, and how do these people differ from one another?
+We think that a better understanding of the relation between personality and privacy is crucial: Several theories argue that personality determines privacy behaviors [e.g., @Masur.2018], however, to date there is almost no empirical research that can be used to deduce well-informed hypotheses.
+As a result, the main question of this paper is: What are personality facets that can be used to best explain peoples' felt need for privacy?
 
@@
 For example, in a theory-driven treatise @Burgoon.1982 argued that privacy has four dimensions: informational, social, psychological, and physical privacy.
-@Pedersen.1979, by contrast, did an empirical factor analysis (initially starting with 94 items) and suggested that privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity.
+@Pedersen.1979, by contrast, argues that on the basis of an empirical factor analysis (initially starting with 94 items) privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity.
 In addition, @Schwartz.1968 differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies).
-Finally, one can also distinguish between the objective privacy context, the subjective privacy perception, the psychological need for privacy (which is both a situational and dispositional need), and the resulting privacy behavior (often represented by self-disclosure) [@Dienlin.2014].
+The need for privacy, then, captures "[a]n individual’s need to selectively control the
+access of others to the individual = self with the aim of achieving a desired level of physical or psychological privacy [...]") [@Trepte.2017d, p.
+1].
+Finally, one can also distinguish between the objective privacy context (e.g., how many users can actually read a post on an SNS?), subjective privacy perceptions (e.g., how many users people _think_ can read a post on an SNS?), and resulting privacy behaviors (e.g., how much do people self-disclose?) [@Dienlin.2014].
 
-For the purpose of this study, we combine the aforementioned notions and focus on (a) vertical privacy with regard to the need for withdrawal from government surveillance, (b) horizontal privacy in terms of the need for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by the general need for anonymity.
+For the purpose of this study, we combine the aforementioned notions and focus on (a) vertical privacy with regard to people's felt need for withdrawal from government surveillance, (b) horizontal privacy in terms of the perceived need for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by people's general felt need for anonymity.
 
-In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually need privacy.
-@Westin.1967 defined four primary positive purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
-Not least, privacy facilitates self-disclosure [@Dienlin.2014], which is vital for attaining social support, initiating relationships, and getting close to one another [@Omarzu.2000].
+In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually feel they need privacy.
+According to @Trepte.2017d, the need for privacy is a secondary need---it is not an end in itself, but rather a way to satisfy other more fundamental needs.
+Specifically, @Westin.1967 defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
+Not least, privacy facilitates self-disclosure [@Dienlin.2014], which is vital for attaining social support, initiating relationships, and getting close to other people [@Omarzu.2000].
 
-On the other hand, however, too much privacy can also be problematic.
+On the other hand, however, there are negative aspects of privacy too.
+For example, too much privacy can be problematic.
 Because human beings are inherently social, being overly cut-off from others can impede flourishing, nurture deviant behavior, or introduce power asymmetries [@Altman.1975].
-"[T]he feminist critique rightfully argued that for men, the private sphere can be a shielded sphere in which female suppression is not sanctioned." [@DeCew.1997, p.
-81, as cited by Masur, 2018, p.
-38].
-Next, and as mentioned above, privacy fosters self-disclosure.
-However, any self-disclosure is also always a potential risk because others might disagree, disapprove, or misuse the information in other contexts [@Petronio.2010].
+Also, and as mentioned above, privacy fosters self-disclosure, which presents a potential risk because others might disagree, disapprove, or misuse the information in other contexts [@Petronio.2010].
+The dialectical tension between the positive and negative aspects of privacy likely causes variability across individuals in their need for privacy.
+This study asks: What role does personality play in determining individual-level variations in need for privacy?
 
@@
 In what follows we now explore several personality aspects that we think might predict the need for privacy.
-As there is no established theory that dovetails privacy and personality, it is difficult to deduct precise and well-informed hypotheses.
-The rationales that we outline below should hence considered to be tentative suggestions.
-Also, please note that we elaborate only on those dimensions of need for privacy for which plausible rationales could be found.
+As there is no established theory that dovetails privacy and personality, it is difficult to deduce precise and well-informed hypotheses.
+The rationales that we outline below should hence be considered tentative suggestions toward a theory of personality and privacy.
+Also, please note that we elaborate only on those dimensions of need for privacy for which plausible rationales could be formed.
 
-The general underlying theoretical framework that guided our selection process was the big five approach [e.g.,@John.1999].
-Note that privacy concerns, a variable conceptually close to need for privacy, shows only negligible relations with the big five factors [@Bansal.2010; @Junglas.2008].
+The general underlying theoretical framework that guided our selection process was the Big Five approach [e.g., @John.1999].
+Note that privacy concerns, a variable that is conceptually close to need for privacy, shows only negligible relations with the Big Five factors [@Bansal.2010; @Junglas.2008].
 In order to be more precise, we hence follow the advice by @Paunonen.2001 and refer to specific personality facets instead of generic personality factors.
-To illustrate, instead of dwelling on the general factor of _extraversion_, we instead focused on the facet _gregariousness_, which we consider to be more pertinent.
+To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.
 
-Our reasoning was guided by another central theoretical thought.
-As implied above, privacy can be either positive or negative.
+Our reasoning further was guided by another central theoretical tenet.
+As suggested above, privacy can be either positive or negative.
 Similarly, other people, the government, and anonymity can be considered either a _resource_ or a _threat_.
@@
 
-First, we argue that need for privacy should be closely related to a person's sociability or gregariousness [which is a subdimension of extraversion, @John.1999].
+First, we argue that need for privacy should be closely related to a person's sociability or gregariousness [which is a subdimension of extraversion, @Costa.1992b].
 Sociability captures whether people prefer to spend their time alone or with company.
@@
 
-This rationale is supported by several empirical studies: Extroverted people desire less privacy [@Morton.2013], people who describe themselves as introverted thinkers are more likely to prefer social isolation [@Pedersen.1982], and introverted people are more likely to report invasions of privacy [@Stone.1986].
+This rationale is supported by several empirical studies: People who score higher on the personality meta-factor _plasticity_, which is a composite of the two personality factors extraversion and openness, have been shown to desire less privacy [@Morton.2013]; people who describe themselves as introverted thinkers are more likely to prefer social isolation [@Pedersen.1982]; and introverted people are more likely to report invasions of privacy [@Stone.1986].
 
@@
 
-More controversially, it has been argued that people need privacy because they have something to hide.
+More controversially, it has been argued by some that people need privacy because they have something to hide.
 The so-called nothing-to-hide argument states that “If you have nothing to hide, you have nothing to fear.” As described by Solove, the nothing-to-hide argument says that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens.
@@
 753].
-Hence, another potential predictor of why people need privacy could also be a so-called "lack of integrity".
+Hence, another potential predictor of why people need privacy could also be a so-called "lack" of integrity.
 
@@
 82].
-In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow @Paunonen.2002 and adopt a lowest common denominator approach, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.
+In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow @Paunonen.2002 and adopt a lowest common denominator definition, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.
 
-It is indeed possible to think of theoretical arguments for why lack of integrity might correlate positively with need for privacy.
-People who have actually committed crimes evidently face even greater risk from self-disclosure compared to others, because government agencies and people sould surely disapprove of their activities [@Petronio.2010].
-Hence, the government and other people are more likely to be a threat, which should render anonymity rather a resource.
+It is possible to think of theoretical arguments for why lack of integrity might correlate positively with a person's felt need for privacy.
+People who actually commit crimes may face even greater risk from self-disclosure compared to others, because government agencies and people would surely disapprove of their activities [@Petronio.2010].
+Hence, the government and other people are more likely to be perceived as a threat, which should render anonymity  a resource.
 As a consequence, people with lower integrity might desire more privacy as a means to mitigate their felt risk [@Altman.1976].
@@
 Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more integrity (i.e., fewer cheating behaviors).
-Next, in a longitudinal sample with 457 respondents in Germany [@Trepte.2013a], people who felt they needed more privacy were also less authentic on their SNSs profiles (_r_ = -.48) and less authentic in their personal relationships (_r_ = -.28).
-Given the argument that authenticity is a subset of integrity [@Sheldon.2004], one could hence reason that also the concept of integrity might relate to a person’s need for privacy.
+Next, in a longitudinal sample with 457 respondents in Germany [@Trepte.2013a], people who felt they needed more privacy were also less authentic on their online social network profiles (_r_ = -.48) and less authentic in their personal relationships (_r_ = -.28).
+Given the argument that authenticity is a subset of integrity [@Sheldon.2004], one could hence also reason that the concept of integrity might relate to a person’s perceived need for privacy.
 Somewhat related, it has been found that people who are more agreeable are also moderately less concerned about their privacy [@Junglas.2008].
 Finally, @Pedersen.1982 showed that three dimensions of need for privacy relate to self-esteem: Respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21), and preferred solitude (_r_ = .24).
-While self-esteem and integrity are distinct concepts, Pedersen’s specific operationalization of self-esteem integrated several aspects of integrity by using items such as “moral, nice, fair, unselfish, good, honest, reputable, sane”.
+While self-esteem and integrity are distinct concepts, Pedersen’s specific operationalization of self-esteem integrated several aspects of integrity by using items such as moral, nice, fair, unselfish, good, honest, and reputable (p.
+12).
 
-In conclusion, we could imagine that lack of integrity may indeed relate to an increased need for privacy from government surveillance, as governments have the legitimate power to prosecute illegal activities.
-Next, it seems plausible that lack of integrity relates to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers.
+In conclusion, we could imagine that lack of integrity may indeed relate to an increased felt need for privacy from government surveillance, as governments have the legitimate power to prosecute illegal activities.
+Next, it seems plausible that lack of integrity may relate to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers.
 Finally, lack of integrity may also relate to an increased need for privacy from other people, as most other people will disapprove of immoral or illegal activities, and could even reveal those activities to authorities.
@@
 
-Next, it seems possible that the need for privacy is also related to people's level of general anxiety [which is a subdimension of neuroticism, @John.1999].
+Next, it seems possible that the need for privacy is also related to people's level of general anxiety [which is a subdimension of neuroticism, @Costa.1992b].
 General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened.
@@
 Concerning the need for privacy from government surveillance, we could imagine that people who are more anxious desire less privacy.
-Despite the fact that only 18% of all US-Americans trust their government "to do what is right" [@PewResearchCenter.2017], almost everyone agrees that "it's the government's job to keep the country safe", with most people also being satisfied with the government's job [@PewResearchCenter.2015c].
-Hence, when being anxious, the government should rather be seen as a resource than a threat.
-It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that these programs promise to prevent crime or to reduce the likelihood of terrorist attacks [@Greenwald.2013], implying that people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.
+Despite the fact that only 18% of all Americans trust their government "to do what is right" [@PewResearchCenter.2017], almost everyone agrees that "it's the government's job to keep the country safe," with most people also being satisfied with the government's job [@PewResearchCenter.2015c].
+Hence, for anxious individuals, the government might be seen as a resource rather than a threat.
+It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that such surveillance promises to prevent crime or to reduce the likelihood of terrorist attacks [@Greenwald.2013], implying that people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.
 
-### Risk aversion
+### Risk avoidance
 
-Similarly, it could be that need for privacy is related to the general tendency to avoid risks, to deliberate, and to plan carefully [deliberation is a subdimension of conscientiousness, @John.1999].
+Similarly, it could be that an individual's felt need for privacy is related to a general tendency to avoid risks, to deliberate, and to plan carefully [deliberation is a subdimension of conscientiousness, @Costa.1992b].
 Risk avoidance captures the degree to which people prefer to abstain from taking risks.
@@
 Moreover, research suggests that conscientious people are slightly more concerned about their privacy [@Junglas.2008].
-But again, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, in order for the government to be able to avert potential threats.
+But as above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, in order for the government to be able to avert potential threats.
+In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study.
 
@@
 
-Next, it seems plausible that need for privacy is also related to traditionality [which is a subdimension of openness to experience, @John.1999].
+Next, it seems plausible that need for privacy is also related to traditionality [which is a subdimension of openness to experience, @Costa.1992b].
 Traditionalism measures whether people prefer to stick with their usual routines.
-The computers and the Internet have rendered the world increasingly knowable: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.
+Computers and the Internet have rendered the world increasingly knowable: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.
 Given that digital information is persistent, searchable, reproducible, and scalable [@boyd.2008c], this allows for unprecedented means and degrees of surveillance.
@@
 Empirical research does find that older people, who are generally less open and more traditional [@Donnellan.2008], are more concerned about their privacy [@Fife.2012].
-On the other hand, @Junglas.2008 report that openness to experience is positively related to privacy concern, which would argue in favor of the exact opposite.
-Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three aforementioned contexts.
+On the other hand, @Junglas.2008 report that openness to experience is positively related to privacy concern, which would argue in favor of the exact opposite pattern of results.
+Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three contexts measured in this study.
 
@@
 Finally, it has often been shown that socio-demographic variables such as sex, age, and affluence can relate to the need for privacy [@Park.2015; @Tifferet.2019; @Weinberger.2017b; @Trepte.2013a].
-Although these variables do not specifically address our research question at hand they will be included---not least as their omission could lead to spurious results or an inflation of false positives.
+Although these variables do not specifically address our research question at hand they will be included as control variables---not least as their omission could lead to spurious results or an inflation of false positives.
 
@@
 First, we tested the factorial validity of the variables we collected.
-In a first step, we ran confirmatory factor analyses (CFAs) to determine whether the variables were uni-dimensional.
+In a first step, we ran confirmatory factor analyses (CFAs) to determine whether the variables were unidimensional.
 If fit was not adequate, we then ran exploratory factor analyses (EFAs) to assess the actual underlying factor structure.
-If more than one factor was revealed, we tried to find a bifactor model solution.[^1] This way we were able to attain a general measure of the predictors, instead of needing to further complicate our analyses by including subdimensions of the predictors.[^2] If no adequate bifactor model could be found, we proceeded by deleting items with low loadings on the general factor and/or the specific factors.
-If also after deletion of individual items no bifactor solution emerged, using a subset of the items we then aimed to extract a single factor with sufficient factorial validity.
+EFAs were run using maximum likelihood estimation and oblimin rotation [@Osborne.2004b, p.
+7].
+If more than one dimension was revealed, we tried to find a bifactor model solution.[^1] This way we were able to attain a general measure of the predictors, instead of needing to further complicate our analyses by including subdimensions of the predictors.[^2] If no adequate bifactor model could be found, we proceeded by deleting items with low loadings on the general factor and/or the specific factors.
+If also after deletion of individual items no bifactor solution emerged, we then aimed to extract a single factor with sufficient factorial validity using a subset of the items.
 
@@
 To get high-quality single indicators of the predictors, we computed the average of the model predicted values / latent factor scores, which we extracted from the CFAs.
-If the CFAs showed a single-factor solution, we used the model predicted values for this latent factor; if the CFAs produced a bifactor solution, we used the model predicted values for the general latent factor.
-As main variable of interest, the outcome need for privacy was measured as a three-dimensional latent factor consisting of overall 12 items (see below).
+If the CFAs showed a unidimensional solution, we used the model predicted values for this latent factor; if the CFAs produced a multidimensional solution, we used the model predicted values for the general latent factor (again, by using this procedure we were able to attain a general measure of the predictors, instead of needing to further complicate analyses by including subdimensions of the predictors.) As the main variable of interest, the outcome need for privacy was measured as a three-dimensional latent factor consisting of overall 12 items (see below).
 
-Finally, combining the information of several items into a latent factors helps to reduce and combine information.
+Finally, combining several items into a latent factors helps to reduce and condense information.
 At the same time, however, this approach also introduces several researcher degrees of freedom.
@@
 
-`r cite_r("../bibliography/r-references.bib", withhold = FALSE, pkgs = c("GGally", "ggplot2", "knitr", "lavaan", "mice", "MVN", "papaja", "PerFit", "psych", "pwr", "semTools", "tidyverse"))` was used for the analyses.
+`r cite_r("../bibliography/r-references.bib", withhold = FALSE, pkgs = c("GGally", "ggplot2", "knitr", "lavaan", "mice", "MVN", "papaja", "PerFit", "psych", "pwr", "semTools", "tidyverse"))` were used for the analyses.
 
@@
 As the main variable of interest, we collected several items to measure need for privacy.
-First, we collected four items capturing the need for informational privacy using the scale developed by @Trepte.2017d.
+First, we collected four items capturing the general need for privacy using the subscale _information_ developed by @Trepte.2017d.
 Second, we measured need for privacy on a societal level using nine self-designed items.
@@
 EFAs and CFAs revealed a well-fitting model with 12 items (one double-loading), which consisted of the three dimensions (a) need for privacy from the government, (b) need for privacy from other people, and (c) need for anonymity.
-For a list of all items, see Table \@ref(tab:need-for-privacy-items).
+For a list of all items, see Table \@ref(tab:privacyitems).
 
-```{r need-for-privacy-items}
+```{r privacyitems}
 d_t_items <- rbind(
@@
   kable_styling(latex_options="scale_down") %>% 
-  group_rows("Privacy need government", 1, 5) %>%
-  group_rows("Privacy need interpersonal", 6, 9) %>%
-  group_rows("Privacy need anonymity", 10, 13)
+  kableExtra::group_rows("Privacy need government", 1, 5) %>%
+  kableExtra::group_rows("Privacy need interpersonal", 6, 9) %>%
+  kableExtra::group_rows("Privacy need anonymity", 10, 13)
 ```
@@
 
-Sociability was measured with the extraversion subscale _gregariousness_ [@John.1999], which consists of eight items.
+Sociability was measured with the Extraversion subscale Gregariousness [@Costa.1992b], which consists of eight items.
 An example item is “I shy away from crowds of people.” Analyses revealed that a bifactor model based on a subset of six items showed good fit to the data.
@@
 
-In order to measure integrity, we used the subscale _integrity_ of the Supernumerary Personality Inventory [@Paunonen.2002], which consists of eight items.
+To measure integrity, we used the subscale Integrity of the Supernumerary Personality Inventory [@Paunonen.2002], which consists of eight items.
 In addition, we designed another three items.
@@
 
-Anxiety was measured with the neuroticism subscale _anxiety_ [@John.1999], which consists of eight items.
+Anxiety was measured with the Neuroticism subscale Worry [@Costa.1992b], which consists of eight items.
 An example item is “I am easily frightened.” Analyses revealed that a bifactor model using all eight items showed good fit to the data.
@@
 
-Risk avoidance was measured with the conscientiousness subscale _deliberation_ [@John.1999], which consists of eight items.
+Risk avoidance was measured with the Conscientiousness subscale Deliberation [@Costa.1992b], which consists of eight items.
 An example item is “I plan ahead carefully when I go on a trip.” Analyses revealed that a bifactor model using all eight items showed good fit to the data.
@@
 
-Traditionalism was measured with the (inverted) openness to experiences subscale _actions_ [@John.1999], which consists of eight items.
+Traditionalism was measured with the (inverted) Openness to Experiences subscale Actions [@Costa.1992b], which consists of eight items.
 An example item is “I’m pretty set in my ways.” Analyses revealed that a model with a single factor based on a subset of five items showed good fit to the data.
@@
 For an overview of the results of the bivariate relations, see Figure \@ref(fig:bivar-fig).
-For the statistical results of the SEM, see Table \@ref(tab:sem-tab), and for a graphical visualization, Figure \@ref(fig:sem-fig).
+For the statistical results of the SEM, see Table \@ref(tab:sem-tab), and for a graphical visualization, see Figure \@ref(fig:sem-fig).
 Note that the final structural regression model that was estimated fit the data comparatively well, `r fit_txt(results_threefactors_fit, scaled = TRUE)`.
+Although fit was not perfect, we decided against further modifications of the model in order to avoid overfitting.
 
@@
 Solid regression lines represent linear regressions, dashed regression lines represent quadratic regressions.
-Calculated with the variables’ latent factor scores.", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
+Calculated with the variables’ latent factor scores.", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!ht", warning=F}
 suppressWarnings(print(p_bivar))
@@
 ```{r sem-fig, fig.cap="Graphical overview of the results of Structural Equation Model.
-Shows the 95% confidence intervals of standardized coefficients.
-Dashed lines indicate the SESOI of |.10|.", fig.height=2.5}
+Shows the 95% confidence intervals (CIs) of standardized coefficients.
+(Standard errors were extracted from Lavaan's standardized solution.
+For the results of a bootstrap approach with 2,000 draws, see OSM.) Dashed lines indicate the SESOI of |.10|.", fig.height=2.5}
 plot(p_results_threefactors)
@@
 Summarizing across the results, the predictors explained `r inspect(results_threefactors_fit, 'r2')["pri_nee_gov"] * 100 %>% round(0)`% of the variance in need for privacy from the government, `r inspect(results_threefactors_fit, 'r2')["pri_nee_int"] * 100 %>% round(0)`% of the variance in need for privacy from other people, and `r inspect(results_threefactors_fit, 'r2')["pri_nee_ano"] * 100 %>% round(0)`% of the variance in need for anonymity.
+All predictors were also above our predefined SESOI of |$\upbeta$| = .10, supporting their theoretical relevance.
+In addition, note that several nonsignificant effects were actually larger than the predefined SESOI (e.g., the potential effect of risk avoidance on the need for privacy from the government).
+Hence, it seems plausible that a larger study, which yields smaller standard errors, would find additional effects.
+
+As stated above, because all predictors were included on the basis of specific a priori rationales we did not control for alpha error inflation.
+To better assess whether the results could also be explained by chance alone, let us briefly reconsider that if the null hypotheses had been true, given the predefined alpha level of 5 % and the `r nrow(t_results_threefactors) %>% as.english()` statistical tests that were run, one would have expected to find `r round(nrow(t_results_threefactors) * .05, 2)` statistically significant results by chance alone.
+In this study we found `r round(nrow(filter(coeffs_tab(results_threefactors_fit), p < .05)), 0) %>% english()` statistically significant results, which is substantially higher.
+Similarly, the average _p_-value _p_ = `r coeffs_tab(results_threefactors_fit)$p %>% mean %>% my_round("std")` was substantially smaller than the average _p_-value of _p_ = .50 that one would have expected to find if the null hypotheses had been true.
 
@@
 First, the results of the bivariate analyses showed that the need for privacy can be predicted surprisingly well by means of specific personality facets.
-Second, also when analyzed together in a structural regression model alongside additional socio-demographic variables, most personality variables remained significant, supporting the robustness of the relations.
+Second, also when analyzed together in a structural regression model alongside additional socio-demographic variables, most of these personality facets remained significant, supporting the robustness of the relations.
 
@@
 This finding hence supports the logic behind the “nothing to hide” argument.
-It also follows Altman’s privacy regulation theory (1976), which states that if exposure of information is risky it is likely that people will use more mechanisms to strengthen their social boundaries and increase their desired level of privacy.	Importantly, however, integrity was not related to need for privacy from other people or to need for privacy from government surveillance, which hence limits the generalisability of the nothing-to-hide argument.
-In addition, note that the items measuring need for anonymity were very difficult (the mean was much lower compared to the other dimensions; see Table \@ref(tab:psychometrics))---hence, the relationship between integrity and need for privacy might show only in very specific domains, for example, when it comes to avoiding places with video surveillance.
+It also follows Altman’s privacy regulation theory [-@Altman.1976], which states that if exposure of information is risky it is likely that people will use more mechanisms to strengthen their social boundaries and increase their desired level of privacy.	Importantly, however, integrity was not related to need for privacy from other people or to need for privacy from government surveillance, which hence limits the generalisability of the nothing-to-hide argument.
+In addition, note that the responses to the items measuring need for anonymity were much lower compared to the other two dimensions of need for privacy (i.e., _M_~anonymity~ = `r t_psyc["Anonymity", "m"]`, _M_~government~ = `r t_psyc["Government", "m"]`, _M_~interpersonal~ = `r t_psyc["Interpersonal", "m"]`).
+Hence, the relationship between integrity and need for privacy might show only in very specific domains, for example, when it comes to avoiding places with video surveillance.
 In conclusion, the relation between integrity and need for privacy seems to be limited to certain aspects of need for privacy only.
-It should hence not be overly generalized.
+It should thus not be overly generalized.
 
 Interestingly, the data showed that people who were more anxious were also more willing to accept government surveillance.
-This might be explained by the fact that governments are explicitly commissioned to help prevent crime or terrorist attacks, which are things more anxious people are more likely to dread.
+This might be explained by the fact that governments are explicitly commissioned to help prevent crime or terrorist attacks, which are things that more anxious people are more likely to fear.
 
 People who were more risk averse desired more privacy from other people.
-Specifically, people who try to avoid risks are less inclined to share secrets with friends.
-This finding makes sense and can be aligned with prospect theory [@Kahneman.1979]: The risks of a secret being publicly disclosed seem to outweigh the potential benefits of sharing it with confidants.
+Specifically, people the data show that who try to avoid risks are less inclined to share secrets with friends.
+This finding makes sense and can be aligned with prospect theory [@Kahneman.1979]: The risks of a secret being publicly disclosed seem to outweigh the potential benefits of sharing it with confidants among risk-averse people.
 
 Finally, in the SEM no significant relations between need for privacy and traditionality were found.
-The results imply that independent from being more open to change or not, people desire the same level of privacy.
-Taken further, this finding might illustrate that a modern way of living does not necessarily imply a reduced need for privacy.
+The results imply that independent from being more or less open to change, people desire the same level of privacy.
+Taken further, this finding might illustrate that people who are more open to change, who are more likely to use novel devices, media, and services, or who might consider themselves as early adopters, do not automatically need less privacy.
 
 At a larger level, the results of this study highlight the importance of making differentiated claims on why people need privacy.
-Indeed, while the results suggest that some people might need anonymity because they may have something to hide, they also show that putting everyone who exhibits an increased need for privacy under suspicion is outright wrong.
-People who are less sociable, more risk averse, and less anxious are also more likely to need a bit more privacy.
+Indeed, while the results suggest that some people might need anonymity because they may have something to hide, they also show that putting everyone who exhibits an increased need for privacy under suspicion is wrong.
+People who are less sociable, more risk averse, and less anxious are also more likely to feel they need more privacy.
 This implies that various personality-related aspects can predict need for privacy in different ways and for different reasons.
@@
 On the one hand, integrity implies absolute criteria in relation to social norms: Stealing is bad and forbidden, whereas helping is good and encouraged.
-On the other hand, integrity implies relative criteria: Whereas some cultures disapprove of lying whatever the context, others consider lying okay (for example, “white lies” in order to avoid hurting someone’s feelings) [@Altman.1977].
+On the other hand, integrity implies relative criteria: Whereas some cultures disapprove of lying whatever the context, others consider lying okay in some situations (for example, “white lies” in order to avoid hurting someone’s feelings) [@Altman.1977].
 Thus, ranking behaviors, opinions, and character traits with regard to integrity presents a moral dilemma.
-As a result, throughout our study we have employed a conservative approach and understood and measured integrity as an explicit transgression of social norms that is strong and that most societies would arguably agree upon (for example, most societies would consider stealing as a sign of low integrity).
+As a result, throughout our study we have employed a conservative approach to understand and measure integrity as an explicit transgression of social norms that is strong and that most societies would arguably agree upon (for example, most societies would consider law-breaking as a sign of low integrity).
 Nonetheless, we recommend that future research should further elaborate on the general understanding of integrity as a theoretical concept.
@@
 In a meta-analysis with 665 correlation coefficients, self-reported integrity tests were associated with counterproductive behaviors with an average correlation coefficient of _r_ = .47 [@Ones.1993].
-Nonetheless, future research would evidently benefit from including behavioral manifestations of integrity, such as concrete cheating behaviors.
+Nonetheless, future research would benefit from including behavioral manifestations of integrity, such as concrete cheating behaviors.
 
-In what follows, we present some methodological points of criticism.
-Despite the fact that we used mostly well-established scales, confirmatory factor analyses showed that some of the original items had to be deleted to achieve adequate factorial validity.
-This resembles the finding by @Hussey.2018, who reported that several widely-used scales in psychological research actually do not show satisfactory factorial validity.
-By using bifactor models, however, it was possible to at least partially alleviate the problem.
-Next, in order to achieve sufficient factorial validity we needed to adapt the scales (for example by deleting items), which introduces problems of overfitting, which in turn potentially impedes the generalisability of the results [see, e.g., @Yarkoni.2017].
-However, by using bifactor models we explicitly tried to retain the largest possible number of items, which should render our results more robust.
-In addition, also when looking at the items individually (see OSM) one can see that the results are not overly dependent on inclusion of specific items.
+Another limitation of the study is that despite using mostly well-established scales, confirmatory factor analyses revealed that most measures did not show satisfactory factorial validity, which resembles the current finding and criticism by @Hussey.2018.
+In order to achieve sufficient factorial validity we therefore needed to adapt the scales (for example by deleting items).
+However, this introduces problems of overfitting, which in turn potentially impedes the generalisability of the results [see, e.g., @Yarkoni.2017].
+By using bifactor models we explicitly tried to retain the largest possible number of items, which should render our results more robust.
+In addition, also when looking at the items individually (see the OSM) one can see that the results are not overly dependent on inclusion of specific items.
+
 Another methodological improvement for future studies concerns the sample, which was comparatively small, leading to a reduced power to detect also small effects.
-Nonetheless, we are still confident that the results should be reliable, because we deliberately selected specific predictors that should exhibit at lest small to moderate relations with need for privacy (i.e., _r_ = .20).
+Nonetheless, we are still confident that the results should be reliable because we deliberately selected specific predictors that should exhibit at least small to moderate relations with need for privacy (i.e., _r_ = .20).
 For small to moderate relations, the current study still had a convincing power of `r power_smallmoderate`%.
-Granted, when aiming to find also small effects (i.e., _r_ = .10) with a probability of 95%, future studies would need to collect the answers of `r sample_95` respondents [@Cohen.1992].
-Finally, generalisability is limited, as our sample was predominantly young, female, highly educated, and collected only in one single country.
+Granted, when aiming to find also small effects (i.e., _r_ = .10) with a probability of 95%, future studies would need to collect data from `r sample_95` respondents [@Cohen.1992].
+Finally, generalisability of our sample is limited, as it was predominantly young, female, highly educated, and collected only in one country.
 
-Next, future research might consider analyzing predictors of privacy needs that are even more specified.
-For example, it is possible that people who hold dissenting political beliefs could also have a higher need for privacy from the government.
+Finally, future research might consider analyzing predictors of privacy needs that are even more specified.
+For example, it is possible that people who hold dissenting political beliefs could also perceive a higher need for privacy from the government.
 In this study we focused mostly on escapist motives for why people desire privacy (e.g., sociability, risk aversion).
@@
 
-In his novel _The Circle_, @Eggers.2013 describes a dystopian society in which people are gradually forfeiting their privacy.
-One after another becomes "transparent": Carrying a small camera around the neck, people begin to broadcast their daily lives to the Internet.
-In the novel, this eventually causes a societal upheaval: "The pressure on those who hadn't gone transparent went from polite to oppressive.
-The question, from pundits and constituents, was obvious and loud: If you aren't transparent, what are you hiding?" [@Eggers.2013, p.
-129].
-
-The results of this study suggest that there might be some truth to the nothing-to-hide argument.
-However, the applicability seems to be limited to (very specific) aspects of anonymity (e.g., avoiding places with video surveillance or leaving one's ID at home).
-In general, the need for privacy seems to be related more closely to other aspects of personality.
+Privacy is getting more impinged on these days with digital surveillance and intense social pressure toward self-disclosure via social networks, which have both negative and positive aspects at the same time.
+In this context it is understandable why people might vary in their felt need for privacy.
+Our study sheds light on what drives that variation, finding that sociability, and to a lesser extent, anxiety, risk aversion, and integrity all contribute to individuals’ need for privacy, albeit in different ways.
 

### 2019-02-26 manuscript/manuscript.tex
Major updates on everything. Specifically, this includes updates on data, including MMs latest feedback, and getting things ready for submission.

@@
 We focus on three dimensions: (a) need for privacy from government surveillance, (b) need for privacy from other individuals, and (c) need for anonymity.
-Using an online questionnaire with 271 student respondents, several significant relationships were found.
+Using an online questionnaire with 273 student respondents, several significant relationships were found.
 For example, results showed that less sociable people desired considerably more privacy on all three dimensions.
-Somewhat more controversially, people who reported less integrity also desired noticeably more anonymity.
+Somewhat more controversially, people who reported less integrity also desired more anonymity.
 While anxious people desired slightly less privacy from government surveillance, risk avoidant people desired considerably more privacy from other people.
@@
 Together, the results have several implications.
-For example, they shed some light on the nothing-to-hide argument: A person who desires more anonymity might indeed be of less integrity.
-However, it is equally plausible that this person is just a little less sociable.
+For example, they shed light on the ``nothing-to-hide argument'': A person who desires more anonymity might indeed be of less integrity.
+The most important predictor of need for privacy, however, was sociability.
+In conclusion, this study is the first to show that if a person desires more privacy, it is most plausible that he or she is less sociable.
 
@@
 
-In light of the increasing digitization of everyday life, which has led to several sweeping societal changes such as the commodification and monetization of personal information (Sevignani, 2016), privacy has become a major topic of interest.
+In light of the increasing digitization of everyday life, which has led to several sweeping societal changes such as the commodification and monetization of personal information (Sevignani, 2016), privacy has become a major topic of societal interest.
 Despite its importance, however, we still know surprisingly little about the relation between privacy and personality (e.g., Masur, 2018, p.
 155).
-Why do some people need more privacy than others, and how do these people differ from one another?
-We think that a better understanding of the relation between personality and privacy is crucial: Several theories argue that personality determines privacy behaviors (e.g., Masur, 2018), however, to date there is almost no empirical research that can be used to deduct well-informed hypotheses.
-As a result, the main question of this paper is as follows: What are personality facets that can be used to best explain peoples' need for privacy?
+Why do some people feel they need or desire more privacy than others do, and how do these people differ from one another?
+We think that a better understanding of the relation between personality and privacy is crucial: Several theories argue that personality determines privacy behaviors (e.g., Masur, 2018), however, to date there is almost no empirical research that can be used to deduce well-informed hypotheses.
+As a result, the main question of this paper is: What are personality facets that can be used to best explain peoples' felt need for privacy?
 
@@
 For example, in a theory-driven treatise Burgoon (1982) argued that privacy has four dimensions: informational, social, psychological, and physical privacy.
-Pedersen (1979), by contrast, did an empirical factor analysis (initially starting with 94 items) and suggested that privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity.
+Pedersen (1979), by contrast, argues that on the basis of an empirical factor analysis (initially starting with 94 items) privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity.
 In addition, Schwartz (1968) differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies).
-Finally, one can also distinguish between the objective privacy context, the subjective privacy perception, the psychological need for privacy (which is both a situational and dispositional need), and the resulting privacy behavior (often represented by self-disclosure) (Dienlin, 2014).
-
-For the purpose of this study, we combine the aforementioned notions and focus on (a) vertical privacy with regard to the need for withdrawal from government surveillance, (b) horizontal privacy in terms of the need for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by the general need for anonymity.
-
-In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually need privacy.
-Westin (1967) defined four primary positive purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
-Not least, privacy facilitates self-disclosure (Dienlin, 2014), which is vital for attaining social support, initiating relationships, and getting close to one another (Omarzu, 2000).
-
-On the other hand, however, too much privacy can also be problematic.
+The need for privacy, then, captures \enquote{{[}a{]}n individual's need to selectively control the
+access of others to the individual = self with the aim of achieving a desired level of physical or psychological privacy {[}\ldots{}{]}}) (Trepte \& Masur, 2017, p.
+1).
+Finally, one can also distinguish between the objective privacy context (e.g., how many users can actually read a post on an SNS?), subjective privacy perceptions (e.g., how many users people \emph{think} can read a post on an SNS?), and resulting privacy behaviors (e.g., how much do people self-disclose?) (Dienlin, 2014).
+
+For the purpose of this study, we combine the aforementioned notions and focus on (a) vertical privacy with regard to people's felt need for withdrawal from government surveillance, (b) horizontal privacy in terms of the perceived need for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by people's general felt need for anonymity.
+
+In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually feel they need privacy.
+According to Trepte and Masur (2017), the need for privacy is a secondary need---it is not an end in itself, but rather a way to satisfy other more fundamental needs.
+Specifically, Westin (1967) defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
+Not least, privacy facilitates self-disclosure (Dienlin, 2014), which is vital for attaining social support, initiating relationships, and getting close to other people (Omarzu, 2000).
+
+On the other hand, however, there are negative aspects of privacy too.
+For example, too much privacy can be problematic.
 Because human beings are inherently social, being overly cut-off from others can impede flourishing, nurture deviant behavior, or introduce power asymmetries (Altman, 1975).
-\enquote{{[}T{]}he feminist critique rightfully argued that for men, the private sphere can be a shielded sphere in which female suppression is not sanctioned.} (DeCew, 1997, p.
-81, as cited by Masur, 2018, p.~38).
-Next, and as mentioned above, privacy fosters self-disclosure.
-However, any self-disclosure is also always a potential risk because others might disagree, disapprove, or misuse the information in other contexts (Petronio, 2010).
+Also, and as mentioned above, privacy fosters self-disclosure, which presents a potential risk because others might disagree, disapprove, or misuse the information in other contexts (Petronio, 2010).
+The dialectical tension between the positive and negative aspects of privacy likely causes variability across individuals in their need for privacy.
+This study asks: What role does personality play in determining individual-level variations in need for privacy?
 
@@
 In what follows we now explore several personality aspects that we think might predict the need for privacy.
-As there is no established theory that dovetails privacy and personality, it is difficult to deduct precise and well-informed hypotheses.
-The rationales that we outline below should hence considered to be tentative suggestions.
-Also, please note that we elaborate only on those dimensions of need for privacy for which plausible rationales could be found.
-
-The general underlying theoretical framework that guided our selection process was the big five approach (e.g., John \& Srivastava, 1999).
-Note that privacy concerns, a variable conceptually close to need for privacy, shows only negligible relations with the big five factors (Bansal, Zahedi, \& Gefen, 2010; Junglas, Johnson, \& Spitzmüller, 2008).
+As there is no established theory that dovetails privacy and personality, it is difficult to deduce precise and well-informed hypotheses.
+The rationales that we outline below should hence be considered tentative suggestions toward a theory of personality and privacy.
+Also, please note that we elaborate only on those dimensions of need for privacy for which plausible rationales could be formed.
+
+The general underlying theoretical framework that guided our selection process was the Big Five approach (e.g., John \& Srivastava, 1999).
+Note that privacy concerns, a variable that is conceptually close to need for privacy, shows only negligible relations with the Big Five factors (Bansal, Zahedi, \& Gefen, 2010; Junglas, Johnson, \& Spitzmüller, 2008).
 In order to be more precise, we hence follow the advice by Paunonen and Ashton (2001) and refer to specific personality facets instead of generic personality factors.
-To illustrate, instead of dwelling on the general factor of \emph{extraversion}, we instead focused on the facet \emph{gregariousness}, which we consider to be more pertinent.
-
-Our reasoning was guided by another central theoretical thought.
-As implied above, privacy can be either positive or negative.
+To illustrate, instead of dwelling on the general factor of \emph{Extraversion}, we instead focused on the facet \emph{Gregariousness}, which we consider to be more pertinent.
+
+Our reasoning further was guided by another central theoretical tenet.
+As suggested above, privacy can be either positive or negative.
 Similarly, other people, the government, and anonymity can be considered either a \emph{resource} or a \emph{threat}.
@@
 
-First, we argue that need for privacy should be closely related to a person's sociability or gregariousness (which is a subdimension of extraversion, John \& Srivastava, 1999).
+First, we argue that need for privacy should be closely related to a person's sociability or gregariousness (which is a subdimension of extraversion, Costa \& McCrae, 1992).
 Sociability captures whether people prefer to spend their time alone or with company.
@@
 
-This rationale is supported by several empirical studies: Extroverted people desire less privacy (Morton, 2013), people who describe themselves as introverted thinkers are more likely to prefer social isolation (Pedersen, 1982), and introverted people are more likely to report invasions of privacy (Stone, 1986).
+This rationale is supported by several empirical studies: People who score higher on the personality meta-factor \emph{plasticity}, which is a composite of the two personality factors extraversion and openness, have been shown to desire less privacy (Morton, 2013); people who describe themselves as introverted thinkers are more likely to prefer social isolation (Pedersen, 1982); and introverted people are more likely to report invasions of privacy (Stone, 1986).
 
@@
 
-More controversially, it has been argued that people need privacy because they have something to hide.
+More controversially, it has been argued by some that people need privacy because they have something to hide.
 The so-called nothing-to-hide argument states that \enquote{If you have nothing to hide, you have nothing to fear.} As described by Solove, the nothing-to-hide argument says that data mining and surveillance by government entities \enquote{is not likely to be threatening to the privacy of law-abiding citizens.
@@
 753).
-Hence, another potential predictor of why people need privacy could also be a so-called \enquote{lack of integrity}.
+Hence, another potential predictor of why people need privacy could also be a so-called \enquote{lack} of integrity.
 
@@
 82).
-In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow Paunonen (2002) and adopt a lowest common denominator approach, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.
-
-It is indeed possible to think of theoretical arguments for why lack of integrity might correlate positively with need for privacy.
-People who have actually committed crimes evidently face even greater risk from self-disclosure compared to others, because government agencies and people sould surely disapprove of their activities (Petronio, 2010).
-Hence, the government and other people are more likely to be a threat, which should render anonymity rather a resource.
+In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow Paunonen (2002) and adopt a lowest common denominator definition, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.
+
+It is possible to think of theoretical arguments for why lack of integrity might correlate positively with a person's felt need for privacy.
+People who actually commit crimes may face even greater risk from self-disclosure compared to others, because government agencies and people would surely disapprove of their activities (Petronio, 2010).
+Hence, the government and other people are more likely to be perceived as a threat, which should render anonymity a resource.
 As a consequence, people with lower integrity might desire more privacy as a means to mitigate their felt risk (Altman, 1976).
@@
 Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more integrity (i.e., fewer cheating behaviors).
-Next, in a longitudinal sample with 457 respondents in Germany (Trepte, Dienlin, \& Reinecke, 2013), people who felt they needed more privacy were also less authentic on their SNSs profiles (\emph{r} = -.48) and less authentic in their personal relationships (\emph{r} = -.28).
-Given the argument that authenticity is a subset of integrity (Sheldon, 2004), one could hence reason that also the concept of integrity might relate to a person's need for privacy.
+Next, in a longitudinal sample with 457 respondents in Germany (Trepte, Dienlin, \& Reinecke, 2013), people who felt they needed more privacy were also less authentic on their online social network profiles (\emph{r} = -.48) and less authentic in their personal relationships (\emph{r} = -.28).
+Given the argument that authenticity is a subset of integrity (Sheldon, 2004), one could hence also reason that the concept of integrity might relate to a person's perceived need for privacy.
 Somewhat related, it has been found that people who are more agreeable are also moderately less concerned about their privacy (Junglas et al., 2008).
 Finally, Pedersen (1982) showed that three dimensions of need for privacy relate to self-esteem: Respondents who held a lower self-esteem were more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21), and preferred solitude (\emph{r} = .24).
-While self-esteem and integrity are distinct concepts, Pedersen's specific operationalization of self-esteem integrated several aspects of integrity by using items such as \enquote{moral, nice, fair, unselfish, good, honest, reputable, sane}.
-
-In conclusion, we could imagine that lack of integrity may indeed relate to an increased need for privacy from government surveillance, as governments have the legitimate power to prosecute illegal activities.
-Next, it seems plausible that lack of integrity relates to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers.
+While self-esteem and integrity are distinct concepts, Pedersen's specific operationalization of self-esteem integrated several aspects of integrity by using items such as moral, nice, fair, unselfish, good, honest, and reputable (p.~12).
+
+In conclusion, we could imagine that lack of integrity may indeed relate to an increased felt need for privacy from government surveillance, as governments have the legitimate power to prosecute illegal activities.
+Next, it seems plausible that lack of integrity may relate to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers.
 Finally, lack of integrity may also relate to an increased need for privacy from other people, as most other people will disapprove of immoral or illegal activities, and could even reveal those activities to authorities.
@@
 
-Next, it seems possible that the need for privacy is also related to people's level of general anxiety (which is a subdimension of neuroticism, John \& Srivastava, 1999).
+Next, it seems possible that the need for privacy is also related to people's level of general anxiety (which is a subdimension of neuroticism, Costa \& McCrae, 1992).
 General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened.
@@
 Concerning the need for privacy from government surveillance, we could imagine that people who are more anxious desire less privacy.
-Despite the fact that only 18\% of all US-Americans trust their government \enquote{to do what is right} (Pew Research Center, 2017), almost everyone agrees that \enquote{it's the government's job to keep the country safe}, with most people also being satisfied with the government's job (Pew Research Center, 2015).
-Hence, when being anxious, the government should rather be seen as a resource than a threat.
-It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that these programs promise to prevent crime or to reduce the likelihood of terrorist attacks (Greenwald, 2013), implying that people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.
-
-\hypertarget{risk-aversion}{%
-\subsubsection{Risk aversion}\label{risk-aversion}}
-
-Similarly, it could be that need for privacy is related to the general tendency to avoid risks, to deliberate, and to plan carefully (deliberation is a subdimension of conscientiousness, John \& Srivastava, 1999).
+Despite the fact that only 18\% of all Americans trust their government \enquote{to do what is right} (Pew Research Center, 2017), almost everyone agrees that \enquote{it's the government's job to keep the country safe,} with most people also being satisfied with the government's job (Pew Research Center, 2015).
+Hence, for anxious individuals, the government might be seen as a resource rather than a threat.
+It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that such surveillance promises to prevent crime or to reduce the likelihood of terrorist attacks (Greenwald, 2013), implying that people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.
+
+\hypertarget{risk-avoidance}{%
+\subsubsection{Risk avoidance}\label{risk-avoidance}}
+
+Similarly, it could be that an individual's felt need for privacy is related to a general tendency to avoid risks, to deliberate, and to plan carefully (deliberation is a subdimension of conscientiousness, Costa \& McCrae, 1992).
 Risk avoidance captures the degree to which people prefer to abstain from taking risks.
@@
 Moreover, research suggests that conscientious people are slightly more concerned about their privacy (Junglas et al., 2008).
-But again, especially with regard to privacy from government surveillance, risk averse people could also desire \emph{less} privacy, in order for the government to be able to avert potential threats.
+But as above, especially with regard to privacy from government surveillance, risk averse people could also desire \emph{less} privacy, in order for the government to be able to avert potential threats.
+In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study.
 
@@
 
-Next, it seems plausible that need for privacy is also related to traditionality (which is a subdimension of openness to experience, John \& Srivastava, 1999).
+Next, it seems plausible that need for privacy is also related to traditionality (which is a subdimension of openness to experience, Costa \& McCrae, 1992).
 Traditionalism measures whether people prefer to stick with their usual routines.
-The computers and the Internet have rendered the world increasingly knowable: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.
+Computers and the Internet have rendered the world increasingly knowable: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.
 Given that digital information is persistent, searchable, reproducible, and scalable (boyd, 2008), this allows for unprecedented means and degrees of surveillance.
@@
 On the other hand, Junglas et al.
-(2008) report that openness to experience is positively related to privacy concern, which would argue in favor of the exact opposite.
-Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three aforementioned contexts.
+(2008) report that openness to experience is positively related to privacy concern, which would argue in favor of the exact opposite pattern of results.
+Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three contexts measured in this study.
 
@@
 Finally, it has often been shown that socio-demographic variables such as sex, age, and affluence can relate to the need for privacy (Park, 2015; Tifferet, 2019; Trepte et al., 2013; Weinberger, Zhitomirsky-Geffet, \& Bouhnik, 2017).
-Although these variables do not specifically address our research question at hand they will be included---not least as their omission could lead to spurious results or an inflation of false positives.
+Although these variables do not specifically address our research question at hand they will be included as control variables---not least as their omission could lead to spurious results or an inflation of false positives.
 
@@
 All students received course credit for participating in the study.
-The initial sample consisted of 296 respondents.
-We removed three cases with problematic response patterns (e.g., straight-lining, missing of inverted items), which we identified using the Guttman value (Meijer, Niessen, \& Tendeiro, 2016).
+The initial sample consisted of 295 respondents.
+We removed two cases with problematic response patterns (e.g., straight-lining, missing of inverted items), which we identified using the Guttman value (Meijer, Niessen, \& Tendeiro, 2016).
 Next, we excluded one participant who provided an illogical age (i.e., 9 years).
-We also excluded 21 respondents because they answered less than 50\% of all questions.
-The remaining missing responses (0.21\%) were imputed using predictive mean matching.
+We also excluded 19 respondents because they answered less than 50\% of all questions.
+The remaining missing responses (0.40\%) were imputed using predictive mean matching.
 Analyses showed no respondents needed to be excluded due to \enquote{speeding} (i.e., \textless{} 5 min answer time).
-The final sample consisted of 271 respondents.
-
-Age of participants ranged from 18 to 56 years (\emph{M} = 20 years), with 27\% of the respondents being male. The median participation time was 25 min.
+The final sample consisted of 273 respondents.
+
+Age of participants ranged from 18 to 56 years (\emph{M} = 20 years), with 27\% of the respondents being male. The median participation time was 24.98 min.
 
@@
 First, we tested the factorial validity of the variables we collected.
-In a first step, we ran confirmatory factor analyses (CFAs) to determine whether the variables were uni-dimensional.
+In a first step, we ran confirmatory factor analyses (CFAs) to determine whether the variables were unidimensional.
 If fit was not adequate, we then ran exploratory factor analyses (EFAs) to assess the actual underlying factor structure.
-If more than one factor was revealed, we tried to find a bifactor model solution.\footnote{Bifactor models implement one factor that explains the variance in all items (the so-called general factor or g-factor).
+EFAs were run using maximum likelihood estimation and oblimin rotation (Costello \& Osborne, 2005, p.
+7).
+If more than one dimension was revealed, we tried to find a bifactor model solution.\footnote{Bifactor models implement one factor that explains the variance in all items (the so-called general factor or g-factor).
 In addition, at least another two more factors are implemented that explain the variance in a subset of the items.
@@
 For more information on bifactor models, see Kline (2016), p.~319.} This way we were able to attain a general measure of the predictors, instead of needing to further complicate our analyses by including subdimensions of the predictors.\footnote{Note that we did not specify a bifactor model of need for privacy, because we were explicitly interested in the relations between the personality facets and the three dimensions of need for privacy.} If no adequate bifactor model could be found, we proceeded by deleting items with low loadings on the general factor and/or the specific factors.
-If also after deletion of individual items no bifactor solution emerged, using a subset of the items we then aimed to extract a single factor with sufficient factorial validity.
+If also after deletion of individual items no bifactor solution emerged, we then aimed to extract a single factor with sufficient factorial validity using a subset of the items.
 
@@
 To get high-quality single indicators of the predictors, we computed the average of the model predicted values / latent factor scores, which we extracted from the CFAs.
-If the CFAs showed a single-factor solution, we used the model predicted values for this latent factor; if the CFAs produced a bifactor solution, we used the model predicted values for the general latent factor.
-As main variable of interest, the outcome need for privacy was measured as a three-dimensional latent factor consisting of overall 12 items (see below).
-
-Finally, combining the information of several items into a latent factors helps to reduce and combine information.
+If the CFAs showed a unidimensional solution, we used the model predicted values for this latent factor; if the CFAs produced a multidimensional solution, we used the model predicted values for the general latent factor (again, by using this procedure we were able to attain a general measure of the predictors, instead of needing to further complicate analyses by including subdimensions of the predictors.) As the main variable of interest, the outcome need for privacy was measured as a three-dimensional latent factor consisting of overall 12 items (see below).
+
+Finally, combining several items into a latent factors helps to reduce and condense information.
 At the same time, however, this approach also introduces several researcher degrees of freedom.
@@
 
-R (Version 3.5.1; R Core Team, 2018) and the R-packages \emph{GGally} (Version 1.4.0; Schloerke et al., 2018), \emph{ggplot2} (Version 3.1.0; Wickham, 2016), \emph{knitr} (Version 1.21; Xie, 2015), \emph{lavaan} (Version 0.6.3; Rosseel, 2012), \emph{mice} (Version 3.3.0; van Buuren \& Groothuis-Oudshoorn, 2011), \emph{MVN} (Version 5.5; Korkmaz, Goksuluk, \& Zararsiz, 2014), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{PerFit} (Version 1.4.3; Tendeiro, Meijer, \& Niessen, 2016), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{pwr} (Version 1.2.2; Champely, 2018), \emph{semTools} (Version 0.5.1; Jorgensen et al., 2018), and \emph{tidyverse} (Version 1.2.1; Wickham, 2017) was used for the analyses.
+R (Version 3.5.1; R Core Team, 2018) and the R-packages \emph{GGally} (Version 1.4.0; Schloerke et al., 2018), \emph{ggplot2} (Version 3.1.0; Wickham, 2016), \emph{knitr} (Version 1.21; Xie, 2015), \emph{lavaan} (Version 0.6.3; Rosseel, 2012), \emph{mice} (Version 3.3.0; van Buuren \& Groothuis-Oudshoorn, 2011), \emph{MVN} (Version 5.6; Korkmaz, Goksuluk, \& Zararsiz, 2014), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{PerFit} (Version 1.4.3; Tendeiro, Meijer, \& Niessen, 2016), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{pwr} (Version 1.2.2; Champely, 2018), \emph{semTools} (Version 0.5.1; Jorgensen et al., 2018), and \emph{tidyverse} (Version 1.2.1; Wickham, 2017) were used for the analyses.
 
@@
 Privacy need &  &  &  &  &  &  &  &  &  &  &  & \\
-\ \ \ (Combined) & 4.17 & 1.62 & 97.74 & 50.00 & < .001 & .95 & .93 & .06 & .06 & .84 & .88 & .46\\
-\ \ \ Government & 4.12 & 1.49 & 6.39 & 5.00 & .270 & 1.00 & .99 & .03 & .02 & .87 & .87 & .57\\
-\ \ \ Interpersonal & 4.21 & 1.59 & 10.61 & 2.00 & .005 & .92 & .76 & .13 & .05 & .61 & .62 & .30\\
-\ \ \ Anonymity & 2.90 & 1.50 & 3.11 & 2.00 & .212 & .99 & .98 & .05 & .03 & .69 & .69 & .36\\
-Sociability & 4.70 & 1.50 & 5.94 & 2.00 & .051 & .98 & .95 & .09 & .03 & .79 & .79 & .49\\
-Integrity & 4.56 & 1.83 & 47.93 & 25.00 & .004 & .96 & .94 & .06 & .04 & .79 & .82 & .40\\
-Anxiety & 4.42 & 1.52 & 38.05 & 18.00 & .004 & .95 & .93 & .06 & .04 & .80 & .82 & .41\\
-Risk aversion & 4.32 & 1.55 & 5.16 & 5.00 & .397 & 1.00 & 1.00 & .01 & .02 & .78 & .78 & .42\\
-Traditionality & 3.90 & 1.60 & 10.71 & 5.00 & .058 & .98 & .95 & .06 & .03 & .74 & .74 & .37\\
+\ \ \ (Combined) & 4.18 & 1.62 & 101.72 & 50 & < .001 & .94 & .92 & .06 & .06 & .85 & .88 & .46\\
+\ \ \ Government & 4.13 & 1.49 & 7.26 & 5 & .202 & 1.00 & .99 & .04 & .02 & .87 & .87 & .57\\
+\ \ \ Interpersonal & 4.21 & 1.59 & 10.22 & 2 & .006 & .93 & .78 & .12 & .04 & .62 & .62 & .30\\
+\ \ \ Anonymity & 2.92 & 1.50 & 3.16 & 2 & .206 & .99 & .98 & .05 & .03 & .69 & .70 & .37\\
+Sociability & 4.70 & 1.50 & 6.20 & 2 & .045 & .98 & .94 & .09 & .03 & .79 & .79 & .49\\
+Integrity & 4.56 & 1.84 & 47.44 & 25 & .004 & .96 & .94 & .06 & .04 & .79 & .83 & .41\\
+Anxiety & 4.41 & 1.53 & 36.98 & 18 & .005 & .96 & .93 & .06 & .04 & .80 & .82 & .42\\
+Risk avoidance & 4.30 & 1.56 & 5.27 & 5 & .384 & 1.00 & 1.00 & .01 & .02 & .79 & .79 & .43\\
+Traditionality & 3.91 & 1.60 & 10.69 & 5 & .058 & .98 & .95 & .06 & .03 & .74 & .74 & .37\\
 \bottomrule
@@
 As the main variable of interest, we collected several items to measure need for privacy.
-First, we collected four items capturing the need for informational privacy using the scale developed by Trepte and Masur (2017).
+First, we collected four items capturing the general need for privacy using the subscale \emph{information} developed by Trepte and Masur (2017).
 Second, we measured need for privacy on a societal level using nine self-designed items.
@@
 EFAs and CFAs revealed a well-fitting model with 12 items (one double-loading), which consisted of the three dimensions (a) need for privacy from the government, (b) need for privacy from other people, and (c) need for anonymity.
-For a list of all items, see Table \ref{tab:need-for-privacy-items}.
+For a list of all items, see Table \ref{tab:privacyitems}.
 
@@
 
-\caption{\label{tab:need-for-privacy-items}Overview of Items Measuring Need for Privacy}
+\caption{\label{tab:privacyitems}Overview of Items Measuring Need for Privacy}
 \centering
@@
 \hspace{1em}I need the information that companies (e.g., Amazon, Facebook, or Google) have about me to stay private so that the government can never access it.\\
-\hspace{1em}I don't want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.\\
-\hspace{1em}I don't want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.\\
+\hspace{1em}I don’t want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.\\
+\hspace{1em}I don’t want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.\\
 \hspace{1em}I feel the need to protect my privacy from government agencies.\\
@@
 \hspace{1em}My need for privacy is so strong that it prevents me from using Facebook \vphantom{1} actively.\\
-\hspace{1em}I don't feel the need to tell my friends all my secrets.\\
+\hspace{1em}I don’t feel the need to tell my friends all my secrets.\\
 \hspace{1em}I feel the need to protect my privacy from other people.\\
@@
 
-Sociability was measured with the extraversion subscale \emph{gregariousness} (John \& Srivastava, 1999), which consists of eight items.
+Sociability was measured with the Extraversion subscale Gregariousness (Costa \& McCrae, 1992), which consists of eight items.
 An example item is \enquote{I shy away from crowds of people.} Analyses revealed that a bifactor model based on a subset of six items showed good fit to the data.
@@
 
-In order to measure integrity, we used the subscale \emph{integrity} of the Supernumerary Personality Inventory (Paunonen, 2002), which consists of eight items.
+To measure integrity, we used the subscale Integrity of the Supernumerary Personality Inventory (Paunonen, 2002), which consists of eight items.
 In addition, we designed another three items.
@@
 
-Anxiety was measured with the neuroticism subscale \emph{anxiety} (John \& Srivastava, 1999), which consists of eight items.
+Anxiety was measured with the Neuroticism subscale Worry (Costa \& McCrae, 1992), which consists of eight items.
 An example item is \enquote{I am easily frightened.} Analyses revealed that a bifactor model using all eight items showed good fit to the data.
 
-\hypertarget{risk-avoidance}{%
-\subsubsection{Risk avoidance}\label{risk-avoidance}}
-
-Risk avoidance was measured with the conscientiousness subscale \emph{deliberation} (John \& Srivastava, 1999), which consists of eight items.
+\hypertarget{risk-avoidance-1}{%
+\subsubsection{Risk avoidance}\label{risk-avoidance-1}}
+
+Risk avoidance was measured with the Conscientiousness subscale Deliberation (Costa \& McCrae, 1992), which consists of eight items.
 An example item is \enquote{I plan ahead carefully when I go on a trip.} Analyses revealed that a bifactor model using all eight items showed good fit to the data.
@@
 
-Traditionalism was measured with the (inverted) openness to experiences subscale \emph{actions} (John \& Srivastava, 1999), which consists of eight items.
+Traditionalism was measured with the (inverted) Openness to Experiences subscale Actions (Costa \& McCrae, 1992), which consists of eight items.
 An example item is \enquote{I'm pretty set in my ways.} Analyses revealed that a model with a single factor based on a subset of five items showed good fit to the data.
@@
 For an overview of the results of the bivariate relations, see Figure \ref{fig:bivar-fig}.
-For the statistical results of the SEM, see Table \ref{tab:sem-tab}, and for a graphical visualization, Figure \ref{fig:sem-fig}.
-Note that the final structural regression model that was estimated fit the data comparatively well, \(\chi^2\)(137) = 218.68, \textit{p} \textless{} .001, cfi = .93, rmsea = .05, 90\% CI {[}.04, .06{]}, srmr = .06.
-
-\begin{figure}[!h]
+For the statistical results of the SEM, see Table \ref{tab:sem-tab}, and for a graphical visualization, see Figure \ref{fig:sem-fig}.
+Note that the final structural regression model that was estimated fit the data comparatively well, \(\chi^2\)(137) = 226.97, \textit{p} \textless{} .001, cfi = .92, rmsea = .05, 90\% CI {[}.04, .06{]}, srmr = .06.
+Although fit was not perfect, we decided against further modifications of the model in order to avoid overfitting.
+
+\begin{figure}[!ht]
 
@@
 \caption{\label{fig:sem-fig}Graphical overview of the results of Structural Equation Model.
-Shows the 95\% confidence intervals of standardized coefficients.
-Dashed lines indicate the SESOI of \textbar{}.10\textbar{}.}
+Shows the 95\% confidence intervals (CIs) of standardized coefficients.
+(Standard errors were extracted from Lavaan's standardized solution.
+For the results of a bootstrap approach with 2,000 draws, see OSM.) Dashed lines indicate the SESOI of \textbar{}.10\textbar{}.}
 \end{figure}
@@
 Privacy need government &  &  &  &  & \\
-\ \ \ Sociability & -0.23 & -0.44 & -0.01 & -.17 & .037\\
-\ \ \ Integrity & -0.07 & -0.37 & 0.22 & -.04 & .622\\
-\ \ \ Anxiety & -0.31 & -0.58 & -0.03 & -.18 & .029\\
-\ \ \ Traditionalism & 0.16 & -0.12 & 0.44 & .10 & .257\\
-\ \ \ Risk avoidance & 0.20 & -0.10 & 0.51 & .12 & .197\\
-\ \ \ Male & 0.38 & 0.08 & 0.68 & .16 & .012\\
-\ \ \ Age & 0.03 & > -0.01 & 0.05 & .06 & .051\\
-\ \ \ Income & 0.07 & -0.06 & 0.20 & .07 & .276\\
+\ \ \ Sociability & -0.24 & -0.46 & -0.03 & -.18 & .027\\
+\ \ \ Integrity & -0.06 & -0.36 & 0.23 & -.04 & .679\\
+\ \ \ Anxiety & -0.27 & -0.53 & -0.01 & -.17 & .042\\
+\ \ \ Traditionalism & 0.16 & -0.12 & 0.44 & .10 & .255\\
+\ \ \ Risk avoidance & 0.24 & -0.08 & 0.55 & .14 & .142\\
+\ \ \ Male & 0.34 & 0.04 & 0.64 & .14 & .025\\
+\ \ \ Age & 0.03 & < 0.01 & 0.05 & .07 & .027\\
+\ \ \ Income & 0.04 & -0.09 & 0.18 & .04 & .518\\
 Privacy need interpersonal &  &  &  &  & \\
-\ \ \ Sociability & -0.39 & -0.58 & -0.19 & -.33 & < .001\\
-\ \ \ Integrity & 0.01 & -0.24 & 0.26 & .01 & .930\\
-\ \ \ Anxiety & > -0.01 & -0.24 & 0.24 & > -.01 & .991\\
-\ \ \ Traditionalism & 0.19 & -0.11 & 0.48 & .14 & .213\\
-\ \ \ Risk avoidance & 0.40 & 0.12 & 0.67 & .27 & .005\\
-\ \ \ Male & 0.28 & > -0.01 & 0.56 & .13 & .053\\
-\ \ \ Age & 0.02 & -0.01 & 0.04 & .05 & .208\\
-\ \ \ Income & 0.03 & -0.12 & 0.19 & .03 & .686\\
+\ \ \ Sociability & -0.38 & -0.57 & -0.19 & -.33 & < .001\\
+\ \ \ Integrity & 0.04 & -0.21 & 0.29 & .02 & .770\\
+\ \ \ Anxiety & < 0.01 & -0.21 & 0.22 & < .01 & .977\\
+\ \ \ Traditionalism & 0.18 & -0.11 & 0.47 & .14 & .215\\
+\ \ \ Risk avoidance & 0.40 & 0.13 & 0.67 & .28 & .004\\
+\ \ \ Male & 0.30 & 0.03 & 0.57 & .14 & .031\\
+\ \ \ Age & 0.02 & -0.01 & 0.04 & .04 & .184\\
+\ \ \ Income & 0.02 & -0.13 & 0.17 & .02 & .775\\
 Privacy need anonymity &  &  &  &  & \\
-\ \ \ Sociability & -0.22 & -0.40 & -0.04 & -.20 & .018\\
-\ \ \ Integrity & -0.40 & -0.67 & -0.14 & -.28 & .003\\
-\ \ \ Anxiety & -0.16 & -0.39 & 0.07 & -.11 & .167\\
-\ \ \ Traditionalism & -0.03 & -0.29 & 0.23 & -.02 & .814\\
-\ \ \ Risk avoidance & 0.04 & -0.21 & 0.28 & .03 & .770\\
-\ \ \ Male & 0.29 & 0.01 & 0.58 & .14 & .041\\
-\ \ \ Age & 0.03 & < 0.01 & 0.07 & .10 & .031\\
-\ \ \ Income & 0.14 & -0.01 & 0.28 & .15 & .065\\
+\ \ \ Sociability & -0.24 & -0.43 & -0.06 & -.21 & .011\\
+\ \ \ Integrity & -0.37 & -0.63 & -0.10 & -.25 & .008\\
+\ \ \ Anxiety & -0.15 & -0.37 & 0.07 & -.11 & .194\\
+\ \ \ Traditionalism & -0.01 & -0.27 & 0.25 & -.01 & .931\\
+\ \ \ Risk avoidance & 0.04 & -0.21 & 0.29 & .03 & .755\\
+\ \ \ Male & 0.30 & 0.02 & 0.59 & .15 & .037\\
+\ \ \ Age & 0.03 & < 0.01 & 0.07 & .10 & .036\\
+\ \ \ Income & 0.13 & -0.01 & 0.27 & .14 & .076\\
 \bottomrule
@@
 
-Summarizing across the results, the predictors explained 12.04\% of the variance in need for privacy from the government, 28.27\% of the variance in need for privacy from other people, and 18.59\% of the variance in need for anonymity.
+Summarizing across the results, the predictors explained 11.84\% of the variance in need for privacy from the government, 29.76\% of the variance in need for privacy from other people, and 17.32\% of the variance in need for anonymity.
+All predictors were also above our predefined SESOI of \textbar{}\(\upbeta\)\textbar{} = .10, supporting their theoretical relevance.
+In addition, note that several nonsignificant effects were actually larger than the predefined SESOI (e.g., the potential effect of risk avoidance on the need for privacy from the government).
+Hence, it seems plausible that a larger study, which yields smaller standard errors, would find additional effects.
+
+As stated above, because all predictors were included on the basis of specific a priori rationales we did not control for alpha error inflation.
+To better assess whether the results could also be explained by chance alone, let us briefly reconsider that if the null hypotheses had been true, given the predefined alpha level of 5 \% and the twenty four statistical tests that were run, one would have expected to find 1.20 statistically significant results by chance alone.
+In this study we found eleven statistically significant results, which is substantially higher.
+Similarly, the average \emph{p}-value \emph{p} = .28 was substantially smaller than the average \emph{p}-value of \emph{p} = .50 that one would have expected to find if the null hypotheses had been true.
 
@@
 Importantly, however, integrity was not related to need for privacy from other people or to need for privacy from government surveillance, which hence limits the generalisability of the nothing-to-hide argument.
-In addition, note that the items measuring need for anonymity were very difficult (the mean was much lower compared to the other dimensions; see Table \ref{tab:psychometrics})---hence, the relationship between integrity and need for privacy might show only in very specific domains, for example, when it comes to avoiding places with video surveillance.
+In addition, note that the responses to the items measuring need for anonymity were much lower compared to the other two dimensions of need for privacy (i.e., \emph{M}\textsubscript{anonymity} = 2.92, \emph{M}\textsubscript{government} = 4.13, \emph{M}\textsubscript{interpersonal} = 4.21).
+Hence, the relationship between integrity and need for privacy might show only in very specific domains, for example, when it comes to avoiding places with video surveillance.
 In conclusion, the relation between integrity and need for privacy seems to be limited to certain aspects of need for privacy only.
-It should hence not be overly generalized.
+It should thus not be overly generalized.
 
 Interestingly, the data showed that people who were more anxious were also more willing to accept government surveillance.
-This might be explained by the fact that governments are explicitly commissioned to help prevent crime or terrorist attacks, which are things more anxious people are more likely to dread.
+This might be explained by the fact that governments are explicitly commissioned to help prevent crime or terrorist attacks, which are things that more anxious people are more likely to fear.
 
 People who were more risk averse desired more privacy from other people.
-Specifically, people who try to avoid risks are less inclined to share secrets with friends.
-This finding makes sense and can be aligned with prospect theory (Kahneman \& Tversky, 1979): The risks of a secret being publicly disclosed seem to outweigh the potential benefits of sharing it with confidants.
+Specifically, people the data show that who try to avoid risks are less inclined to share secrets with friends.
+This finding makes sense and can be aligned with prospect theory (Kahneman \& Tversky, 1979): The risks of a secret being publicly disclosed seem to outweigh the potential benefits of sharing it with confidants among risk-averse people.
 
 Finally, in the SEM no significant relations between need for privacy and traditionality were found.
-The results imply that independent from being more open to change or not, people desire the same level of privacy.
-Taken further, this finding might illustrate that a modern way of living does not necessarily imply a reduced need for privacy.
+The results imply that independent from being more or less open to change, people desire the same level of privacy.
+Taken further, this finding might illustrate that people who are more open to change, who are more likely to use novel devices, media, and services, or who might consider themselves as early adopters, do not automatically need less privacy.
 
 At a larger level, the results of this study highlight the importance of making differentiated claims on why people need privacy.
-Indeed, while the results suggest that some people might need anonymity because they may have something to hide, they also show that putting everyone who exhibits an increased need for privacy under suspicion is outright wrong.
-People who are less sociable, more risk averse, and less anxious are also more likely to need a bit more privacy.
+Indeed, while the results suggest that some people might need anonymity because they may have something to hide, they also show that putting everyone who exhibits an increased need for privacy under suspicion is wrong.
+People who are less sociable, more risk averse, and less anxious are also more likely to feel they need more privacy.
 This implies that various personality-related aspects can predict need for privacy in different ways and for different reasons.
@@
 On the one hand, integrity implies absolute criteria in relation to social norms: Stealing is bad and forbidden, whereas helping is good and encouraged.
-On the other hand, integrity implies relative criteria: Whereas some cultures disapprove of lying whatever the context, others consider lying okay (for example, \enquote{white lies} in order to avoid hurting someone's feelings) (Altman, 1977).
+On the other hand, integrity implies relative criteria: Whereas some cultures disapprove of lying whatever the context, others consider lying okay in some situations (for example, \enquote{white lies} in order to avoid hurting someone's feelings) (Altman, 1977).
 Thus, ranking behaviors, opinions, and character traits with regard to integrity presents a moral dilemma.
-As a result, throughout our study we have employed a conservative approach and understood and measured integrity as an explicit transgression of social norms that is strong and that most societies would arguably agree upon (for example, most societies would consider stealing as a sign of low integrity).
+As a result, throughout our study we have employed a conservative approach to understand and measure integrity as an explicit transgression of social norms that is strong and that most societies would arguably agree upon (for example, most societies would consider law-breaking as a sign of low integrity).
 Nonetheless, we recommend that future research should further elaborate on the general understanding of integrity as a theoretical concept.
@@
 In a meta-analysis with 665 correlation coefficients, self-reported integrity tests were associated with counterproductive behaviors with an average correlation coefficient of \emph{r} = .47 (Ones et al., 1993).
-Nonetheless, future research would evidently benefit from including behavioral manifestations of integrity, such as concrete cheating behaviors.
-
-In what follows, we present some methodological points of criticism.
-Despite the fact that we used mostly well-established scales, confirmatory factor analyses showed that some of the original items had to be deleted to achieve adequate factorial validity.
-This resembles the finding by Hussey and Hughes (2018), who reported that several widely-used scales in psychological research actually do not show satisfactory factorial validity.
-By using bifactor models, however, it was possible to at least partially alleviate the problem.
-Next, in order to achieve sufficient factorial validity we needed to adapt the scales (for example by deleting items), which introduces problems of overfitting, which in turn potentially impedes the generalisability of the results (see, e.g., Yarkoni \& Westfall, 2017).
-However, by using bifactor models we explicitly tried to retain the largest possible number of items, which should render our results more robust.
-In addition, also when looking at the items individually (see OSM) one can see that the results are not overly dependent on inclusion of specific items.
+Nonetheless, future research would benefit from including behavioral manifestations of integrity, such as concrete cheating behaviors.
+
+Another limitation of the study is that despite using mostly well-established scales, confirmatory factor analyses revealed that most measures did not show satisfactory factorial validity, which resembles the current finding and criticism by Hussey and Hughes (2018).
+In order to achieve sufficient factorial validity we therefore needed to adapt the scales (for example by deleting items).
+However, this introduces problems of overfitting, which in turn potentially impedes the generalisability of the results (see, e.g., Yarkoni \& Westfall, 2017).
+By using bifactor models we explicitly tried to retain the largest possible number of items, which should render our results more robust.
+In addition, also when looking at the items individually (see the OSM) one can see that the results are not overly dependent on inclusion of specific items.
+
 Another methodological improvement for future studies concerns the sample, which was comparatively small, leading to a reduced power to detect also small effects.
-Nonetheless, we are still confident that the results should be reliable, because we deliberately selected specific predictors that should exhibit at lest small to moderate relations with need for privacy (i.e., \emph{r} = .20).
-For small to moderate relations, the current study still had a convincing power of 91\%.
-Granted, when aiming to find also small effects (i.e., \emph{r} = .10) with a probability of 95\%, future studies would need to collect the answers of 1293 respondents (Cohen, 1992).
-Finally, generalisability is limited, as our sample was predominantly young, female, highly educated, and collected only in one single country.
-
-Next, future research might consider analyzing predictors of privacy needs that are even more specified.
-For example, it is possible that people who hold dissenting political beliefs could also have a higher need for privacy from the government.
+Nonetheless, we are still confident that the results should be reliable because we deliberately selected specific predictors that should exhibit at least small to moderate relations with need for privacy (i.e., \emph{r} = .20).
+For small to moderate relations, the current study still had a convincing power of 92\%.
+Granted, when aiming to find also small effects (i.e., \emph{r} = .10) with a probability of 95\%, future studies would need to collect data from 1293 respondents (Cohen, 1992).
+Finally, generalisability of our sample is limited, as it was predominantly young, female, highly educated, and collected only in one country.
+
+Finally, future research might consider analyzing predictors of privacy needs that are even more specified.
+For example, it is possible that people who hold dissenting political beliefs could also perceive a higher need for privacy from the government.
 In this study we focused mostly on escapist motives for why people desire privacy (e.g., sociability, risk aversion).
@@
 
-In his novel \emph{The Circle}, Eggers (2013) describes a dystopian society in which people are gradually forfeiting their privacy.
-One after another becomes \enquote{transparent}: Carrying a small camera around the neck, people begin to broadcast their daily lives to the Internet.
-In the novel, this eventually causes a societal upheaval: \enquote{The pressure on those who hadn't gone transparent went from polite to oppressive.
-The question, from pundits and constituents, was obvious and loud: If you aren't transparent, what are you hiding?} (Eggers, 2013, p.
-129).
-
-The results of this study suggest that there might be some truth to the nothing-to-hide argument.
-However, the applicability seems to be limited to (very specific) aspects of anonymity (e.g., avoiding places with video surveillance or leaving one's ID at home).
-In general, the need for privacy seems to be related more closely to other aspects of personality.
+Privacy is getting more impinged on these days with digital surveillance and intense social pressure toward self-disclosure via social networks, which have both negative and positive aspects at the same time.
+In this context it is understandable why people might vary in their felt need for privacy.
+Our study sheds light on what drives that variation, finding that sociability, and to a lesser extent, anxiety, risk aversion, and integrity all contribute to individuals' need for privacy, albeit in different ways.
 
@@
 
+\leavevmode\hypertarget{ref-Costa.1992b}{}%
+Costa, P.
+T., \& McCrae, R.
+R.
+(1992).
+Normal personality assessment in clinical practice: The NEO Personality Inventory.
+\emph{Psychological Assessment}, \emph{4}(1), 5--13.
+doi:\href{https://doi.org/10.1037/1040-3590.4.1.5}{10.1037/1040-3590.4.1.5}
+
+\leavevmode\hypertarget{ref-Osborne.2004b}{}%
+Costello, A.
+B., \& Osborne, J.
+W.
+(2005).
+Best practices in exploratory factor analysis: Four recommendations for getting the most from your analysis.
+\emph{Practical Assessment, Research \& Evaluation}, \emph{7}(10).
+Retrieved from \url{http://pareonline.net/pdf/v10n7.pdf}
+
 \leavevmode\hypertarget{ref-Covey.1989}{}%
@@
 
-\leavevmode\hypertarget{ref-DeCew.1997}{}%
-DeCew, J. W. (1997). \emph{In pursuit of privacy: Law, ethics, and the rise of technology}. Ithaca, NY: Cornell Univ. Press.
-
 \leavevmode\hypertarget{ref-Dienlin.2014}{}%
@@
 doi:\href{https://doi.org/10.1037/a0012897}{10.1037/a0012897}
-
-\leavevmode\hypertarget{ref-Eggers.2013}{}%
-Eggers, D. (2013). \emph{The circle}. New York, NY: Knopf Publishing Group.
 

### 2019-02-26 manuscript/manuscript.RmD
manuscript: Provided link to osf.

@@
 
-All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found on this paper’s project page on the open science framework (https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f).
-In addition, we invite everyone to suggest changes and improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/tree/master).
+All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found in the Online Supplementary Material on the open science framework (https://osf.io/7ncpk/).
+In addition, we invite everyone to suggest changes and improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/).

### 2019-02-27 manuscript/manuscript.RmD
- Integrated last edits by MM

@@
 The most important predictor of need for privacy, however, was sociability.
-In conclusion, this study is the first to show that if a person desires more privacy, it is most plausible that he or she is less sociable.'
+Indeed, this study is the first to show empirically that if a person desires more privacy, it is most plausible that he or she is less sociable.'
 keywords          : "Privacy, need for privacy, personality, anonymity, integrity, SEM"
@@
 The need for privacy, then, captures "[a]n individual’s need to selectively control the
-access of others to the individual = self with the aim of achieving a desired level of physical or psychological privacy [...]") [@Trepte.2017d, p.
+access of others to the individual self with the aim of achieving a desired level of physical or psychological privacy [...]") [@Trepte.2017d, p.
 1].
@@
 In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually feel they need privacy.
-According to @Trepte.2017d, the need for privacy is a secondary need---it is not an end in itself, but rather a way to satisfy other more fundamental needs.
+According to @Trepte.2017d, the need for privacy is a secondary need---it is not an end in itself, but rather a way to satisfy other more fundamental needs (e.g., time to oneself).
 Specifically, @Westin.1967 defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
@@
 
-# Methods
+# Method
 
@@
 In addition, note that several nonsignificant effects were actually larger than the predefined SESOI (e.g., the potential effect of risk avoidance on the need for privacy from the government).
-Hence, it seems plausible that a larger study, which yields smaller standard errors, would find additional effects.
+Hence, it is plausible that a larger study, which yields smaller standard errors, would find additional effects.
 
 As stated above, because all predictors were included on the basis of specific a priori rationales we did not control for alpha error inflation.
-To better assess whether the results could also be explained by chance alone, let us briefly reconsider that if the null hypotheses had been true, given the predefined alpha level of 5 % and the `r nrow(t_results_threefactors) %>% as.english()` statistical tests that were run, one would have expected to find `r round(nrow(t_results_threefactors) * .05, 2)` statistically significant results by chance alone.
-In this study we found `r round(nrow(filter(coeffs_tab(results_threefactors_fit), p < .05)), 0) %>% english()` statistically significant results, which is substantially higher.
+To better assess whether the results could also be explained by chance alone, let us briefly consider that if the null hypotheses had been true, given the predefined alpha level of 5 % and the `r nrow(t_results_threefactors)` statistical tests that were run, one would have expected to find `r round(nrow(t_results_threefactors) * .05, 2)` statistically significant results by chance alone.
+In this study we found `r round(nrow(filter(coeffs_tab(results_threefactors_fit), p < .05)), 0)` statistically significant results, which is substantially higher.
 Similarly, the average _p_-value _p_ = `r coeffs_tab(results_threefactors_fit)$p %>% mean %>% my_round("std")` was substantially smaller than the average _p_-value of _p_ = .50 that one would have expected to find if the null hypotheses had been true.
@@
 This finding hence supports the logic behind the “nothing to hide” argument.
-It also follows Altman’s privacy regulation theory [-@Altman.1976], which states that if exposure of information is risky it is likely that people will use more mechanisms to strengthen their social boundaries and increase their desired level of privacy.	Importantly, however, integrity was not related to need for privacy from other people or to need for privacy from government surveillance, which hence limits the generalisability of the nothing-to-hide argument.
+It also follows Altman’s privacy regulation theory [-@Altman.1976], which states that if exposure of information is risky it is likely that people will use more mechanisms to strengthen their social boundaries and increase their desired level of privacy.	Importantly, however, integrity was not related to need for privacy from other people or to need for privacy from government surveillance, which hence limits the generalizability of the nothing-to-hide argument.
 In addition, note that the responses to the items measuring need for anonymity were much lower compared to the other two dimensions of need for privacy (i.e., _M_~anonymity~ = `r t_psyc["Anonymity", "m"]`, _M_~government~ = `r t_psyc["Government", "m"]`, _M_~interpersonal~ = `r t_psyc["Interpersonal", "m"]`).
-Hence, the relationship between integrity and need for privacy might show only in very specific domains, for example, when it comes to avoiding places with video surveillance.
+Hence, the relationship between integrity and need for privacy might show only in very specific domains that are related to anonymity (for example, avoiding places with video surveillance).
 In conclusion, the relation between integrity and need for privacy seems to be limited to certain aspects of need for privacy only.
@@
 The results imply that independent from being more or less open to change, people desire the same level of privacy.
-Taken further, this finding might illustrate that people who are more open to change, who are more likely to use novel devices, media, and services, or who might consider themselves as early adopters, do not automatically need less privacy.
+Taken further, this finding might illustrate that people who are more open to change, who are more likely to use novel devices, media, and services, or who might consider themselves as early adopters, do not need less privacy.
 
@@
 In order to achieve sufficient factorial validity we therefore needed to adapt the scales (for example by deleting items).
-However, this introduces problems of overfitting, which in turn potentially impedes the generalisability of the results [see, e.g., @Yarkoni.2017].
+However, this introduces problems of overfitting, which in turn potentially impedes the generalizability of the results [see, e.g., @Yarkoni.2017].
 By using bifactor models we explicitly tried to retain the largest possible number of items, which should render our results more robust.
@@
 Granted, when aiming to find also small effects (i.e., _r_ = .10) with a probability of 95%, future studies would need to collect data from `r sample_95` respondents [@Cohen.1992].
-Finally, generalisability of our sample is limited, as it was predominantly young, female, highly educated, and collected only in one country.
+Finally, generalizability of our sample is limited, as it was predominantly young, female, highly educated, and collected only in one country.
 
